### 2016-09-05 Interacting Classical Gas_Zhiyu.tex
I deleted an wrong example of LE I made before

\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \maketitle
 \tableofcontents
 \newpage

\section{Preparation}
\subsection{Scaling behaviour}
We investigated the classical gas in harmonic trap with a repulsive interaction. We chose one of the simplest types of interaction:
\begin{equation}
F=\left\lbrace
\begin{aligned}
&F=F0 	&,x\textless\sigma\\
&F=0 	&,x\textgreater\sigma
\end{aligned}
\right.
\label{eq:preparation1}
\end{equation}

\begin{equation}
H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
\label{eq:preparation2}
\end{equation}
It can be easily shown that eq.\ref{eq:preparation2} can be rewrite into the following form:
\begin{equation}
\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
\end{equation}
with the transformation:
\begin{equation}
\left\lbrace
\begin{aligned}
&\tilde{H}&=&\frac{H}{m\omega_0^2\sigma^2}\\
&\tilde{x_i}&=&\frac{x_i}{\sigma}\\
&\tilde{t}&=&\omega_0t\\
&\tilde{F_0}&=&\frac{F_0}{m\omega_0^2\sigma}\\
\end{aligned}
\right.
\end{equation}

In this manner, we reduced number of the parameters in our model into three: $\tilde{H}$, $\tilde{F_0}$, $N$. Equivalently, we set $\sigma$, $\omega$ and $m$ to 1 in our numerical simulation. Throughout, we will use ``E" and ``$F_0$" to denote their reduced version  $\tilde{H}$, $\tilde{F_0}$.

\section{Thermalization}
\subsection{Dynamics Study}
It is natural to think that a many-body system with interaction will be thermalized in ``usual" case. To study the condition of thermalization is equivalent to find out the mechanism that prohibits the system from ergodic. In view of this, we begin the study with two-particle motion. 
\paragraph{two-particle}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{C:/Users/admin/Desktop/test.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

To see the way interaction change the orbit (energy level) of the particles, we had better start from two-particle case.

We can always think of them in the reference frame of their center of mass ``C". In frame C, one can easily show that when there is no interaction, what we will see is that two particles are bound together by a harmonic trap center at C(cf). So their relative motion is also a harmonic oscillation.

In this case, the system has two frequency components. The first one is the frequency of C, which is just $\omega_0$ . The other one is the frequency of their relative motion $\omega_r$, which is slightly deviated from $\omega_0$. The deviation grows with the increase of $F_0$ and the decrease of internal energy of the pair. As a result, when the $F_0$ is small and when the E is large, a beat with frequency $\omega_r-\omega_0=\delta$ will exist.

\begin{figure}[hbtp]
\begin{center}

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}
\end{center}
\caption{the dependence of beat frequency on internal energy} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly. Here, $E_i$ is large(compare to $F_0\sigma$). In this case, the larger $E_i$ is, the lower the beat frequency is. Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
\label{fig:thermalization1}
\end{figure}

%-------------%
\begin{comment}
\subparagraph{Detailed discussion on two-particle motion}
From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system. In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame. As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical). We label the position of center of mass as 0. And we may only analyse the motion on positive axis since positive and negative are symmetric.

Now, let's consider the interaction between them. Because of interaction, the potential curve between $+-\frac{\sigma}{2}$ should be modified to another parabolic curve that simultaneously satisfies the following two condition:\\
1) intersect with black curve at $+-\frac{\sigma}{2}$\\
2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a SHO with an extra constant force $F_0$\\
Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
For those three types of curve, the significant difference is only at low energy case:\\
For the red one, particle will oscillate at constant frequency $\omega$;
For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}}
\end{comment}
%-------------%

\paragraph{More particles}
Now let's consider the three-particle case. For two particle, the motion is non-chaotic. On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon. However, in some cases, the time scale of thermalizing could still be very long. Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small. Meanwhile, suppose particle C has some energy quite different from A \& B. In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period. How will energy transfer between C and the two-particle system A and B? Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau$ ($\tau\ll\frac{2\pi}{\omega}$). When C pass A, it gives A a push, and then push A back.  As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\tau)$) in the background of a trap. Since the position and velocity of A and B are both close, the effect of C on A \& B are almost the same (difference$\sim O(\tau\sigma)\sim O(\tau^2)$). In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected. In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass. The physics of the ``dance" is similar to the dance between two particle. %We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g. change $m$ to $\mu$ , which is the reduced mass of m \& 2m.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.35]{../matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

The argument above still holds in many-particle case. Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems dancing together on the energy level diagram. 
The discussion above gives us some pictures about the non-ergodic state. For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.

\subsection{Thermalization condition}
The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before. Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$). As a result, to achieve ergodic state, we have to avoid such low frequency oscillation. According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large". Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the energy interval, which is $\frac{E}{N}$. At least they are of the same order. The thermalization condition could be given by:
$F_0\sigma\sim\frac{E}{N}$

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
\label{fig:thermalization5}
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}

\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
\caption{energy of each particle, $F_0=2$}
\label{fig:thermalization6}

\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
\caption{energy of each particle, $F_0=10$}
\label{fig:thermalization7}
\end{figure}

As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ while the energy interval of particles $\sim 10$, as we expected, they are of the same order. As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e. in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic. Till now, we have verified that the criteria of non-ergodic and ergodic state, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution.

\newpage
\subsection{Verifying Boltzmann distribution}
Thermalization could have different definition. In our system, the "thermalization" we want to find means "losing all the memory of initial state". One of the most important information of initial state is energy distribution. We can check whether a system has gone to equilibrium by measuring its energy distribution.

\paragraph{energy distribution}
For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state. However, for an isolated system where the total energy is conserved, it not obvious to draw some strict conclusion about the distribution.

Intuitively, one will expect that if we measure the energy of a subsystem , e.g. one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle. The temperature of this isolated system is defined according to $Nk_BT=E$. It is evident that this argument only hold when the energy of the single particle is not too big--if one particle has 50\% of the total energy, the rest could no longer be think of as a good bath.

In the first picture below, we verify this argument by measuring the energy distribution of every particle at N=10 for different F0 at E=1000 (parameters here satisfy thermalizing condition). In the other two, we tested different N.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}
\includegraphics[scale=0.47]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000}
\label{fig:thermalization9}
\includegraphics[scale=0.52]{../matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

\begin{flushleft}
To take the first one as an example, Y axis is logarithmically scaled. X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system. The blue dotted line is the predicted Boltzmann distribution (normalized according to counts). Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare. In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction. When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.

It is evident form $Nk_BT=E$ that the slope of Boltzmann distribution in this figure only depend on N. That is the reason why we want to measure at different N below.

In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states. Possibility is proportional to Boltzmann exponential factor multiplied by density of states. The reason why we did not take DOS into account previously lies in that the DOS is a constant for simple harmonic oscillator. However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant. But since $\sigma<<R$, one can think of this as a small modification. Therefore, the tendency of the curve in fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10} is deviated slightly from Boltzmann distribution.

\end{flushleft}

\newpage
\section{Relaxation in Phase-space (unfinished)}
Till now we have verified the energy distribution will go to Boltzmann distribution. However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state. There is other information that could still exist, for instance, the shape of distribution cloud in phase-space. One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour. For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large. On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all. Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).

\paragraph{Shape of Distribution in Phase-space}
If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse. If the phase of oscillation is completely random, the cloud should be isotropic in phase space. In view of this, we defined a shape factor S:
\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
S=1 for line-shape distribution, S=0 for circular distribution.
The time evolution of S will probably show how fast the distribution ``forget" its initial shape.

\begin{figure}[hbtp]

\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
\caption{N=5,F0=10000,E=1000, initial S=1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
\caption{Zoom in at the beginning part}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
\caption{average over every 30s to see the main tendency}
\label{fig:relaxationPS1}
\end{figure}

From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge. Maybe the fluctuation of S is so large that make it hard to identify the convergence of S. The only way to solve this problem is using more particle simulation to suppress the fluctuation, while the cost is that the simulation time will be limited.

\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
\caption{N=20, F0=1000, E=3000, initial S=1}
Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
\label{fig:relaxationPS2}
\end{figure}
\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
\caption{N=20, F0=1000, E=10000, initial S=1}
\label{fig:relaxationPS3}
\end{figure}

For N=20(fig.\ref{fig:relaxationPS3}), the S start evolving from 1 will soon decay and start fluctuating around some lower value(0.1-0.5, perhaps dependent on temperature). To tell whether this value correspond to a stable state of the system, we can set the initial state S to be other value (e.g. zero) to see whether it will come back to the same stable value(see fig.\ref{fig:relaxationPS4}).

\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
\caption{N=20, F0=1000, E=10000, Initial S=0.05}
\label{fig:thermailzationPS4}
\end{figure}

We may zoom in to understand how the distribution cloud is deforming. 
in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips. The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis. Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back. So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
\label{fig:relaxationPS5}
\end{figure}

In view of this, we take average of a short time to clear this peaks and dips in order to see the time evolution of the overall value of S (the second picture in fig.\ref{fig:relaxationPS2},\ref{fig:relaxationPS3},\ref{fig:relaxationPS4}).

However, there is still no sufficient evidence of convergence for the overall value of S for N=20. 
\begin{figure}[hbtp]

\centering
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
\caption{N=50, E=20000, F0=10000 ,t=1500}
\label{fig:relaxationPS6}
\end{figure}

\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
\end{minipage}
}
\subfigure[$E=5E4$]{
\begin{minipage}[n]{0.4\textwidth}

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
\end{minipage}
}
\end{center}
\end{figure}

\subsection{Lyapunov Exponents(unfinished)}
Lyapunov exponents describes how fast one orbit diverge from its nearby orbits in phase-space. The largest LE reflects  the time scale that system lose its memory in phase-space. We will measure the largest LE along our trajectory and plot its distribution.

\newpage
\section{Breathing Frequency}
Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one. Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas. In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$. Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator. If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized. The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space. If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
\caption{breathing mode frequency measured at different E and $F_0$}
\label{Breathingfrequency1}
\end{figure}

Without interaction, the breathing mode frequency is exactly 2. When there is interaction, the frequency will drift to some other value near 2. We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behaviour by Fourier transform. Then we take the peak frequency near 2 as the breathing mode frequency. The frequency measured in different E and $F_0$ is shown in the Fig.\ref{Breathingfrequency1}.

Before discussion about the mechanism of $\delta$, let us first introduce a approach to simplify this problem:

\subsection{Rotating frame in Phase-space}
Traditionally, we think of there is a distribution cloud in phase space, and due to harmonic trap, the cloud will rotate at frequency $\omega_0$. When there is interaction, we may think there is a small modification of the frequency $\omega=\omega_0+\delta$. Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase space. In this frame, the picture we will see is as follow:\\
\begin{enumerate}[\textbf{*}]
\item All particles are stationary when there is no interaction.
\item The real X and P axis are rotating counter-clockwise, using real X axis to measure distance between particles to determine the interaction at each moment.
\item When there is interaction, particles will gain a ``velocity" in phase space: $\dot{P}=F/m$ . Other effects are all cancelled by frame rotation.
\end{enumerate}

This picture is actually a classical version of the interaction picture. With this picture, we will soon find the dynamic analysis greatly simplified.

In our system, we choose initial velocity to be zero, which means, the particles are aligned on $X|_{t=0}$ axis in phase-space at the beginning. If the breathing frequency of the system is $\omega=\omega_0+\delta$, we will expect to see a line (which may gradually deform into an oval cloud or even an isotropic cloud) rotating at $\delta$ in rotating frame. If we plot x-p with t, we expect to see a spiral motion. Since the motion we see is an additional rotation in rotating frame, we will call it precession. This precession directly leads to the $\delta$.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
\label{Breathingfrequency2}
\end{figure}

\subsection{Estimating Breathing Frequency}
What mechanism leads to the precession motion? To answer this question we may turn to two-particle case first. When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$. In the rotating frame in phase-space, this process can be interpret as follows:

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/collision.png}
\caption{a schematic diagram of the collision process}
\label{Breathingfrequency3}
\end{figure}

Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration. Similar process happen when there are more particles. In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in figure\ref{Breathingfrequency3}. (As for the remaining half of collisions, colliding particles have small difference in their momentum. Let us say, both particles have positive momentum. In fig.\ref{Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)

Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
We will get the precession angular velocity 
\begin{equation}
\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
\label{eq:breathingfrequency1}
\end{equation}
\begin{figure}[hbtp]
\begin{center}
\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
\caption{Frequency measured at N=5} 
Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
\caption{Spectrum at the beginning and the end of measurement}
\end{center}
 Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
\end{figure}

\begin{figure}[hbtp]

\centering
\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
\caption{N=20}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
\end{figure}

When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}). Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2. The reason could also be well understood with the mechanism described before. In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time. For F0 is not very big, the finite interaction time should be taken into consideration. During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$. Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time. There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line). At this point, we will see the precession stop so that the frequency is 2. Thus the relation between frequency and F0 shown in fig.\ref{Breathingfrequency1} is well explained.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
\caption{frequency for N=20}
\end{figure}

Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization". In addition, if the system is completely thermalized in terms of their phase of orbit in phase space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.

\section{Supplement}
The picture of breathing frequency is simple in real space. When two particle bounce, they exchange momentum immediately. It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left. In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ . Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will retrieve $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.

 \end{document}

### 2016-09-05 Interacting Classical Gas_Zhiyu.tex
debug

@@
 \begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
-\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
+\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
 \end{minipage}
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
+\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
 \end{minipage}
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
+\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
 \end{minipage}
@@
 \centering
-\includegraphics[scale=0.35]{../matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
+\includegraphics[scale=0.35]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
 \caption{evolution of single-particle energy}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
 \caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
 \label{fig:thermalization5}
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
 \caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
 \caption{energy of each particle, $F_0=2$}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
 \caption{energy of each particle, $F_0=10$}
@@
 \centering
-\includegraphics[scale=0.5]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
 \caption{Energy distribution, N=5, F0=10000}
 \label{fig:thermalization8}
-\includegraphics[scale=0.47]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
+\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
 \caption{Energy distribution, N=10, E=1000}
 \label{fig:thermalization9}
-\includegraphics[scale=0.52]{../matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
+\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
 \caption{Energy distribution, N=20, F0=10000}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
 \caption{N=5,F0=10000,E=1000, initial S=1}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
 \caption{Zoom in at the beginning part}
@@
 \centering
-\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
 \caption{average over every 30s to see the main tendency}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
 \caption{N=20, F0=1000, E=3000, initial S=1}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
 \caption{N=20, F0=1000, E=10000, initial S=1}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
 \caption{N=20, F0=1000, E=10000, Initial S=0.05}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
 \caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
@@
 \centering
-\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
-\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
 \caption{N=50, E=20000, F0=10000 ,t=1500}
@@
 \begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
 \end{minipage}
@@
 \begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
 \end{minipage}
@@
 \begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}
 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
 \end{minipage}
@@
 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
 \end{minipage}
@@
 \center
-\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
 \caption{breathing mode frequency measured at different E and $F_0$}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
 \caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/collision.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/collision.png}
 \caption{a schematic diagram of the collision process}
@@
 \begin{center}
-\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
+\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
 \caption{Frequency measured at N=5} 
@@
 
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
 \caption{Spectrum at the beginning and the end of measurement}
@@
 \centering
-\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
+\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
 \caption{N=20}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
 \caption{frequency for N=20}

### 2016-09-22 Interacting Classical Gas_Zhiyu.tex
Sept 22

@@
  \usepackage{verbatim}% for \begin{comment} \end{comment}
+ \usepackage{color}
  \begin{document}
@@
 Throughout, we will use ``E" and ``$F_0$" to denote their reduced version  $\tilde{H}$, $\tilde{F_0}$.
+
+\subsection{overview of the system}
+\paragraph{relation between Radius and Energy}
+radius R is defined as the mean-square-root of each particles position $\left\lbrace x_i\right\rbrace$.
+When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators.
+Thus, $E=2*\frac{1}{2}\omega_0^2*\sum_{i}x_i^2=N\omega_0^2R^2$
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
+-\caption{E-R} This picture shows $E=kR^2$ when energy is large. ($k=N\omega_0^2$)
+\end{figure}
+
+\paragraph{Ground states}
+For the ground state of this system, one could predict that \\(1) When the sigma is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small F0 limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keep a equal distance with its nearest neighbours, which is $\frac{2F0}{\omega_0^2}$.
+The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{F0 is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
+
+In the picture below, you can see this crossover from the ``solid-like" limit to the ``hardcore gas" limit.
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/groundstate1.eps}
+\caption{particles' position at ground states }
+\end{figure}
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
+\caption{ground state Energy with $F_0$}
+\end{figure}
+
+\newpage
+\section{Breathing Frequency}
+Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
+In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
+In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one.
+Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas.
+In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$.
+Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator.
+If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized.
+The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space.
+If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
+If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
+Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
+\begin{figure}[hbtp]
+\center
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
+\caption{breathing mode frequency measured at different E and $F_0$}
+\label{Breathingfrequency1}
+\end{figure}
+
+Without interaction, the breathing mode frequency is exactly 2.
+When there is interaction, the frequency will drift to some other value near 2.
+We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behaviour by Fourier transform.
+Then we take the peak frequency near 2 as the breathing mode frequency.
+The frequency measured in different E and $F_0$ is shown in the Fig.\ref{Breathingfrequency1}.
+
+The mechanism that deviate breathing frequency from 2 is simple in real space.
+When two particle bounce, they exchange momentum immediately.
+It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left.
+In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ .
+Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will get $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.
+
+To see this picture better, let us first introduce a approach to simplify this problem:
+
+\subsection{Rotating frame in Phase-space}
+Traditionally, we think of there is a distribution cloud in phase space, and due to harmonic trap, the cloud will rotate at frequency $\omega_0$.
+When there is interaction, we may think there is a small modification of the frequency $\omega=\omega_0+\delta$.
+Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase space.
+In this frame, the picture we will see is as follow:\\
+\begin{enumerate}[\textbf{*}]
+\item All particles are stationary when there is no interaction.
+\item The real X and P axis are rotating counter-clockwise, using real X axis to measure distance between particles to determine the interaction at each moment.
+\item When there is interaction, particles will gain a ``velocity" in phase space: $\dot{P}=F/m$ . Other effects are all cancelled by frame rotation.
+\end{enumerate}
+
+This picture is actually a classical version of the interaction picture. With this picture, we will soon find the dynamic analysis greatly simplified.
+
+In our system, we choose initial velocity to be zero, which means, the particles are aligned on $X|_{t=0}$ axis in phase-space at the beginning.
+If the breathing frequency of the system is $\omega=\omega_0+\delta$, we will expect to see a line (which may gradually deform into an oval cloud or even an isotropic cloud) rotating at $\delta$ in rotating frame.
+If we plot x-p with t, we expect to see a spiral motion.
+Since the motion we see is an additional rotation in rotating frame, we will call it precession.
+This precession directly leads to the $\delta$.
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
+\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
+\label{Breathingfrequency2}
+\end{figure}
+
+{\color{red}{ONE SET OF PICTURES HERE TO SHOW THE TIME EVOLUTION OF THE CLOUD IN PHASE-SPACE:}}
+N=20, same E and F0, several initial states:
+Stationary frame: T/4 T/2 3T/4 T
+rotating frame: T/4 T/2 3T/4 T
+
+\subsection{Estimating Breathing Frequency}
+Let us begin with two-particle case.
+When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$.
+In the rotating frame in phase-space, this process can be interpret as follows:
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/collision.png}
+\caption{a schematic diagram of the collision process}
+\label{Breathingfrequency3}
+\end{figure}
+
+Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
+Similar process happen when there are more particles.
+In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in figure\ref{Breathingfrequency3}.
+(As for the remaining half of collisions, colliding particles have small difference in their momentum.
+Let us say, both particles have positive momentum.
+In fig.\ref{Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)
+
+Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
+We will get the precession angular velocity 
+\begin{equation}
+\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
+\label{eq:breathingfrequency1}
+\end{equation}
+\begin{figure}[hbtp]
+\begin{center}
+\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
+\caption{Frequency measured at N=5} 
+Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.
+
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
+\caption{Spectrum at the beginning and the end of measurement}
+\end{center}
+ Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
+\end{figure}
+
+\begin{figure}[hbtp]
+
+\centering
+\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
+\caption{N=20}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
+\end{figure}
+
+When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}).
+Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
+The reason could also be well understood with the mechanism described before.
+In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time.
+For F0 is not very big, the finite interaction time should be taken into consideration.
+During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
+Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
+There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line).
+At this point, we will see the precession stop so that the frequency is 2.
+
+Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization".
+In addition, if the system is completely thermalized in terms of their phase of orbit in phase space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.
 
@@
 
-%-------------%
-\begin{comment}
-\subparagraph{Detailed discussion on two-particle motion}
+\paragraph{More particles}
+Now let's consider the three-particle case.
+For two particle, the motion is non-chaotic.
+On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon.
+However, in some cases, the time scale of thermalizing could still be very long.
+Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small.
+Meanwhile, suppose particle C has some energy quite different from A \& B.
+In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period.
+How will energy transfer between C and the two-particle system A and B?
+Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau\sim\frac{\sigma}{R}$ ($\tau\ll\frac{2\pi}{\omega}$).
+C gives A a push when approaching it, and then push A back when leaving.
+As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\frac{\sigma}{R})$) in the background of a trap.
+Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$).
+In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected.
+In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass.
+The physics of the ``dance" is similar to the dance between two particle.
+As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.
+%We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g.
+change $m$ to $\mu$ , which is the reduced mass of m \& 2m.
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.35]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
+\caption{evolution of single-particle energy}
+\label{fig:thermalization4}
+\end{figure}
+
+The argument above still holds in many-particle case.
+Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems oscillating on the energy level diagram at low frequency.
+The discussion above gives us some pictures about the non-ergodic state.
+For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.
+
+\subsection{Thermalization condition}
+The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before.
+Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$).
+As a result, to achieve ergodic state, we have to avoid such low frequency oscillation.
+According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large".
+Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the average energy, which is $\frac{E}{N}$.
+At least they are of the same order.
+The thermalization condition could be given by:
+$F_0\sigma\sim\frac{E}{N}$
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
+\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
+\label{fig:thermalization5}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
+\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}
+
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
+\caption{energy of each particle, $F_0=2$}
+\label{fig:thermalization6}
+
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
+\caption{energy of each particle, $F_0=10$}
+\label{fig:thermalization7}
+\end{figure}
+
+As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ (we always set $\sigma=1$), while the average energy $\sim 10$, as we expected, they are of the same order.
+As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e.
+in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
+To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
+
+\newpage
+\subsection{Verifying Boltzmann distribution}
+Thermalization could have different definition.
+In our system, the ``thermalization" we want to find means ``losing all the memory of initial state".
+One of the most important information of initial state is energy distribution.
+We can check whether a system has gone to equilibrium by measuring its energy distribution.
+
+\paragraph{energy distribution}
+For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
+However, to our knowledge, there is not any obvious conclusion about the distribution for an isolated system where the total energy is conserved.
+
+But intuitively, one will expect that if we measure the energy of a subsystem , e.g.
+one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle.
+The temperature of this isolated system is defined according to $Nk_BT=E$.
+It is evident that this argument only hold when the energy of the single particle is not too big --- if one particle take up 50\% of the total energy, the rest could no longer be thought of as a good bath.
+
+In the first picture below, we verify this argument by measuring the energy distribution of every particle at N=10 for different F0 at E=1000 (parameters here satisfy thermalizing condition).
+In the other two, we tested different N.
+
+\newpage
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
+\caption{Energy distribution, N=5, F0=10000}
+\label{fig:thermalization8}
+
+\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
+\caption{Energy distribution, N=10, E=1000}
+\label{fig:thermalization9}
+
+\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
+\caption{Energy distribution, N=20, F0=10000}
+\label{fig:thermalization10}
+\end{figure}
+
+\newpage
+\begin{flushleft}
+To take the first one as an example, Y axis is logarithmically scaled.
+X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system.
+The blue dotted line is the predicted Boltzmann distribution (normalized according to counts).
+Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare.
+In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction.
+When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.
+
+It is evident form $Nk_BT=E$ that the slope of Boltzmann distribution in this figure only depend on N. That is the reason why we want to measure at different N below.
+
+In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states.
+Possibility is proportional to Boltzmann exponential factor multiplied by density of states.
+The reason why we did not take DOS into account previously lies in that the DOS is a constant for simple harmonic oscillator.
+However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
+But since $\sigma<<R$, one can think of this as a small modification.
+Therefore, the tendency of the curve in fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10} is deviated slightly from Boltzmann distribution.
+
+\end{flushleft}
+
+\newpage
+\section{Relaxation in Phase-space}
+To date, we have verified that the energy distribution will go to Boltzmann distribution.
+However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state.
+There is other information that could still exist, for instance, the shape of distribution cloud in phase-space.
+One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour.
+For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large.
+On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all.
+Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).
+
+\paragraph{Shape of Distribution in Phase-space}
+If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
+If the phase of oscillation is completely random, the cloud should be isotropic in phase space.
+In view of this, we defined a shape factor S:
+\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively.
+a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
+S=1 for line-shape distribution, S=0 for circular distribution.
+The time evolution of S will probably show how fast the distribution ``forget" its initial shape.
+
+\begin{figure}[hbtp]
+
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
+\caption{N=5,F0=10000,E=1000, initial S=1}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
+\caption{Zoom in at the beginning part}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
+\caption{average over every 30s to see the main tendency}
+\label{fig:relaxationPS1}
+\end{figure}
+
+From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge.
+Maybe the fluctuation of S is so large that make it hard to identify the convergence of S.
+The only way to solve this problem is using more particle simulation to suppress the fluctuation.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
+\caption{N=20, F0=1000, E=3000, initial S=1}
+\begin{flushleft}
+Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
+\end{flushleft}
+\label{fig:relaxationPS2}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
+\caption{N=20, F0=1000, E=10000, initial S=1}
+\label{fig:relaxationPS3}
+\end{figure}
+
+For N=20(fig.\ref{fig:relaxationPS3}), the S start evolving from 1 will soon decay and start fluctuating around some lower value(0.1-0.5, perhaps dependent on temperature).
+To tell whether this value correspond to a stable state of the system, we can set the initial state S to be other value (e.g.
+zero) to see whether it will come back to the same stable value(see fig.\ref{fig:relaxationPS4}).
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
+\caption{N=20, F0=1000, E=10000, Initial S=0.05}
+\label{fig:relaxationPS4}
+\end{figure}
+
+We may zoom in to understand how the distribution cloud is deforming. 
+in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips.
+The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis.
+Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back.
+So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
+\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
+\label{fig:relaxationPS5}
+\end{figure}
+
+In view of this, we take average of a short time to clear this peaks and dips in order to see the time evolution of the overall value of S (the second picture in fig.\ref{fig:relaxationPS2},\ref{fig:relaxationPS3},\ref{fig:relaxationPS4}).
+
+However, there is still no sufficient evidence of convergence for the overall value of S for N=20. 
+\begin{figure}[hbtp]
+
+\centering
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
+\caption{N=50, E=20000, F0=10000 ,t=1500}
+\label{fig:relaxationPS6}
+\end{figure}
+
+\newpage
+\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
+\begin{figure}[hbtp]
+\begin{center}
+\subfigure[$E=3E5$]{
+\begin{minipage}[n]{0.4\textwidth}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
+\end{minipage}
+}
+\subfigure[$E=2E5$]{
+\begin{minipage}[n]{0.4\textwidth}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
+\end{minipage}
+}
+\subfigure[$E=1E5$]{
+\begin{minipage}[n]{0.4\textwidth}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}
+
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
+\end{minipage}
+}
+\subfigure[$E=5E4$]{
+\begin{minipage}[n]{0.4\textwidth}
+
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
+\end{minipage}
+}
+\end{center}
+\end{figure}
+
+\newpage
+\subsection{Lyapunov Exponents(unfinished)}
+Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
+The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space.
+We will measure the LLEs along our trajectory and plot its distribution.
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
+\caption{N=5, F0=1000, E=3000, Gaussian interaction}
+\label{fig:LLEexample1}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
+\caption{N=5, F0=1000, E=10000, Gaussian interaction}
+\label{fig:LLEexample2}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
+\caption{N=5, F0=1000, E=100000, Gaussian interaction}
+\label{fig:LLEexample3}
+\end{figure}
+
+Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement.
+\textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_22.eps}
+\caption{LLE distribution for N=5, F0=1000, scan E.
+(It seems that MATLAB has difficulty changing .fig into .eps files.
+To get rid of the annoying white lines you may open this figure in MATLAB with .fig format.)}
+\label{fig:LLEdistribution1}
+\end{figure}
+
+fig.\ref{fig:LLEdistribution1} shows the distribution of LLE by color.
+The LLE decrease with the growth of Energy.
+The crucial part is near E=5000.
+The most probable value of LLE goes down from 1 to 0.1,which indicate that \textbf{the shortest time scale becomes longer than an oscillation period when E is larger than 5000}.
+And E=5000 is exactly our prediction value of thermalization threshold.
+So there is a correspondence between energy thermalization and LLE.
+The size of bin(resolution of LLE) in fig.\ref{fig:LLEdistribution1} is 0.01, so when E goes far beyond the thermalization threshold, the LLE distribution is not that clear.
+We only know that LLE is concentrated close to zero in high E regime.
+
+\section{others(those I haven't organized it into the text in logical order but may be useful)}
+
+\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
+Results are shown in fig.\ref{fig:others1}
+
+\begin{figure}[hbtp]
+
+\centering
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
+\caption{fluctuation of R with time }
+sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
+\label{fig:others1}
+\end{figure}
+
+\subsection{Detailed discussion of two-particle motion}
+{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization".
+But then I found we haven't used these result.
+So I put it at the end for the time being}}.
+
 From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system.
@@
 \label{fig:thermalization3}
-\end{figure}}
-\end{comment}
-%-------------%
-
-\paragraph{More particles}
-Now let's consider the three-particle case.
-For two particle, the motion is non-chaotic.
-On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon.
-However, in some cases, the time scale of thermalizing could still be very long.
-Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small.
-Meanwhile, suppose particle C has some energy quite different from A \& B.
-In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period.
-How will energy transfer between C and the two-particle system A and B?
-Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau$ ($\tau\ll\frac{2\pi}{\omega}$).
-When C pass A, it gives A a push, and then push A back.
-As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\tau)$) in the background of a trap.
-Since the position and velocity of A and B are both close, the effect of C on A \& B are almost the same (difference$\sim O(\tau\sigma)\sim O(\tau^2)$).
-In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected.
-In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass.
-The physics of the ``dance" is similar to the dance between two particle.
-%We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g.
-change $m$ to $\mu$ , which is the reduced mass of m \& 2m.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.35]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
-\caption{evolution of single-particle energy}
-\label{fig:thermalization4}
 \end{figure}
 
-The argument above still holds in many-particle case.
-Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems dancing together on the energy level diagram.
-The discussion above gives us some pictures about the non-ergodic state.
-For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.
-
-\subsection{Thermalization condition}
-The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before.
-Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$).
-As a result, to achieve ergodic state, we have to avoid such low frequency oscillation.
-According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large".
-Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the energy interval, which is $\frac{E}{N}$.
-At least they are of the same order.
-The thermalization condition could be given by:
-$F_0\sigma\sim\frac{E}{N}$
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
-\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
-\label{fig:thermalization5}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
-\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}
-
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
-\caption{energy of each particle, $F_0=2$}
-\label{fig:thermalization6}
-
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
-\caption{energy of each particle, $F_0=10$}
-\label{fig:thermalization7}
-\end{figure}
-
-As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ while the energy interval of particles $\sim 10$, as we expected, they are of the same order.
-As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e.
-in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
-Till now, we have verified that the criteria of non-ergodic and ergodic state, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution.
-
-\newpage
-\subsection{Verifying Boltzmann distribution}
-Thermalization could have different definition.
-In our system, the "thermalization" we want to find means "losing all the memory of initial state".
-One of the most important information of initial state is energy distribution.
-We can check whether a system has gone to equilibrium by measuring its energy distribution.
-
-\paragraph{energy distribution}
-For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
-However, for an isolated system where the total energy is conserved, it not obvious to draw some strict conclusion about the distribution.
-
-Intuitively, one will expect that if we measure the energy of a subsystem , e.g.
-one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle.
-The temperature of this isolated system is defined according to $Nk_BT=E$.
-It is evident that this argument only hold when the energy of the single particle is not too big--if one particle has 50\% of the total energy, the rest could no longer be think of as a good bath.
-
-In the first picture below, we verify this argument by measuring the energy distribution of every particle at N=10 for different F0 at E=1000 (parameters here satisfy thermalizing condition).
-In the other two, we tested different N.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
-\caption{Energy distribution, N=5, F0=10000}
-\label{fig:thermalization8}
-\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
-\caption{Energy distribution, N=10, E=1000}
-\label{fig:thermalization9}
-\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
-\caption{Energy distribution, N=20, F0=10000}
-\label{fig:thermalization10}
-\end{figure}
-
-\begin{flushleft}
-To take the first one as an example, Y axis is logarithmically scaled.
-X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system.
-The blue dotted line is the predicted Boltzmann distribution (normalized according to counts).
-Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare.
-In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction.
-When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.
-
-It is evident form $Nk_BT=E$ that the slope of Boltzmann distribution in this figure only depend on N. That is the reason why we want to measure at different N below.
-
-In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states.
-Possibility is proportional to Boltzmann exponential factor multiplied by density of states.
-The reason why we did not take DOS into account previously lies in that the DOS is a constant for simple harmonic oscillator.
-However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
-But since $\sigma<<R$, one can think of this as a small modification.
-Therefore, the tendency of the curve in fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10} is deviated slightly from Boltzmann distribution.
-
-\end{flushleft}
-
-\newpage
-\section{Relaxation in Phase-space (unfinished)}
-Till now we have verified the energy distribution will go to Boltzmann distribution.
-However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state.
-There is other information that could still exist, for instance, the shape of distribution cloud in phase-space.
-One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour.
-For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large.
-On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all.
-Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).
-
-\paragraph{Shape of Distribution in Phase-space}
-If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
-If the phase of oscillation is completely random, the cloud should be isotropic in phase space.
-In view of this, we defined a shape factor S:
-\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively.
-a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
-S=1 for line-shape distribution, S=0 for circular distribution.
-The time evolution of S will probably show how fast the distribution ``forget" its initial shape.
-
-\begin{figure}[hbtp]
-
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
-\caption{N=5,F0=10000,E=1000, initial S=1}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
-\caption{Zoom in at the beginning part}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
-\caption{average over every 30s to see the main tendency}
-\label{fig:relaxationPS1}
-\end{figure}
-
-From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge.
-Maybe the fluctuation of S is so large that make it hard to identify the convergence of S.
-The only way to solve this problem is using more particle simulation to suppress the fluctuation, while the cost is that the simulation time will be limited.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
-\caption{N=20, F0=1000, E=3000, initial S=1}
-Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
-\label{fig:relaxationPS2}
-\end{figure}
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
-\caption{N=20, F0=1000, E=10000, initial S=1}
-\label{fig:relaxationPS3}
-\end{figure}
-
-For N=20(fig.\ref{fig:relaxationPS3}), the S start evolving from 1 will soon decay and start fluctuating around some lower value(0.1-0.5, perhaps dependent on temperature).
-To tell whether this value correspond to a stable state of the system, we can set the initial state S to be other value (e.g.
-zero) to see whether it will come back to the same stable value(see fig.\ref{fig:relaxationPS4}).
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
-\caption{N=20, F0=1000, E=10000, Initial S=0.05}
-\label{fig:thermailzationPS4}
-\end{figure}
-
-We may zoom in to understand how the distribution cloud is deforming. 
-in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips.
-The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis.
-Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back.
-So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
-\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
-\label{fig:relaxationPS5}
-\end{figure}
-
-In view of this, we take average of a short time to clear this peaks and dips in order to see the time evolution of the overall value of S (the second picture in fig.\ref{fig:relaxationPS2},\ref{fig:relaxationPS3},\ref{fig:relaxationPS4}).
-
-However, there is still no sufficient evidence of convergence for the overall value of S for N=20. 
-\begin{figure}[hbtp]
-
-\centering
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
-\caption{N=50, E=20000, F0=10000 ,t=1500}
-\label{fig:relaxationPS6}
-\end{figure}
-
-\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
-\begin{figure}[hbtp]
-\begin{center}
-\subfigure[$E=3E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=2E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=1E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=5E4$]{
-\begin{minipage}[n]{0.4\textwidth}
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
-\end{minipage}
-}
-\end{center}
-\end{figure}
-
-\subsection{Lyapunov Exponents(unfinished)}
-Lyapunov exponents describes how fast one orbit diverge from its nearby orbits in phase-space.
-The largest LE reflects  the time scale that system lose its memory in phase-space.
-We will measure the largest LE along our trajectory and plot its distribution.
-
-\newpage
-\section{Breathing Frequency}
-Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
-In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
-In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one.
-Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas.
-In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$.
-Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator.
-If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized.
-The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space.
-If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
-If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
-Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
-\begin{figure}[hbtp]
-\center
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
-\caption{breathing mode frequency measured at different E and $F_0$}
-\label{Breathingfrequency1}
-\end{figure}
-
-Without interaction, the breathing mode frequency is exactly 2.
-When there is interaction, the frequency will drift to some other value near 2.
-We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behaviour by Fourier transform.
-Then we take the peak frequency near 2 as the breathing mode frequency.
-The frequency measured in different E and $F_0$ is shown in the Fig.\ref{Breathingfrequency1}.
-
-Before discussion about the mechanism of $\delta$, let us first introduce a approach to simplify this problem:
-
-\subsection{Rotating frame in Phase-space}
-Traditionally, we think of there is a distribution cloud in phase space, and due to harmonic trap, the cloud will rotate at frequency $\omega_0$.
-When there is interaction, we may think there is a small modification of the frequency $\omega=\omega_0+\delta$.
-Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase space.
-In this frame, the picture we will see is as follow:\\
-\begin{enumerate}[\textbf{*}]
-\item All particles are stationary when there is no interaction.
-\item The real X and P axis are rotating counter-clockwise, using real X axis to measure distance between particles to determine the interaction at each moment.
-\item When there is interaction, particles will gain a ``velocity" in phase space: $\dot{P}=F/m$ . Other effects are all cancelled by frame rotation.
-\end{enumerate}
-
-This picture is actually a classical version of the interaction picture. With this picture, we will soon find the dynamic analysis greatly simplified.
-
-In our system, we choose initial velocity to be zero, which means, the particles are aligned on $X|_{t=0}$ axis in phase-space at the beginning.
-If the breathing frequency of the system is $\omega=\omega_0+\delta$, we will expect to see a line (which may gradually deform into an oval cloud or even an isotropic cloud) rotating at $\delta$ in rotating frame.
-If we plot x-p with t, we expect to see a spiral motion.
-Since the motion we see is an additional rotation in rotating frame, we will call it precession.
-This precession directly leads to the $\delta$.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
-\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
-\label{Breathingfrequency2}
-\end{figure}
-
-\subsection{Estimating Breathing Frequency}
-What mechanism leads to the precession motion?
-To answer this question we may turn to two-particle case first.
-When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$.
-In the rotating frame in phase-space, this process can be interpret as follows:
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/collision.png}
-\caption{a schematic diagram of the collision process}
-\label{Breathingfrequency3}
-\end{figure}
-
-Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
-Similar process happen when there are more particles.
-In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in figure\ref{Breathingfrequency3}.
-(As for the remaining half of collisions, colliding particles have small difference in their momentum.
-Let us say, both particles have positive momentum.
-In fig.\ref{Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)
-
-Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
-We will get the precession angular velocity 
-\begin{equation}
-\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
-\label{eq:breathingfrequency1}
-\end{equation}
-\begin{figure}[hbtp]
-\begin{center}
-\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
-\caption{Frequency measured at N=5} 
-Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
-\caption{Spectrum at the beginning and the end of measurement}
-\end{center}
- Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
-\end{figure}
-
-\begin{figure}[hbtp]
-
-\centering
-\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
-\caption{N=20}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
-\end{figure}
-
-When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}).
-Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
-The reason could also be well understood with the mechanism described before.
-In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time.
-For F0 is not very big, the finite interaction time should be taken into consideration.
-During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
-Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
-There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line).
-At this point, we will see the precession stop so that the frequency is 2.
-Thus the relation between frequency and F0 shown in fig.\ref{Breathingfrequency1} is well explained.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
-\caption{frequency for N=20}
-\end{figure}
-
-Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization".
-In addition, if the system is completely thermalized in terms of their phase of orbit in phase space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.
-
-\section{Supplement}
-The picture of breathing frequency is simple in real space.
-When two particle bounce, they exchange momentum immediately.
-It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left.
-In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ .
-Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will retrieve $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.
-
  \end{document}

### 2016-10-02 Interacting Classical Gas_Zhiyu_APS.tex
Oct2 APS's PRE format, tex

--- 2016-09-22 Interacting Classical Gas_Zhiyu.tex
@@
-\documentclass[a4paper,onecolumn,12pt]{article}
+\documentclass[aps,pre,twocolumn
+,groupedaddress]{revtex4-1}
+%\documentclass[a4paper,onecolumn,12pt]{article}
 \usepackage{amsmath}
@@
  \usepackage{color}
+ \usepackage{bm}
  \begin{document}
@@
  \author{Zhiyu}
+ \affiliation{Fudan University}
+\begin{abstract}
+\end{abstract}
  \maketitle
- \tableofcontents
- \newpage
+% \tableofcontents
+% \newpage
+\section{Introduction}
 
@@
 \end{equation}
-
+so the Hamiltonian is
 \begin{equation}
@@
 \end{equation}
-It can be easily shown that eq.\ref{eq:preparation2} can be rewrite into the following form:
+It can be shown that eq.\ref{eq:preparation2} can be rewrite into the following form:
 \begin{equation}
@@
 In this manner, we reduced number of the parameters in our model into three: $\tilde{H}$, $\tilde{F_0}$, $N$.
-Equivalently, we set $\sigma$, $\omega$ and $m$ to 1 in our numerical simulation.
+Equivalently, we set $\sigma$, $\omega_0$ and $m$ to 1 in our numerical simulation.
 Throughout, we will use ``E" and ``$F_0$" to denote their reduced version  $\tilde{H}$, $\tilde{F_0}$.
 
-\subsection{overview of the system}
-\paragraph{relation between Radius and Energy}
-radius R is defined as the mean-square-root of each particles position $\left\lbrace x_i\right\rbrace$.
+\subsection{Overview}
+\subsubsection{Relation between Radius and Energy}
+The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$.
 When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators.
-Thus, $E=2*\frac{1}{2}\omega_0^2*\sum_{i}x_i^2=N\omega_0^2R^2$
+Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$
 \begin{figure}[hbtp]
 \centering
-\includegraphics[scale=0.5]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
+\includegraphics[scale=0.3]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
 -\caption{E-R} This picture shows $E=kR^2$ when energy is large. ($k=N\omega_0^2$)
@@
 
-\paragraph{Ground states}
-For the ground state of this system, one could predict that \\(1) When the sigma is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small F0 limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keep a equal distance with its nearest neighbours, which is $\frac{2F0}{\omega_0^2}$.
-The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{F0 is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
+\subsubsection{Ground states}
+For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small $\mathbf{F_0}$ limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$.
+The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{$\mathbf{F_0}$ is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
 
-In the picture below, you can see this crossover from the ``solid-like" limit to the ``hardcore gas" limit.
+In the fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the ``hardcore gas" limit (right).
 
@@
 \centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/groundstate1.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/groundstate1.eps}
 \caption{particles' position at ground states }
+\label{fig:GS1}
 \end{figure}
 
+\begin{comment}
 \begin{figure}[hbtp]
@@
 \end{figure}
+\end{comment}
 
@@
 \section{Breathing Frequency}
-Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
+Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
 In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
-In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one.
-Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas.
-In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$.
-Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator.
-If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized.
-The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space.
-If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
-If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
+However, it is quite different in the classical version.
+Firstly, the ground state may be meaningless.
+In quantum case, the reason why we care about ground state and low lying excitations is that BEC occur at low temperature.
+But in classical case, there is no BEC.
+So it is not necessary to focus on low lying excitations in classical case.
+Besides, since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $\bar{h}/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one.
+Secondly, it is no longer necessary to vary parameters ``by a little" in the quench.
+In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}).
+But in classical case, since $\bar{h}$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case.
+Thus it is not necessary to limit ourselves to small quench.
+
+Furthermore, notice that X and P (normalized) are symmetric for simple harmonic oscillator.
+In weak interaction limit, the distribution cloud should be circular when the gas is completely thermalized.
+The difference between thermalized cloud before and after quench is that they are circular under different normalization of phase-space.
+If we look at both of them in the phase-space normalized according to the final $\omega_0$, we will find shape of the cloud before the quench is an ellipse while the final one is a circle.
+
+Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant.
+If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
 Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
@@
 \center
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2.eps}
 \caption{breathing mode frequency measured at different E and $F_0$}
@@
 \centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
-\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
+\caption{precession motion in phase-space observed in rotating frame (only show one(two) particles' trajectory in upper(lower) picture for clarity)}
 \label{Breathingfrequency2}
@@
 
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
+\caption{•}
+\end{figure}
+
 Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization".
@@
 In view of this, we begin the study with two-particle motion.
-\paragraph{two-particle}
+\subsubsection{two particles}
 
@@
 We can always think of them in the reference frame of their center of mass ``C".
-In frame C, one can easily show that when there is no interaction, what we will see is that two particles are bound together by a harmonic trap center at C(cf).
+In frame C, one can easily show that when there is no interaction what we will see is that two particles are bound together by a harmonic trap center at C(black line in fig.\ref{fig:thermalization2}).
 So their relative motion is also a harmonic oscillation.
@@
 
-\paragraph{More particles}
+\subsubsection{More particles}
 Now let's consider the three-particle case.
@@
 
-\paragraph{energy distribution}
+\subsubsection{energy distribution}
 For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
@@
 
-\paragraph{Shape of Distribution in Phase-space}
+\subsubsection{Shape of Distribution in Phase-space}
 If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
@@
 \centering
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_22.eps}
+\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27.eps}
 \caption{LLE distribution for N=5, F0=1000, scan E.

### 2016-10-03 Interacting Classical Gas_Zhiyu_APS.tex
Oct4 APS's PRE format, tex

@@
 We can always think of them in the reference frame of their center of mass ``C".
-In frame C, one can easily show that when there is no interaction what we will see is that two particles are bound together by a harmonic trap center at C(black line in fig.\ref{fig:thermalization2}).
+In frame C, one can easily show that when there is no interaction what we will see is that two particles are bound together by a harmonic trap center at C (black line in fig.\ref{fig:thermalization2}).
 So their relative motion is also a harmonic oscillation.
@@
 The deviation grows with the increase of $F_0$ and the decrease of internal energy of the pair.
-As a result, when the $F_0$ is small and when the E is large, a beat with frequency $\omega_r-\omega_0=\delta$ will exist.
+As a result, when the $F_0$ is small and when the E is large, a beat with low frequency $\omega_r-\omega_0=\delta$ will exist.
+This phenomenon means energy transfer between particles are inefficient, thus it will slow down the thermalization process.
 
-\begin{figure}[hbtp]
+\begin{figure*}
 \begin{center}
@@
 \end{center}
-\caption{the dependence of beat frequency on internal energy} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly.
+\caption{the dependence of beat frequency on internal energy\label{fig:thermalization1}} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly.
 Here, $E_i$ is large(compare to $F_0\sigma$).
@@
 Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
-\label{fig:thermalization1}
-\end{figure}
+
+\end{figure*}
 
@@
 To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
+
+\subsection{Bouncing and Passing} 
+Back to two-particle case, we notice that there are two dynamically distinct regime: \\1) when the maximum of interaction energy is smaller than internal energy, two particle pass each other every time they meet;\\2) when the maximum of interaction energy is higher than internal energy, two particle bounce back.
+
+We call them passing and bouncing regime respectively.
+If we estimate internal energy of a pair with E/N, the criterion between these two regime is $\frac{NF_0\sigma}{E}=1 $,which is just the thermalization threshold!
+Naturally one will ask whether thermalization is related to passing and bouncing.
+As is shown in last two subsections, in passing regime, the situation can be described by the long-term beat behaviour, which obstruct the thermalization.
+So in this subsection, we focus on the bouncing regime.
+
+To see how the bouncing process thermalize the system, let's consider the strong interaction limit in bouncing regime: $F_0\rightarrow \infty$.
+In that case, the bouncing happens in a moment.
+The picture is completely the same as what we have discussed in section ''Breathing Frequency": One can relabel two particles after the bounce and describe the collision as ''particle A comes from the left and jump by $\sigma$ to the right while particle B comes from the right and jump by $\sigma$ to the left".
+Now if we consider the energy transfer in this process, the only term changed is the potential term.
+The magnitude of energy transfer in a collision is $m\omega_0^2x_{coll}\sigma$ (suppose $\sigma<<x_{coll}$), where $x_{coll}$ is the position where the collision occur, and is, generally speaking, proportional to cloud radius R.
+
+In bouncing regime, when F0 increase the collision time $\tau$ decrease to zero, but thanks to the finite interaction range, the energy transfer rate stay finite, which is essentially different from the case in passing regime, where when the F0 decrease to zero, since interaction vanishes the energy transfer rate definitely vanishes.
+
+There is one last concern: as is shown in fig.\ref{fig:thermalization3}, the frequency of two-body motion can go to 2 in bouncing regime.
+Will there be a long-term beat effect as described in passing regime?
+The long-term beat may occur when $\omega_r$ is close to 2, which means the collision time $\tau$ compensate the time saved by jumping for $\sigma$.
+In the language of energy transfer, particle pick up some energy since the trap force act on it for time $\tau$ and lose some energy because leaping $\sigma$ in the trap.
+The mechanism is similar to that in passing regime.
+Thus it seems that it is possible to form a long-term beat.
+However, one should bear in mind that in more-particle case, other particles will strongly interfere the motion of the two we are analysing.
+It is quite different from long-term beat in small F0 limit.
+In that limit, if pairs with smallest internal energy form a long-term beat, one can deduce that other particles act like transparent to them.
+But in bouncing regime, long-term beat is like a ``coincidence"-- it only occurs when one pair's internal energy and F0 is in certain relation, so one pair forming a beat does not ensures that other particles are ``transparent" to them.
 

### 2016-10-07 Interacting Classical Gas_Zhiyu_APS.tex
Oct7 APS's PRE format, tex

--- 2016-10-02 Interacting Classical Gas_Zhiyu_APS.tex
@@
  \author{Zhiyu}
- \affiliation{Fudan University}
+ \affiliation{Fudan University, Shanghai, China}
+
 \begin{abstract}
@@
 To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
+
+One will say that this condition only means that the energy transfer in every collision is much smaller than the energy interval.
+It seems that these two regime are not so distinct.
+It is necessary to emphasis that the essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer.
+What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives.
+It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time!
+In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us.
+Thus the particles energy is localized in certain value.
+On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners.
+As a result, the energy transferred in every collision between two particles are no longer correlated, which is equivalent to say that two-particle analysis breaks down.
+Instead, the energy transfer is completely random, with a non-zero amplitude.
+On the single-particle energy diagram, what we expected to see is a ``one dimensional random walk" ,so energy levels quickly spread around the diagram.
+
+To sum up, the thermalization threshold not only tells us whether the amplitude of energy transfer in every collision is small enough compared to particles' energy, but also shows whether the ``correlation time" of particle pair is much longer than the characteristic time of the system (the oscillation period).
 

### 2016-10-07 Interacting Classical Gas_Zhiyu_APS.tex
Oct7 APS's PRE format, tex

@@
 Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$
-\begin{figure}[hbtp]
+\begin{figure}
 \centering
@@
 \caption{breathing mode frequency measured at different E and $F_0$}
-\label{Breathingfrequency1}
+\label{fig:Breathingfrequency1}
 \end{figure}
@@
 Then we take the peak frequency near 2 as the breathing mode frequency.
-The frequency measured in different E and $F_0$ is shown in the Fig.\ref{Breathingfrequency1}.
+The frequency measured in different E and $F_0$ is shown in the Fig.\ref{fig:Breathingfrequency1}.
 
@@
 \caption{precession motion in phase-space observed in rotating frame (only show one(two) particles' trajectory in upper(lower) picture for clarity)}
-\label{Breathingfrequency2}
+\label{fig:Breathingfrequency2}
 \end{figure}
 
-{\color{red}{ONE SET OF PICTURES HERE TO SHOW THE TIME EVOLUTION OF THE CLOUD IN PHASE-SPACE:}}
-N=20, same E and F0, several initial states:
+{\color{red}{ONE SET OF PICTURES HERE TO SHOW THE TIME EVOLUTION OF THE CLOUD IN PHASE-SPACE:
+N=20, same E and $F_0$, several initial states:
 Stationary frame: T/4 T/2 3T/4 T
-rotating frame: T/4 T/2 3T/4 T
+rotating frame: T/4 T/2 3T/4 T}}
 
@@
 
-\begin{figure}[hbtp]
+\begin{figure}
 \centering
@@
 \caption{a schematic diagram of the collision process}
-\label{Breathingfrequency3}
+\label{fig:Breathingfrequency3}
 \end{figure}
@@
 Similar process happen when there are more particles.
-In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in figure\ref{Breathingfrequency3}.
+In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in fig.\ref{fig:Breathingfrequency3}.
 (As for the remaining half of collisions, colliding particles have small difference in their momentum.
 Let us say, both particles have positive momentum.
-In fig.\ref{Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)
+In fig.\ref{fig:Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)
 
-Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
+Let us estimate the precession angle $\alpha$ in one collision by $\frac{\sigma}{R}$, which follows from the two-particle case study.
+Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
 We will get the precession angular velocity 
@@
 \end{equation}
-\begin{figure}[hbtp]
-\begin{center}
+
+\begin{comment}
+\begin{figure}
 \includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
@@
 \caption{Spectrum at the beginning and the end of measurement}
-\end{center}
  Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
@@
 
-\begin{figure}[hbtp]
-
+\begin{figure}
 \centering
@@
 \end{figure}
+\end{comment}
+{\color{red}{Here, I hide some figures showing the error of Fourier transform.}}
 
-When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}).
-Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
+When $F_0$ is not that large, the frequency behaviour seems complicated (see fig.\ref{fig:Breathingfrequency1}).
+Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
 The reason could also be well understood with the mechanism described before.
-In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time.
-For F0 is not very big, the finite interaction time should be taken into consideration.
+In the former discussion, we goes to high $F_0$ limit, which means particles exchange momentum in infinitesimal time.
+For $F_0$ is not very big, the finite interaction time should be taken into consideration.
 During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
-Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
+Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
 There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line).
@@
 
-\begin{figure}[hbtp]
+\begin{figure}
 \centering
 \includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
-\caption{•}
+\caption{{\color{red}{run with more initial state}}}
+\label{fig:Breathingfrequency4}
 \end{figure}
+
+The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}.
+For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction eq.\ref{eq:breathingfrequency1}.
+Secondly, the figure shows the frequency's dependence on $F_0$.
+As we explained, when $F_0$ is not so large, the precession angle decrease.
+In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision.
+As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.
+
+the critical point that frequency falls to 2 can be estimate by:
+\begin{equation}
+\omega_0 \tau=\alpha
+\end{equation}
+which states that the approaching time $\tau$ exactly cancels the precession angle derived before
+$\tau$ can be estimated by $R/F_0$. With some math, one can show that this condition is equivalent to
+
+\begin{equation}
+\frac{E}{N}=F_0\sigma
+\end{equation}
+which is the same as the criterion of whether two particle will bounce or pass by if one estimate the average internal energy of a pair with $\frac{E}{N}$.
+This argument indicate the reason why we see frequency stop falling down below 2 as one should expect with previous discussion:\
+All our previous analysis based on fig.\ref{fig:Breathingfrequency3} only studies the case of bouncing.
+If the energy of particles are so large that they often overcome the interaction potential barrier and pass each other, the situation would be completely different.
+In that case, in fig.\ref{fig:Breathingfrequency3}, particles will move a little bit out of their initial position, and soon move back, almost return to their initial place.
+In this manner, the interaction do not affect the distribution of the cloud in phase space.
+Thus, the frequency will stay near 2 when E is large.
 
@@
 To study the condition of thermalization is equivalent to find out the mechanism that prohibits the system from ergodic.
-In view of this, we begin the study with two-particle motion.
+We begin the study with two-particle motion.
 \subsubsection{two particles}
@@
 \begin{figure*}
-\begin{center}
 
@@
 }
-\end{center}
+
 \caption{the dependence of beat frequency on internal energy\label{fig:thermalization1}} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly.
@@
 As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.
-%We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g.
-change $m$ to $\mu$ , which is the reduced mass of m \& 2m.
 
-\begin{figure}[hbtp]
+\begin{figure}
 \centering
-\includegraphics[scale=0.35]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1_pre.eps}
 \caption{evolution of single-particle energy}
@@
 \centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
-\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
+\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
 \label{fig:thermalization5}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
-\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}
 
@@
 \centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
+\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
 \caption{energy of each particle, $F_0=2$}
@@
 \centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
+\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
 \caption{energy of each particle, $F_0=10$}
@@
 
-As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ (we always set $\sigma=1$), while the average energy $\sim 10$, as we expected, they are of the same order.
+As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=5$ (we always set $\sigma=1$), while the average energy $\sim 10$, as we expected, they are of the same order.
 As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e.
@@
 
-One will say that this condition only means that the energy transfer in every collision is much smaller than the energy interval.
+One may think that this condition only means that the energy transfer in every collision is much smaller than the energy interval.
 It seems that these two regime are not so distinct.
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
 \caption{Energy distribution, N=5, F0=10000}
@@
 \includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
-\caption{Energy distribution, N=10, E=1000}
+\caption{Energy distribution, N=10, E=1000 {\color{red}{Run with N=10 F0=10000 to substitute this one}} }
 \label{fig:thermalization9}
 
-\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=20_F0=10000_pre.eps} 
 \caption{Energy distribution, N=20, F0=10000}
@@
 \newpage
-\begin{flushleft}
+
 To take the first one as an example, Y axis is logarithmically scaled.
@@
 Therefore, the tendency of the curve in fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10} is deviated slightly from Boltzmann distribution.
-
-\end{flushleft}
 
@@
 1) intersect with black curve at $+-\frac{\sigma}{2}$\\
-2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a SHO with an extra constant force $F_0$\\
+2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
 Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\

### 2016-10-23 Interacting Classical Gas_Zhiyu_APS.tex
Oct23 APS's PRE format, tex

@@
 Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$
+
+\begin{comment}
 \begin{figure}
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/groundstate1.eps}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2.eps}
 \caption{particles' position at ground states }
@@
 
-\begin{comment}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
-\caption{ground state Energy with $F_0$}
-\end{figure}
-\end{comment}
+%\begin{figure}[hbtp]
+%\centering
+%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
+%\caption{ground state Energy with $F_0$}
+%\end{figure}
+%\end{comment}
 
-\newpage
 \section{Breathing Frequency}
@@
 
-\begin{figure}[hbtp]
+Fig.\ref{fig:Breathingfrequency2} and Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
+
+\begin{figure}
 \centering
@@
 
-{\color{red}{ONE SET OF PICTURES HERE TO SHOW THE TIME EVOLUTION OF THE CLOUD IN PHASE-SPACE:
-N=20, same E and $F_0$, several initial states:
-Stationary frame: T/4 T/2 3T/4 T
-rotating frame: T/4 T/2 3T/4 T}}
+\begin{figure*}
+\subfigure[$t=0$]{
+\begin{minipage}[b]{0.18\linewidth}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T.eps}
+\end{minipage}
+}
+\subfigure[$t=\frac{1}{5}T$]{
+\begin{minipage}[b]{0.18\linewidth}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T.eps}
+\end{minipage}
+}\subfigure[$t=\frac{2}{5}T$]{
+\begin{minipage}[b]{0.18\linewidth}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T.eps}
+\end{minipage}
+}\subfigure[$t=\frac{3}{5}T$]{
+\begin{minipage}[b]{0.18\linewidth}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T.eps}
+\end{minipage}
+}\subfigure[$t=\frac{4}{5}T$]{
+\begin{minipage}[b]{0.18\linewidth}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T.eps}
+\end{minipage}
+}
+\caption{N=50,F0=100,E=50000}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=10T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=30T.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=50T.eps} 
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=70T.eps}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=90T.eps} 
+\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
+\label{fig:Breathingfrequency2_1}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_19trajectory_in_rotating_frame_t=130T_pre.eps}
+\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space, one snapshot in each 10 periods.}
+\label{fig:Breathingfrequency2_2}
+\end{figure}
 
@@
 \centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/collision.png}
-\caption{a schematic diagram of the collision process}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/bounce.png}
+\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/pass.png}
+\caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.
+\textbf{(b)} (Lower) When $F_0*\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous, their trajectory has a turning point(the dashed bright blue trajectory is identical with the one in the upper figure, which is the critical situation between passing and bouncing, that is to say, particles have zero relative velocity when they collide.) }
 \label{fig:Breathingfrequency3}
@@
 
-Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
+(See fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
 Similar process happen when there are more particles.
@@
 
-\begin{comment}
-\begin{figure}
-\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
-\caption{Frequency measured at N=5} 
-Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
-\caption{Spectrum at the beginning and the end of measurement}
- Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
-\caption{N=20}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
-\end{figure}
-\end{comment}
-{\color{red}{Here, I hide some figures showing the error of Fourier transform.}}
-
 When $F_0$ is not that large, the frequency behaviour seems complicated (see fig.\ref{fig:Breathingfrequency1}).
@@
 \centering
-\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
-\caption{{\color{red}{run with more initial state}}}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_scanE_pre.eps}
+\caption{dependence of breathing frequency on Energy, N=20.
+Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000.
+Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
+The black dashed line is the prediction of eq.\ref{eq:breathingfrequency1}.}
 \label{fig:Breathingfrequency4}
@@
 
-\begin{figure*}
+\begin{figure}
 
 \subfigure[$E_i=2$]{
-\begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
+\begin{minipage}[b]{0.22\textwidth}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
 \end{minipage}
@@
 \subfigure[$E_i=3$]{
-\begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
+\begin{minipage}[b]{0.22\textwidth}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
 \end{minipage}
@@
 \subfigure[$E_i=5$]{
-\begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
+\begin{minipage}[b]{0.22\textwidth}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
 \end{minipage}
@@
 \subfigure[$E_i=10$]{
-\begin{minipage}[b]{0.2\textwidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
+\begin{minipage}[b]{0.22\textwidth}
+\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
 \end{minipage}
@@
 
-\caption{the dependence of beat frequency on internal energy\label{fig:thermalization1}} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly.
-Here, $E_i$ is large(compare to $F_0\sigma$).
+\caption{the dependence of beat frequency on internal energy.
+The diagram is the energy of two particles.
+Here, $F_0$ is set to be 1.
 In this case, the larger $E_i$ is, the lower the beat frequency is.
-Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
+\label{fig:thermalization1}}%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
 
-\end{figure*}
+\end{figure}
 
@@
 The thermalization condition could be given by:
-$F_0\sigma\sim\frac{E}{N}$
+\begin{equation}
+F_0\sigma\sim\frac{E}{N}
+\label{eq:thermalizatiton condition}
+\end{equation}
 
@@
 \centering
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
-\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
+%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
+%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre.eps}
+\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold".
+In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in eq.\ref{eq:thermalizatiton condition}}
 \label{fig:thermalization5}
@@
 \begin{figure}
-\centering
-\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
-\caption{energy of each particle, $F_0=2$}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
+\caption{energy of each particle, $F_0=200$}
 \label{fig:thermalization6}
 
-\centering
-\includegraphics[scale=0.25]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
-\caption{energy of each particle, $F_0=10$}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
+\caption{energy of each particle, $F_0=1000$}
 \label{fig:thermalization7}
@@
 
-As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=5$ (we always set $\sigma=1$), while the average energy $\sim 10$, as we expected, they are of the same order.
-As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e.
-in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
+As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500$-$F_0=1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
+As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
 To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
@@
 One may think that this condition only means that the energy transfer in every collision is much smaller than the energy interval.
-It seems that these two regime are not so distinct.
-It is necessary to emphasis that the essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer.
+But this is not the whole story.
+The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer.
 What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives.
-It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time!
+It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time.
 In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us.
@@
 
-\newpage
 \subsection{Verifying Boltzmann distribution}
@@
 One of the most important information of initial state is energy distribution.
-We can check whether a system has gone to equilibrium by measuring its energy distribution.
 
-\subsubsection{energy distribution}
 For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
@@
 
-\newpage
-
 To take the first one as an example, Y axis is logarithmically scaled.
@@
 
-In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states.
+In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states (DOS).
 Possibility is proportional to Boltzmann exponential factor multiplied by density of states.
 The reason why we did not take DOS into account previously lies in that the DOS is a constant for simple harmonic oscillator.
-However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
+However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the small region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
 But since $\sigma<<R$, one can think of this as a small modification.
@@
 
-\newpage
 \section{Relaxation in Phase-space}
-To date, we have verified that the energy distribution will go to Boltzmann distribution.
+
+When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
+In the phase-space, the motion becomes circular, so each of these particles has two independent degree of freedom, i.e., modulus and phase angle.
+Here, independent means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
+In view of this, when it comes to ``thermalization", one may notice that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
+To distinguish these two kind of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
+The time scale of thermalization and relaxation could be different in principle.
+We start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is line shape at the beginning.
+If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to isotropic in a short time, and radius distribution slowly evolves to Boltzmann distribution.
+If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or elliptical shape for a long time while the radius distribution is already Boltzmann.
+
+To study the relaxation, it is convenient to go back to the picture introduced in discussing breathing frequency, since in that chapter, we focus on the average effect of collision on precession motion, but now we focus on the fluctuation near this average effect.
+Let's recall two distinct regime discussed in Fig.\ref{fig:Breathingfrequency3}.
+These two regime will show different behaviour of relaxation.
+
+In ``bouncing regime", (see Fig.\ref{fig:Breathingfrequency3}(a))particles' position in phase-space have a finite shift $\sim\sigma$ in one collision.
+As is discussed in former chapter, the average effect of this shift result in precession motion in phase-space and lead to a perturbed breathing frequency.
+This result is based on approximating the mean effect of collision process with the the collision between two particles aligned symmetrically on P axis.
+However, in reality, the particles
+are everywhere so that the shift do not rotate the particles' phase angle by the same amount in every collision, thus the increase of the phase angle of each particle can be thought of as a wide distribution with a non-zero mean value.
+As a result of this distribution, the phase angle soon got thermalized, which means the ``relaxation time" is short.
+
+In `` passing regime", (see Fig.\ref{fig:Breathingfrequency3}(b)),the maximal shift of position in phase-space starts to decrease with the decrease of $F_0$.
+The shift $\delta$ decrease as $\delta\sim F_0^2$.
+This means the particles are localized in their original position when $F_0$ is smaller-- it is natural to get this conclusion, since the weaker the interaction is, the longer time it takes to ``relax".
+
+All our discussion before is based on the approximation that every particle collide with each other once in one period.
+But this is hardly true in reality.
+If the number of collision in every period is taken into account, these two regime looks even more different: In ``bouncing regime", the average precession speed is significant, (see Fig.\ref{fig:Breathingfrequency4}), which means each collision cause a finite precession.
+The fluctuation of the number of collision one particle has in each period will contribute to the divergence of their phase angles.
+On the contrary, in ``passing regime", (see Fig.\ref{fig:Breathingfrequency4}), the breathing frequency is close to 2, which means the average effect of collision create zero precession speed.
+As a result, even though the number of collision is not a constant, it has no effect on average whether one particle collide more or less in one period.
+
+%To date, we have verified that the energy distribution will go to Boltzmann distribution.
 However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state.
@@
 \end{figure}
+\cite{Tsuchiya2000}
+
+\bibliographystyle{plain}
+\bibliography{Interacting Classical Gas_Zhiyu_bib.bib}
 

### 2016-11-01 Interacting Classical Gas_Zhiyu_APS.tex
Nov1 APS's PRE format, tex

@@
  \usepackage{bm}
+   \usepackage[colorlinks,
+            linkcolor=red,
+            anchorcolor=blue,
+            citecolor=green
+            ]{hyperref}
  \begin{document}
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
-\caption{Energy distribution, N=5, F0=10000}
-\label{fig:thermalization8}
+%\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
+%\caption{Energy distribution, N=5, F0=10000}
+%\label{fig:thermalization8}
 
-\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
-\caption{Energy distribution, N=10, E=1000 {\color{red}{Run with N=10 F0=10000 to substitute this one}} }
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=10_F=10000_pre.eps}
+\caption{Energy distribution, N=10, F0=10000}
 \label{fig:thermalization9}
 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=20_F0=10000_pre.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=20_F=10000_pre.eps} 
 \caption{Energy distribution, N=20, F0=10000}
@@
 
-\section{Relaxation in Phase-space}
+\subsection{Relaxation in Phase-space}
 
@@
 On the contrary, in ``passing regime", (see Fig.\ref{fig:Breathingfrequency4}), the breathing frequency is close to 2, which means the average effect of collision create zero precession speed.
-As a result, even though the number of collision is not a constant, it has no effect on average whether one particle collide more or less in one period.
+As a result, even though the number of collision is not a constant, it has on average no effect whether one particle collide more or less in one period.
+
+To directly check this argument, we can inspect the frequency spectrum of $R(t)$.
+As is shown in FIG.\ref{fig:frequencyspectrum}, when $F_0$ is very small (red curve), the peak is very sharp and peak frequency is exactly 2.
+When $F_0$ goes far beyond the threshold value of $\frac{E}{N\sigma}$ (blue, purple, pink, etc.), the peak becomes a wide distribution with a peak value deviated far from 2, which lead to  fast thermalization according to our argument before.
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre.eps}
+\caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
+\end{figure}
+
+\subsection{Lyapunov Exponents}
+To see the time scale of ``thermalization" and ``relaxation" more systemetically, we may measure the Lyapunov Exponents.
+Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
+The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space.
+We will measure the LLEs along our trajectory and plot its distribution.
+
+\begin{comment}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
+\caption{N=5, F0=1000, E=3000, Gaussian interaction}
+\label{fig:LLEexample1}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
+\caption{N=5, F0=1000, E=10000, Gaussian interaction}
+\label{fig:LLEexample2}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
+\caption{N=5, F0=1000, E=100000, Gaussian interaction}
+\label{fig:LLEexample3}
+\end{figure}
+
+Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement.
+\textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}
+\end{comment}
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27_pre_screenshot.png}
+\caption{LLE distribution for N=5, F0=1000, scan E.}
+\label{fig:LLEdistribution1}
+\end{figure}
+
+fig.\ref{fig:LLEdistribution1} shows the distribution of LLE by color.
+The LLE decrease with the growth of Energy.
+The crucial part is near E=5000.
+The most probable value of LLE goes down from 1 to 0.1,which indicate that \textbf{the shortest time scale becomes longer than an oscillation period when E is larger than 5000}.
+And E=5000 is exactly our prediction value of thermalization threshold.
+So there is a correspondence between energy thermalization and LLE.
+The size of bin(resolution of LLE) in fig.\ref{fig:LLEdistribution1} is 0.01, so when E goes far beyond the thermalization threshold, the LLE distribution is not that clear.
+We only know that LLE is concentrated close to zero in high E regime.
 
@@
 
-\subsubsection{Shape of Distribution in Phase-space}
+\subsection{{\color{red}{Shape of Distribution in Phase-space}}}
 If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
@@
 
+\begin{comment}
 \begin{figure}[hbtp]
@@
 \end{figure}
+\end{comment}
 
-\newpage
-\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
+\begin{comment}
+%\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
 \begin{figure}[hbtp]
@@
 \end{figure}
+\end{comment}
 
 \newpage
-\subsection{Lyapunov Exponents(unfinished)}
-Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
-The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space.
-We will measure the LLEs along our trajectory and plot its distribution.
 
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
-\caption{N=5, F0=1000, E=3000, Gaussian interaction}
-\label{fig:LLEexample1}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
-\caption{N=5, F0=1000, E=10000, Gaussian interaction}
-\label{fig:LLEexample2}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
-\caption{N=5, F0=1000, E=100000, Gaussian interaction}
-\label{fig:LLEexample3}
-\end{figure}
-
-Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement.
-\textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27.eps}
-\caption{LLE distribution for N=5, F0=1000, scan E.
-(It seems that MATLAB has difficulty changing .fig into .eps files.
-To get rid of the annoying white lines you may open this figure in MATLAB with .fig format.)}
-\label{fig:LLEdistribution1}
-\end{figure}
-
-fig.\ref{fig:LLEdistribution1} shows the distribution of LLE by color.
-The LLE decrease with the growth of Energy.
-The crucial part is near E=5000.
-The most probable value of LLE goes down from 1 to 0.1,which indicate that \textbf{the shortest time scale becomes longer than an oscillation period when E is larger than 5000}.
-And E=5000 is exactly our prediction value of thermalization threshold.
-So there is a correspondence between energy thermalization and LLE.
-The size of bin(resolution of LLE) in fig.\ref{fig:LLEdistribution1} is 0.01, so when E goes far beyond the thermalization threshold, the LLE distribution is not that clear.
-We only know that LLE is concentrated close to zero in high E regime.
+\section{Conclusion}
 
@@
 
-\bibliographystyle{plain}
-\bibliography{Interacting Classical Gas_Zhiyu_bib.bib}
+\newpage
+\renewcommand\refname{Reference}
+%\bibliographystyle{plain}
+\bibliography{E:/Reference/mybib}
 

### 2016-11-29 Interacting Classical Gas_Zhiyu_APS.tex
Nov29 APS's PRE format, tex

@@
  \begin{document}
- \title{Interacting Classical Gas}
+ \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
  \author{Zhiyu}
@@
 \section{Introduction}
+In cold atom experiment, when BEC happens, atoms condense into their groud state.
+If one suddenly modify the trap potential or interaction parameter, which is just a ``quench", then the low lying collective modes will be excited.
+One of the most consipicuous collective phenomenon is the breathing mode.
+Breathing mode, also called as monopole mode, is periodic expanding and contracting behaviour of the cloud of atoms.
+The frequency of breathing mode is widely discussed in literature.
+When the atoms have interaction, it is observed that the frequncy is dependent on the interaction.
+xxx used mean-field technique to calculate the relation between breathing frequency and interaction[ ].
+While xxx numerically calculated the frequency[ ]...
+BEC is a quantum gas, so the existing literature on breathing modes all focus on quantum gas.
+But the quantum property is not necessary to the breathing mode phenomenon, though the question of breathing mode generate from BEC.
+For classical gas, there is also such breathing behaviour.
+So a natural question would be asked is, how do the breathing frequency of classical gas dependent on interaction or other parameters.
+Surprisingly, to the best of our knowledge this question is not answered yet in the literature and thus need study.
+
+Moreover, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
+Thermalization is among the most fundamental process for a many-body interacting system.
+All systems do not thermalize.
+An example is the Fermi–Pasta–Ulam paradox [ ] where shows confinement in phase-space so that the system stay non-thermalized for a long time.
+A lot of research on thermalization property has been done in other classical system.
+H De Raedt, et al.
+studied the one dimensional gravitational system with Lyapunov exponents[ ].
+xxx studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem[ ].
+
+In this paper, we answer these two questions.
+In the first part, we give an estimation of breathing, along with its explanation, and compare that with the numerical simulation result.
+We will also show a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems.
+In the second part, we study the thermalization property.
+We first examine the canonical disribution of energy to find out the threshold of thermalization, i.e.
+under what parameter the thermalization time scale is very large.
+Then we point out that there are two kind of thermalization (or relaxation) behaviour that could be measured in this system.
+In the end we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
 
@@
 Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
+But for high dimensional system, LE is a sorectrum that manifest the instability of the trajectory along each direction.
 The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space.
@@
 
-\newpage
+\section{Conclusion}
+We studied the nonequilibrium property of one-dimensional classical gas with finite range repulsive interaction.
+We first studied the relation between breathing mode frequency and interaction parameter as well as total energy.
+We found the breathing frequency could be estimated by \ref{eq:breathingfrequency1}.
+And the mechanism behind this relation is that the momentum transfer which happens instantly in collision saves the particles some time from traveling this distance.
+So the physics is completely the same as hardcore particle.
+We found that the thermalization behaviour is controled by th competition between the interaction strength and the average energy.
+We point out that there could be two independent time scales in simple harmonic system in principle.
+One of them corresponds to the relaxtation time of the energy distribution.
+The other one corresponds to the relaxation time of the angular distribution in phase space, which will determine the decay rate of the amplitude of the breathing mode.
+However, with the form of interaction we used, i.e.
+finite range constant repusive force, we found those two time scales diverge only when interaction vanish, which is a trivial singular point.
+In addition, the relaxation behaviour of the angular distribution and radial distrbution in phase space are similiar.
+We attribute it to the fact that there is no essential bias between angular and radial transfer in phase-space for this simple form of interaction.
+The longest time scale is verified numerically by largest lyapunov exponent.
+A further question could be asked is whether there is a subtle form of interaction that could give those two time scales essentially different behaviour.
+The observation of two different time scales in one system would be interesting.
 
-\section{Conclusion}
-
+\begin{comment}
 \section{others(those I haven't organized it into the text in logical order but may be useful)}
@@
 \end{figure}
-\cite{Tsuchiya2000}
+\end{comment}
 

### 2016-12-11 Zhiyu.tex
Dec11 PRE format, tex

--- 2016-11-29 Interacting Classical Gas_Zhiyu_APS.tex
@@
-\documentclass[aps,pre,twocolumn
-,groupedaddress]{revtex4-1}
+\documentclass[aps,pre,twocolumn,groupedaddress]{revtex4-1}
 %\documentclass[a4paper,onecolumn,12pt]{article}
+%\documentclass[reprint, amsmath,amssymb,aps,]{revtex4-1}
+
+\bibliographystyle{apsrev4-1}
 \usepackage{amsmath}
@@
  \usepackage{color}
+ \usepackage{xcolor}
  \usepackage{bm}
-   \usepackage[colorlinks,
-            linkcolor=red,
-            anchorcolor=blue,
-            citecolor=green
-            ]{hyperref}
+ \usepackage{hyperref}
+\hypersetup{
+    colorlinks = false,
+    linkbordercolor = {red},
+    citebordercolor = {green},
+}
  \begin{document}
@@
 \section{Introduction}
-In cold atom experiment, when BEC happens, atoms condense into their groud state.
-If one suddenly modify the trap potential or interaction parameter, which is just a ``quench", then the low lying collective modes will be excited.
-One of the most consipicuous collective phenomenon is the breathing mode.
-Breathing mode, also called as monopole mode, is periodic expanding and contracting behaviour of the cloud of atoms.
-The frequency of breathing mode is widely discussed in literature.
-When the atoms have interaction, it is observed that the frequncy is dependent on the interaction.
-xxx used mean-field technique to calculate the relation between breathing frequency and interaction[ ].
-While xxx numerically calculated the frequency[ ]...
-BEC is a quantum gas, so the existing literature on breathing modes all focus on quantum gas.
-But the quantum property is not necessary to the breathing mode phenomenon, though the question of breathing mode generate from BEC.
-For classical gas, there is also such breathing behaviour.
-So a natural question would be asked is, how do the breathing frequency of classical gas dependent on interaction or other parameters.
-Surprisingly, to the best of our knowledge this question is not answered yet in the literature and thus need study.
+Controlled and tunable experimental realizations of confined quantum systems with ultracold atoms enable nonequilibrium studies of quantum many-body states in novel geometries.
+A common feature of many cold-atom experiments is the confinement of a many-body system in a harmonic trap.
+Trapping introduces many distinctive features which have no analog in uniform many-body states, including collective excitations such as breathing modes, dipole modes, and scissors modes.
+Such trap-related collective modes have been widely studied both experimentally and theoretically for continuum systems, especially in the mean-field regime, since the early days after quantum degeneracy was achieved with trapped atoms \cite{Dalfovo1997}\cite{Jin1996}.
 
-Moreover, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
+In mean-field perspective, the physics of atom gas in Bose-Einstein Condensation can be described by the Gross-Pitaevskii equation\cite{Dalfovo1999}\cite{Stringari1996}, where the breathing frequency for 1D Bose gas is calculated to be $\Omega_{GP}=\sqrt{3}\omega_0$.
+Meanwhile, the experiment of Ref.\cite{Haller2009} has found a regime of interactions where the breathing-mode frequency approaches the Gross-Pitaevskii prediction.
+However, since mean-field approach which generally omit quantum fluctuation is successful in this problem, one may wonder how quantum effect plays the role in the breathing mode.
+Thus, a natural question would be asked is how breathing frequency is dependent on interaction for classical gas.
+Though generated in BEC, the breathing mode phenomenon is not restricted to BEC.
+For a classical gas, the breathing mode still can be excited with a quench.
+A good knowledge of classical version may help us understand the quantum question better.
+Surprisingly,  to the best of our knowledge, all the literature focus on the breathing mode in BEC, without a careful study of their classical counterpart, which actually seems easier.
+Since this classical version question has not been answered yet, more study is needed.
+
+One the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
 Thermalization is among the most fundamental process for a many-body interacting system.
 All systems do not thermalize.
-An example is the Fermi–Pasta–Ulam paradox [ ] where shows confinement in phase-space so that the system stay non-thermalized for a long time.
+An example is the Fermi-Pasta-Ulam paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a long time.
 A lot of research on thermalization property has been done in other classical system.
-H De Raedt, et al.
-studied the one dimensional gravitational system with Lyapunov exponents[ ].
-xxx studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem[ ].
+Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with Lyapunov exponents.
+Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem .
+In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as wel as Lyapunov exponent.
+Wiht these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behaviour in the thermalization time scales except the trivial divergence at zero interaction.
 
-In this paper, we answer these two questions.
-In the first part, we give an estimation of breathing, along with its explanation, and compare that with the numerical simulation result.
-We will also show a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems.
-In the second part, we study the thermalization property.
+This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the parameter of the system.
+In addition, we briefly observe the ground state and reveal two dynamically distinct regime of the system, i.e.
+strong interaction regime and weak interaction regime.
+In Section \ref{section:breathing frequency}, we evaluate the breathing frequency according to its mechanism, and compare that with our numerical simulation result.
+Besides, we also introduce a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems.
+In section \ref{section:Thermalization}, we focus on the thermalization property.
 We first examine the canonical disribution of energy to find out the threshold of thermalization, i.e.
@@
 Then we point out that there are two kind of thermalization (or relaxation) behaviour that could be measured in this system.
-In the end we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
+In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
 
-\section{Preparation}
+\section{Preparation}\label{section:preparation}
 \subsection{Scaling behaviour}
@@
 \begin{aligned}
-&F=F0 	&,x\textless\sigma\\
+&F=F_0 	&,x\textless\sigma\\
 &F=0 	&,x\textgreater\sigma
@@
 
-\section{Breathing Frequency}
+\section{Breathing Frequency}\label{section:breathing frequency}
 Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
@@
 
-\section{Thermalization}
+\section{Thermalization}\label{section:Thermalization}
 \subsection{Dynamics Study}
@@
 
-\newpage
 \begin{figure}[hbtp]
@@
 \end{comment}
-
-\newpage
-\renewcommand\refname{Reference}
-%\bibliographystyle{plain}
-\bibliography{E:/Reference/mybib}
+\cite{Dalfovo1997}
+\cite{Tschischik2013}
+\cite{Tschischik2015}
+\cite{Guery-Odelin1999}
+\cite{Yawn1997}
+\cite{El-Zant1998}
+\cite{Jin1996}
+\cite{Tsuchiya2000}
+\bibliography{mybib}
 

### 2017-01-10 Zhiyu.tex
Jan10 PRE format, tex

@@
 Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$
-
-\begin{comment}
-\begin{figure}
-\centering
-\includegraphics[scale=0.3]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
--\caption{E-R} This picture shows $E=kR^2$ when energy is large. ($k=N\omega_0^2$)
-\end{figure}
-\end{comment}
 
@@
 \centering
-\includegraphics[scale=0.2]{C:/Users/admin/Desktop/test.png}
+\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/effective_potential.png}
 \caption{effective potential for two-particle system}

### 2017-01-11 Zhiyu.tex
Jan11 PRE format, tex

@@
  \usepackage{bm}
- \usepackage{hyperref}
+ \usepackage[]{hyperref}
 \hypersetup{
@@
 \end{equation}
-It can be shown that eq.\ref{eq:preparation2} can be rewrite into the following form:
+It can be shown that Eq.\ref{eq:preparation2} can be rewrite into the following form:
 \begin{equation}
@@
 \subsubsection{Relation between Radius and Energy}
-The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$.
+The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$
+\begin{equation}
+R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2}
+\label{eq:def_of_R}
+\end{equation}.
 When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators.
@@
 \subsubsection{Ground states}
-For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small $\mathbf{F_0}$ limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$.
-The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{$\mathbf{F_0}$ is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
+For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$.
+The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
 
@@
 \centering
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2.eps}
+\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2_rev.eps}
 \caption{particles' position at ground states }
@@
 \center
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2.eps}
-\caption{breathing mode frequency measured at different E and $F_0$}
+\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
+\caption{breathing mode frequency measured at different E and $F_0$.
+Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation of radius R defined in Eq.\ref{eq:def_of_R}}
 \label{fig:Breathingfrequency1}
@@
 
-Fig.\ref{fig:Breathingfrequency2} and Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
-\caption{precession motion in phase-space observed in rotating frame (only show one(two) particles' trajectory in upper(lower) picture for clarity)}
-\label{fig:Breathingfrequency2}
-\end{figure}
+Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
 
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T.eps}
+\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T_rev.eps} 
+\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T.eps}
+\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T_rev.eps} 
+\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T.eps}
+\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T_rev.eps} 
+\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T.eps}
+\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T_rev.eps} 
+\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T.eps}
+\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T_rev.eps} 
+\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T_rev.eps}
 \end{minipage}
 }
-\caption{N=50,F0=100,E=50000}
+\caption{N=50,F0=100,E=50000.
+Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=10T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=30T.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=50T.eps} 
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=70T.eps}
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=90T.eps} 
+\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=0T_rev.eps} 
+\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=20T_rev.eps}
+\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=40T_rev.eps} 
+\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=60T_rev.eps}
+\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=80T_rev.eps} 
 \caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
@@
 \end{figure*}
-
-\begin{figure}
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_19trajectory_in_rotating_frame_t=130T_pre.eps}
-\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space, one snapshot in each 10 periods.}
-\label{fig:Breathingfrequency2_2}
-\end{figure}
 
@@
 Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
-The black dashed line is the prediction of eq.\ref{eq:breathingfrequency1}.}
+The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
 \label{fig:Breathingfrequency4}
@@
 The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}.
-For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction eq.\ref{eq:breathingfrequency1}.
+For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}.
 Secondly, the figure shows the frequency's dependence on $F_0$.
@@
 %\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre.eps} 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre.eps} 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev.eps}
 \caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold".
-In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in eq.\ref{eq:thermalizatiton condition}}
+In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
 \label{fig:thermalization5}
@@
 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=10_F=10000_pre.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=10_F=10000_pre_rev.eps}
 \caption{Energy distribution, N=10, F0=10000}
@@
 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=20_F=10000_pre.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=20_F=10000_pre_rev.eps} 
 \caption{Energy distribution, N=20, F0=10000}
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre_rev.eps}
 \caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
@@
 \centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27_pre_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_1_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_2_screenshot.png}
 \caption{LLE distribution for N=5, F0=1000, scan E.}
 \label{fig:LLEdistribution1}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
+\caption{``hot". top(bottom): default(modified)}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula1_screenshot.png}
+\caption{``parula". top(bottom): default(modified)}
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
+\caption{``bone". top(bottom): default(modified)}
 \end{figure}
@@
 \end{comment}
-\cite{Dalfovo1997}
-\cite{Tschischik2013}
-\cite{Tschischik2015}
-\cite{Guery-Odelin1999}
-\cite{Yawn1997}
-\cite{El-Zant1998}
-\cite{Jin1996}
-\cite{Tsuchiya2000}
+
 \bibliography{mybib}

### 2017-01-12 Zhiyu.tex
Jan12 PRE format, tex

@@
 \caption{breathing mode frequency measured at different E and $F_0$.
-Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation of radius R defined in Eq.\ref{eq:def_of_R}}
+Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behaviour of radius R(t) defined in Eq.\ref{eq:def_of_R}.
+The breathing frequency is measured by taking Fourier transformation of R(t).}
 \label{fig:Breathingfrequency1}
@@
 \centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_1_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_2_screenshot.png}
-\caption{LLE distribution for N=5, F0=1000, scan E.}
-\label{fig:LLEdistribution1}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot2_screenshot.png}
+\caption{LLE distribution for N=5, F0=1000, scan E.``hot". top(bottom):modified(reversed)}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
-\caption{``hot". top(bottom): default(modified)}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula1_screenshot.png}
-\caption{``parula". top(bottom): default(modified)}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone_screenshot.png}
 \includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
-\caption{``bone". top(bottom): default(modified)}
+\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone2_screenshot.png}
+\caption{``bone". top(bottom):modified(reversed)}
 \end{figure}

### 2017-01-12 Zhiyu.tex
Jan12 PRE format, tex

@@
 
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev1.eps} 
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev1.eps}
+\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev1.eps}
+\caption{test}
+\end{figure}
+
 \begin{figure}

### 2017-01-19 Zhiyu.tex
Jan19 PRE format, tex

--- 2017-01-12 Zhiyu.tex
@@
 Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem .
-In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as wel as Lyapunov exponent.
-Wiht these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behaviour in the thermalization time scales except the trivial divergence at zero interaction.
+In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as well as Lyapunov exponent.
+With these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behavior in the thermalization time scales except the trivial divergence at zero interaction.
 
@@
 In section \ref{section:Thermalization}, we focus on the thermalization property.
-We first examine the canonical disribution of energy to find out the threshold of thermalization, i.e.
+We first examine the canonical distribution of energy to find out the threshold of thermalization, i.e.
 under what parameter the thermalization time scale is very large.
-Then we point out that there are two kind of thermalization (or relaxation) behaviour that could be measured in this system.
+Then we point out that there are two kind of thermalization (or relaxation) behavior that could be measured in this system.
 In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
@@
 \subsubsection{Ground states}
-For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$.
+For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbors, which is $\frac{2F_0}{\omega_0^2}$.
 The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
@@
 \centering
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2_rev.eps}
+\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
 \caption{particles' position at ground states }
@@
 So it is not necessary to focus on low lying excitations in classical case.
-Besides, since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $\bar{h}/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one.
+Besides, since classical limit is $\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one.
 Secondly, it is no longer necessary to vary parameters ``by a little" in the quench.
 In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}).
-But in classical case, since $\bar{h}$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case.
+But in classical case, since $\hbar$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case.
 Thus it is not necessary to limit ourselves to small quench.
@@
 \center
-\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
+\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
 \caption{breathing mode frequency measured at different E and $F_0$.
-Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behaviour of radius R(t) defined in Eq.\ref{eq:def_of_R}.
+Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behavior of radius R(t) defined in Eq.\ref{eq:def_of_R}.
 The breathing frequency is measured by taking Fourier transformation of R(t).}
@@
 When there is interaction, the frequency will drift to some other value near 2.
-We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behaviour by Fourier transform.
+We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behavior by Fourier transform.
 Then we take the peak frequency near 2 as the breathing mode frequency.
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T_rev.eps} 
-\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T_rev.eps}
+\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
+\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T_rev.eps} 
-\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T_rev.eps}
+\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=2-5T_rev.eps} 
+\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T_rev.eps} 
-\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T_rev.eps}
+\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
+\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T_rev.eps} 
-\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T_rev.eps}
+\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
+\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T_rev.eps} 
-\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T_rev.eps}
+\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
+\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
 \end{minipage}
@@
 \begin{figure*}
-\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=0T_rev.eps} 
-\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=20T_rev.eps}
-\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=40T_rev.eps} 
-\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=60T_rev.eps}
-\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=80T_rev.eps} 
-\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
+\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
+\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
+\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
+\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
+\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps} 
+\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
 \label{fig:Breathingfrequency2_1}
@@
 \centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/bounce.png}
-\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/pass.png}
+\includegraphics[scale=0.3]{ZhiyuPictures/bounce.png}
+\includegraphics[scale=0.32]{ZhiyuPictures/pass.png}
 \caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.
@@
 
-When $F_0$ is not that large, the frequency behaviour seems complicated (see fig.\ref{fig:Breathingfrequency1}).
+When $F_0$ is not that large, the frequency behavior seems complicated (see fig.\ref{fig:Breathingfrequency1}).
 Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
@@
 For $F_0$ is not very big, the finite interaction time should be taken into consideration.
-During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
+During this time, the behavior of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
 Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
@@
 \centering
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_scanE_pre.eps}
+\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre.eps}
 \caption{dependence of breathing frequency on Energy, N=20.
@@
 The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}.
-For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}.
+For the first thing, as expected when $F_0$ is high the frequency behavior is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}.
 Secondly, the figure shows the frequency's dependence on $F_0$.
@@
 \centering
-\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/effective_potential.png}
+\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
 \caption{effective potential for two-particle system}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
-%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
+\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
-%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
+\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
-%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
+\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
 \end{minipage}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
-%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
+\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
+%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
 \end{minipage}
@@
 C gives A a push when approaching it, and then push A back when leaving.
-As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\frac{\sigma}{R})$) in the background of a trap.
+As has been discussed in the two-particle case, this process is equivalent to giving A a very small velocity ($\sim O(\frac{\sigma}{R})$) in the background of a trap.
 Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$).
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1_pre.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
 \caption{evolution of single-particle energy}
@@
 \centering
-%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
+%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
 %\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev.eps} 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev.eps} 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/N=5_energydistribution_pre_rev1.eps} 
+\includegraphics[scale=0.5]{ZhiyuPictures/N=10_energydistribution_pre_rev1.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/N=20_energydistribution_pre_rev1.eps}
 \caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold".
@@
 \begin{figure}
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
+\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
 \caption{energy of each particle, $F_0=200$}
@@
 
-\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
+\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
 \caption{energy of each particle, $F_0=1000$}
@@
 But this is not the whole story.
-The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer.
+The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitely slows down the energy transfer.
 What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives.
@@
 
-But intuitively, one will expect that if we measure the energy of a subsystem , e.g.
+But intuitively, one will expect that if we measure the energy of a subsystem, e.g.
 one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle.
@@
 \centering
-%\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
+%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
 %\caption{Energy distribution, N=5, F0=10000}
@@
 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=10_F=10000_pre_rev.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
 \caption{Energy distribution, N=10, F0=10000}
@@
 
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=20_F=10000_pre_rev.eps} 
+\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
 \caption{Energy distribution, N=20, F0=10000}
@@
 Let's recall two distinct regime discussed in Fig.\ref{fig:Breathingfrequency3}.
-These two regime will show different behaviour of relaxation.
+These two regime will show different behavior of relaxation.
 
@@
 As is discussed in former chapter, the average effect of this shift result in precession motion in phase-space and lead to a perturbed breathing frequency.
-This result is based on approximating the mean effect of collision process with the the collision between two particles aligned symmetrically on P axis.
+This result is based on approximating the mean effect of collision process with the collision between two particles aligned symmetrically on P axis.
 However, in reality, the particles
@@
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre_rev.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/freq_spectrum_N=10_E=1000_pre_rev.eps}
 \caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
@@
 \subsection{Lyapunov Exponents}
-To see the time scale of ``thermalization" and ``relaxation" more systemetically, we may measure the Lyapunov Exponents.
-Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
-But for high dimensional system, LE is a sorectrum that manifest the instability of the trajectory along each direction.
+To see the time scale of ``thermalization" and ``relaxation" more systematically, we may measure the Lyapunov Exponents.
+Lyapunov Exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
+But for high dimensional system, LE is a spectrum that manifest the instability of the trajectory along each direction.
 The largest Lyapunov exponents (LLE) reflects the time scale that system lose its memory in phase-space.
@@
 
-\begin{comment}
 \begin{figure}[hbtp]
 \centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
-\caption{N=5, F0=1000, E=3000, Gaussian interaction}
-\label{fig:LLEexample1}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
-\caption{N=5, F0=1000, E=10000, Gaussian interaction}
-\label{fig:LLEexample2}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
-\caption{N=5, F0=1000, E=100000, Gaussian interaction}
-\label{fig:LLEexample3}
+%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
+\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
+\caption{LLE distribution for N=5, F0=1000, scan E.``hot"(reversed)}\label{fig:LLEdistribution1}
 \end{figure}
 
-Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement.
-\textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}
-\end{comment}
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot2_screenshot.png}
-\caption{LLE distribution for N=5, F0=1000, scan E.``hot". top(bottom):modified(reversed)}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone2_screenshot.png}
-\caption{``bone". top(bottom):modified(reversed)}
-\end{figure}
+%\begin{figure}[hbtp]
+%\centering
+%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
+%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
+%\caption{``bone". top(bottom):modified(reversed)}
+%\end{figure}
 
@@
 
+\subsection{{\color{red}{Shape of Distribution in Phase-space}}}
 %To date, we have verified that the energy distribution will go to Boltzmann distribution.
@@
 There is other information that could still exist, for instance, the shape of distribution cloud in phase-space.
-One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour.
+One of the reasons why we care about this quantity is that it has a strong effect on breathing behavior.
 For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large.
@@
 
-\subsection{{\color{red}{Shape of Distribution in Phase-space}}}
 If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
@@
 
-\begin{comment}
-\begin{figure}[hbtp]
-
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
-\caption{N=5,F0=10000,E=1000, initial S=1}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
-\caption{Zoom in at the beginning part}
-\end{figure}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
-\caption{average over every 30s to see the main tendency}
-\label{fig:relaxationPS1}
-\end{figure}
-
-From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge.
-Maybe the fluctuation of S is so large that make it hard to identify the convergence of S.
-The only way to solve this problem is using more particle simulation to suppress the fluctuation.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
-\caption{N=20, F0=1000, E=3000, initial S=1}
-\begin{flushleft}
-Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
-\end{flushleft}
-\label{fig:relaxationPS2}
-\end{figure}
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
-\caption{N=20, F0=1000, E=10000, initial S=1}
-\label{fig:relaxationPS3}
-\end{figure}
-
-For N=20(fig.\ref{fig:relaxationPS3}), the S start evolving from 1 will soon decay and start fluctuating around some lower value(0.1-0.5, perhaps dependent on temperature).
-To tell whether this value correspond to a stable state of the system, we can set the initial state S to be other value (e.g.
-zero) to see whether it will come back to the same stable value(see fig.\ref{fig:relaxationPS4}).
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
-\caption{N=20, F0=1000, E=10000, Initial S=0.05}
-\label{fig:relaxationPS4}
-\end{figure}
-
-We may zoom in to understand how the distribution cloud is deforming. 
-in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips.
-The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis.
-Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back.
-So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
-\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
-\label{fig:relaxationPS5}
-\end{figure}
-
-In view of this, we take average of a short time to clear this peaks and dips in order to see the time evolution of the overall value of S (the second picture in fig.\ref{fig:relaxationPS2},\ref{fig:relaxationPS3},\ref{fig:relaxationPS4}).
-
-However, there is still no sufficient evidence of convergence for the overall value of S for N=20. 
-\begin{figure}[hbtp]
-
-\centering
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
-\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
-\caption{N=50, E=20000, F0=10000 ,t=1500}
-\label{fig:relaxationPS6}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-%\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
-\begin{figure}[hbtp]
-\begin{center}
-\subfigure[$E=3E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=2E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=1E5$]{
-\begin{minipage}[n]{0.4\textwidth}
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
-\end{minipage}
-}
-\subfigure[$E=5E4$]{
-\begin{minipage}[n]{0.4\textwidth}
-
-\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
-\end{minipage}
-}
-\end{center}
-\end{figure}
-\end{comment}
-
 \section{Conclusion}
@@
 So the physics is completely the same as hardcore particle.
-We found that the thermalization behaviour is controled by th competition between the interaction strength and the average energy.
+We found that the thermalization behavior is controlled by the competition between the interaction strength and the average energy.
 We point out that there could be two independent time scales in simple harmonic system in principle.
-One of them corresponds to the relaxtation time of the energy distribution.
+One of them corresponds to the relaxation time of the energy distribution.
 The other one corresponds to the relaxation time of the angular distribution in phase space, which will determine the decay rate of the amplitude of the breathing mode.
 However, with the form of interaction we used, i.e.
-finite range constant repusive force, we found those two time scales diverge only when interaction vanish, which is a trivial singular point.
-In addition, the relaxation behaviour of the angular distribution and radial distrbution in phase space are similiar.
+finite range constant repulsive force, we found those two time scales diverge only when interaction vanish, which is a trivial singular point.
+In addition, the relaxation behavior of the angular distribution and radial distribution in phase space are similar.
 We attribute it to the fact that there is no essential bias between angular and radial transfer in phase-space for this simple form of interaction.
-The longest time scale is verified numerically by largest lyapunov exponent.
-A further question could be asked is whether there is a subtle form of interaction that could give those two time scales essentially different behaviour.
+The longest time scale is verified numerically by Largest Lyapunov Exponent.
+A further question could be asked is whether there is a subtle form of interaction that could give those two time scales essentially different behavior.
 The observation of two different time scales in one system would be interesting.
@@
 We label the position of center of mass as 0.
-And we may only analyse the motion on positive axis since positive and negative are symmetric.
+And we may only analyze the motion on positive axis since positive and negative are symmetric.
 
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
+\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
 \end{minipage}
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
+\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
 \end{minipage}
@@
 \begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
+\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
 \end{minipage}

### 2017-01-20 Zhiyu.tex
Jan20 PRE format, tex

@@
 If the phase of oscillation is completely random, the cloud should be isotropic in phase space.
-In view of this, we defined a shape factor S:
+In view of this, we defined a shape polarization S:
 \\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively.
-a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
+a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$.
 S=1 for line-shape distribution, S=0 for circular distribution.
 The time evolution of S will probably show how fast the distribution ``forget" its initial shape.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000.eps}
+\caption{N=20, F=1000, E=3000(top), E=20000(middle), E=100000(bottom). All start with initial states S=1. \label{fig:shape}}
+\end{figure}
+
+The time evolution of shape polarization S is shown in Fig.\ref{fig:shape}, when E is much lower than the thermalizaion threshold, S decreases to 0.3 in almost no time.
+On the contrary, when E is much higher than the threshold value, it takes a long time for S to dacay.
 

### 2017-01-26 Zhiyu.tex
Jan20 PRE format, tex
Jan21 PRE format, tex
Jan26 PRE format, tex

--- 2017-01-19 Zhiyu.tex
@@
 
+\begin{comment}
 \subsection{Relaxation in Phase-space}
@@
 
+\end{comment}
+
 \subsection{Lyapunov Exponents}
@@
 Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).
+When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
+In the phase-space, the motion becomes circular, so each of these particles has two independent degree of freedom, i.e., modulus and phase angle.
+Here, independent means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
+In view of this, when it comes to ``thermalization", one may notice that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
+To distinguish these two kind of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
+The time scale of thermalization and relaxation could be different in principle.
+We start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning.
+If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to some stable shape in a short time, e.g.
+a circle in high energy.
+Meanwhile, the distribution of particle number  along radius slowly evolves to Boltzmann distribution.
+If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or some oscillation between different shapes for a long time while the radius distribution is already Boltzmann.
 
-If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse.
-If the phase of oscillation is completely random, the cloud should be isotropic in phase space.
-In view of this, we defined a shape factor S:
-\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively.
-a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
+To quantify the shape of distribution in phase-space, we defined a shape polarization S:
+\begin{equation}
+S=\frac{a-b}{a+b}
+\end{equation}
+where a and b are long axis and short axis of inertia ellipse in phase space respectively.
+a,b can be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2}, I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.
 S=1 for line-shape distribution, S=0 for circular distribution.
-The time evolution of S will probably show how fast the distribution ``forget" its initial shape.
+The advantage of defining the S lies in that S is independent of all rotating behavior of the cloud in phase-space and thus extract the information of shape alone.
+One could also use eigenvalues of quadrupole moment Q to define S, since the inertia tensor I is similar to quadrupole moment Q (only different up to a factor and an identity matrix).
+
+%First, let's see the overall value of S in Fig.\ref{fig:shape}.
+In Fig.\ref{fig:shape}, each data point is the average of S over several periods to show the overall value of S.
+If the shape relax to equilibrium, the overall value should decrease to zero.
+At first sight, it seems S does relax, and the conclusion looks similar to the one we got from Boltzmann distribution--When energy is lower than thermalizing threshold(top pannel), S relax in almost no time; when energy is higher than thermalizing threshold(bottom pannel), it takes a relativly long time for S to relax.
+The reason why S never decay to zero could be explained as the contribution of random fluctuation, since S is defined to be positive.
+
+%However, it is not the whole story.
+If we inspect the original data or smoothen it by taking a finer average, e.g.
+average over 0.2 time units (Fig.\ref), we will see the ''sinusoidal"  oscillation of S (S is defined to be positive) with a period of about $2\pi$ time units.
+So the whole picture is that the shape of the cloud is oscillating: \\elliptical with long axis lying along x axis $\rightarrow$ circular $\rightarrow$ elliptical with long axis lying along y axis $\rightarrow$ circular ...
+
+%If we think of the cloud as 2D cloud in x-p space, we have 2D monopole, dipole and quadrupole mode.
+In our system, since energy conserves, $x^2+p^2$ is a constant interaction energy is neglected), the monopole mode do not exist.
+And dipole mode describes the center of mass of the cloud oscillate along x or p, but since we set center of mass to be stationary and at x=0, neither does this mode exist.
+The lowest order mode is quadrupole mode.
+
+The time evolution of S is shown in Fig.\ref{fig:time_evolution_of_S}.
+The top three pannels are the overall value of S, where every data point is the average value of original data over several period (about $2\pi$ time unit).
+The lower six pannels are the original data measured in the beginning and after thousands of time units, which shows the finer structure in one period.
+
+\begin{figure*}
+\subfigure[$N=20, F_0=1000, E=3000$]{
+\begin{minipage}[b]{0.3\linewidth}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_2_crude_begin.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_2_crude_end.eps}
+\end{minipage}
+}
+\subfigure[$N=20, F_0=1000, E=20000$]{
+\begin{minipage}[b]{0.3\linewidth}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_1.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_2_crude_begin.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_2_crude_end.eps}
+\end{minipage}
+}
+\subfigure[$N=20, F_0=1000, E=100000$]{
+\begin{minipage}[b]{0.3\linewidth}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_1.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_2_crude_begin.eps}
+\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_2_crude_end.eps}
+\end{minipage}
+}
+\caption{Time evolution of S in low-enrgy regime(a), intermidiate(b), high-energy regime(c).
+The overall value (top three pannels), where every point represent the average of original data over several periods, show that S decays to a low value in a short time in low-energy case, but persist for a relative long time in high-energy case.
+The snapshots of original data at beginning and after thousands of periods evolution are shown in the lower six pannels.
+The finer structure of S(t) indicates that there is some long-lasting oscillating mode.
+Especially in low-energy case, the amplitude is more conspicuous.}\label{fig:time_evolution_of_S}
+\end{figure*}
+
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1.eps}
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000.eps}
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000.eps}
+%\caption{N=20, F=1000, E=3000(top), E=20000(middle), E=100000(bottom).
+All start with initial states S=1.
+Five different curves in each picture represent simulating with 5 random initial states in each case.
+\label{fig:shape}}
+%\end{figure}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_original1.eps}
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_original2.eps}
+%\caption{N=20, F=1000, E=3000. Original data}
+%\end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1_fine1.eps}
+%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1_fine2.eps}
+%\caption{N=20, F=1000, E=3000. Start with initial states S=1. Smoothened (every point represents taking the average of S in 0.2 time unit)}
+%\end{figure*}
+
+The original data can be decomposed into two components: the background value and the frequent fluctuation(sharp peaks and dips) on the background.
+The fluctuation is generated from the two-particle transportation process(See Fig.\ref{fig:Breathingfrequency3}), e.g.
+a pair transportation event along the long-axis of the cloud makes a dip.
+In the thermalized regime (Fig.\ref{fig:time_evolution_of_S}), the background value of S is oscillating with an amplitude of 0.2-0.4 and does not decay to zero over 4000 time unit.
+In the high-energy case, the amplitude of background oscillation is small compared with fluctuation.
+We assume that over a long enough time, all macroscopic quantity should be constant because the randomness has wash out all possible orders to make entropy as large as possible.
+Since we see a periodical behaviour of S, we know the whole system doesn't relax to its equilibrium state.
+
+The oscillating background value of S indicate that the shape of the cloud in phase space is deformed periodically between a circle and an ellipse($S=0.4$ means $\frac{a}{b}\sim 2.5$).
+To further reveal the nature of this oscillating mode, we focus on the low-energy case and plot the distribution of the cloud in the phase space as Fig.\ref{fig:N=50_F=1000_E=30000_movie}.
+The time interval between each pannels is $0.1*2\pi$ time units.
+The direction of the yellow arrows and red arrows are the eigenvector of inertia tensor, while their lengths are the square root of correspondent eigenvalue (I take the squareroot to maintain the length unit).
+In most of the pannels in Fig.\ref{fig:N=50_F=1000_E=30000_movie}, the long and short axis are rotating and extending or contracting continuosly.
+The exception is the 3rd and 4th pannel in the first row, 2nd and 3rd pannel in the second row, 1st and 2nd pannel in the third row.
+At those moment, the long and short axis are almost equal, giving the system a chance to choose a new preferred axis to polarize.
+The whole picture of this collective mode can be described by Fig.\ref{fig:Schemetic_description_of_the_mode}, which is consistant with the pattern of time evolution of S shown in Fig.\ref{fig:N=50_F=1000_E=30000_Send}.
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s.eps}
+\caption{Distribution in phase-space after evolving for about 500 time units ($N=50, F_0=1000, E=30000$).
+Please notice that the yellow(red) arrows shows the length of long(short) axis of inertia ellipse, which is prependicular to the long(short) axis of distribution cloud.
+For instance, if the yellow arrow lies in p-axis, it means the long axis of distribution cloud is lying along x-axis.}\label{fig:N=50_F=1000_E=30000_movie}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.4]{ZhiyuPictures/quadrupole_mode_2.png}
+\caption{Schemetic description of the excited mode.
+Red ellipse is the shape of cloud in low-energy regime when there is repulsive interaction.
+Gray cloud is the imaginary shape of cloud when there is no interaction, they are plotted here as a reference.
+One may think of the effect of interaction as a kind of potential that prefer to place particles along x axis, because in low energy regime the system is not allowed to be squeezed too much along x axis since doing this cost a large amount of interaction energy.}\label{fig:Schemetic_description_of_the_mode}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.4]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s_Send.eps}
+\caption{Time evolution of S after evolving for about 500 time units ($N=50, F_0=1000, E=30000$). The oscillating behaviour of S persists over 500 time units.}\label{fig:N=50_F=1000_E=30000_Send}
+\end{figure*}
+
+To sum up, the existence of the long-lasting oscillation of S indicate that the system does not relax to its equilibrium state in terms of shape although it is already thermalized in terms of energy distribution.
+With this long-lasting mode, the radius R of the cloud will keep oscillating, enabling the breathing mode to last for a long time.
+
+%The time evolution of shape polarization S is shown in Fig.\ref{fig:shape}, when E is much lower than the thermalizaion threshold, S decreases to 0.3 in almost no time.
+On the contrary, when E is much higher than the threshold value, it takes a long time for S to dacay.
 
@@
 The other one corresponds to the relaxation time of the angular distribution in phase space, which will determine the decay rate of the amplitude of the breathing mode.
-However, with the form of interaction we used, i.e.
+We have shown that in the low-energy regime, although the energy distribution reach Boltzmann distribution within several periods of oscillation, the shape keep oscillating for thousands of periods.
+%However, with the form of interaction we used, i.e.
 finite range constant repulsive force, we found those two time scales diverge only when interaction vanish, which is a trivial singular point.
@@
 We attribute it to the fact that there is no essential bias between angular and radial transfer in phase-space for this simple form of interaction.
-The longest time scale is verified numerically by Largest Lyapunov Exponent.
+The shortest time scale is verified numerically by Largest Lyapunov Exponent.
 A further question could be asked is whether there is a subtle form of interaction that could give those two time scales essentially different behavior.

### 2017-03-20 Zhiyu.tex
Jan26 PRE format, tex

@@
 Meanwhile, the experiment of Ref.\cite{Haller2009} has found a regime of interactions where the breathing-mode frequency approaches the Gross-Pitaevskii prediction.
-However, since mean-field approach which generally omit quantum fluctuation is successful in this problem, one may wonder how quantum effect plays the role in the breathing mode.
-Thus, a natural question would be asked is how breathing frequency is dependent on interaction for classical gas.
+However, since mean-field approach which generally omit quantum fluctuation is successful in this problem, one may wonder how quantum effects play the role in the breathing mode.
+Thus, a natural question would be asked is that how breathing frequency is dependent on interaction for classical gas.
 Though generated in BEC, the breathing mode phenomenon is not restricted to BEC.
 For a classical gas, the breathing mode still can be excited with a quench.
-A good knowledge of classical version may help us understand the quantum question better.
-Surprisingly, to the best of our knowledge, all the literature focus on the breathing mode in BEC, without a careful study of their classical counterpart, which actually seems easier.
-Since this classical version question has not been answered yet, more study is needed.
+Usually, a good knowledge of the classical version may help us understand the quantum one better.
+David Guéry-Odelin, Francesca Zambelli, Jean Dalibard, and Sandro Stringari answered this question in ref.\cite{Guery-Odelin1999}.
+They used the Boltzmann equation as well as molecular dynamics simulation to study the monople mode and quarulple mode of the 2-D classical gas in a harmonic trap.
+But in that work, the interaction is elastic collision, i.e.
+zero-range-infinite-strength interaction.
+We think introducing a finite range for the repulsive interaction will definitely enrich the physics in this system which looks simple, thus producing a different equilibrium and non-equilibrium behaviour.
+Surprisingly, to the best of our knowledge, there is no in-depth study of this case.
+For this reason, more study is necessary.
 
-One the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
-Thermalization is among the most fundamental process for a many-body interacting system.
+On the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
+Thermalization is among the most fundamental processes for a many-body interacting system.
 All systems do not thermalize.
@@
 In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as well as Lyapunov exponent.
-With these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behavior in the thermalization time scales except the trivial divergence at zero interaction.
+%With these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behavior in the thermalization time scales except the trivial divergence at zero interaction.
 
-This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the parameter of the system.
+This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the number of parameters of the system.
 In addition, we briefly observe the ground state and reveal two dynamically distinct regime of the system, i.e.
@@
 under what parameter the thermalization time scale is very large.
-Then we point out that there are two kind of thermalization (or relaxation) behavior that could be measured in this system.
 In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
+Then we point out that there are two kind of thermalization behavior that could be measured in this system, one is about energy distribution while another is about shape of cloud in phase-space.
+Since here we find two sense of ``thermalizing", we will redefine our terms -- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".
+But when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish it from ``thermalized".
+So in section \ref{section:Shape} we actually study the ``thermalizing" of the shape of the cloud in phase-space, or the ``relaxation" behavior of the system.
+There we discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
 
@@
 \end{equation}
-It can be shown that Eq.\ref{eq:preparation2} can be rewrite into the following form:
+
+Using the transformation Eq.\ref{eq:transform}, we can rewrite Eq.\ref{eq:preparation2} into the following form:
 \begin{equation}
@@
 \end{equation}
-with the transformation:
 \begin{equation}
@@
 \right.
+\label{eq:transform}
 \end{equation}
 
-In this manner, we reduced number of the parameters in our model into three: $\tilde{H}$, $\tilde{F_0}$, $N$.
+In this manner, we reduced the number of the parameters in our model to three: $\tilde{H}$, $\tilde{F_0}$, $N$.
 Equivalently, we set $\sigma$, $\omega_0$ and $m$ to 1 in our numerical simulation.
@@
 \subsubsection{Ground states}
-For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbors, which is $\frac{2F_0}{\omega_0^2}$.
+For the ground state of this system, one could make the following prediction: \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is a solid-like state, where each particle keeps an equal distance ($\frac{2F_0}{\omega_0^2}$) with its nearest neighbors .
 The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
 
-In the fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the ``hardcore gas" limit (right).
+In the Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the ``hardcore gas" limit (right).
 
@@
 Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
-In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
+In that case, one will observe the radius R of the cloud oscillating at a certain frequency, which is usually called ``breathing mode".
 However, it is quite different in the classical version.
-Firstly, the ground state may be meaningless.
+Firstly, it is no longer necessary to focus on ground state.
 In quantum case, the reason why we care about ground state and low lying excitations is that BEC occur at low temperature.
@@
 So it is not necessary to focus on low lying excitations in classical case.
-Besides, since classical limit is $\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one.
+Besides, since classical limit is $\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so even in low energy regime, the classical behaviors could be quite different from the quantum one.
 Secondly, it is no longer necessary to vary parameters ``by a little" in the quench.
-In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}).
-But in classical case, since $\hbar$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case.
+In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum of Hamiltonian is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}).
+But in classical case, since $\hbar$ vanishes, no matter how small the quench is, the reason that cause beats in quantum case no longer work in classical context.
 Thus it is not necessary to limit ourselves to small quench.
 
-Furthermore, notice that X and P (normalized) are symmetric for simple harmonic oscillator.
+Let's consider quenching the harmonic potential, i.e., $\omega_0\rightarrow\omega_0'=\omega_0+\Delta\omega_0$.
+We notice that X and P (scaled) are symmetric for simple harmonic oscillator.
 In weak interaction limit, the distribution cloud should be circular when the gas is completely thermalized.
-The difference between thermalized cloud before and after quench is that they are circular under different normalization of phase-space.
-If we look at both of them in the phase-space normalized according to the final $\omega_0$, we will find shape of the cloud before the quench is an ellipse while the final one is a circle.
+The difference between thermalized cloud before and after quench is that they are circular under different scaling ratio of P and X axis.
+If we look at both of them in the phase-space rescaled according to $\omega_0'$, we will find shape of the cloud before the quench is an ellipse while the final one is a circle.
 
-Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant.
+Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the random noise is significant.
 If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
@@
 \subsection{Rotating frame in Phase-space}
-Traditionally, we think of there is a distribution cloud in phase space, and due to harmonic trap, the cloud will rotate at frequency $\omega_0$.
+If there is a non-circular distribution cloud in phase-space, e.g., a line-shape cloud in Fig.\ref{fig:Breathingfrequency2_0}, driven by the harmonic trap, the cloud will rotate at frequency $\omega_0$.
 When there is interaction, we may think there is a small modification of the frequency $\omega=\omega_0+\delta$.
-Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase space.
+Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase-space.
 In this frame, the picture we will see is as follow:\\
@@
 
-This picture is actually a classical version of the interaction picture. With this picture, we will soon find the dynamic analysis greatly simplified.
+This rotating frame picture is actually a classical version of the interaction picture, which turns out to symplifly our dynamic analysis.
+The stationary frame and rotating frame is shown in Fig.\ref{fig:Breathingfrequency2_1}.
 
@@
 If the breathing frequency of the system is $\omega=\omega_0+\delta$, we will expect to see a line (which may gradually deform into an oval cloud or even an isotropic cloud) rotating at $\delta$ in rotating frame.
-If we plot x-p with t, we expect to see a spiral motion.
 Since the motion we see is an additional rotation in rotating frame, we will call it precession.
-This precession directly leads to the $\delta$.
-
+This precession directly leads to the $\delta$ shift in breathing frequency.
 Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
@@
 Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
+\label{fig:Breathingfrequency2_0}
 \end{figure*}
@@
 
-(See fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
+(See Fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
 Similar process happen when there are more particles.
-In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in fig.\ref{fig:Breathingfrequency3}.
+In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in Fig.\ref{fig:Breathingfrequency3}.
 (As for the remaining half of collisions, colliding particles have small difference in their momentum.
 Let us say, both particles have positive momentum.
-In fig.\ref{fig:Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis cannot have strong effect on the rotation of distribution.)
+In Fig.\ref{fig:Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis seldom contribute to the rotation of distribution.)
 
-Let us estimate the precession angle $\alpha$ in one collision by $\frac{\sigma}{R}$, which follows from the two-particle case study.
+Let us estimate the precession angle $\alpha$ in one collision event by $\frac{\sigma}{R}$, which follows from the two-particle case study.
 Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
@@
 
-When $F_0$ is not that large, the frequency behavior seems complicated (see fig.\ref{fig:Breathingfrequency1}).
+When $F_0$ is not that large, the frequency behavior seems complicated (see Fig.\ref{fig:Breathingfrequency1}).
 Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
 The reason could also be well understood with the mechanism described before.
-In the former discussion, we goes to high $F_0$ limit, which means particles exchange momentum in infinitesimal time.
+In the discussion above, we go to high $F_0$ limit, which means particles exchange momentum in infinitesimal time.
 For $F_0$ is not very big, the finite interaction time should be taken into consideration.
-During this time, the behavior of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
-Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
+During this time, the motion of each particle in phase-space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
+Since the real P axis is rotating counter-clockwise, the particle will follow a circular trajectory(orange and green dashed line in Fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
 There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line).
-At this point, we will see the precession stop so that the frequency is 2.
+It is easy to see that the contribution of each collision event to the phase-space precession of the cloud is negative in Fig.\ref{fig:Breathingfrequency3})(b).
+So at this point, we will see the precession  slows down or even be reversed, which means the breathing frequency is 2 or a little bit lower than 2.
 
@@
 
-The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}.
+The dependence of frequency on energy and $F_0$ is shown in Fig.\ref{fig:Breathingfrequency4}.
 For the first thing, as expected when $F_0$ is high the frequency behavior is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}.
@@
 
-the critical point that frequency falls to 2 can be estimate by:
+the critical point that frequency decreases to 2 can be estimate by:
 \begin{equation}
@@
 \end{equation}
-which states that the approaching time $\tau$ exactly cancels the precession angle derived before
-$\tau$ can be estimated by $R/F_0$. With some math, one can show that this condition is equivalent to
-
+which means that the approaching time $\tau$ (estimated by $R/F_0$) exactly cancels the precession angle we derived before. One can show that this condition is equivalent to
 \begin{equation}
@@
 \end{equation}
-which is the same as the criterion of whether two particle will bounce or pass by if one estimate the average internal energy of a pair with $\frac{E}{N}$.
-This argument indicate the reason why we see frequency stop falling down below 2 as one should expect with previous discussion:\
-All our previous analysis based on fig.\ref{fig:Breathingfrequency3} only studies the case of bouncing.
-If the energy of particles are so large that they often overcome the interaction potential barrier and pass each other, the situation would be completely different.
-In that case, in fig.\ref{fig:Breathingfrequency3}, particles will move a little bit out of their initial position, and soon move back, almost return to their initial place.
-In this manner, the interaction do not affect the distribution of the cloud in phase space.
-Thus, the frequency will stay near 2 when E is large.
+which can also be understood as the criterion of whether two particles will bounce or pass by if one estimate the average internal energy of a pair with $\frac{E}{N}$.
 
 Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization".
-In addition, if the system is completely thermalized in terms of their phase of orbit in phase space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.
+In addition, if the system is completely thermalized in terms of their phase angles in phase-space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.
 
@@
 
-We can always think of them in the reference frame of their center of mass ``C".
-In frame C, one can easily show that when there is no interaction what we will see is that two particles are bound together by a harmonic trap center at C (black line in fig.\ref{fig:thermalization2}).
+We can consider their motion in their center of mass frame ``C".
+In frame C, one can easily show that when there is no interaction what we will see is that two particles bound together by a harmonic trap centered at C (black line in Fig.\ref{fig:thermalization2}).
 So their relative motion is also a harmonic oscillation.
@@
 The deviation grows with the increase of $F_0$ and the decrease of internal energy of the pair.
-As a result, when the $F_0$ is small and when the E is large, a beat with low frequency $\omega_r-\omega_0=\delta$ will exist.
-This phenomenon means energy transfer between particles are inefficient, thus it will slow down the thermalization process.
+As a result, when $F_0$ is small or when E is large, a beat with low frequency $\omega_r-\omega_0=\delta$ will exist.
+This phenomenon means energy transfer between particles are inefficient, thus the thermalization should be slow.
 
@@
 The physics of the ``dance" is similar to the dance between two particle.
-As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.
+As is shown in Fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.
 
@@
 \subsection{Thermalization condition}
-The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before.
-Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$).
+The main obstruct to get an thermalized state is the low frequency beat mentioned before.
 As a result, to achieve ergodic state, we have to avoid such low frequency oscillation.
@@
 
-As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500$-$F_0=1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
-As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
+As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500$-$F_0=1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
+As a supplementary proof of our argument, Fig.\ref{fig:thermalization6} and Fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
 To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
@@
 The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitely slows down the energy transfer.
-What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives.
+What is more, because of this, the particles is less interferred by other particles so that two-particle analysis survives.
 It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time.
-In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us.
+In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the low frequency beat effect tells us.
 Thus the particles energy is localized in certain value.
 On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners.
-As a result, the energy transferred in every collision between two particles are no longer correlated, which is equivalent to say that two-particle analysis breaks down.
+As a result, the energy transferred in every collision between two particles are no longer correlated so that our two-particle analysis breaks down.
 Instead, the energy transfer is completely random, with a non-zero amplitude.
@@
 For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
-However, to our knowledge, there is not any obvious conclusion about the distribution for an isolated system where the total energy is conserved.
-
+However, there is not any obvious conclusion about the distribution for an isolated system where the total energy is conserved.
 But intuitively, one will expect that if we measure the energy of a subsystem, e.g.
-one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle.
+one particle, then we will get a Boltzmann distribution because the rest part of the system can be considered as a bath for this particle.
 The temperature of this isolated system is defined according to $Nk_BT=E$.
@@
 
-To take the first one as an example, Y axis is logarithmically scaled.
-X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system.
-The blue dotted line is the predicted Boltzmann distribution (normalized according to counts).
-Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare.
-In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction.
-When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.
-
-It is evident form $Nk_BT=E$ that the slope of Boltzmann distribution in this figure only depend on N. That is the reason why we want to measure at different N below.
-
-In fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states (DOS).
+In Fig.\ref{fig:thermalization9} and Fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states (DOS).
 Possibility is proportional to Boltzmann exponential factor multiplied by density of states.
@@
 However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the small region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
-But since $\sigma<<R$, one can think of this as a small modification.
-Therefore, the tendency of the curve in fig.\ref{fig:thermalization9} and fig.\ref{fig:thermalization10} is deviated slightly from Boltzmann distribution.
+The effect of interaction is conspicuous in low energy part: when interaction is weak, particles prefer to stay near zero energy according to Boltzmann distribution, but when interaction grows, they are no longer allowed to accumulate near zero energy, in another word DOS at low energy decreases with the increase of interaction.
+Therefore, counts at the low energy part of Fig.\ref{fig:thermalization9} and \ref{fig:thermalization10} is always a little bit lower than the Boltzmann prediction.
+But since $\sigma<<R$, we can think of interaction as a small modification, so the overall tendency still fits well.
 
@@
 When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
-In the phase-space, the motion becomes circular, so each of these particles has two independent degree of freedom, i.e., modulus and phase angle.
-Here, independent means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
-In view of this, when it comes to ``thermalization", one may notice that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
+In the phase-space, the motion becomes circular, so each of these particles has two independent degrees of freedom, i.e., modulus and phase angle.
+Here, ``independent" means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
+In view of this, when it comes to ``thermalization", one may expect that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
 To distinguish these two kind of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
@@
 \subsection{Lyapunov Exponents}
-To see the time scale of ``thermalization" and ``relaxation" more systematically, we may measure the Lyapunov Exponents.
-Lyapunov Exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space.
+The Lyapunov Exponents is a good tool to quantify the time scale of ``thermalization".
+Lyapunov Exponents(LE) describes how fast one orbit diverge from its nearby orbits in $\Gamma$-space.
 But for high dimensional system, LE is a spectrum that manifest the instability of the trajectory along each direction.
-The largest Lyapunov exponents (LLE) reflects the time scale that system lose its memory in phase-space.
-We will measure the LLEs along our trajectory and plot its distribution.
+The largest Lyapunov exponents (LLE) reflects the shortest time scale that system lose its memory.
+Each point along one trajectory in $\Gamma$-space could have different LLE value, but the distribution of LLE is dependent on macroscopic parameters.
+As is shown in Fig.\ref{fig:LLEdistribution1}, we measured the LLEs along our trajectory and plot its distribution as a function of total energy.
 
@@
 \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
-\caption{LLE distribution for N=5, F0=1000, scan E.``hot"(reversed)}\label{fig:LLEdistribution1}
+\caption{LLE distribution for N=5, F0=1000, scan E. The size of bin is 0.01}\label{fig:LLEdistribution1}
 \end{figure}
@@
 
-fig.\ref{fig:LLEdistribution1} shows the distribution of LLE by color.
 The LLE decrease with the growth of Energy.
 The crucial part is near E=5000.
-The most probable value of LLE goes down from 1 to 0.1,which indicate that \textbf{the shortest time scale becomes longer than an oscillation period when E is larger than 5000}.
-And E=5000 is exactly our prediction value of thermalization threshold.
+The most probable value of LLE goes down from 1 to 0.1,which indicate that the shortest time scale becomes longer than an oscillation period when E is larger than 5000, which is consistent with our prediction value of thermalization threshold.
 So there is a correspondence between energy thermalization and LLE.
-The size of bin(resolution of LLE) in fig.\ref{fig:LLEdistribution1} is 0.01, so when E goes far beyond the thermalization threshold, the LLE distribution is not that clear.
-We only know that LLE is concentrated close to zero in high E regime.
+As E goes far beyond the thermalization threshold value, the LLE is restricted close to zero, suggesting the divergence of correlation time.
 
-\subsection{{\color{red}{Shape of Distribution in Phase-space}}}
+\section{Shape of Distribution in Phase-space}\label{section:Shape}
 %To date, we have verified that the energy distribution will go to Boltzmann distribution.
@@
 When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
-In the phase-space, the motion becomes circular, so each of these particles has two independent degree of freedom, i.e., modulus and phase angle.
-Here, independent means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
-In view of this, when it comes to ``thermalization", one may notice that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
-To distinguish these two kind of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
-The time scale of thermalization and relaxation could be different in principle.
-We start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning.
-If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to some stable shape in a short time, e.g.
-a circle in high energy.
-Meanwhile, the distribution of particle number  along radius slowly evolves to Boltzmann distribution.
-If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or some oscillation between different shapes for a long time while the radius distribution is already Boltzmann.
+In the phase-space, the motion becomes circular, so each of these particles has two independent degrees of freedom, i.e., modulus and phase angle.
+Here, ``independent" means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
+In view of this, when it comes to ``thermalization", one will expect that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
+As ins explained in the Introduction part, in order to distinguish two kinds of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
+The time scale of thermalization and relaxation could be quite different in principle.
+We will start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning.
+If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to some stable shape in a short time (a circle if interaction is not significant compared to total energy) while the distribution of particle number along radius slowly evolves to Boltzmann distribution.
+If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or some oscillation between different shapes for a long time while the energy distribution is already Boltzmann.
 
@@
 The advantage of defining the S lies in that S is independent of all rotating behavior of the cloud in phase-space and thus extract the information of shape alone.
-One could also use eigenvalues of quadrupole moment Q to define S, since the inertia tensor I is similar to quadrupole moment Q (only different up to a factor and an identity matrix).
+One could also use eigenvalues of quadrupole moment Q to define S.
+Two choice of definition is equivalent, since I and Q are only different up to a factor and an identity matrix.
 
@@
 }
-\caption{Time evolution of S in low-enrgy regime(a), intermidiate(b), high-energy regime(c).
+\caption{Time evolution of S in low-energy regime(a), intermidiate(b), high-energy regime(c).
 The overall value (top three pannels), where every point represent the average of original data over several periods, show that S decays to a low value in a short time in low-energy case, but persist for a relative long time in high-energy case.
@@
 We assume that over a long enough time, all macroscopic quantity should be constant because the randomness has wash out all possible orders to make entropy as large as possible.
-Since we see a periodical behaviour of S, we know the whole system doesn't relax to its equilibrium state.
+Since we see a periodical behavior of S, we know the whole system doesn't relax to its equilibrium state.
 
 The oscillating background value of S indicate that the shape of the cloud in phase space is deformed periodically between a circle and an ellipse($S=0.4$ means $\frac{a}{b}\sim 2.5$).
-To further reveal the nature of this oscillating mode, we focus on the low-energy case and plot the distribution of the cloud in the phase space as Fig.\ref{fig:N=50_F=1000_E=30000_movie}.
+To further reveal the nature of this oscillating mode, we focus on the low-energy case and plot the distribution of the cloud in the phase-space as Fig.\ref{fig:N=50_F=1000_E=30000_movie}.
 The time interval between each pannels is $0.1*2\pi$ time units.
@@
 We first studied the relation between breathing mode frequency and interaction parameter as well as total energy.
-We found the breathing frequency could be estimated by \ref{eq:breathingfrequency1}.
+We found the breathing frequency could be estimated by eq.\ref{eq:breathingfrequency1}.
 And the mechanism behind this relation is that the momentum transfer which happens instantly in collision saves the particles some time from traveling this distance.
@@
 \subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
-Results are shown in fig.\ref{fig:others1}
+Results are shown in Fig.\ref{fig:others1}
 

### 2017-03-20 Zhiyu.tex
Mar21 PRE format, tex

@@
 
-\begin{comment}
-\subsection{Relaxation in Phase-space}
-
-When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
-In the phase-space, the motion becomes circular, so each of these particles has two independent degrees of freedom, i.e., modulus and phase angle.
-Here, ``independent" means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
-In view of this, when it comes to ``thermalization", one may expect that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
-To distinguish these two kind of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
-The time scale of thermalization and relaxation could be different in principle.
-We start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is line shape at the beginning.
-If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to isotropic in a short time, and radius distribution slowly evolves to Boltzmann distribution.
-If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or elliptical shape for a long time while the radius distribution is already Boltzmann.
-
-To study the relaxation, it is convenient to go back to the picture introduced in discussing breathing frequency, since in that chapter, we focus on the average effect of collision on precession motion, but now we focus on the fluctuation near this average effect.
-Let's recall two distinct regime discussed in Fig.\ref{fig:Breathingfrequency3}.
-These two regime will show different behavior of relaxation.
-
-In ``bouncing regime", (see Fig.\ref{fig:Breathingfrequency3}(a))particles' position in phase-space have a finite shift $\sim\sigma$ in one collision.
-As is discussed in former chapter, the average effect of this shift result in precession motion in phase-space and lead to a perturbed breathing frequency.
-This result is based on approximating the mean effect of collision process with the collision between two particles aligned symmetrically on P axis.
-However, in reality, the particles
-are everywhere so that the shift do not rotate the particles' phase angle by the same amount in every collision, thus the increase of the phase angle of each particle can be thought of as a wide distribution with a non-zero mean value.
-As a result of this distribution, the phase angle soon got thermalized, which means the ``relaxation time" is short.
-
-In `` passing regime", (see Fig.\ref{fig:Breathingfrequency3}(b)),the maximal shift of position in phase-space starts to decrease with the decrease of $F_0$.
-The shift $\delta$ decrease as $\delta\sim F_0^2$.
-This means the particles are localized in their original position when $F_0$ is smaller-- it is natural to get this conclusion, since the weaker the interaction is, the longer time it takes to ``relax".
-
-All our discussion before is based on the approximation that every particle collide with each other once in one period.
-But this is hardly true in reality.
-If the number of collision in every period is taken into account, these two regime looks even more different: In ``bouncing regime", the average precession speed is significant, (see Fig.\ref{fig:Breathingfrequency4}), which means each collision cause a finite precession.
-The fluctuation of the number of collision one particle has in each period will contribute to the divergence of their phase angles.
-On the contrary, in ``passing regime", (see Fig.\ref{fig:Breathingfrequency4}), the breathing frequency is close to 2, which means the average effect of collision create zero precession speed.
-As a result, even though the number of collision is not a constant, it has on average no effect whether one particle collide more or less in one period.
-
-To directly check this argument, we can inspect the frequency spectrum of $R(t)$.
-As is shown in FIG.\ref{fig:frequencyspectrum}, when $F_0$ is very small (red curve), the peak is very sharp and peak frequency is exactly 2.
-When $F_0$ goes far beyond the threshold value of $\frac{E}{N\sigma}$ (blue, purple, pink, etc.), the peak becomes a wide distribution with a peak value deviated far from 2, which lead to  fast thermalization according to our argument before.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=0.5]{ZhiyuPictures/freq_spectrum_N=10_E=1000_pre_rev.eps}
-\caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
-\end{figure}
-
-\end{comment}
-
 \subsection{Lyapunov Exponents}
@@
 \section{Shape of Distribution in Phase-space}\label{section:Shape}
-%To date, we have verified that the energy distribution will go to Boltzmann distribution.
-However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state.
-There is other information that could still exist, for instance, the shape of distribution cloud in phase-space.
-One of the reasons why we care about this quantity is that it has a strong effect on breathing behavior.
-For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large.
-On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all.
-Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).
 When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
@@
 
-%The time evolution of shape polarization S is shown in Fig.\ref{fig:shape}, when E is much lower than the thermalizaion threshold, S decreases to 0.3 in almost no time.
-On the contrary, when E is much higher than the threshold value, it takes a long time for S to dacay.
-
 \section{Conclusion}

### 2017-10-18 draft_02.tex
minor changes

--- 2017-03-20 Zhiyu.tex
@@
-\documentclass[aps,pre,twocolumn,groupedaddress]{revtex4-1}
+\documentclass[aps,preprintnumbers,onecolumn,amsmath,amssymb,floatfix,pra]{revtex4-1}
+
+%\documentclass[aps,preprintnumbers,onecolumn,amsmath,amssymb,floatfix,pra]{revtex4}
+
+%\documentclass[aps,pre,twocolumn,groupedaddress]{revtex4-1}
 %\documentclass[a4paper,onecolumn,12pt]{article}
@@
 \begin{abstract}
+
+Abstract --  to be written last
+
 \end{abstract}
+
 \maketitle
-% \tableofcontents
-% \newpage
+
 \section{Introduction}
-Controlled and tunable experimental realizations of confined quantum systems with ultracold atoms enable nonequilibrium studies of quantum many-body states in novel geometries.
-A common feature of many cold-atom experiments is the confinement of a many-body system in a harmonic trap.
-Trapping introduces many distinctive features which have no analog in uniform many-body states, including collective excitations such as breathing modes, dipole modes, and scissors modes.
-Such trap-related collective modes have been widely studied both experimentally and theoretically for continuum systems, especially in the mean-field regime, since the early days after quantum degeneracy was achieved with trapped atoms \cite{Dalfovo1997}\cite{Jin1996}.
 
-In mean-field perspective, the physics of atom gas in Bose-Einstein Condensation can be described by the Gross-Pitaevskii equation\cite{Dalfovo1999}\cite{Stringari1996}, where the breathing frequency for 1D Bose gas is calculated to be $\Omega_{GP}=\sqrt{3}\omega_0$.
-Meanwhile, the experiment of Ref.\cite{Haller2009} has found a regime of interactions where the breathing-mode frequency approaches the Gross-Pitaevskii prediction.
-However, since mean-field approach which generally omit quantum fluctuation is successful in this problem, one may wonder how quantum effects play the role in the breathing mode.
-Thus, a natural question would be asked is that how breathing frequency is dependent on interaction for classical gas.
-Though generated in BEC, the breathing mode phenomenon is not restricted to BEC.
-For a classical gas, the breathing mode still can be excited with a quench.
-Usually, a good knowledge of the classical version may help us understand the quantum one better.
-David Guéry-Odelin, Francesca Zambelli, Jean Dalibard, and Sandro Stringari answered this question in ref.\cite{Guery-Odelin1999}.
-They used the Boltzmann equation as well as molecular dynamics simulation to study the monople mode and quarulple mode of the 2-D classical gas in a harmonic trap.
-But in that work, the interaction is elastic collision, i.e.
-zero-range-infinite-strength interaction.
-We think introducing a finite range for the repulsive interaction will definitely enrich the physics in this system which looks simple, thus producing a different equilibrium and non-equilibrium behaviour.
-Surprisingly, to the best of our knowledge, there is no in-depth study of this case.
-For this reason, more study is necessary.
+Controlled and tunable experimental realizations of confined quantum systems with ultracold atoms
+enable nonequilibrium studies of quantum many-body states in novel geometries. A common feature of
+many cold-atom experiments is the confinement of a many-body system in a harmonic trap. Trapping
+introduces many distinctive features which have no analog in uniform many-body states, including
+collective excitations such as breathing modes, dipole modes, and scissors modes. Such trap-related
+collective modes have been widely studied both experimentally and theoretically for continuum
+systems, especially in the mean-field regime, since the early days after quantum degeneracy was
+achieved with trapped atoms \cite{Dalfovo1997}\cite{Jin1996}.
 
-On the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property.
-Thermalization is among the most fundamental processes for a many-body interacting system.
-All systems do not thermalize.
-An example is the Fermi-Pasta-Ulam paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a long time.
-A lot of research on thermalization property has been done in other classical system.
-Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with Lyapunov exponents.
-Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem .
-In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as well as Lyapunov exponent.
-%With these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behavior in the thermalization time scales except the trivial divergence at zero interaction.
+In mean-field perspective, the physics of atom gas in Bose-Einstein Condensation can be described by
+the Gross-Pitaevskii equation\cite{Dalfovo1999}\cite{Stringari1996}, where the breathing frequency
+for 1D Bose gas is calculated to be $\Omega_{GP}=\sqrt{3}\omega_0$. Meanwhile, the experiment of
+Ref.\cite{Haller2009} has found a regime of interactions where the breathing-mode frequency
+approaches the Gross-Pitaevskii prediction. However, since mean-field approach which generally omit
+quantum fluctuation is successful in this problem, one may wonder how quantum effects play the role
+in the breathing mode. Thus, a natural question would be asked is that how breathing frequency is
+dependent on interaction for classical gas. Though generated in BEC, the breathing mode phenomenon
+is not restricted to BEC. For a classical gas, the breathing mode still can be excited with a
+quench. Usually, a good knowledge of the classical version may help us understand the quantum one
+better. David Guery-Odelin, Francesca Zambelli, Jean Dalibard, and Sandro Stringari answered this
+question in ref.\cite{Guery-Odelin1999}. They used the Boltzmann equation as well as molecular
+dynamics simulation to study the monople mode and quarulple mode of the 2-D classical gas in a
+harmonic trap. But in that work, the interaction is elastic collision,
+i.e. zero-range-infinite-strength interaction. We think introducing a finite range for the repulsive
+interaction will definitely enrich the physics in this system which looks simple, thus producing a
+different equilibrium and non-equilibrium behaviour. Surprisingly, to the best of our knowledge,
+there is no in-depth study of this case. For this reason, more study is necessary.
 
-This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the number of parameters of the system.
-In addition, we briefly observe the ground state and reveal two dynamically distinct regime of the system, i.e.
-strong interaction regime and weak interaction regime.
-In Section \ref{section:breathing frequency}, we evaluate the breathing frequency according to its mechanism, and compare that with our numerical simulation result.
-Besides, we also introduce a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems.
-In section \ref{section:Thermalization}, we focus on the thermalization property.
-We first examine the canonical distribution of energy to find out the threshold of thermalization, i.e.
-under what parameter the thermalization time scale is very large.
-In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.
-Then we point out that there are two kind of thermalization behavior that could be measured in this system, one is about energy distribution while another is about shape of cloud in phase-space.
-Since here we find two sense of ``thermalizing", we will redefine our terms -- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".
-But when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish it from ``thermalized".
-So in section \ref{section:Shape} we actually study the ``thermalizing" of the shape of the cloud in phase-space, or the ``relaxation" behavior of the system.
-There we discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
+On the other hand, in a nonquilibrium many-body system, a more intriguing question is about its
+thermalization or relaxation property. Thermalization is among the most fundamental processes for a
+many-body interacting system. All systems do not thermalize. An example is the Fermi-Pasta-Ulam
+paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a
+long time. A lot of research on thermalization property has been done in other classical
+system. Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with
+Lyapunov exponents. Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment
+by examine the canonical distribution of a subsystem . In our paper, we will also probe the system's
+thermalization time scales from the perspective of canonical distribution as well as Lyapunov
+exponent. %With these approaches, we will show that the thermalization time scale manifest a
+          %competition between total energy and interaction energy, so there is not any singular
+          %behavior in the thermalization time scales except the trivial divergence at zero
+          %interaction.
+
+This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
+reduce the number of parameters of the system. In addition, we briefly observe the ground state and
+reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak
+interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing
+frequency according to its mechanism, and compare that with our numerical simulation
+result. Besides, we also introduce a rotating frame method of treating this problem, which is a
+convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we
+focus on the thermalization property. We first examine the canonical distribution of energy to find
+out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very
+large. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and
+confirm the former discussion. Then we point out that there are two kind of thermalization behavior
+that could be measured in this system, one is about energy distribution while another is about shape
+of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
+-- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
+when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
+it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
+the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
+discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
 
@@
 
-In this manner, we reduced the number of the parameters in our model to three: $\tilde{H}$, $\tilde{F_0}$, $N$.
-Equivalently, we set $\sigma$, $\omega_0$ and $m$ to 1 in our numerical simulation.
-Throughout, we will use ``E" and ``$F_0$" to denote their reduced version $\tilde{H}$, $\tilde{F_0}$.
+In this manner, we reduced the number of the parameters in our model to three: $\tilde{H}$,
+$\tilde{F_0}$, $N$. Equivalently, we set $\sigma$, $\omega_0$ and $m$ to 1 in our numerical
+simulation. Throughout, we will use ``E" and ``$F_0$" to denote their reduced version $\tilde{H}$,
+$\tilde{F_0}$.
 
@@
 \subsubsection{Ground states}
-For the ground state of this system, one could make the following prediction: \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is a solid-like state, where each particle keeps an equal distance ($\frac{2F_0}{\omega_0^2}$) with its nearest neighbors .
-The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.
+
+For the ground state of this system, one could make the following prediction: \\(1) When the
+$\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is
+equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground
+state is a solid-like state, where each particle keeps an equal distance ($\frac{2F_0}{\omega_0^2}$)
+with its nearest neighbors . The low-lying excitation is particles' independent harmonic oscillation
+around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore
+gas, while the size of particle is just $\sigma$.
 
@@
 \section{Breathing Frequency}\label{section:breathing frequency}
-Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$.
-In that case, one will observe the radius R of the cloud oscillating at a certain frequency, which is usually called ``breathing mode".
-However, it is quite different in the classical version.
-Firstly, it is no longer necessary to focus on ground state.
-In quantum case, the reason why we care about ground state and low lying excitations is that BEC occur at low temperature.
-But in classical case, there is no BEC.
-So it is not necessary to focus on low lying excitations in classical case.
-Besides, since classical limit is $\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so even in low energy regime, the classical behaviors could be quite different from the quantum one.
-Secondly, it is no longer necessary to vary parameters ``by a little" in the quench.
-In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum of Hamiltonian is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}).
-But in classical case, since $\hbar$ vanishes, no matter how small the quench is, the reason that cause beats in quantum case no longer work in classical context.
-Thus it is not necessary to limit ourselves to small quench.
 
-Let's consider quenching the harmonic potential, i.e., $\omega_0\rightarrow\omega_0'=\omega_0+\Delta\omega_0$.
-We notice that X and P (scaled) are symmetric for simple harmonic oscillator.
-In weak interaction limit, the distribution cloud should be circular when the gas is completely thermalized.
-The difference between thermalized cloud before and after quench is that they are circular under different scaling ratio of P and X axis.
-If we look at both of them in the phase-space rescaled according to $\omega_0'$, we will find shape of the cloud before the quench is an ellipse while the final one is a circle.
+Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state
+and then suddenly vary some parameter by a little, for instance,
+$\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R
+of the cloud oscillating at a certain frequency, which is usually called ``breathing mode".
 
-Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the random noise is significant.
-If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise.
-Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
+However, it is quite different in the classical version. Firstly, it is no longer necessary to focus
+on ground state. In quantum case, the reason why we care about ground state and low lying
+excitations is that BEC occur at low temperature. But in classical case, there is no BEC. So it is
+not necessary to focus on low lying excitations in classical case. Besides, since classical limit is
+$\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so even in low energy
+regime, the classical behaviors could be quite different from the quantum one. Secondly, it is no
+longer necessary to vary parameters ``by a little" in the quench. In quantum case, the small quench
+$\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum of Hamiltonian is shifted
+slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}). But in classical case,
+since $\hbar$ vanishes, no matter how small the quench is, the reason that cause beats in quantum
+case no longer work in classical context. Thus it is not necessary to limit ourselves to small
+quench.
+
+Let's consider quenching the harmonic potential, i.e.,
+$\omega_0\rightarrow\omega_0'=\omega_0+\Delta\omega_0$. We notice that X and P (scaled) are
+symmetric for simple harmonic oscillator. In weak interaction limit, the distribution cloud should
+be circular when the gas is completely thermalized. The difference between thermalized cloud before
+and after quench is that they are circular under different scaling ratio of P and X axis. If we look
+at both of them in the phase-space rescaled according to $\omega_0'$, we will find shape of the
+cloud before the quench is an ellipse while the final one is a circle.
+
+Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the
+random noise is significant. If we start with a state whose configuration in phase-space is an
+ellipse slightly deviated from circle, the oscillating amplitude will be too small to be
+distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x,
+zero p) and observe the oscillation of R(t).
 \begin{figure}[hbtp]
@@
 
-Without interaction, the breathing mode frequency is exactly 2.
-When there is interaction, the frequency will drift to some other value near 2.
-We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behavior by Fourier transform.
-Then we take the peak frequency near 2 as the breathing mode frequency.
-The frequency measured in different E and $F_0$ is shown in the Fig.\ref{fig:Breathingfrequency1}.
+Without interaction, the breathing mode frequency is exactly 2. When there is interaction, the
+frequency will drift to some other value near 2. We measure the radius of the cloud $R(t)$ and get
+the frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak
+frequency near 2 as the breathing mode frequency. The frequency measured in different E and $F_0$ is
+shown in the Fig.\ref{fig:Breathingfrequency1}.
 
-The mechanism that deviate breathing frequency from 2 is simple in real space.
-When two particle bounce, they exchange momentum immediately.
-It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left.
-In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ .
-Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will get $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.
+The mechanism that deviate breathing frequency from 2 is simple in real space. When two particle
+bounce, they exchange momentum immediately. It can be interpret as particle A carries its momentum
+$P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$
+to the left. In this manner, every collision will save a particle some time $\frac{\sigma}{v}$
+. Since $v$ is proportional to R while the number of collision each particle experiences in one
+period of harmonic oscillation can be estimated by N, we will get $\delta\sim
+N^{\frac{3}{2}}E^{-\frac{1}{2}}$.
 
@@
 \subsection{Rotating frame in Phase-space}
-If there is a non-circular distribution cloud in phase-space, e.g., a line-shape cloud in Fig.\ref{fig:Breathingfrequency2_0}, driven by the harmonic trap, the cloud will rotate at frequency $\omega_0$.
-When there is interaction, we may think there is a small modification of the frequency $\omega=\omega_0+\delta$.
-Now we want to understand how $\delta$ is dependent on parameters, so it is better to stand in the rotating frame in the phase-space.
-In this frame, the picture we will see is as follow:\\
+If there is a non-circular distribution cloud in phase-space, e.g., a line-shape cloud in
+Fig.\ref{fig:Breathingfrequency2_0}, driven by the harmonic trap, the cloud will rotate at frequency
+$\omega_0$. When there is interaction, we may think there is a small modification of the frequency
+$\omega=\omega_0+\delta$. Now we want to understand how $\delta$ is dependent on parameters, so it
+is better to stand in the rotating frame in the phase-space. In this frame, the picture we will see
+is as follow:\\
 \begin{enumerate}[\textbf{*}]
@@
 
-\bibliography{mybib}
+%\bibliography{mybib}
+%\bibliographystyle{ieeetr}
+
+\begin{thebibliography}{1}
+
+\bibitem{Dalfovo1997}
+F.~Dalfovo, S.~Giorgini, M.~Guilleumas, L.~Pitaevskii, and S.~Stringari,
+  ``Collective and single-particle excitations of a trapped bose gas,'' {\em
+  Phys. Rev. A}, vol.~56, pp.~3840--3845, Nov. 1997.
+
+\bibitem{Jin1996}
+D.~S. Jin, J.~R. Ensher, M.~R. Matthews, C.~E. Wieman, and E.~A. Cornell,
+  ``Collective excitations of a bose-einstein condensate in a dilute gas,''
+  {\em Phys. Rev. Lett.}, vol.~77, pp.~420--423, July 1996.
+
+\bibitem{Dalfovo1999}
+F.~Dalfovo, S.~Giorgini, L.~P. Pitaevskii, and S.~Stringari, ``Theory of
+  bose-einstein condensation in trapped gases,'' {\em Rev. Mod. Phys.},
+  vol.~71, pp.~463--512, Apr. 1999.
+
+\bibitem{Stringari1996}
+S.~Stringari, ``Collective excitations of a trapped bose-condensed gas,'' {\em
+  Phys. Rev. Lett.}, vol.~77, pp.~2360--2363, Sept. 1996.
+
+\bibitem{Haller2009}
+E.~Haller, M.~Gustavsson, M.~J. Mark, J.~G. Danzl, R.~Hart, G.~Pupillo, and
+  H.-C. Nägerl, ``Realization of an excited, strongly correlated quantum gas
+  phase,'' {\em Science}, vol.~325, p.~1224, Sept. 2009.
+
+\bibitem{Guery-Odelin1999}
+D.~Gu\'ery-Odelin, F.~Zambelli, J.~Dalibard, and S.~Stringari, ``Collective
+  oscillations of a classical gas confined in harmonic traps,'' {\em Phys. Rev.
+  A}, vol.~60, pp.~4851--4856, Dec 1999.
+
+\bibitem{Tsuchiya2000}
+T.~Tsuchiya and N.~Gouda, ``Relaxation and lyapunov time scales in a
+  one-dimensional gravitating sheet system,'' {\em Phys. Rev. E}, vol.~61,
+  pp.~948--951, Jan. 2000.
+
+\bibitem{Yawn1997}
+K.~R. Yawn and B.~N. Miller, ``Ergodic properties and equilibrium of
+  one-dimensional self-gravitating systems,'' {\em Phys. Rev. E}, vol.~56,
+  pp.~2429--2436, Sept. 1997.
+
+\bibitem{Jin2013}
+F.~Jin, T.~Neuhaus, K.~Michielsen, S.~Miyashita, M.~A. Novotny, M.~I.
+  Katsnelson, and H.~D. Raedt, ``Equilibration and thermalization of classical
+  systems,'' {\em New Journal of Physics}, vol.~15, no.~3, p.~033009, 2013.
+
+\end{thebibliography}
 

### 2017-10-19 draft_02_zhiyu01.tex

--- 2017-10-18 draft_02.tex
@@
 \bibliographystyle{apsrev4-1}
+
 \usepackage{amsmath}
@@
 }
+\usepackage{epstopdf}
  \begin{document}
@@
 \begin{figure*}
-\subfigure[$t=0$]{
-\begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
-\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
-\end{minipage}
-}
-\subfigure[$t=\frac{1}{5}T$]{
-\begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=2-5T_rev.eps} 
-\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
-\end{minipage}
-}\subfigure[$t=\frac{2}{5}T$]{
-\begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
-\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
-\end{minipage}
-}\subfigure[$t=\frac{3}{5}T$]{
-\begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
-\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
-\end{minipage}
-}\subfigure[$t=\frac{4}{5}T$]{
-\begin{minipage}[b]{0.18\linewidth}
-\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
-\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
-\end{minipage}
-}
+%\subfigure[$t=0$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
+%\end{minipage}
+%}
+%\subfigure[$t=\frac{1}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{2}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{3}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{4}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
+%\end{minipage}
+%}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}
+
 \caption{N=50,F0=100,E=50000.
@@
 \begin{figure*}
-\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
-\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
-\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
-\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
-\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps} 
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
 \caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
@@
 \centering
-\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre.eps}
+\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
 \caption{dependence of breathing frequency on Energy, N=20.
-Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000.
+Different color stands for different $F_0$: Red for $F_0$=2000; Yellow for $F_0$=3000; Green for $F_0$=10000;  Blue for $F_0$=100000.
 Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
@@
 \begin{figure}
-\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
 \caption{energy of each particle, $F_0=200$}
@@
 
-\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
 \caption{energy of each particle, $F_0=1000$}

### 2017-10-24 draft_02_zhiyu02.tex
Oct_19_2017

--- 2017-10-19 draft_02_zhiyu01.tex
@@
 
-\begin{figure}[hbtp]
+\begin{figure}[h]
 \centering
@@
 
-%\begin{figure}[hbtp]
+%\begin{figure}[h]
 %\centering
@@
 zero p) and observe the oscillation of R(t).
-\begin{figure}[hbtp]
+\begin{figure}[h]
 \center
@@
 
-\begin{figure*}
+\begin{figure*}[h]
 %\subfigure[$t=0$]{
@@
 
-\begin{figure}
-\centering
-\includegraphics[scale=0.3]{ZhiyuPictures/bounce.png}
-\includegraphics[scale=0.32]{ZhiyuPictures/pass.png}
-\caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.
-\textbf{(b)} (Lower) When $F_0*\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous, their trajectory has a turning point(the dashed bright blue trajectory is identical with the one in the upper figure, which is the critical situation between passing and bouncing, that is to say, particles have zero relative velocity when they collide.) }
+\begin{figure}[h
+]
+\subfigure[]{
+\begin{minipage}[b]{0.4\textwidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/bounce.png}
+\end{minipage}
+}
+\subfigure[]{
+\begin{minipage}[b]{0.4\textwidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/pass.png}
+\end{minipage}
+}
+
+\caption{a schematic diagram of the collision process: \textbf{(a)}When $F_0\sigma$ is large, particles can not pass each other.
+Subduing to a constant repulsive force in collision, their trajectory in rotating frame is a circular arc.
+\textbf{(b)} When $F_0\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous.
+Their trajectory has a turning point.
+The dashed bright blue trajectory is identical with the one in (a), which is the critical situation between passing and bouncing.
+In that case, particles have zero relative velocity when they collide.
+}
 \label{fig:Breathingfrequency3}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 \caption{dependence of breathing frequency on Energy, N=20.
-Different color stands for different $F_0$: Red for $F_0$=2000; Yellow for $F_0$=3000; Green for $F_0$=10000;  Blue for $F_0$=100000.
-Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
+Different color stands for different $F_0$: Red for $F_0=2\times10^3$; Yellow for $F_0=3\times10^3$; Green for $F_0=1\times10^4$;  Blue for $F_0=1\times10^5$.
+Run with three different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
 The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
@@
 
-\begin{figure}
+\begin{figure}[h]
 
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
+\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_600_500_Font24.eps} 
 %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
+\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_600_500_Font24.eps} 
 %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
+\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_600_500_Font24.eps} 
 %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
@@
 \begin{minipage}[b]{0.22\textwidth}
-\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
+\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_600_500_Font24.eps} 
 %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
@@
 Here, $F_0$ is set to be 1.
-In this case, the larger $E_i$ is, the lower the beat frequency is.
+In this case, the larger the $E_i$, the lower the beat frequency.
 \label{fig:thermalization1}}%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
@@
 \includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
-\caption{evolution of single-particle energy}
+\caption{Time evolution of single-particle energy}
 \label{fig:thermalization4}
@@
 %\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
-\includegraphics[scale=0.5]{ZhiyuPictures/N=5_energydistribution_pre_rev1.eps} 
-\includegraphics[scale=0.5]{ZhiyuPictures/N=10_energydistribution_pre_rev1.eps}
-\includegraphics[scale=0.5]{ZhiyuPictures/N=20_energydistribution_pre_rev1.eps}
-\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold".
-In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
+\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
+\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
+\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
+\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, Green curves corresponds to Boltzmann distribution; Red curves are obviously non-Boltzmann, while the yellow ones are intermediate case, represent ``thermalization threshold".
+In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500\sim1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
 \label{fig:thermalization5}
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
-\caption{energy of each particle, $F_0=200$}
+%\begin{figure}
+%\subfigure[N=10, $F_0=200$]{
+%\begin{minipage}[b]{0.4\linewidth}
+%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
+%\label{fig:thermalization6}
+%\end{minipage}
+%}
+
+%\subfigure[N=10, $F_0=1000$]{
+%\begin{minipage}[b]{0.4\linewidth}
+%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
+%\label{fig:thermalization7}
+%\end{minipage}
+%}
+
+%\end{figure}
+
+\begin{figure}[h]
+\subfigure[N=10, $F_0=200$]{
+\begin{minipage}[b]{0.4\linewidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_s_400_300_Font12.eps}
 \label{fig:thermalization6}
+\end{minipage}
+}
+\subfigure[N=10, $F_0=1000$]{
+\begin{minipage}[b]{0.4\linewidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_s_400_300_Font12.eps} 
+\label{fig:thermalization7}
+\end{minipage}
+}
 
-\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
-\caption{energy of each particle, $F_0=1000$}
-\label{fig:thermalization7}
+\caption{Time evolution of the particles' energy $\epsilon$}
+
 \end{figure}
 
-As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500$-$F_0=1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
+As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500\sim1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
 As a supplementary proof of our argument, Fig.\ref{fig:thermalization6} and Fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
@@
 
-\begin{figure}[hbtp]
-\centering
-%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
-%\caption{Energy distribution, N=5, F0=10000}
-%\label{fig:thermalization8}
+%\begin{figure*}
+%%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
+%%\caption{Energy distribution, N=5, F0=10000}
+%%\label{fig:thermalization8}
+%\subfigure[N=10, $F_0=1\times10^4$]{
+%\begin{minipage}[b]{0.1\textwidth}
+%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
+%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
+%\label{fig:thermalization9}
+%\end{minipage}
+%}
 
-\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
-\caption{Energy distribution, N=10, F0=10000}
+%\subfigure[N=20, $F_0=1\times10^4$]{
+%\begin{minipage}[b]{0.1\textwidth}
+%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
+%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
+%\label{fig:thermalization10}
+%\end{minipage}
+%}
+
+%\end{figure*}
+
+\begin{figure}[h]
+\subfigure[N=10, $F_0=1\times10^4$]{
+\begin{minipage}[b]{0.4\linewidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=10_F=10000_500_400_Font16.eps}
 \label{fig:thermalization9}
+%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
+\end{minipage}
+}
+\subfigure[N=20, $F_0=1\times10^4$]{
+\begin{minipage}[b]{0.4\linewidth}
+\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=20_F=10000_500_400_Font16.eps} 
+\label{fig:thermalization10}
+%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
+\end{minipage}
+}
 
-\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
-\caption{Energy distribution, N=20, F0=10000}
-\label{fig:thermalization10}
+\caption{Fitting energy distribution $\rho(\epsilon)$ with Boltzmann distribution}
+
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s.eps}
+\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s_1100_600_Font18.eps}
 \caption{Distribution in phase-space after evolving for about 500 time units ($N=50, F_0=1000, E=30000$).
@@
 Red ellipse is the shape of cloud in low-energy regime when there is repulsive interaction.
-Gray cloud is the imaginary shape of cloud when there is no interaction, they are plotted here as a reference.
+Gray cloud is the imaginary shape of cloud when there is no interaction, which is plotted here as a reference.
 One may think of the effect of interaction as a kind of potential that prefer to place particles along x axis, because in low energy regime the system is not allowed to be squeezed too much along x axis since doing this cost a large amount of interaction energy.}\label{fig:Schemetic_description_of_the_mode}
@@
 
-\begin{comment}
-\section{others(those I haven't organized it into the text in logical order but may be useful)}
+%\begin{comment}
+%\section{others(those I haven't organized it into the text in logical order but may be useful)}
 
-\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
-Results are shown in Fig.\ref{fig:others1}
+%\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
+%Results are shown in Fig.\ref{fig:others1}
 
-\begin{figure}[hbtp]
+%\begin{figure}[h]
 
-\centering
-\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
-\caption{fluctuation of R with time }
-sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
-\label{fig:others1}
-\end{figure}
+%\centering
+%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
+%\caption{fluctuation of R with time }
+%sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
+%\label{fig:others1}
+%\end{figure}
 
-\subsection{Detailed discussion of two-particle motion}
-{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization".
+%\subsection{Detailed discussion of two-particle motion}
+%{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization".
 But then I found we haven't used these result.
@@
 
-From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system.
+%From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system.
 In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame.
@@
 
-Now, let's consider the interaction between them.
+%Now, let's consider the interaction between them.
 Because of interaction, the potential curve between $+-\frac{\sigma}{2}$ should be modified to another parabolic curve that simultaneously satisfies the following two condition:\\
-1) intersect with black curve at $+-\frac{\sigma}{2}$\\
-2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
-Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
-1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
-2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
-3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
-For those three types of curve, the significant difference is only at low energy case:\\
-For the red one, particle will oscillate at constant frequency $\omega$;
-For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
-For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.
+%1) intersect with black curve at $+-\frac{\sigma}{2}$\\
+%2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
+%Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
+%1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
+%2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
+%3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
+%For those three types of curve, the significant difference is only at low energy case:\\
+%For the red one, particle will oscillate at constant frequency $\omega$;
+%For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
+%For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.
 
-\begin{figure}
-\subfigure[]{
-\begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
-\end{minipage}
-}
-\subfigure[]{
-\begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
-\end{minipage}
-}
-\subfigure[]{
-\begin{minipage}[b]{0.3\textwidth}
-\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
-\end{minipage}
-}
-\centering
-\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
-\label{fig:thermalization3}
-\end{figure}
-\end{comment}
+%\begin{figure}
+%\subfigure[]{
+%\begin{minipage}[b]{0.3\textwidth}
+%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
+%\end{minipage}
+%}
+%\subfigure[]{
+%\begin{minipage}[b]{0.3\textwidth}
+%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
+%\end{minipage}
+%}
+%\subfigure[]{
+%\begin{minipage}[b]{0.3\textwidth}
+%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
+%\end{minipage}
+%}
+%\centering
+%\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value %of $\frac{F_0}{m\omega_0^2\sigma}$
+%\label{fig:thermalization3}
+%\end{figure}
+%\end{comment}
 

### 2017-11-30 draft_04.tex
edited first (preparatory) section

--- 2017-10-24 draft_02_zhiyu02.tex
@@
 }
+
  \usepackage{epstopdf}
+
 \begin{document}
@@
  \affiliation{Fudan University, Shanghai, China}
+
+\date{\today}
 
@@
 \section{Introduction}
+
+Will write Introduction after everything else is written.
+
+---------
+
+Stat-mech from the `bottom up'.  Find papers that do the same.
+
+More detailed citations of breathing mode.  There are also papers on classical breathing mode, e.g.,
+by Bonitz.
 
@@
 thermalization time scales from the perspective of canonical distribution as well as Lyapunov
-exponent. %With these approaches, we will show that the thermalization time scale manifest a
+exponent.
+
+%With these approaches, we will show that the thermalization time scale manifest a
 %competition between total energy and interaction energy, so there is not any singular
@@
 
-This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
-reduce the number of parameters of the system. In addition, we briefly observe the ground state and
-reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak
-interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing
-frequency according to its mechanism, and compare that with our numerical simulation
-result. Besides, we also introduce a rotating frame method of treating this problem, which is a
-convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we
-focus on the thermalization property. We first examine the canonical distribution of energy to find
-out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very
-large. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and
-confirm the former discussion. Then we point out that there are two kind of thermalization behavior
-that could be measured in this system, one is about energy distribution while another is about shape
-of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
--- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
-when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
-it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
-the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
-discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
+------------------
 
-\section{Preparation}\label{section:preparation}
-\subsection{Scaling behaviour}
-We investigated the classical gas in harmonic trap with a repulsive interaction. We chose one of the simplest types of interaction:
-\begin{equation}
-F=\left\lbrace
-\begin{aligned}
-&F=F_0 	&,x\textless\sigma\\
-&F=0 	&,x\textgreater\sigma
-\end{aligned}
-\right.
-\label{eq:preparation1}
-\end{equation}
-so the Hamiltonian is
-\begin{equation}
-H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
-\label{eq:preparation2}
-\end{equation}
-
-Using the transformation Eq.\ref{eq:transform}, we can rewrite Eq.\ref{eq:preparation2} into the following form:
-\begin{equation}
-\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
-\end{equation}
-\begin{equation}
-\left\lbrace
-\begin{aligned}
-&\tilde{H}&=&\frac{H}{m\omega_0^2\sigma^2}\\
-&\tilde{x_i}&=&\frac{x_i}{\sigma}\\
-&\tilde{t}&=&\omega_0t\\
-&\tilde{F_0}&=&\frac{F_0}{m\omega_0^2\sigma}\\
-\end{aligned}
-\right.
-\label{eq:transform}
-\end{equation}
-
-In this manner, we reduced the number of the parameters in our model to three: $\tilde{H}$,
-$\tilde{F_0}$, $N$. Equivalently, we set $\sigma$, $\omega_0$ and $m$ to 1 in our numerical
-simulation. Throughout, we will use ``E" and ``$F_0$" to denote their reduced version $\tilde{H}$,
-$\tilde{F_0}$.
-
-\subsection{Overview}
-\subsubsection{Relation between Radius and Energy}
-The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$
-\begin{equation}
-R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2}
-\label{eq:def_of_R}
-\end{equation}.
-When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators.
-Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$
-
-\subsubsection{Ground states}
-
-For the ground state of this system, one could make the following prediction: \\(1) When the
-$\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is
-equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground
-state is a solid-like state, where each particle keeps an equal distance ($\frac{2F_0}{\omega_0^2}$)
-with its nearest neighbors . The low-lying excitation is particles' independent harmonic oscillation
-around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore
-gas, while the size of particle is just $\sigma$.
-
-In the Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the ``hardcore gas" limit (right).
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
-\caption{particles' position at ground states }
-\label{fig:GS1}
-\end{figure}
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
-%\caption{ground state Energy with $F_0$}
-%\end{figure}
-%\end{comment}
-
-\section{Breathing Frequency}\label{section:breathing frequency}
+Breathing frequency
 
@@
 cloud before the quench is an ellipse while the final one is a circle.
+
+------------------
+
+This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
+reduce the number of parameters of the system. In addition, we briefly observe the ground state and
+reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak
+interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing
+frequency according to its mechanism, and compare that with our numerical simulation
+result. Besides, we also introduce a rotating frame method of treating this problem, which is a
+convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we
+focus on the thermalization property. We first examine the canonical distribution of energy to find
+out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very
+large. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and
+confirm the former discussion. Then we point out that there are two kind of thermalization behavior
+that could be measured in this system, one is about energy distribution while another is about shape
+of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
+-- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
+when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
+it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
+the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
+discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
+
+\section{The model and its equilibrium properties}\label{section:preparation}
+
+\subsection{Model and Scaling}
+
+Our model for the interacting classical gas involves particles with a simple finite-range repulsive
+interaction.  Two particles repel each other whenever they are within a distance $\sigma$ from each
+other.  The force of repulsion is a constant, $F_0$, within this distance and zero when the distance
+is larger. 
+%
+\begin{equation}
+F(|x|) ~=~ \begin{cases}
+F_0  &\quad |x|<\sigma\\
+0  &\quad |x|>\sigma
+\end{cases}
+\label{eq:preparation1}
+\end{equation}
+where $|x|$ is the distance between two particles.  This equation describes the magnitude of the
+interparticle force; the direction is always repulsive.
+
+The gas contains $N$ such identical particles, each of mass $m$, in a harmonic trap.  The
+Hamiltonian describing the gas is 
+\begin{equation}
+H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i
+v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
+\label{eq:preparation2}
+\end{equation}
+%
+It is useful to rescale the quantities, and measure distance, time, energy and force in units of
+$\sigma$, $1/\omega$, $m\omega_0^2\sigma^2$ and $m\omega_0^2\sigma$ respectively:
+\begin{equation} \label{eq:transform}
+  \tilde{x_i} = \frac{x_i}{\sigma}\ , \quad 
+  \tilde{H} = \frac{H}{m\omega_0^2\sigma^2}\ ,  \quad \tilde{t} = \omega_0t \ ,  \quad 
+\tilde{F_0} = \frac{F_0}{m\omega_0^2\sigma}\ .
+\end{equation}
+%
+Eq.~\ref{eq:preparation2} is then rewritten as
+\begin{equation}
+\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
+\end{equation}
+%
+Through this rescaling, we have reduced the number of the parameters in our model to three: the
+energy $\tilde{H}$, the interaction strength $\tilde{F_0}$, and the number of particles $N$.  The
+rescaling is equivalent to setting $\sigma$, $\omega_0$ and $m$ to $1$; this is what we do in our
+numerical simulation.  In the rest of this paper, we will use ``E" and ``$F_0$" to denote the
+reduced versions $\tilde{H}$ and $\tilde{F_0}$.
+
+We will be concerned with the size of the cloud, which we quantify through the root-mean-square of
+particle positions  $\left\lbrace x_i\right\rbrace$
+\begin{equation}
+R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2}
+\label{eq:def_of_R}
+\end{equation}
+and refer to as the `radius' or `cloud radius'.
+
+In the parameter regime where the energy $E$ is very large ($E\gg F_0$), it is dominated by the trap
+energy, i.e., the interaction energy is negligible.  Thus,
+$E\approx\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$ in this regime
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
+\caption{The ground state of a system with $N=5$ particles, shown via the positions of the
+  particles.  At large interactions, the particles position themselves just outside the range of
+  interactions of the neighboring particles.}
+\label{fig:GS1}
+\end{figure}
+
+%\begin{figure}[h]
+%\centering
+%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
+%\caption{ground state Energy with $F_0$}
+%\end{figure}
+%\end{comment}
+
+\subsection{Ground states}
+
+The lowest-energy state of the system has zero kinetic energy; in this state the particles find
+stationary positions which minimize the trap (potential) and interaction energies.  The trap
+potential tries to squeeze the particles at the trap center, while the interaction tries to push
+them apart.
+
+Because of the `Heaviside theta' form of our interaction, at large enough interactions (large $F_0$)
+the particles are spaced exactly at distance equal to the range $\sigma$, which is distance $1$ in
+our rescaled units.  The interaction is effectively a `hard-core' interaction.
+
+At smaller $F_0$, the energy is minimized by having the particles approximately equidistant, at
+distance $\approx 2F_0/\omega_0^2$ from each other.  In this `solid'-like state, the low-lying
+excitation involves independent oscillation of the particles around their equilibrium position.
+
+In the Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
+``hardcore gas" limit (right).
+
+\section{Breathing Frequency}\label{section:breathing frequency}
 
@@
 }
-
 \caption{a schematic diagram of the collision process: \textbf{(a)}When $F_0\sigma$ is large, particles can not pass each other.
@@
 
-\caption{the dependence of beat frequency on internal energy.
-The diagram is the energy of two particles.
-Here, $F_0$ is set to be 1.
-In this case, the larger the $E_i$, the lower the beat frequency.
-\label{fig:thermalization1}}%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
+\caption{the dependence of beat frequency on internal energy. The diagram is the energy of two
+  particles. Here, $F_0$ is set to be 1. In this case, the larger the $E_i$, the lower the beat
+  frequency. \label{fig:thermalization1}}
+%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a
+%beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
 
@@
 
-\begin{figure*}
+\begin{figure*}[h]
 \subfigure[$N=20, F_0=1000, E=3000$]{
@@
 
-\begin{figure*}
+\begin{figure*}[h]
 \centering

### 2017-12-01 draft_04.tex
edited first (preparatory) section

@@
 
+\subsection{Phase space snapshots}
+
+\begin{figure*}[h]
+%\subfigure[$t=0$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
+%\end{minipage}
+%}
+%\subfigure[$t=\frac{1}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{2}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{3}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
+%\end{minipage}
+%}\subfigure[$t=\frac{4}{5}T$]{
+%\begin{minipage}[b]{0.18\linewidth}
+%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
+%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
+%\end{minipage}
+%}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}
+
+\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the
+  cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$,
+  $\frac{4}{5}T$, $T$ respectively.
+WHAT IS T?
+}
+\label{fig:Breathingfrequency2_0}
+\end{figure*}
+
+\begin{figure*}
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
+%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
+\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
+\label{fig:Breathingfrequency2_1}
+\end{figure*}
+
+A very useful way to visualize the state and evolution of the gas is to plot the position and
+momentum of each particle, i.e., to plot the locations of the particles in the single-particle phase
+space.  This will be useful for visuualizing both the breathing mode and relaxation.
+
+Figures \ref{fig:Breathingfrequency2_0} and \ref{fig:Breathingfrequency2_1} show such phase space
+snapshots.
+
 \section{Breathing Frequency}\label{section:breathing frequency}
@@
 Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
-
-\begin{figure*}[h]
-%\subfigure[$t=0$]{
-%\begin{minipage}[b]{0.18\linewidth}
-%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
-%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
-%\end{minipage}
-%}
-%\subfigure[$t=\frac{1}{5}T$]{
-%\begin{minipage}[b]{0.18\linewidth}
-%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
-%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
-%\end{minipage}
-%}\subfigure[$t=\frac{2}{5}T$]{
-%\begin{minipage}[b]{0.18\linewidth}
-%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
-%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
-%\end{minipage}
-%}\subfigure[$t=\frac{3}{5}T$]{
-%\begin{minipage}[b]{0.18\linewidth}
-%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
-%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
-%\end{minipage}
-%}\subfigure[$t=\frac{4}{5}T$]{
-%\begin{minipage}[b]{0.18\linewidth}
-%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
-%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
-%\end{minipage}
-%}
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}
-
-\caption{N=50,F0=100,E=50000.
-Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
-\label{fig:Breathingfrequency2_0}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
-%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
-%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
-%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
-%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps}
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
-\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
-\label{fig:Breathingfrequency2_1}
-\end{figure*}
 

### 2017-12-04 draft_05.tex
working on the breathing mode section

--- 2017-11-30 draft_04.tex
@@
 
-Breathing frequency
+Breathing frequency, comparisong to quantum case ------
 
@@
 %
-It is useful to rescale the quantities, and measure distance, time, energy and force in units of
-$\sigma$, $1/\omega$, $m\omega_0^2\sigma^2$ and $m\omega_0^2\sigma$ respectively:
+It is useful to rescale the quantities.  We will measure distance, time, energy and force in units
+of $\sigma$, $1/\omega$, $m\omega_0^2\sigma^2$ and $m\omega_0^2\sigma$ respectively:
 \begin{equation} \label{eq:transform}
@@
 \begin{equation}
-\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
+\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}_i}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
 \end{equation}
@@
 energy, i.e., the interaction energy is negligible.  Thus,
-$E\approx\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$ in this regime
+$E\approx\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$ in this regime.
 
@@
 \includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
-\caption{The ground state of a system with $N=5$ particles, shown via the positions of the
-  particles.  At large interactions, the particles position themselves just outside the range of
-  interactions of the neighboring particles.}
+\caption{The ground state of a system with $N=5$ particles, shown via the positions of each
+  particle, labeled 1 through 5.  At large interactions, the particles position themselves just
+  outside the range of interactions of the neighboring particles.}
 \label{fig:GS1}
@@
 stationary positions which minimize the trap (potential) and interaction energies.  The trap
-potential tries to squeeze the particles at the trap center, while the interaction tries to push
+potential tries to squeeze the particles towards the trap center, while the interaction tries to push
 them apart.
@@
 the particles are spaced exactly at distance equal to the range $\sigma$, which is distance $1$ in
-our rescaled units.  The interaction is effectively a `hard-core' interaction.
+our rescaled units.  The interaction is then effectively a `hard-core' interaction.
 
@@
 
-In the Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
+In Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
 ``hardcore gas" limit (right).
 
-\section{Breathing Frequency}\label{section:breathing frequency}
+\subsection{Phase space snapshots}
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure*}[h]
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}
+%
+\caption{Upper (lower) panels are snapshots of the cloud configuration in phase space in the
+  stationary (rotating) frame, at instants within the first trap period.  Here $N=50$, $F_0=100$,
+  and $E=50000$.  }
+\label{fig:Breathingfrequency2_0}
+\end{figure*}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
+\caption{Phase space snapshots of the cloud dynamics viewed in the rotating frame, at longer
+  timescales.}
+\label{fig:Breathingfrequency2_1}
+\end{figure*}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+A useful way to visualize the state and evolution of the gas is to plot the position and momentum of
+each particle, i.e., to plot the locations of the particles in the single-particle phase space.
+This will be useful for visualizing both the breathing mode and relaxation.
+
+Figures \ref{fig:Breathingfrequency2_0} and \ref{fig:Breathingfrequency2_1} show such phase space
+snapshots.  We generally start with particles distributed at random positions around the trap
+center, initially with no velocity (zero momentum).  The initial state thus has the points lined up
+along the $X$ axis.  In the absence of interactions, each particle would undergo simple harmonic
+oscillation with period $T=2\pi/\omega_0 = 2\pi$.  The point corresponding to each particle than
+executes clockwise elliptical motion around in the $X$-$P$ plane.  (In our units, the elliptical
+trajectory is actually circular.)  This results in the initial line remaining a straight line and
+rotating clockwise with exact period $T$.  The effect of interaction is to smear out the line and
+spread the points out toward a rotationally invariant distribution in the  $X$-$P$ plane.  The top
+panel of Figure  \ref{fig:Breathingfrequency2_0} shows this during the first period and Figure
+\ref{fig:Breathingfrequency2_1} shows this process over a much longer timescale.
+
+Since the rotation of the initial line of points is simple to understand as a single-particle
+(non-interacting) effect, we can focus on interaction effects by viewing the phase space in a
+`rotating' frame.  The rotating frame is used in the lower panel of Figure
+\ref{fig:Breathingfrequency2_0} and in Figure \ref{fig:Breathingfrequency2_1}.  In this picture, the
+`real' $X$ and $P$ axes are rotating counter-clockwise.  This rotating frame picture may be regarded
+as a classical version of the ``interaction picture'' of quantum dynamics.  This picture highlights
+effects of interactions because the other effects are already encoded in the frame rotation.
+
+In the absence of interactions, each point (each particle) is stationary in the rotating-frame
+phase-space picture.  As seen in lower panel of Figure \ref{fig:Breathingfrequency2_0} and in Figure
+\ref{fig:Breathingfrequency2_1}, interactions cause a gradual distortion of the line as well as some
+degree of rotation.
+%
+The rotation that is visible in the already rotating $X_{\rm rot}$-$P_{\rm rot}$ frame is the
+interaction-induced shift of the breathing frequency from the noninteracting value,
+$\omega=2\omega_0$.  The distortion of the line toward an eventually rotationally invariant
+distribution may be regarded as thermalization or ergodicity.  In the next sections we explore these
+two interaction-induced effects.
+
+\subsection{Numerical calculations}
 
@@
 zero p) and observe the oscillation of R(t).
+
+\section{Breathing Frequency}\label{section:breathing frequency}
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}[h]
@@
 \includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
-\caption{breathing mode frequency measured at different E and $F_0$.
-Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behavior of radius R(t) defined in Eq.\ref{eq:def_of_R}.
-The breathing frequency is measured by taking Fourier transformation of R(t).}
+\caption{Breathing mode frequency measured at different $E$ and $F_0$. Inset: a demonstration of the
+  oscillation of $E_{trap}$, the total potential energy of particles in the trap, Since
+  $E_{trap}\propto \sum_{is}{x_i^2}$, it manifests the oscillation behavior of the radius $R(t)$ as
+  defined in Eq.~\ref{eq:def_of_R}.  The breathing frequency is obtained from the Fourier transform
+  of $R(t)$.}
 \label{fig:Breathingfrequency1}
 \end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
-Without interaction, the breathing mode frequency is exactly 2. When there is interaction, the
-frequency will drift to some other value near 2. We measure the radius of the cloud $R(t)$ and get
-the frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak
-frequency near 2 as the breathing mode frequency. The frequency measured in different E and $F_0$ is
-shown in the Fig.\ref{fig:Breathingfrequency1}.
+We are interested in the oscillations of the size $R(t)$ of the cloud.  It is convenient that our
+finite-size simulations start with a line distribution in phase space.  If we started with a state
+whose configuration in phase-space is only slightly different from a circle, the oscillating
+amplitude would be too small to be distinguished from noise.
 
-The mechanism that deviate breathing frequency from 2 is simple in real space. When two particle
-bounce, they exchange momentum immediately. It can be interpret as particle A carries its momentum
-$P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$
-to the left. In this manner, every collision will save a particle some time $\frac{\sigma}{v}$
-. Since $v$ is proportional to R while the number of collision each particle experiences in one
-period of harmonic oscillation can be estimated by N, we will get $\delta\sim
-N^{\frac{3}{2}}E^{-\frac{1}{2}}$.
+Without interaction, the breathing mode frequency is exactly 2.  This is visualized readily from the
+top panel of \ref{fig:Breathingfrequency2_0}, where $R(t)$ is the extent of the distribution in the
+horizontal ($X$) direction.  As the line rotates clockwise with frequency $\omega=1$, within each
+period the line is twice horizontally aligned (maximum $R$) and twice vertically aligned (minimum
+$R$), so that the frequency of $R(t)$ is $\omega_0=2$.  When there is interaction, the frequency
+will get shifted: $\omega_0 = 2+\delta$.  We measure the radius of the cloud $R(t)$ and get the
+frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak frequency
+near 2 as the breathing mode frequency.
+
+The frequency measured in this way for different $E$ and $F_0$ is shown in the
+Fig.\ref{fig:Breathingfrequency1}, plotted as a function of $F_0$.  The points each correspond to
+breathing-mode dynamics following from a single initial state; there is no averaging.  The curves
+therefore show some randomness.  However, two prominent features are clear from these curves.  At
+large interactions, $F_0\gg E$, the breathing frequency is larger than $2$, and saturates around a
+value which decreases with the system energy $E$.  At small interactions, the breathing frequency is
+actually smaller than the non-interacting value $2$.
+
+Below, we will provide a detailed phase-space argument for these behaviors.  However, a simple
+real-space picture explains both effects qualitatively as well.  For very large $F_0$, when the
+interaction is `hard-core'-like, two particles exchange momentum immediately at a collision.  By
+exchanging the labels of the particles during the collision, this can be interpreted as follows:
+particle $A$ carrying momentum $P_A$ jumps by distance $\sigma$ to the right, while particle $B$
+carries its momentum $P_B$ and jumps by distance $\sigma$ to the left.  In this manner, every
+collision will save a particle some time, $\frac{\sigma}{v}$.  This translates into an increase of
+the breathing frequency.  The speed $v$ per particle is on average $\sim\sqrt{E/N}$, and the number
+of collision each particle experiences in one period of harmonic oscillation is $\sim N$; hence we
+obtain $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.  When $F_0$ is smaller, we can no longer think
+of the particles as hard rods; the collisions now take finite time during which the speeds of the
+particles are actually slowed down and then sped up again, as they either cross paths or bounce from
+each other.  When $F_0$ is small enough, this approaching time will at some critical value of $F_0$
+consume the time saved by the finite range of the interaction.  This explains why there is a
+small-$F_0$ regime for which the shift $\delta$ is negative.
+
+---------
 
@@
 
-This rotating frame picture is actually a classical version of the interaction picture, which turns out to symplifly our dynamic analysis.
-The stationary frame and rotating frame is shown in Fig.\ref{fig:Breathingfrequency2_1}.
-
 In our system, we choose initial velocity to be zero, which means, the particles are aligned on $X|_{t=0}$ axis in phase-space at the beginning.

### 2017-12-05 draft_05.tex
working on the breathing mode section

@@
 
-In the parameter regime where the energy $E$ is very large ($E\gg F_0$), it is dominated by the trap
-energy, i.e., the interaction energy is negligible.  Thus,
-$E\approx\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$ in this regime.
+In the dilute gas limit, there are few or no interactions occuring at most times.  Thus the energy
+$E$ is dominated by the trap energy, i.e., $E\approx m\omega_0^2\sum_{i}x_i^2= Nm\omega_0^2R^2$, or,
+in our units, $E\approx NR^2$.
 
@@
 \caption{Phase space snapshots of the cloud dynamics viewed in the rotating frame, at longer
-  timescales.}
+  timescales.  The broadening and rotation observed here are interaction effects: in the
+  non-interacting gas the particles are stationary in this frame.}
 \label{fig:Breathingfrequency2_1}
@@
 \includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
-\caption{Breathing mode frequency measured at different $E$ and $F_0$. Inset: a demonstration of the
-  oscillation of $E_{trap}$, the total potential energy of particles in the trap, Since
-  $E_{trap}\propto \sum_{is}{x_i^2}$, it manifests the oscillation behavior of the radius $R(t)$ as
-  defined in Eq.~\ref{eq:def_of_R}.  The breathing frequency is obtained from the Fourier transform
-  of $R(t)$.}
+\caption{Breathing mode frequency measured at different $E$ and $F_0$, for $N=5$ particles. Inset: a
+  demonstration of the oscillation of $E_{trap}$, the total potential energy of particles in the
+  trap, Since $E_{trap}\propto \sum_{is}{x_i^2}$, it manifests the oscillation behavior of the
+  radius $R(t)$ as defined in Eq.~\ref{eq:def_of_R}.  The breathing frequency is obtained from the
+  Fourier transform of $R(t)$.}
 \label{fig:Breathingfrequency1}
@@
 period the line is twice horizontally aligned (maximum $R$) and twice vertically aligned (minimum
-$R$), so that the frequency of $R(t)$ is $\omega_0=2$.  When there is interaction, the frequency
-will get shifted: $\omega_0 = 2+\delta$.  We measure the radius of the cloud $R(t)$ and get the
+$R$), so that the frequency of $R(t)$ is $\omega_B=2$.  When there is interaction, the frequency
+will get shifted: $\omega_B = 2+\delta$.  We measure the radius of the cloud $R(t)$ and get the
 frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak frequency
@@
 
----------
-
-To see this picture better, let us first introduce a approach to simplify this problem:
-
-\subsection{Rotating frame in Phase-space}
-If there is a non-circular distribution cloud in phase-space, e.g., a line-shape cloud in
-Fig.\ref{fig:Breathingfrequency2_0}, driven by the harmonic trap, the cloud will rotate at frequency
-$\omega_0$. When there is interaction, we may think there is a small modification of the frequency
-$\omega=\omega_0+\delta$. Now we want to understand how $\delta$ is dependent on parameters, so it
-is better to stand in the rotating frame in the phase-space. In this frame, the picture we will see
-is as follow:\\
-\begin{enumerate}[\textbf{*}]
-\item All particles are stationary when there is no interaction.
-\item The real X and P axis are rotating counter-clockwise, using real X axis to measure distance between particles to determine the interaction at each moment.
-\item When there is interaction, particles will gain a ``velocity" in phase space: $\dot{P}=F/m$ . Other effects are all cancelled by frame rotation.
-\end{enumerate}
-
-In our system, we choose initial velocity to be zero, which means, the particles are aligned on $X|_{t=0}$ axis in phase-space at the beginning.
-If the breathing frequency of the system is $\omega=\omega_0+\delta$, we will expect to see a line (which may gradually deform into an oval cloud or even an isotropic cloud) rotating at $\delta$ in rotating frame.
-Since the motion we see is an additional rotation in rotating frame, we will call it precession.
-This precession directly leads to the $\delta$ shift in breathing frequency.
-Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.
-
-\subsection{Estimating Breathing Frequency}
-Let us begin with two-particle case.
-When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$.
-In the rotating frame in phase-space, this process can be interpret as follows:
-
+\subsection{Phase space estimate}
+
+Since we are interested in the deviation $\delta=\omega_B-2$ from the non-interacting breathing
+frequency, it is useful to work in the rotating frame, in which a non-interacting cloud would be
+stationary (non-rotating).  The rotation frequency of the cloud in this frame is then $\delta$.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}[h
@@
 \end{figure}
-
-(See Fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which deviate a small angle $\alpha$ away from original configuration.
-Similar process happen when there are more particles.
-In every period of harmonic oscillation, each particle meet N particles and collide 2N times, while half of the collisions (N times) are between particles with huge difference in momentum, which is just the process shown in Fig.\ref{fig:Breathingfrequency3}.
-(As for the remaining half of collisions, colliding particles have small difference in their momentum.
-Let us say, both particles have positive momentum.
-In Fig.\ref{fig:Breathingfrequency3}, it can be shown that two particles on the same half of the P-axis seldom contribute to the rotation of distribution.)
-
-Let us estimate the precession angle $\alpha$ in one collision event by $\frac{\sigma}{R}$, which follows from the two-particle case study.
-Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
-We will get the precession angular velocity 
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+To analyze the rotation relative to the $X_{\rm rot}$-$P_{\rm rot}$ frame, we consider two-particle
+collisions.  In Figure \ref{fig:Breathingfrequency3}(a), we show schematics of such a collision near
+the trap center at strong interactions.  For very large $F_0$, the particles simply change momentum
+when they are at distance $\sigma$ from each other; this process is shown in red as two straight
+lines.  (The particles are initially at $X=\pm\frac{1}{2}\sigma$ and remain at these $X$ values,
+but exchange their momenta.)   For smaller $F_0$, there is change of both position and momentum, as shown in yellow, green
+and blue for successively weaker interactions. The blue line shows a case where $F_0$ is smaller
+enough such that the particles can actually cross each other.
+
+In Figure \ref{fig:Breathingfrequency3}(a) we show collisions for small $F_0$, so that the particles
+pass each other.  in the $X_{\rm rot}$-$P_{\rm rot}$ plane, this is seen as a turning point in the trajectory.
+
+We now estimate $\delta$ at large $F_0$.  The relevant collision process is that shown by the red
+lines in Figure \ref{fig:Breathingfrequency3}(a).  The two particles, which are initially on the
+$X_{\rm rot}$ axis, are moved to two other points, on the thick gray line, which deviates a small
+angle $\alpha$ away from original configuration.  In every period of the harmonic oscillation, each
+particle meets each of the other particles twice.  Half of these collisions (about $N$ collision)
+are between particles with large difference in momentum, which is the process shown in
+Fig.\ref{fig:Breathingfrequency3}.  (As for the remaining half of the collisions, colliding
+particles have smaller difference in their momentume, e.g., both particles having positive
+momentum.  In this estimate we  ignore the effects of these collisions, as they clearly contribute
+far less to the rotation of the particle distribution.)
+
+The precession angle is $\alpha\sim \sigma/P$.  In our rescaled units, the momenta that the
+particles have near $x=0$ are of the order $R$, the size of the cloud.  (In phase space $R$ can be
+interpreted either as the extent in real space when the velocities are small, or as the extent in
+momentum space when the particles approach $x=0$, i.e. when the distribution is along the $P$
+direction.)  Thus, we can estimate  $\alpha\sim \sigma/R$, i.e.,   $\alpha\sim 1/R$, since our unit
+of length is $\sigma$.  This is the rotation per unit collision.  Since there are $\sim N$
+collistions per period $T=2\pi$, we have the estimate for the interaction-induced rotation per unit
+time as
 \begin{equation}
-\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
+\delta ~=~ 2 \frac{N}{2\pi} \frac{1}{R} ~=~  \frac{1}{\pi}  N^{3/2}E^{-1/2}
 \label{eq:breathingfrequency1}
 \end{equation}
+The factor $2$ accounts for the fact that each rotation of the elongated cloud in phase space
+corresponds to two breathing mode periods.  In the last step we have used the estimate $E\sim
+NR^2$.
+
+---------
+
+%% \subsection{Estimating Breathing Frequency}
+
+%% Let us begin with two-particle case. When interaction is very strong, the effect of interaction is
+%% equivalent to exchanging momentum when two particles approach each other at distance $\sigma$. In
+%% the rotating frame in phase-space, this process can be interpret as follows:
+
+%% (See Fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which
+%% deviate a small angle $\alpha$ away from original configuration. Similar process happen when there
+%% are more particles. In every period of harmonic oscillation, each particle meet N particles and
+%% collide 2N times, while half of the collisions (N times) are between particles with huge difference
+%% in momentum, which is just the process shown in Fig.\ref{fig:Breathingfrequency3}. (As for the
+%% remaining half of collisions, colliding particles have small difference in their momentum. Let us
+%% say, both particles have positive momentum. In Fig.\ref{fig:Breathingfrequency3}, it can be shown
+%% that two particles on the same half of the P-axis seldom contribute to the rotation of
+%% distribution.)
+
+%% Let us estimate the precession angle $\alpha$ in one collision event by $\frac{\sigma}{R}$, which
+%% follows from the two-particle case study. Radius of the cloud R can be estimated according to
+%% $E=Nm\omega_0^2R^2$ We will get the precession angular velocity
+%% \begin{equation}
+%% \delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
+%% \label{eq:breathingfrequency1}
+%% \end{equation}
 

### 2017-12-05 draft_05.tex
almost done with breathing mode section

@@
 \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
- \author{Zhiyu}
- \affiliation{Fudan University, Shanghai, China}
+
+\author{
+Zhiyu Dong,$^{1,2}$
+R. Moessner,$^2$
+and Masudul Haque$^{2,3}$}
+
+\affiliation{
+  $^1$ Fudan University, Shanghai, China\\ 
+  $^2$ Max Planck Institute for the Physics of Complex Systems, N{\"o}thnitzer Str.~38, 01187 Dresden, Germany\\
+  $^3$ Department of Theoretical Physics, Maynooth University, Co. Kildare, Ireland
+}
 
@@
 \begin{equation}
-F(|x|) ~=~ \begin{cases}
+\Big| F(|x|) \Big| ~=~ \begin{cases}
 F_0  &\quad |x|<\sigma\\
@@
 \begin{equation}
-\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}_i}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
+  \tilde{H} =
+  \frac{1}{2}\sum_{i}\tilde{x_i}^2
+  + \frac{1}{2}\sum_i\left(\frac{d\tilde{x}_i}{d\tilde{t}}\right)^2 
+  + \sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless
+    1}\tilde{F}_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)  
 \end{equation}
@@
 
-We will be concerned with the size of the cloud, which we quantify through the root-mean-square of
-particle positions  $\left\lbrace x_i\right\rbrace$
+We will be concerned with the size of the cloud.  We quantify the size through the root-mean-square
+of particle positions $\left\lbrace x_i\right\rbrace$, 
 \begin{equation}
-R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2}
+R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2} \, ,
 \label{eq:def_of_R}
 \end{equation}
-and refer to as the `radius' or `cloud radius'.
+and refer to this quantity as the `radius' or `cloud radius'.
 
@@
 $E$ is dominated by the trap energy, i.e., $E\approx m\omega_0^2\sum_{i}x_i^2= Nm\omega_0^2R^2$, or,
-in our units, $E\approx NR^2$.
-
+in our units,
+\begin{equation}
+  E\approx NR^2 \, .
+  \label{eq:E_and_R}
+\end{equation}
+This is a good approximation at large $F_0$ because, for very large interactions, the particles
+behave has hard rods which bounce off each other very rapidly, so that at most instants one can
+expect no collisions to be taking place.  It is also expected to be a good approximation at very
+small $F_0$ since we can then simply neglect the interaction energy.  Thus, we will use this as a common
+estimate for $R$ in terms of the energy.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}[tbhp]
@@
 \end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
@@
 
-At smaller $F_0$, the energy is minimized by having the particles approximately equidistant, at
+At very small $F_0$, the energy is minimized by having the particles approximately equidistant, at
 distance $\approx 2F_0/\omega_0^2$ from each other.  In this `solid'-like state, the low-lying
@@
 In Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
-``hardcore gas" limit (right).
+``hardcore gas" limit (right).  In between, there is a rich staircase-like structure, as the
+particles attempt to minimize the interaction by being at distance $>1$ from as many other particles
+as allowed by the trap energy.
 
@@
 along the $X$ axis.  In the absence of interactions, each particle would undergo simple harmonic
-oscillation with period $T=2\pi/\omega_0 = 2\pi$.  The point corresponding to each particle than
-executes clockwise elliptical motion around in the $X$-$P$ plane.  (In our units, the elliptical
-trajectory is actually circular.)  This results in the initial line remaining a straight line and
-rotating clockwise with exact period $T$.  The effect of interaction is to smear out the line and
-spread the points out toward a rotationally invariant distribution in the  $X$-$P$ plane.  The top
-panel of Figure  \ref{fig:Breathingfrequency2_0} shows this during the first period and Figure
+oscillation with period $T=2\pi/\omega_0 = 2\pi$.  The point corresponding to each particle executes
+clockwise elliptical motion around the $X$-$P$ plane.  (In our units, the elliptical trajectory is
+actually circular.)  This results in the initial line remaining a straight line and rotating
+clockwise with exact period $T$.  The effect of the interaction is to smear out the line and spread
+the points out toward a rotationally invariant distribution in the $X$-$P$ plane.  The top panel of
+Figure \ref{fig:Breathingfrequency2_0} shows this during the first period and Figure
 \ref{fig:Breathingfrequency2_1} shows this process over a much longer timescale.
@@
 interaction-induced shift of the breathing frequency from the noninteracting value,
-$\omega=2\omega_0$.  The distortion of the line toward an eventually rotationally invariant
+$\omega_B=2\omega_0$.  The distortion of the line toward an eventually rotationally invariant
 distribution may be regarded as thermalization or ergodicity.  In the next sections we explore these
@@
 
-Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the
-random noise is significant. If we start with a state whose configuration in phase-space is an
-ellipse slightly deviated from circle, the oscillating amplitude will be too small to be
-distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x,
-zero p) and observe the oscillation of R(t).
-
-\section{Breathing Frequency}\label{section:breathing frequency}
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
+We use the Verlet algorithm (molecular dynamics) to numerically simulate the cloud, using particle
+numbers between 5 and 50.  Our force is simple, so that calculating the force at each step is
+inexpensive, however, the theta function dependence of the force on particle positions requires the
+use of fine timesteps at the beginning and end of each collision process.
+
+The initial state is taken to have particles with zero velocity and random positions; hence the line
+distribution in the phase space picture.  This has the advantage that the breathing motion is
+prominently visible.  In addition, the question of long-time relaxation has the simple
+interpretation of evolving from the line distribution to a circularly symmetric distribution.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tbp]
 \center
@@
 
+\section{Breathing Frequency}\label{section:breathing frequency}
+
 We are interested in the oscillations of the size $R(t)$ of the cloud.  It is convenient that our
 finite-size simulations start with a line distribution in phase space.  If we started with a state
-whose configuration in phase-space is only slightly different from a circle, the oscillating
+whose configuration in phase-space deviates only slightly from circular symmetry, the oscillating
 amplitude would be too small to be distinguished from noise.
@@
 top panel of \ref{fig:Breathingfrequency2_0}, where $R(t)$ is the extent of the distribution in the
-horizontal ($X$) direction.  As the line rotates clockwise with frequency $\omega=1$, within each
+horizontal ($X$) direction.  As the line rotates clockwise with frequency $\omega_0=1$, within each
 period the line is twice horizontally aligned (maximum $R$) and twice vertically aligned (minimum
@@
 consume the time saved by the finite range of the interaction.  This explains why there is a
-small-$F_0$ regime for which the shift $\delta$ is negative.
-
-\subsection{Phase space estimate}
+small-$F_0$ regime for which the shift $\delta$ is negative.  Figure \ref{fig:Breathingfrequency1}
+shows that this critical value of $F_0$, where $\delta$ changes sign and $\omega_B$ crosses $2$,
+increases with energy.
+
+\subsection{Estimates using the rotating phase space}
 
@@
 }
-\caption{a schematic diagram of the collision process: \textbf{(a)}When $F_0\sigma$ is large, particles can not pass each other.
-Subduing to a constant repulsive force in collision, their trajectory in rotating frame is a circular arc.
-\textbf{(b)} When $F_0\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous.
-Their trajectory has a turning point.
-The dashed bright blue trajectory is identical with the one in (a), which is the critical situation between passing and bouncing.
-In that case, particles have zero relative velocity when they collide.
-}
+\caption{Schematic diagrams of two-particle collision process in the $X_{\rm rot}$-$P_{\rm rot}$
+  plane. \textbf{(a)}When $F_0$ is large, particles cannot pass each other.  Being subject to a
+  constant repulsive force, their trajectories during collision are circular arcs.  For very strong
+  interactions (red dashed line, straight), they exchange momenta instantaneously.  The yellow,
+  green, and blue dashed curves are for successively weaker interactions.  \textbf{(b)} When $F_0$
+  is small, particles pass each other, so that the force they feel is not continuous.  Their
+  trajectory has a turning point. The dashed bright blue trajectory is identical with the one in
+  (a), which is the critical situation between passing and bouncing. In that case, particles have
+  zero relative velocity when they collide. }
 \label{fig:Breathingfrequency3}
@@
 collisions.  In Figure \ref{fig:Breathingfrequency3}(a), we show schematics of such a collision near
-the trap center at strong interactions.  For very large $F_0$, the particles simply change momentum
+the trap center at strong interactions.  For very large $F_0$, the particles simply exchange momentum
 when they are at distance $\sigma$ from each other; this process is shown in red as two straight
@@
 In Figure \ref{fig:Breathingfrequency3}(a) we show collisions for small $F_0$, so that the particles
-pass each other.  in the $X_{\rm rot}$-$P_{\rm rot}$ plane, this is seen as a turning point in the trajectory.
+pass each other.  The force changes direction discontinuously when the particles cross.  In the
+$X_{\rm rot}$-$P_{\rm rot}$ plane, this is seen as a sharp turning point in the trajectory.
 
@@
 angle $\alpha$ away from original configuration.  In every period of the harmonic oscillation, each
-particle meets each of the other particles twice.  Half of these collisions (about $N$ collision)
+particle meets each of the other particles twice.  Half of these collisions (about $N$ collisions)
 are between particles with large difference in momentum, which is the process shown in
 Fig.\ref{fig:Breathingfrequency3}.  (As for the remaining half of the collisions, colliding
-particles have smaller difference in their momentume, e.g., both particles having positive
-momentum.  In this estimate we  ignore the effects of these collisions, as they clearly contribute
-far less to the rotation of the particle distribution.)
-
-The precession angle is $\alpha\sim \sigma/P$.  In our rescaled units, the momenta that the
-particles have near $x=0$ are of the order $R$, the size of the cloud.  (In phase space $R$ can be
-interpreted either as the extent in real space when the velocities are small, or as the extent in
-momentum space when the particles approach $x=0$, i.e. when the distribution is along the $P$
-direction.)  Thus, we can estimate  $\alpha\sim \sigma/R$, i.e.,   $\alpha\sim 1/R$, since our unit
-of length is $\sigma$.  This is the rotation per unit collision.  Since there are $\sim N$
-collistions per period $T=2\pi$, we have the estimate for the interaction-induced rotation per unit
-time as
+particles have smaller difference in their momenta.  In this estimate we ignore the effects of these
+collisions, as they clearly contribute far less to the rotation of the particle distribution.)
+
+The precession angle is $\alpha\sim \sigma/P$.  In our rescaled units, the typical momenta of
+interacting partilces is of the order $R$.  (In phase space $R$ can be interpreted either as the
+extent in real space when the velocities are small, or as the extent in momentum space when the
+particles approach $x=0$, i.e. when the distribution is along the $P$ direction.)  Thus, we can
+estimate $\alpha\sim \sigma/R$, i.e., $\alpha\sim 1/R$, since our unit of length is $\sigma$.  This
+is the rotation per unit collision.  Since there are $\sim N$ collistions per period $T=2\pi$, we
+have the estimate for the interaction-induced rotation per unit time as
 \begin{equation}
@@
 
----------
-
-%% \subsection{Estimating Breathing Frequency}
-
-%% Let us begin with two-particle case. When interaction is very strong, the effect of interaction is
-%% equivalent to exchanging momentum when two particles approach each other at distance $\sigma$. In
-%% the rotating frame in phase-space, this process can be interpret as follows:
-
-%% (See Fig.\ref{fig:Breathingfrequency3}(a))Two particles flip to another line(thick gray line) which
-%% deviate a small angle $\alpha$ away from original configuration. Similar process happen when there
-%% are more particles. In every period of harmonic oscillation, each particle meet N particles and
-%% collide 2N times, while half of the collisions (N times) are between particles with huge difference
-%% in momentum, which is just the process shown in Fig.\ref{fig:Breathingfrequency3}. (As for the
-%% remaining half of collisions, colliding particles have small difference in their momentum. Let us
-%% say, both particles have positive momentum. In Fig.\ref{fig:Breathingfrequency3}, it can be shown
-%% that two particles on the same half of the P-axis seldom contribute to the rotation of
-%% distribution.)
-
-%% Let us estimate the precession angle $\alpha$ in one collision event by $\frac{\sigma}{R}$, which
-%% follows from the two-particle case study. Radius of the cloud R can be estimated according to
-%% $E=Nm\omega_0^2R^2$ We will get the precession angular velocity
-%% \begin{equation}
-%% \delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
-%% \label{eq:breathingfrequency1}
-%% \end{equation}
-
-When $F_0$ is not that large, the frequency behavior seems complicated (see Fig.\ref{fig:Breathingfrequency1}).
-Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2.
-The reason could also be well understood with the mechanism described before.
-In the discussion above, we go to high $F_0$ limit, which means particles exchange momentum in infinitesimal time.
-For $F_0$ is not very big, the finite interaction time should be taken into consideration.
-During this time, the motion of each particle in phase-space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$.
-Since the real P axis is rotating counter-clockwise, the particle will follow a circular trajectory(orange and green dashed line in Fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time.
-There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line).
-It is easy to see that the contribution of each collision event to the phase-space precession of the cloud is negative in Fig.\ref{fig:Breathingfrequency3})(b).
-So at this point, we will see the precession  slows down or even be reversed, which means the breathing frequency is 2 or a little bit lower than 2.
-
+The effect of interaction on breathing frequency is more complicated at smaller $F_0$.  As we have
+seen in Figure \ref{fig:Breathingfrequency1}, the effect of a small $F_0$ is to \emph{decrease} the
+breathing frequency from its non-interacting value $\omega_B=2$.  This can also be understood using
+phase-space pictures of collision processes.  For $F_0$ is not very big, the finite interaction time
+needs to be taken into consideration.  During this time, the motion of each particle in phase-space
+is moving exactly along the direction of the real $P$ axis at the rate $F_0/m$. Since the real $P$
+axis is rotating counter-clockwise, the particle will follow a circular trajectory, e.g., following
+the orange or green dashed lines in Fig.~\ref{fig:Breathingfrequency3}(a).  The angle $\alpha$ that
+we used above to estimate $\delta$ thus decreases with the increase of interaction time; it is
+smaller for the yellow line and even opposite for the green line.  This explains the negative
+contribution of interaction to $\delta$, for small enough values of $F_0$.  At even smaller values
+of $F_0$, shown in Fig.~\ref{fig:Breathingfrequency3})(b), the particles cross each other.  The
+resulting final values are such that the line joining the post-interaction locations of the two
+particles has negative $\alpha$, i.e., is tilted clockwise with respect to the $X_{\rm rot}$ axis,
+meaning a negative contribution to the breathing frequency.
+
+We can also estimate the critical value of $F_0$ for a given energy (or alternatively the critical
+value of $E$ for a given $F_0$) between positive and negative contributions to the breathing
+frequency.  Since the $P$ axis rotates with frequency $\omega_0=1$ in the $X_{\rm rot}$-$P_{\rm
+  rot}$ plane, the post-collistion position of the particle in the $X_{\rm rot}$-$P_{\rm rot}$ plane
+makes angle $\omega_0\tau$ with the red line in Figure \ref{fig:Breathingfrequency3}(a).  Here
+$\tau$ is the time over which the interaction acts.  The crossover between positive and negative
+$\delta$ is found by comparing this angle to $\alpha$:
+\begin{equation}
+\omega_0 \tau=\alpha
+\end{equation}
+The time $\tau$ is approximately the time it takes for the momentum to change sign due to a constant
+force $F_0$, since the momentum is $\sim R$, this means $\tau\sim R/F_0$.  Using our previous
+estimate  $\alpha\sim \sigma/R$, together with $E\sim NR^2$, gives us the condition
+\begin{equation}
+  \frac{E}{N} \sim F_0
+  \label{eq_freq_turning_condition}
+\end{equation}
+for the breathing frequency to cross the non-interacting value $\omega_B=2$.  This is roughly the
+same criterion for whether two particles will bounce or cross each other in a typical collision.
+
+The condition \eqref{eq_freq_turning_condition} is consistent with Figure
+\ref{fig:Breathingfrequency1}, where we noted that the critical $F_0$ grows with increasing energy.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}[h]
@@
 \end{figure}
-
-The dependence of frequency on energy and $F_0$ is shown in Fig.\ref{fig:Breathingfrequency4}.
-For the first thing, as expected when $F_0$ is high the frequency behavior is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}.
-Secondly, the figure shows the frequency's dependence on $F_0$.
-As we explained, when $F_0$ is not so large, the precession angle decrease.
-In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision.
-As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.
-
-the critical point that frequency decreases to 2 can be estimate by:
-\begin{equation}
-\omega_0 \tau=\alpha
-\end{equation}
-which means that the approaching time $\tau$ (estimated by $R/F_0$) exactly cancels the precession angle we derived before. One can show that this condition is equivalent to
-\begin{equation}
-\frac{E}{N}=F_0\sigma
-\end{equation}
-which can also be understood as the criterion of whether two particles will bounce or pass by if one estimate the average internal energy of a pair with $\frac{E}{N}$.
-
-Before completing the discussion, it is necessary to point out that none of the argument here require ``energy thermalization".
-In addition, if the system is completely thermalized in terms of their phase angles in phase-space, the argument will no longer work -- there is a stable isotropic distribution in phase space, no matter how the cloud rotate, no oscillation can be observed.
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+In Figure \ref{fig:Breathingfrequency4} we show a quantitative test of the main rotating-phase-space
+prediction, Eq.~\eqref{eq:breathingfrequency1}.  For large $F_0$, the frequency indeed scales as
+$E^{-1/2}$ and for $F_0=10^5$ is quite close to the actual numerical values prediction
+\eqref{eq:breathingfrequency1}.  Even for smaller $F_0$, at small enough energies (larger $E^{-1/2}$
+values) the breathing mode becomes proportional to  $E^{-1/2}$.
+
+---------
 
@@
 
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}[h]
@@
 
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
 \begin{figure}
@@
 \label{fig:thermalization5}
-
 \end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
@@
 }
-
 \caption{Time evolution of the particles' energy $\epsilon$}
-
 \end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
@@
 }
-
 \caption{Fitting energy distribution $\rho(\epsilon)$ with Boltzmann distribution}
-
 \end{figure}
-
-In Fig.\ref{fig:thermalization9} and Fig.\ref{fig:thermalization10}, the curve is slightly deviated from the standard Boltzmann distribution, which is probably due to the contribution of density of states (DOS).
-Possibility is proportional to Boltzmann exponential factor multiplied by density of states.
-The reason why we did not take DOS into account previously lies in that the DOS is a constant for simple harmonic oscillator.
-However, for simple harmonic oscillators with short range interaction, the energy shell is deformed in the small region of $|x_i-x_j|<\sigma$ so that the DOS is no longer a constant.
-The effect of interaction is conspicuous in low energy part: when interaction is weak, particles prefer to stay near zero energy according to Boltzmann distribution, but when interaction grows, they are no longer allowed to accumulate near zero energy, in another word DOS at low energy decreases with the increase of interaction.
-Therefore, counts at the low energy part of Fig.\ref{fig:thermalization9} and \ref{fig:thermalization10} is always a little bit lower than the Boltzmann prediction.
-But since $\sigma<<R$, we can think of interaction as a small modification, so the overall tendency still fits well.
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+In Fig.\ref{fig:thermalization9} and Fig.\ref{fig:thermalization10}, the curve is slightly deviated
+from the standard Boltzmann distribution, which is probably due to the contribution of density of
+states (DOS). Possibility is proportional to Boltzmann exponential factor multiplied by density of
+states. The reason why we did not take DOS into account previously lies in that the DOS is a
+constant for simple harmonic oscillator. However, for simple harmonic oscillators with short range
+interaction, the energy shell is deformed in the small region of $|x_i-x_j|<\sigma$ so that the DOS
+is no longer a constant. The effect of interaction is conspicuous in low energy part: when
+interaction is weak, particles prefer to stay near zero energy according to Boltzmann distribution,
+but when interaction grows, they are no longer allowed to accumulate near zero energy, in another
+word DOS at low energy decreases with the increase of interaction. Therefore, counts at the low
+energy part of Fig.\ref{fig:thermalization9} and \ref{fig:thermalization10} is always a little bit
+lower than the Boltzmann prediction. But since $\sigma<<R$, we can think of interaction as a small
+modification, so the overall tendency still fits well.
 

### 2017-12-07 draft_05.tex
more or less done with breathing mode section

@@
 \affiliation{
-  $^1$ Fudan University, Shanghai, China\\ 
+  $^1$ Department of Physics and State Key Laboratory of Surface Physics, Fudan University, Shanghai 200433, China\\ 
   $^2$ Max Planck Institute for the Physics of Complex Systems, N{\"o}thnitzer Str.~38, 01187 Dresden, Germany\\
@@
 
-%\begin{figure}[h]
-%\centering
-%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
-%\caption{ground state Energy with $F_0$}
-%\end{figure}
-%\end{comment}
-
 \subsection{Ground states}
@@
 
-At very small $F_0$, the energy is minimized by having the particles approximately equidistant, at
-distance $\approx 2F_0/\omega_0^2$ from each other.  In this `solid'-like state, the low-lying
+At very small $F_0$, the particles in the ground state are close enough to the trap center that each
+particle interacts with every other particle.  Equating the interaction force due to all the other
+particles with the trapping force, one finds that the position of the $i$-th particle is
+\begin{equation}
+x_i ~=~ \frac{2F_0}{m\omega_0^2} \left( i - \frac{N+1}{2} \right) ~=~ 2F_0 \left( i - \frac{N+1}{2} \right)
+\end{equation}
+where the particles are labeled $i=1$ to $i=N$ from left to right.  Thus the particles are
+equidistant in this regime.  In this `solid'-like state, the low-lying
 excitation involves independent oscillation of the particles around their equilibrium position.
 
-In Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
-``hardcore gas" limit (right).  In between, there is a rich staircase-like structure, as the
+In this regime, the distance between the leftmost and rightmost particles is at most $\sigma=1$.
+Thus, this situation extends up to $F_0 = \frac{1}{2(N-1)}$.  For the $N=5$ case shown in Figure
+\ref{fig:GS1}, this behavior is seen up to $F_0 < 1/8$.
+
+In Figure \ref{fig:GS1}, we can see this crossover from the ``solid-like'' limit (left) to the
+``hardcore gas'' limit (right).  In between, there is a rich staircase-like structure, as the
 particles attempt to minimize the interaction by being at distance $>1$ from as many other particles
-as allowed by the trap energy.
+as is compatible with the trap energy.
 
@@
 
+\subsection{Comparisons with numerical data}
+
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
@@
 \includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
-\caption{dependence of breathing frequency on Energy, N=20.
-Different color stands for different $F_0$: Red for $F_0=2\times10^3$; Yellow for $F_0=3\times10^3$; Green for $F_0=1\times10^4$;  Blue for $F_0=1\times10^5$.
-Run with three different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles).
-The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
+\caption{Dependence of breathing frequency, calculated for $N=20$ particles, on energy.  Different
+  colors represent different $F_0$ --- red for $F_0=2\times10^3$, yellow for $F_0=3\times10^3$,
+  green for $F_0=1\times10^4$, and blue for $F_0=1\times10^5$.  Runs with three different initial
+  states are shown in each case.  In each run, the frequency is measured both in the time window
+  0-100 (labeled as crosses) and in the time window 900-1000 (labeled as circles). The black dashed
+  line is the prediction of Eq.~\eqref{eq:breathingfrequency1}.}
 \label{fig:Breathingfrequency4}
@@
 values) the breathing mode becomes proportional to  $E^{-1/2}$.
+
+One might ask whether the breathing frequency predictions are also valid at late times, after the
+system has `relaxed' from the initial line distribution in phase space to a more spread-out cloud,
+as we have seen in Figure \ref{fig:Breathingfrequency2_1}.  In \ref{fig:Breathingfrequency4} we show
+the breathing frequency calculated from $R(t)$ oscillations in the first 100 time units, and also
+the frequency from data in a later time window. The frequencies appear to be overall stable and dependent
+primarily on $F_0$ and $E$.
 
@@
 \centering
-\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/effective_potential.png}
 \caption{effective potential for two-particle system}

### 2017-12-08 draft_05.tex
working on thermalization section

@@
 
----------
-
 \section{Thermalization}\label{section:Thermalization}
-\subsection{Dynamics Study}
-It is natural to think that a many-body system with interaction will be thermalized in ``usual" case.
-To study the condition of thermalization is equivalent to find out the mechanism that prohibits the system from ergodic.
-We begin the study with two-particle motion.
-\subsubsection{two particles}
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
+
+For any nonzero interaction, the system is expected to be ergodic for $N>2$.  Once there are many
+particles, one expects thermalization in the long-time limit.  From the few-particle perspective,
+several interesting questions pose themselves.  First, although we expect ergodicity, the question
+of how long it takes to thermalize is an open question for small $N$. We treat below a
+coarse-grained version of this question: namely, we ask whether particles show ergodic behavior
+within reasonable timescales chosen to be (somewhat arbitrarily) in the timestep range of
+$10^3$--$10^4$.  Another question is the connection between thermalization, as defined by the
+appearance of a Boltzmann distribution and other intuitive characteristics of ergodic behavior such
+as whether the single-particle phase space is isotropically occupied.  We find cases where one
+aspect is seen while the other is not.
+
+In the subsections below, we first ***  then ****
+
+\subsection{Few-particle considerations}
+
+Since we are interested in thermalization within finite timescales, it is useful to consider
+mechanisms which hinder relaxation or thermalization.  We begin with considerations of few-particle
+motion.  Since ergodicity and relaxation are generally expected to be more robust and efficient with
+larger particle numbers, consideration of small particle numbers will highlight effects which slow
+down relaxation.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tbph]
 \centering
-\includegraphics[width=0.5\textwidth]{ZhiyuPictures/effective_potential.png}
-\caption{effective potential for two-particle system}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/two_particles_a_01.pdf}
+\caption{Left: Effective potential for two-particle system.  Center and right: beats at internal
+  energy $E_i=2$ and $E_i=5$.  The curves show the individual energies of the two particles.  Here
+  $F_0=1$. In this case, the larger the $E_i$, the lower the beat frequency. }
 \label{fig:thermalization2}
@@
 
-To see the way interaction change the orbit (energy level) of the particles, we had better start from two-particle case.
-
-We can consider their motion in their center of mass frame ``C".
-In frame C, one can easily show that when there is no interaction what we will see is that two particles bound together by a harmonic trap centered at C (black line in Fig.\ref{fig:thermalization2}).
-So their relative motion is also a harmonic oscillation.
-
-In this case, the system has two frequency components.
-The first one is the frequency of C, which is just $\omega_0$ .
-The other one is the frequency of their relative motion $\omega_r$, which is slightly deviated from $\omega_0$.
-The deviation grows with the increase of $F_0$ and the decrease of internal energy of the pair.
-As a result, when $F_0$ is small or when E is large, a beat with low frequency $\omega_r-\omega_0=\delta$ will exist.
-This phenomenon means energy transfer between particles are inefficient, thus the thermalization should be slow.
-
-\begin{figure}[h]
-
-\subfigure[$E_i=2$]{
-\begin{minipage}[b]{0.22\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_600_500_Font24.eps} 
-%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
-\end{minipage}
-}
-\subfigure[$E_i=3$]{
-\begin{minipage}[b]{0.22\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_600_500_Font24.eps} 
-%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
-\end{minipage}
-}
-\subfigure[$E_i=5$]{
-\begin{minipage}[b]{0.22\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_600_500_Font24.eps} 
-%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
-\end{minipage}
-}
-\subfigure[$E_i=10$]{
-\begin{minipage}[b]{0.22\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_600_500_Font24.eps} 
-%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
-\end{minipage}
-}
-
-\caption{the dependence of beat frequency on internal energy. The diagram is the energy of two
-  particles. Here, $F_0$ is set to be 1. In this case, the larger the $E_i$, the lower the beat
-  frequency. \label{fig:thermalization1}}
-%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a
-%beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
-
-\end{figure}
+\subsubsection{Two particles}
+
+We consider the two-particle motion in their center of mass frame.  The center of mass itself
+executes simple harmonic oscillation.  In the absence of interactions ($F_0=0$), the effective
+potential within the center of mass frame is itself parabolic, with the same frequency.  So their
+relative motion is also a harmonic oscillation, with the same frequency $\omega_0$.
+
+With interactions, a term $F_0(1-|r|)\theta(1-|r|)$ is added, where $r$ is the relative
+displacement; as shown in Figure \ref{fig:thermalization2}.  Now, the relative motion is no longer
+harmonic; one could regard the resulting motion has having a slightly different frequency, or a
+collection of frequencies whose center is shifted slightly from $\omega_0$.  Since the
+center-of-mass motion is still of frequency $\omega_0$, we have a superposition of slightly
+different frequencies, resulting in beating dynamics.  This is clearly seen in the time evolution of
+individual energies shown in Figure \ref{fig:thermalization2}.  The two panels correspond to
+different internal energy $E_i$ (defined as the total energy minus the center-of-mass energy).  For
+larger $E_i$, the distortion of the effective potential (at constant $F_0$) plays a smaller role in
+shifting the effective frequency of relative motion; hence the beat frequency is smaller.
+
+This illustrates a simple mechanism hindering the redistribution of energy between particles, which
+is necessary for thermalization or relaxation.  As seen in the example dynamics shown, the
+difference in energy between the two particles is sustained over time.  Of course thermalization is
+not expected anyway in a two-particle system, but we will see below how this basic effect continues
+to play a role for larger $N$.
+
+-------
+
+%% \begin{figure}[h]
+%% \subfigure[$E_i=2$]{
+%% \begin{minipage}[b]{0.22\textwidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_600_500_Font24.eps} 
+%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
+%% \end{minipage}
+%% }
+%% \subfigure[$E_i=3$]{
+%% \begin{minipage}[b]{0.22\textwidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_600_500_Font24.eps} 
+%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
+%% \end{minipage}
+%% }
+%% \subfigure[$E_i=5$]{
+%% \begin{minipage}[b]{0.22\textwidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_600_500_Font24.eps} 
+%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
+%% \end{minipage}
+%% }
+%% \subfigure[$E_i=10$]{
+%% \begin{minipage}[b]{0.22\textwidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_600_500_Font24.eps} 
+%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
+%% \end{minipage}
+%% }
+
+%% \caption{the dependence of beat frequency on internal energy. The diagram is the energy of two
+%%   particles. Here, $F_0$ is set to be 1. In this case, the larger the $E_i$, the lower the beat
+%%   frequency. \label{fig:thermalization1}}
+%% %Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a
+%% %beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
+%% %
+%% \end{figure}
 
 \subsubsection{More particles}
+
 Now let's consider the three-particle case.

### 2017-12-09 draft_06.tex
working on thermalization section, changed some figures

--- 2017-12-08 draft_05.tex
@@
 displacement; as shown in Figure \ref{fig:thermalization2}.  Now, the relative motion is no longer
-harmonic; one could regard the resulting motion has having a slightly different frequency, or a
-collection of frequencies whose center is shifted slightly from $\omega_0$.  Since the
-center-of-mass motion is still of frequency $\omega_0$, we have a superposition of slightly
-different frequencies, resulting in beating dynamics.  This is clearly seen in the time evolution of
-individual energies shown in Figure \ref{fig:thermalization2}.  The two panels correspond to
-different internal energy $E_i$ (defined as the total energy minus the center-of-mass energy).  For
-larger $E_i$, the distortion of the effective potential (at constant $F_0$) plays a smaller role in
-shifting the effective frequency of relative motion; hence the beat frequency is smaller.
+harmonic.  When the internal energy is much larger than $F_0$, one could regard the resulting motion
+has having a slightly different frequency, or a collection of frequencies whose center is shifted
+slightly from $\omega_0$.  Since the center-of-mass motion is still of frequency $\omega_0$, we have
+a superposition of slightly different frequencies, resulting in beating dynamics.  This is clearly
+seen in the time evolution of individual energies shown in Figure \ref{fig:thermalization2}.  The
+two panels correspond to different internal energy $E_i$ (defined as the total energy minus the
+center-of-mass energy).  For larger $E_i$, the distortion of the effective potential (at constant
+$F_0$) plays a smaller role in shifting the effective frequency of relative motion; hence the beat
+frequency is smaller.
 
 This illustrates a simple mechanism hindering the redistribution of energy between particles, which
-is necessary for thermalization or relaxation.  As seen in the example dynamics shown, the
-difference in energy between the two particles is sustained over time.  Of course thermalization is
-not expected anyway in a two-particle system, but we will see below how this basic effect continues
-to play a role for larger $N$.
-
--------
-
-%% \begin{figure}[h]
-%% \subfigure[$E_i=2$]{
-%% \begin{minipage}[b]{0.22\textwidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_600_500_Font24.eps} 
-%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
-%% \end{minipage}
-%% }
-%% \subfigure[$E_i=3$]{
-%% \begin{minipage}[b]{0.22\textwidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_600_500_Font24.eps} 
-%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
-%% \end{minipage}
-%% }
-%% \subfigure[$E_i=5$]{
-%% \begin{minipage}[b]{0.22\textwidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_600_500_Font24.eps} 
-%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
-%% \end{minipage}
-%% }
-%% \subfigure[$E_i=10$]{
-%% \begin{minipage}[b]{0.22\textwidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_600_500_Font24.eps} 
-%% %\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
-%% \end{minipage}
-%% }
-
-%% \caption{the dependence of beat frequency on internal energy. The diagram is the energy of two
-%%   particles. Here, $F_0$ is set to be 1. In this case, the larger the $E_i$, the lower the beat
-%%   frequency. \label{fig:thermalization1}}
-%% %Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a
-%% %beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
-%% %
-%% \end{figure}
+is necessary for thermalization or relaxation.  As seen in the example dynamics shown in Figure
+\ref{fig:thermalization2}, the difference in energy between the two particles is sustained over
+time.  Of course thermalization is not expected anyway in a two-particle system, but we will see
+below how this basic effect continues to play a role for larger $N$.
 
@@
 
-Now let's consider the three-particle case.
-For two particle, the motion is non-chaotic.
-On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon.
-However, in some cases, the time scale of thermalizing could still be very long.
-Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small.
-Meanwhile, suppose particle C has some energy quite different from A \& B.
-In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period.
-How will energy transfer between C and the two-particle system A and B?
-Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau\sim\frac{\sigma}{R}$ ($\tau\ll\frac{2\pi}{\omega}$).
-C gives A a push when approaching it, and then push A back when leaving.
-As has been discussed in the two-particle case, this process is equivalent to giving A a very small velocity ($\sim O(\frac{\sigma}{R})$) in the background of a trap.
-Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$).
-In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected.
-In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass.
-The physics of the ``dance" is similar to the dance between two particle.
-As is shown in Fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.
+Once we have more than two particles, we expect chaotic or ergodic behavior.  However, it is easy to
+imagine mechanisms which drastically slow down redistribution of energy.
+
+Generally, whenever we have some particles with energy very different from others, the dynamics
+occurs mostly independently within particle groups of different energies.  For example, considering
+a situation with three particles, consider the situation where two of them, say A and B, have small
+internal energy, which means their mutual distance and relative velocity are both small, whereas the
+third particle (C) has some energy quite different from A and B.
+%
+Then, A and B will often be interacting, and if their internal energy is smaller than $F_0$,
+significant energy exchange can occur between them.  C will generally exchange little energy with
+the pair during interactions, in which (due to larger internal energy between C and either A or B),
+the interaction is not effective in energy exchange.
+%
+An example is shown in Figure \ref{fig:thermalization4}, showing the dynamics of $N=5$ particles.
+Two pairs of particles persist in performing `internal' dynamics.  The lone particle participates
+only in some slow beating motion with the center of mass of one of the pairs.  Clearly, the energy
+mismatch acts as a hurdle to the relaxation process.
 
@@
 \centering
-\includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
-\caption{Time evolution of single-particle energy}
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/pair1_pre.eps}
+\caption{Time evolution of single-particle energies in a system of five particles, showing a case of
+  inefficient energy redistribution.  The energies of the two partiles with highest energy show a beating
+  similar to the two-particle case.}
 \label{fig:thermalization4}
@@
 
-The argument above still holds in many-particle case.
-Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems oscillating on the energy level diagram at low frequency.
-The discussion above gives us some pictures about the non-ergodic state.
-For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.
-
-\subsection{Thermalization condition}
-The main obstruct to get an thermalized state is the low frequency beat mentioned before.
-As a result, to achieve ergodic state, we have to avoid such low frequency oscillation.
-According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large".
-Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the average energy, which is $\frac{E}{N}$.
-At least they are of the same order.
-The thermalization condition could be given by:
+%% The argument above still holds in many-particle case. Once we start from some configuration where n
+%% particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles
+%% have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and
+%% $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will
+%% find these two systems oscillating on the energy level diagram at low frequency.  The discussion
+%% above gives us some pictures about the non-ergodic state. For these state, life time is rather long
+%% so that once the system reach such configuration (or certain energy distribution), it will take a
+%% long time(more than $10^4$ periods for N=5 case) to decay.
+
+\subsection{Condition for relaxation}
+
+The main obstruct to get an thermalized state is the low frequency beat mentioned before. As a
+result, to achieve ergodic state, we have to avoid such low frequency oscillation. According to our
+discussion before, the solution is to make internal energy of each two-particle pair not ``too
+large". Though it is impossible to express the internal energy of every pair in terms of the total
+energy $E$, we can estimate it by the average energy, which is $\frac{E}{N}$. At least they are of
+the same order. The thermalization condition could be given by:
 \begin{equation}
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
+\begin{figure}[tbhp]
 \centering
@@
 %\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
-\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
-\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
-\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
+%
+\includegraphics[width=0.85\textwidth]{ZhiyuPictures/Boltzmann_2panels_01-crop.pdf}
+%
 \caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, Green curves corresponds to Boltzmann distribution; Red curves are obviously non-Boltzmann, while the yellow ones are intermediate case, represent ``thermalization threshold".
@@
 
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
-\subfigure[N=10, $F_0=200$]{
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_s_400_300_Font12.eps}
-\label{fig:thermalization6}
-\end{minipage}
-}
-\subfigure[N=10, $F_0=1000$]{
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_s_400_300_Font12.eps} 
-\label{fig:thermalization7}
-\end{minipage}
-}
-\caption{Time evolution of the particles' energy $\epsilon$}
-\end{figure}
+%% %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+%% \begin{figure}[h]
+%% \subfigure[N=10, $F_0=200$]{
+%% \begin{minipage}[b]{0.4\linewidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_s_400_300_Font12.eps}
+%% \label{fig:thermalization6}
+%% \end{minipage}
+%% }
+%% \subfigure[N=10, $F_0=1000$]{
+%% \begin{minipage}[b]{0.4\linewidth}
+%% \includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_s_400_300_Font12.eps} 
+%% \label{fig:thermalization7}
+%% \end{minipage}
+%% }
+%% \caption{Time evolution of the particles' energy $\epsilon$}
+%% \end{figure}
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%

### 2017-12-14 draft_06.tex
working on introduction

@@
-\documentclass[aps,preprintnumbers,onecolumn,amsmath,amssymb,floatfix,pra]{revtex4-1}
+\documentclass[onecolumn,pra]{revtex4-1}
 
@@
 
-Will write Introduction after everything else is written.
+The non-equilibrium dynamics of isolated systems has been the subject of a large volume of work in
+recent years.  In particular, in the quantum context, the study of unitary quantum evolution of
+many-body and few-body systems has undergone an explosive growth.  This interest was partly fueled
+by the availability of experimental systems, e.g., trapped ultracold atomic and ionic systems, where
+non-dissipative dynamics can be studied explicitly due to excellent isolation (CITE).  There are
+also fundamental reasons for studying dynamics in isolation: recent activity has led to advances in
+the understanding of basic principles connecting quantum dynamics, quantum chaos and the emergence
+of statistical mechanics and thermalization (CITE).  For classical many-body systems, explorations
+of the connections between microscopic dynamical rules, chaos, ergodicity and statistical mechanics
+have a much longer history, dating back to the time of Boltzmann and Poincare.
+\cite{Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85}.
+
+Motivated by questions and issues arising in the field of quantum many-body and few-body dynamics,
+in this work we will study the classical dynamics of a collection of interacting particles confined
+in a one-dimensional harmonic trap.  The analogs of two questions, studied intensively in the
+quantum literature, will be investigated: (1) the influence of interactions on the breathing mode
+frequency of the trapped gas, and (2) the relaxation and possible thermalization of the finite
+system under its own evolution, in the absence of any external baths or dissipation mechanisms.
+
+Experiments with cold atoms, which have had an essential motivational role for the current interest
+in many-body quantum dynamics, are generally performed in a trapping potential, either optical or
+magnetic.  As a result, in the last two decades many questions of many-body quantum physics have
+been reformulated in the presence of a harmonic trap.  The presence of a harmonic trap often results
+in new dynamical phenomena; for example the motion of vortices in a trapped condensate (CITE) has
+new features (such as precession) compared to vortex motion in uniform condensates (CITE).  Trapping
+also results in new collective phenomena which have no analog in uniform situations: for example,
+collective modes like dipole, breathing and quadrupole modes are specific to trapped many-body
+systems.  Dipole modes (center of mass oscillations) and breathing modes (size oscillations) appear
+even for one-dimensional trapped systems; higher-dimensional systems display additional, more
+complicated modes like quadrupole and scissors modes.  Because of the omnipresence of trapping
+potentials in cold-atom experiments, dipole and breathing mode dynamics are pervasive across the
+field: These modes have been intensively studied and used for diagnostic purposes since the early
+days of research with trapped quantum-degenerate gases, and continue to generate interest today
+\cite{Naegerl_Science2009, Esslinger_exp_PRL2003, collective_modes_early_papers,
+  Tschischik_BHbreathing_PRA_2013, KroenkeSchmelcher_BM, Bonitz_Review, Bouchoule_PRL2014,
+  our_superTG_PRA_2015, STG_Astrakharchik_PRL2005, STG_Chen-etal_PRA2010,
+  br_mode_long_range_interactions, 1D_breathing_mode_recent, KohnMode, Cominotti_2015,
+  ZarembaTowers_PRA2014, Wetterich_JPB2011, fermion2Dbreathing, Stringari_lowDcollective_PRA15,
+  Mazets_1Dbreathing_EPJD11}.  (CITE).
+%
+In one of the best-known experiments on quantum many-body dynamics,
+Ref.~\cite{NewtonsCradle_Nature06}, the dynamics of an integrable system (Lieb-Liniger bosons) was
+seen to have ultraslow relaxation in a trap, supposedly due to integrability.  This experiment has
+led to continuing efforts to understand how a trap breaks integrability (CITE).
+
+The presence of harmonic trapping is thus a paradigmatic aspect in the field of quantum many-body
+dynamics.  This motivates our study of classical dynamics of trapped interacting systems.  Similarly
+motivated by quantum dynamics, classical trapped dynamics of hard rods has recently been studied in
+Refs.\ \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10}, focusing on integrability-breaking effects of
+the trap.  In this work, we consider trapped classical particles which interact via a simple
+finite-range potential between any pair of particles: a constant repulsive force acts whenever the
+particles are less than a certain distance apart.  The interaction strength can be tuned, leading to
+different regimes of behavior.
+
+Our first theme will be a study of the breathing mode of the classical interacting gas, and the
+effect of interactions on the frequency of the breathing mode.  In the quantum case, this has long
+been a topic of interest for both fermions and bosons.  For bosons with short-range interactions,
+the situation has been studied in one, two and three dimensions.  At zero interactions, the
+breathing mode is twice the trapping frequency $\omega_0$ (assuming isotropic trapping) in each
+case.  A mean field (Gross-Pitaevskii) calculation gives the frequency to be $\sqrt{D+2}$ times the
+trapping frequency, where $D$ is the spatial dimension.  For three-dimensional (3D) traps, the
+mean-field description can be expected to be qualitatively correct, thus the breathing mode
+frequency is expected to change monotonically from $2\omega_0$ at zero interactions to
+$\sqrt{5}\omega_0$ at large interactions.  For 2D traps, the breathing frequency is exactly
+$2\omega_0$ for any interaction strength \cite{PitaevskiiRosch_PRA97}.  This remarkable result
+follows from a symmetry in 2D.  Classical trapped particles with scale-invariant interaction
+potentials also have breathing frequency $2\omega_0$ independent of interaction strength
+\cite{PitaevskiiRosch_PRA97}.  The interaction dependence in 1D (trapped Lieb-Liniger gas) is also
+remarkable: as the interaction is increased, the breathing frequency first decreases from
+$2\omega_0$ to the mean-field prediction $\sqrt{3}\omega_0$, and then at larger interactions
+increases again, returning to $2\omega_0$ in the infinite interaction (Tonks-Girardeau) limit
+\cite{Naegerl_Science2009, Tschischik_BHbreathing_PRA_2013, 1D_breathing_mode_recent,
+  Bouchoule_PRL2014, KroenkeSchmelcher_BM}.
+%
+The breathing mode has also been investigated extensively for fermionic systems with contact
+interactions \cite{GrimmSmith_unitaryfermions_PRA08, fermion2Dbreathing,
+  Stringari_lowDcollective_PRA15}, and also for fermionic and bosonic systems with long-range
+interactions \cite{br_mode_long_range_interactions, Bonitz_Review}.  The breathing mode has also
+been studied for a high-temperature trapped gas where a Boltzmann-equation description is valid,
+both theoretically \cite{Guery-Odelin1999} and experimentally
+\cite{Cornell_classsical_3Dexpt_NatPhys15}.
+
+In this work, we use an explicit microscopic model, rather than a Boltzmann equation approach.
+Unlike the quantum case, the harmonic potential does not impose a length scale or an energy scale.
+The interaction range can thus be scaled away by a redefinition of length, i.e., by measuring
+lengths in units of the interaction range.  There are only two important parameters determining the
+system behavior, namely the interaction strength and the energy per particle.  We find that the
+breathing mode frequency has a non-monotonic dependence on the interaction parameter.  At small
+interactions, when the particles pass through each other, the effect of collisions is to slow down
+the dynamics, so that the breathing frequency drops below the non-interacting value $2\omega_0$.  At
+very large interactions, the particles bounce off each other, a process which speeds up the size
+oscillations, resulting in the breathing frequency being larger than $2\omega_0$.
+
+Our second theme is the process of relaxation at long timescales, and possible thermalization.  This
+topic is also motivated by intense recent research in the quantum context.  In quantum isolated
+systems, thermalization is now understood in terms of the so-called eigenstate thermalization
+hypothesis (ETH), which postulates that in ergodic systems the expectation values of observables in
+individual eigenstates depend ony on the eigenenergy, and hence represents the thermal value (CITE).
+The connection to statistical mechanics is particularly difficult for explicitly finite systems, in
+which case ETH is to be understood in terms of finite size scaling (CITE).  In classical systems,
+the connection between microscopic dynamics and statistical mechanics has been continually studied
+since the 19th century.  It is generally understood that systems with positive Lyapunov exponents
 
@@
 
+The words ergodic, relaxation and thermalization
+
+Loss of memory of initial state --- our two definitions
+
+------------------
+
 This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
@@
 \begin{equation}
-\Big| F(|x|) \Big| ~=~ \begin{cases}
+\Big| F(x) \Big| ~=~ \begin{cases}
 F_0  &\quad |x|<\sigma\\
@@
 \end{equation}
-This is a good approximation at large $F_0$ because, for very large interactions, the particles
-behave has hard rods which bounce off each other very rapidly, so that at most instants one can
+%
+This approximation is good when the average distance betwen particles is much larger than the
+interaction range $\sigma=1$, i.e., whenever $R\gg1$, which is the regime we consider dynamics in.
+Another way of describing this dilute-gas regime is that the gas is far from the ground state
+(described in the next subsection).  Neglecting the interaction energy to estimate $E$ is reasonable
+even at very large interactions ($F_0\gg E/N$), because for very large interactions, the particles
+behave as hard rods which bounce off each other very rapidly, so that at most instants one can
 expect no collisions to be taking place.  It is also expected to be a good approximation at very
-small $F_0$ since we can then simply neglect the interaction energy.  Thus, we will use this as a common
-estimate for $R$ in terms of the energy.
+small $F_0$ since we can then simply neglect the interaction energy.  Thus, we will use this as a
+common estimate for $R$ in terms of the energy.
 
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure*}[h]
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}
+\begin{figure*}[tbph]
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.pdf}
 %
@@
 \begin{figure*}
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.pdf}  
 \caption{Phase space snapshots of the cloud dynamics viewed in the rotating frame, at longer
@@
 \includegraphics[width=0.9\textwidth]{ZhiyuPictures/two_particles_a_01.pdf}
-\caption{Left: Effective potential for two-particle system.  Center and right: beats at internal
-  energy $E_i=2$ and $E_i=5$.  The curves show the individual energies of the two particles.  Here
-  $F_0=1$. In this case, the larger the $E_i$, the lower the beat frequency. }
+\caption{Two-particle dynamics.  Left: Effective potential for relative motion.  Center and right:
+  evolution of the individual energies of the two particles.  The two panels correspond to internal
+  energy $E_i=2$ and $E_i=5$; the interaction is $F_0=1$.  The beat frequency is lower for larger
+  $E_i$. }
 \label{fig:thermalization2}
@@
 harmonic.  When the internal energy is much larger than $F_0$, one could regard the resulting motion
-has having a slightly different frequency, or a collection of frequencies whose center is shifted
+as having a slightly different frequency, or a collection of frequencies whose center is shifted
 slightly from $\omega_0$.  Since the center-of-mass motion is still of frequency $\omega_0$, we have
@@
 \caption{Time evolution of single-particle energies in a system of five particles, showing a case of
-  inefficient energy redistribution.  The energies of the two partiles with highest energy show a beating
-  similar to the two-particle case.}
+  inefficient energy redistribution.  The energies of the two particles with highest energy (4 \& 5)
+  show a clear beating similar to the two-particle case, as does the pair 2 \& 3, although less
+  visible.  The `unpaired' particle 1 performs slow beating dynamics with the center of mass of the
+  2 \& 3 pair.}
 \label{fig:thermalization4}
@@
 
-\subsection{Condition for relaxation}
-
-The main obstruct to get an thermalized state is the low frequency beat mentioned before. As a
-result, to achieve ergodic state, we have to avoid such low frequency oscillation. According to our
-discussion before, the solution is to make internal energy of each two-particle pair not ``too
-large". Though it is impossible to express the internal energy of every pair in terms of the total
-energy $E$, we can estimate it by the average energy, which is $\frac{E}{N}$. At least they are of
-the same order. The thermalization condition could be given by:
+\subsection{Relaxation condition and the Boltzmann distribution}
+
+Our consideration of few-particle motion has shown that relaxation is slow when the internal energy
+of pairs is large compared to $F_0$.  This allows us to conjecture a condition for relaxation in
+reasonable time.  Although it is impossible to express the internal energy of every pair in terms of
+the total energy $E$, we can estimate the typical internal energy by the average energy,
+$\frac{E}{N}$. At least they are of the same order.  Thus we have the condition
 \begin{equation}
-F_0\sigma\sim\frac{E}{N}
-\label{eq:thermalizatiton condition}
+F_0 \gtrsim \frac{E}{N}
+\label{eq:thermalizatiton_condition}
 \end{equation}
+for relaxation.  This is the same condition we obtained for the breathing frequency to be increased
+(rather than decreased) by the interaction.
 
@@
 %
-\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, Green curves corresponds to Boltzmann distribution; Red curves are obviously non-Boltzmann, while the yellow ones are intermediate case, represent ``thermalization threshold".
-In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500\sim1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
+\caption{The distribution of single-particle energies measured in $\sim 10000$ time units. Green
+  curves obey the relaxation condition \eqref{eq:thermalizatiton_condition}, and yellow/orange
+  corresponds to smaller $F_0$.  In each panel (different $N$), we choose $E/N$ identical ($=1000$),
+  so that the threshold interaction between the two behaviors is  $F_0\sim1000$. }
 \label{fig:thermalization5}
@@
 
-%\begin{figure}
-%\subfigure[N=10, $F_0=200$]{
-%\begin{minipage}[b]{0.4\linewidth}
-%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
-%\label{fig:thermalization6}
-%\end{minipage}
-%}
-
-%\subfigure[N=10, $F_0=1000$]{
-%\begin{minipage}[b]{0.4\linewidth}
-%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
-%\label{fig:thermalization7}
-%\end{minipage}
-%}
-
-%\end{figure}
-
-%% %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-%% \begin{figure}[h]
-%% \subfigure[N=10, $F_0=200$]{
-%% \begin{minipage}[b]{0.4\linewidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_s_400_300_Font12.eps}
-%% \label{fig:thermalization6}
-%% \end{minipage}
-%% }
-%% \subfigure[N=10, $F_0=1000$]{
-%% \begin{minipage}[b]{0.4\linewidth}
-%% \includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_s_400_300_Font12.eps} 
-%% \label{fig:thermalization7}
-%% \end{minipage}
-%% }
-%% \caption{Time evolution of the particles' energy $\epsilon$}
-%% \end{figure}
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
-
-As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500\sim1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order.
-As a supplementary proof of our argument, Fig.\ref{fig:thermalization6} and Fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic.
-To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.
-
-One may think that this condition only means that the energy transfer in every collision is much smaller than the energy interval.
-But this is not the whole story.
-The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitely slows down the energy transfer.
-What is more, because of this, the particles is less interferred by other particles so that two-particle analysis survives.
-It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time.
-In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the low frequency beat effect tells us.
-Thus the particles energy is localized in certain value.
-On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners.
-As a result, the energy transferred in every collision between two particles are no longer correlated so that our two-particle analysis breaks down.
-Instead, the energy transfer is completely random, with a non-zero amplitude.
-On the single-particle energy diagram, what we expected to see is a ``one dimensional random walk" ,so energy levels quickly spread around the diagram.
-
-To sum up, the thermalization threshold not only tells us whether the amplitude of energy transfer in every collision is small enough compared to particles' energy, but also shows whether the ``correlation time" of particle pair is much longer than the characteristic time of the system (the oscillation period).
-
-\subsection{Verifying Boltzmann distribution}
-Thermalization could have different definition.
-In our system, the ``thermalization" we want to find means ``losing all the memory of initial state".
-One of the most important information of initial state is energy distribution.
-
-For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state.
-However, there is not any obvious conclusion about the distribution for an isolated system where the total energy is conserved.
-But intuitively, one will expect that if we measure the energy of a subsystem, e.g.
-one particle, then we will get a Boltzmann distribution because the rest part of the system can be considered as a bath for this particle.
-The temperature of this isolated system is defined according to $Nk_BT=E$.
-It is evident that this argument only hold when the energy of the single particle is not too big --- if one particle take up 50\% of the total energy, the rest could no longer be thought of as a good bath.
-
-In the first picture below, we verify this argument by measuring the energy distribution of every particle at N=10 for different F0 at E=1000 (parameters here satisfy thermalizing condition).
-In the other two, we tested different N.
-
-%\begin{figure*}
-%%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
-%%\caption{Energy distribution, N=5, F0=10000}
-%%\label{fig:thermalization8}
-%\subfigure[N=10, $F_0=1\times10^4$]{
-%\begin{minipage}[b]{0.1\textwidth}
-%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
-%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
-%\label{fig:thermalization9}
-%\end{minipage}
-%}
-
-%\subfigure[N=20, $F_0=1\times10^4$]{
-%\begin{minipage}[b]{0.1\textwidth}
-%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
-%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
-%\label{fig:thermalization10}
-%\end{minipage}
-%}
-
-%\end{figure*}
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
-\subfigure[N=10, $F_0=1\times10^4$]{
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=10_F=10000_500_400_Font16.eps}
-\label{fig:thermalization9}
-%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
-\end{minipage}
-}
-\subfigure[N=20, $F_0=1\times10^4$]{
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=20_F=10000_500_400_Font16.eps} 
-\label{fig:thermalization10}
-%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
-\end{minipage}
-}
-\caption{Fitting energy distribution $\rho(\epsilon)$ with Boltzmann distribution}
+Because the model is expected to be ergodic for $N>2$ particles, we expect the same condition to
+lead to thermalization.  In fact, the proposed condition works even quantitatively, as we show in
+Figure \ref{fig:thermalization5}.  Here, the distribution of energies among the different particles
+is presented.  Given our small particle number, a single snapshot of the energies will not yield
+enough statistics to investigate the distribution of single-particle energies.  Therefore,
+single-particle energies are recorded at once every time unit (i.e., at time intervals of
+$1/omega_0$) as the simulation evolves, up to around $t\sim10^4$.  The distribution of these
+observed values then shows whether or not the system has thermalized to a Boltzmann distribution.
+In the two panels of Figure \ref{fig:thermalization5}, we show the distributions obtained for a
+$N=5$ system and a $N=20$ system.  In both cases, we choose the total energy to be $E=1000N$.  In
+accordance with our conjectured condition, we find that the observed single-particle distributions
+are qualitatively different for $F_0\gtrsim10^3$ and for smaller interactions.  When the
+``thermalization condition'' $F_0\gtrsim E/N$ is satisfied, the distribution is roughly exponential
+($\sim e^{-\beta\epsilon}$.  For smaller $F_0$, thermalization in this sense is not seen in the
+single-particle energy distribution.  Since the systems are expected to be ergodic, it is assumed
+that the smaller-$F_0$ systems will also eventually show a Boltzmann distribution of energy, but
+that this appears only at (much) longer timescales.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tbph]
+\includegraphics[width=0.8\textwidth]{ZhiyuPictures/Boltzmann_log_2panels_01-crop.pdf}
+%
+\caption{\label{fig:thermalization9} Complaring the single-particle energy distribution
+  $\rho(\epsilon)$ with the Boltzmann distribution.  The energy values all satisfy the relaxation
+  condition \eqref{eq:thermalizatiton_condition}.  The Boltzmann distribution $\propto
+  e^{-\beta\epsilon}$, with the temperature defined as $\beta^{-1}= E/N$, is the thick dashed line.}
 \end{figure}
@@
 
-In Fig.\ref{fig:thermalization9} and Fig.\ref{fig:thermalization10}, the curve is slightly deviated
-from the standard Boltzmann distribution, which is probably due to the contribution of density of
-states (DOS). Possibility is proportional to Boltzmann exponential factor multiplied by density of
-states. The reason why we did not take DOS into account previously lies in that the DOS is a
-constant for simple harmonic oscillator. However, for simple harmonic oscillators with short range
-interaction, the energy shell is deformed in the small region of $|x_i-x_j|<\sigma$ so that the DOS
-is no longer a constant. The effect of interaction is conspicuous in low energy part: when
-interaction is weak, particles prefer to stay near zero energy according to Boltzmann distribution,
-but when interaction grows, they are no longer allowed to accumulate near zero energy, in another
-word DOS at low energy decreases with the increase of interaction. Therefore, counts at the low
-energy part of Fig.\ref{fig:thermalization9} and \ref{fig:thermalization10} is always a little bit
-lower than the Boltzmann prediction. But since $\sigma<<R$, we can think of interaction as a small
-modification, so the overall tendency still fits well.
+In several `thermalizing' situations, $F_0\gtrsim E/N$, we display the agreement with the Boltzmann
+distribution in Figure \ref{fig:thermalization9}.  In each panel, the calculated distributions from
+simulations is plotted against the Boltzmann distribution.  The overall agreement shows that the
+energy is well-thermalized among the particles on average within the timescales under consideration.
+
+There are some small deviations from the Boltzmann distribution visible in Figure
+\ref{fig:thermalization9}.  Most of the deviation is probably due to numerical noise, and
+unsurprising given our small system sizes.  However, some deviation is also expected due to the
+contribution of the density of states (DOS).  The probability of finding an energy is actually
+proportional to the Boltzmann exponential factor multiplied by the DOS.  For the simple harmonic
+oscillator, the DOS is constant.  The interaction deforms the energy shell in the small region
+$|x_i-x_j|<\sigma$; so that the DOS is no longer a constant.  The effect of interaction is
+conspicuous in low energy part: when interaction is weak, particles prefer to stay near zero energy
+according to Boltzmann distribution, but when interaction grows, they are no longer allowed to
+accumulate near zero energy, in another word DOS at low energy decreases with the increase of
+interaction. Therefore, counts at the low energy part of Fig.\ref{fig:thermalization9} is slightly
+lower than the Boltzmann prediction.  The correction to the density of states is not simple to
+calculate explicitly.  Since we are in the regime of a dilute gas ($\sigma\ll R$), the effect is
+very small.
 
 \subsection{Lyapunov Exponents}
-The Lyapunov Exponents is a good tool to quantify the time scale of ``thermalization".
-Lyapunov Exponents(LE) describes how fast one orbit diverge from its nearby orbits in $\Gamma$-space.
-But for high dimensional system, LE is a spectrum that manifest the instability of the trajectory along each direction.
-The largest Lyapunov exponents (LLE) reflects the shortest time scale that system lose its memory.
-Each point along one trajectory in $\Gamma$-space could have different LLE value, but the distribution of LLE is dependent on macroscopic parameters.
-As is shown in Fig.\ref{fig:LLEdistribution1}, we measured the LLEs along our trajectory and plot its distribution as a function of total energy.
-
-\begin{figure}[h]
+
+The general idea that thermalization is faster for larger $F_0$ can be seen through the Lyapunov
+exponents.  For high-dimensional systems, there is a spectrum of exponents which manifests the
+instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects
+the shortest time scale for the system lose memory of the initial state.  We follow the method
+described in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently
+late times, the LLE for an ergodic system is uniquely defined and independent of the starting
+state.  We would like to deal with parameter regimes both within and outside our relaxation
+condition $E<F_0N$ and $E>F_0N$, and in the latter case we have seen that ergodicity does not become
+apparent at reasonable timescales.  Therefore, we carry out the computation of the LLE upto
+$t\sim10^3$, which means that we can only get initial-configuration-dependent estimates.  The
+collection of these estimates forms a distribution which we show in Figure
+\ref{fig:LLEdistribution1}.
+
+%% The Lyapunov Exponents is a good tool to quantify the time scale of ``thermalization". Lyapunov
+%% Exponents(LE) describes how fast one orbit diverge from its nearby orbits in $\Gamma$-space. But for
+%% high dimensional system, LE is a spectrum that manifest the instability of the trajectory along each
+%% direction. The largest Lyapunov exponents (LLE) reflects the shortest time scale that system lose
+%% its memory. Each point along one trajectory in $\Gamma$-space could have different LLE value, but
+%% the distribution of LLE is dependent on macroscopic parameters. As is shown in
+%% Fig.\ref{fig:LLEdistribution1}, we measured the LLEs along our trajectory and plot its distribution
+%% as a function of total energy.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tbph]
 \centering
@@
 \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
-\caption{LLE distribution for N=5, F0=1000, scan E. The size of bin is 0.01}\label{fig:LLEdistribution1}
+\caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
+  energies.  The color indicates the probability of a measured LLE value being found in a bin; the
+  bins are of size 0.01}\label{fig:LLEdistribution1}
 \end{figure}
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
-%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
-%\caption{``bone". top(bottom):modified(reversed)}
-%\end{figure}
-
-The LLE decrease with the growth of Energy.
-The crucial part is near E=5000.
-The most probable value of LLE goes down from 1 to 0.1,which indicate that the shortest time scale becomes longer than an oscillation period when E is larger than 5000, which is consistent with our prediction value of thermalization threshold.
-So there is a correspondence between energy thermalization and LLE.
-As E goes far beyond the thermalization threshold value, the LLE is restricted close to zero, suggesting the divergence of correlation time.
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+%% \begin{figure}[h]
+%% \centering
+%% \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
+%% \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
+%% \caption{``bone". top(bottom):modified(reversed)}
+%% \end{figure}
+
+The LLE decreases with the growth of energy. The critical part is near $E=5000$. The most probable
+value of LLE goes down from around 1 to around 0.1,which indicates that the shortest time scale
+becomes longer than an oscillation period when $E\gtrsim5000$.  This is consistent with our
+predicted thermalization threshold.  As $E$ increases far beyond the thermalization threshold value,
+the LLE distribution is close to zero, suggesting a divergence of relaxation time.
+%
+We have thus shown a correspondence between energy thermalization and LLE.
+
+\subsection{Shape of distribution in single-particle phase space}\label{section:Shape}
+
+We have studied thermalization in terms of energy.  More generally, thermalization may be taken to
+mean that a many-body system loses memory of its initial state.  In the single-particle phase-space
+picture, Figures \ref{fig:Breathingfrequency2_0} and \ref{fig:Breathingfrequency2_1}, our initial
+state is very special: The particles are lined up along the $X$ axis.  The effect of interaction is
+to distort this line toward a circularly symmetric distribution.  Thus, we would consider that the
+memory of the initial state is lost when the distribution of points in the $X$-$P$ plane are not
+elongated in any one direction.
+
+To quantify the shape of distribution in phase-space, we define a shape parameter $S$ measuring the
+degree of ellipticity:
+\begin{equation}
+S=\frac{a-b}{a+b}
+\end{equation}
+where $a$ and $b$ are long axis and short axis of inertia ellipse in phase space respectively. These
+can be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
+I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.  The shape parameter is $S=1$ for line-shaped
+distributions and $S=0$ for circularly symmertic distributions.
+
+------
 
 \section{Shape of Distribution in Phase-space}\label{section:Shape}
-When describing simple harmonic motion, it is usually convenient to use the language of phase-space (of single particle).
-In the phase-space, the motion becomes circular, so each of these particles has two independent degrees of freedom, i.e., modulus and phase angle.
-Here, ``independent" means that the simple harmonic oscillation never ``mix" these two degrees of freedom.
-In view of this, when it comes to ``thermalization", one will expect that the thermalization of energy, which is just the modulus, does not ensure the thermalization of phase angle.
-As ins explained in the Introduction part, in order to distinguish two kinds of meanings of ``thermalization", we will call the process of energy distribution going to equilibrium ``thermalization", while the process of phase angle going to equilibrium ``relaxation".
-The time scale of thermalization and relaxation could be quite different in principle.
-We will start with the configuration where particles' velocities are set to be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning.
-If the time scale of thermalization is much longer than that of relaxation, we will see cloud going to some stable shape in a short time (a circle if interaction is not significant compared to total energy) while the distribution of particle number along radius slowly evolves to Boltzmann distribution.
-If the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape or some oscillation between different shapes for a long time while the energy distribution is already Boltzmann.
+
+When describing simple harmonic motion, it is usually convenient to use the language of phase-space
+(of single particle). In the phase-space, the motion becomes circular, so each of these particles
+has two independent degrees of freedom, i.e., modulus and phase angle. Here, ``independent" means
+that the simple harmonic oscillation never ``mix" these two degrees of freedom. In view of this,
+when it comes to ``thermalization", one will expect that the thermalization of energy, which is just
+the modulus, does not ensure the thermalization of phase angle. As ins explained in the Introduction
+part, in order to distinguish two kinds of meanings of ``thermalization", we will call the process
+of energy distribution going to equilibrium ``thermalization", while the process of phase angle
+going to equilibrium ``relaxation". The time scale of thermalization and relaxation could be quite
+different in principle. We will start with the configuration where particles' velocities are set to
+be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning. If the
+time scale of thermalization is much longer than that of relaxation, we will see cloud going to some
+stable shape in a short time (a circle if interaction is not significant compared to total energy)
+while the distribution of particle number along radius slowly evolves to Boltzmann distribution. If
+the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape
+or some oscillation between different shapes for a long time while the energy distribution is
+already Boltzmann.
 
@@
 \end{equation}
-where a and b are long axis and short axis of inertia ellipse in phase space respectively.
-a,b can be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2}, I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.
-S=1 for line-shape distribution, S=0 for circular distribution.
-The advantage of defining the S lies in that S is independent of all rotating behavior of the cloud in phase-space and thus extract the information of shape alone.
-One could also use eigenvalues of quadrupole moment Q to define S.
-Two choice of definition is equivalent, since I and Q are only different up to a factor and an identity matrix.
+where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can
+be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
+I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$. S=1 for line-shape distribution, S=0 for circular
+distribution. The advantage of defining the S lies in that S is independent of all rotating behavior
+of the cloud in phase-space and thus extract the information of shape alone. One could also use
+eigenvalues of quadrupole moment Q to define S. Two choice of definition is equivalent, since I and
+Q are only different up to a factor and an identity matrix.
 
@@
 \section{Conclusion}
-We studied the nonequilibrium property of one-dimensional classical gas with finite range repulsive interaction.
-We first studied the relation between breathing mode frequency and interaction parameter as well as total energy.
-We found the breathing frequency could be estimated by eq.\ref{eq:breathingfrequency1}.
-And the mechanism behind this relation is that the momentum transfer which happens instantly in collision saves the particles some time from traveling this distance.
-So the physics is completely the same as hardcore particle.
-We found that the thermalization behavior is controlled by the competition between the interaction strength and the average energy.
-We point out that there could be two independent time scales in simple harmonic system in principle.
-One of them corresponds to the relaxation time of the energy distribution.
-The other one corresponds to the relaxation time of the angular distribution in phase space, which will determine the decay rate of the amplitude of the breathing mode.
-We have shown that in the low-energy regime, although the energy distribution reach Boltzmann distribution within several periods of oscillation, the shape keep oscillating for thousands of periods.
-%However, with the form of interaction we used, i.e.
-finite range constant repulsive force, we found those two time scales diverge only when interaction vanish, which is a trivial singular point.
-In addition, the relaxation behavior of the angular distribution and radial distribution in phase space are similar.
-We attribute it to the fact that there is no essential bias between angular and radial transfer in phase-space for this simple form of interaction.
-The shortest time scale is verified numerically by Largest Lyapunov Exponent.
-A further question could be asked is whether there is a subtle form of interaction that could give those two time scales essentially different behavior.
-The observation of two different time scales in one system would be interesting.
+
+Other forms of interaction.
+
+We studied the nonequilibrium property of one-dimensional classical gas with finite range repulsive
+interaction. We first studied the relation between breathing mode frequency and interaction
+parameter as well as total energy. We found the breathing frequency could be estimated by
+eq.\ref{eq:breathingfrequency1}. And the mechanism behind this relation is that the momentum
+transfer which happens instantly in collision saves the particles some time from traveling this
+distance. So the physics is completely the same as hardcore particle.
+
+We found that the thermalization behavior is controlled by the competition between the interaction
+strength and the average energy. We point out that there could be two independent time scales in
+simple harmonic system in principle. One of them corresponds to the relaxation time of the energy
+distribution. The other one corresponds to the relaxation time of the angular distribution in phase
+space, which will determine the decay rate of the amplitude of the breathing mode. We have shown
+that in the low-energy regime, although the energy distribution reach Boltzmann distribution within
+several periods of oscillation, the shape keep oscillating for thousands of periods.
+
+%However, with the form of interaction we used, i.e. finite range constant repulsive force, we found
+%those two time scales diverge only when interaction vanish, which is a trivial singular point. In
+%addition, the relaxation behavior of the angular distribution and radial distribution in phase
+%space are similar. We attribute it to the fact that there is no essential bias between angular and
+%radial transfer in phase-space for this simple form of interaction. The shortest time scale is
+%verified numerically by Largest Lyapunov Exponent. A further question could be asked is whether
+%there is a subtle form of interaction that could give those two time scales essentially different
+%behavior. The observation of two different time scales in one system would be interesting.
 
@@
 
+\bibitem{Dorfman_book_1999} J.~P.~Dorfman, ``An Introduction to Chaos in Non-equilibrium Statistical
+  Mechanics'', Cambridge University Press, 1999.
+
+\bibitem{Dumas_book_KAMstory} H.~S.~Dumas: ``The KAM Story: A Friendly Introduction to the Content,
+History, and Significance of Classical Kolmogorov-Arnold-Moser Theory'', World Scientific, 2014.
+
+\bibitem{Boltzmann_legacy_book} ``Boltzmann's Legacy'', edited by G.~Gallavotti, W.~L.~Reiter, and
+  J.~Yngvason; European Mathematical Society (2007).
+
+\bibitem{EckmannRuelle_RMP85}  
+  J.-P.~Eckmann and D.~Ruelle,
+  ``Ergodic theory of chaos and strange attractors'', 
+  \emph{Rev. Mod. Phys.}, {\bf 57}, 617  (1985).
+
+\bibitem{NewtonsCradle_Nature06}  
+T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, ``A quantum Newton's cradle'', {\em Nature}, {\bf 440,} 900 (2006).
+
+\bibitem{Naegerl_Science2009} E.~Haller, M.~Gustavsson, M.~J.~Mark, 
+J.~G.~Danzl,  R.~Hart, G.~Pupillo, H.-C.~N\"agerl, Science \textbf{325}, 1224 
+(2009).
+
+\bibitem{collective_modes_early_papers}
+S.~Stringari, Phys.\ Rev.\ Lett.\ \textbf{77}, 2360 (1996); 
+%
+M.-O.~Mewes, M.~R.~Andrews, N.~J.~van~Druten, D.~M.~Kurn, D.~S.~Durfee, 
+C.~G.~Townsend, and W.~Ketterle, Phys.\ Rev.\ Lett.\ \textbf{77}, 988 (1996);
+%
+M.~Amoruso, I.~Meccoli, A.~Minguzzi, and M.~P.~Tosi, Eur.\ Phys.\ J.~D \textbf{8}, 361 (2000);
+%
+R.~Combescot and X.~Leyronas, Phys.\ Rev.\ Lett.\ \textbf{89}, 190405 (2002);
+%
+F.~Chevy, V.~Bretin, P.~Rosenbusch, K.~W.~Madison, and J.~Dalibard, 
+Phys.\ Rev.\ Lett.\ \textbf{88}, 250402 (2002);
+%
+C.~Menotti and S.~Stringari, ``Collective oscillations of a one-dimensional trapped Bose-Einstein
+gas'', {\em Phys.\ Rev.\ A} \textbf{66}, 043610 (2002).
+%
+J.~Fuchs, X.~Leyronas, and R.~Combescot, Phys.\ Rev.\ A \textbf{68}, 043610 (2003).
+
+\bibitem{PitaevskiiRosch_PRA97}
+%
+L.~P.~Pitaevskii and A.~Rosch, {\em Phys.\ Rev.\ A} \textbf{55}, R853 (1997);
+
+\bibitem{Esslinger_exp_PRL2003} H.~Moritz, T.~St\"oferle, M.~K\"ohl, and 
+T.~Esslinger,
+Phys.\ Rev.\ Lett.\ \textbf{91}, 250402 (2003).
+
+\bibitem{Wetterich_JPB2011}
+I.~Boettcher, S.~Floerchinger, and C.~Wetterich, J.~Phys.\ B \textbf{44}, 235301 (2011).
+
+\bibitem{Tschischik_BHbreathing_PRA_2013} W.~Tschischik, R.~Moessner, M.~Haque, Phys.\ Rev.~A 
+  \textbf{88}, 063636 (2013).
+
+\bibitem{KroenkeSchmelcher_BM} R.~Schmitz, S.~Kr\"onke, L.~Cao, and 
+  P.~Schmelcher, Phys.\ Rev.\ A \textbf{88}, 043601 (2013).
+
+\bibitem{Mazets_1Dbreathing_EPJD11}
+I. E. Mazets, ``Integrability breakdown in longitudinaly trapped, one-dimensional bosonic gases'', 
+{\em Eur.~Phys.~J.~D} {\bf 65}, 43 (2011).
+
+%%  \bibitem{GaoYu_fermionbreathing_PRA12} 
+%% Chao Gao and Zhenhua Yu, 
+%%   ``Breathing mode of two-dimensional atomic Fermi gases in harmonic traps'', 
+%% {\em Phys. Rev. A} {\bf 86}, 043609 (2012).
+
+\bibitem{fermion2Dbreathing}
+%
+
+E.~Vogt, M.~Feld, B.~Fr\"ohlich, D.~Pertot, M.~Koschorreck, and M.~K\"ohl, ``Scale Invariance and
+Viscosity of a Two-Dimensional Fermi Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 070404 (2012).
+%
+\\ 
+%
+Chao Gao and Zhenhua Yu, ``Breathing mode of two-dimensional atomic Fermi gases in harmonic traps'',
+{\em Phys. Rev. A} {\bf 86}, 043609 (2012).
+%
+\\ 
+%
+J.~Hofmann, ``Quantum Anomaly, Universal Relations, and Breathing Mode of a Two-Dimensional Fermi
+Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 185303 (2012).
+%
+\\ 
+%
+S.~K.~Baur, E.~Vogt, M.~K\"ohl, and G.~M.~Bruun, ``Collective modes of a two-dimensional spin-1/2
+Fermi gas in a harmonic trap'', {\em Phys. Rev. A} {\bf 87}, 043612 (2013).
+%
+\\ 
+%
+B.~P.~van~Zyl, E.~Zaremba, and J.~Towers,
+``Collective excitations of a harmonically trapped, two-dimensional, spin-polarized dipolar Fermi
+gas in the hydrodynamic regime'', 
+{\em Phys. Rev. A} {\bf 90}, 043621 (2014). 
+%
+\\ 
+%
+Yi-Cai Zhang and Shizhong Zhang, ``Strongly interacting p -wave Fermi gas in two dimensions:
+Universal relations and breathing mode'', {\em Phys. Rev. A} {\bf 95}, 023603 (2017).
+
+%% \bibitem{ZarembaTowers_PRA2014} B.~P.~van~Zyl, E.~Zaremba, and J.~Towers, Phys. Rev. A \textbf{90},
+%%   043621 (2014).
+
+\bibitem{Stringari_lowDcollective_PRA15}
+G.~De~Rosi and S.~Stringari, ``Collective oscillations of a trapped quantum gas in low dimensions'', 
+{\em Phys. Rev. A} {\bf 92}, 053617 (2015).
+
+\bibitem{GrimmSmith_unitaryfermions_PRA08}
+S.~Riedl, E.~R.~S\'anchez~Guajardo, C.~Kohstall, A.~Altmeyer, M.~J.~Wright, J.~Hecker~Denschlag,
+R.~Grimm, G.~M.~Bruun, and H.~Smith, ``Collective oscillations of a Fermi gas in the unitarity
+limit: Temperature effects and the role of pair correlations'', Phys. Rev. A {\bf 78}, 053609
+(2008).
+
+\bibitem{Bouchoule_PRL2014}
+B.~Fang, G.~Carleo, A.~Johnson, and I.~Bouchoule,  Phys.\ Rev.\ Lett.\ 
+\textbf{113}, 035301 (2014).
+
+\bibitem{our_superTG_PRA_2015} W.~Tschischik and M.~Haque, Phys.\ Rev.~A 
+  \textbf{91}, 053607 (2015).
+
+\bibitem{Tschischik_ladder_PRA15} W.~Tschischik, R.~Moessner, and M.~Haque, ``Bose-Hubbard ladder
+  subject to effective magnetic field: Quench dynamics in a harmonic trap'',
+{\em Phys. Rev. A},  {\bf 92}, 023845 (2015).
+
+% Dipole mode of a strongly correlated one-dimensional Bose gas in a split trap: 
+% parity effect and barrier renormalization
+\bibitem{Cominotti_2015} M.~Cominotti, F.~Hekking, and A.~Minguzzi, 
+arXiv:1503.07776.
+
+\bibitem{STG_Chen-etal_PRA2010} S.~Chen, L.~Guan, X.~Yin, Y.~Hao, and X-W.~Guan,   Phys.\ Rev.\ A
+  \textbf{81}, 031609(R) (2010).
+
+\bibitem{STG_Astrakharchik_PRL2005} G.~E.~Astrakharchik, J.~Boronat, J.~Casulleras, and
+  S.~Giorgini, Phys.\ Rev.\ Lett.\ \textbf{95}, 190407 (2005).
+
+\bibitem{1D_breathing_mode_recent}  
+A.~Iu.~Gudyma, G. E.~Astrakharchik, and M.~B.~Zvonarev, ``Reentrant behavior of the
+breathing-mode-oscillation frequency in a one-dimensional Bose gas'', 
+Phys. Rev. A \textbf{92}, 021601(R) (2015). \\ 
+%
+S. Choi, V. Dunjko, Z.~D.~Zhang, and M.~Olshanii,
+``Monopole Excitations of a Harmonically Trapped One-Dimensional Bose Gas from the Ideal Gas to the
+Tonks-Girardeau Regime'', 
+{\em Phys. Rev. Lett.} \textbf{115}, 115302 (2015)
+%
+\\
+%
+X.-L.~Chen, Y.~Li, and H.~Hu,  Phys.\ Rev.\ A \textbf{91}, 063631 (2015).
+
+\bibitem{br_mode_long_range_interactions} 
+%
+S.~Bauch, K.~Balzer, C.~Henning, and M.~Bonitz, Phys. Rev. B \textbf{80}, 054515 
+(2009);
+%
+\\
+%
+J.~W.~Abraham, K.~Balzer, D.~Hochstuhl, and M.~Bonitz, Phys. Rev. B \textbf{86}, 
+125112 (2012);
+%
+\\
+%
+C.~R.~McDonald, G.~Orlando, J.~W.~Abraham, D.~Hochstuhl, M.~Bonitz, and T.~Brabec, Phys.\ Rev.\
+Lett.\ \textbf{111}, 256801 (2013);
+%
+\\
+%
+J.~W.~Abraham, M.~Bonitz, C.~McDonald, G.~Orlando, and T.~Brabec, New J.~Phys \textbf{16}, 013001
+(2014).
+
+\bibitem{Bonitz_Review} J.~W.~Abraham, and M.~Bonitz, ``Quantum Breathing Mode of Trapped Particles:
+  from nanoplasmas to ultracold gases'', {\em Contributions to Plasma Physics}, \textbf{54}, 27
+  (2014).
+
+\bibitem{KohnMode} L.~Brey, N.~F.~Johnson, and B.~I.~Halperin, Phys.\ Rev.\ B 
+  \textbf{40}, 10647 (1989).  M.~Bonitz, K.~Balzer, and R.~van~Leeuwen, 
+  {\em Phys. Rev. B} \textbf{76}, 045341 (2007).
+
+\bibitem{DoyonSpohn_JSTAT17} B.~Doyon and H.~Spohn, ``Dynamics of hard rods with initial domain wall
+  state'', {\em J.~Stat. Mech.}, {\bf 2017}, 073210 (2017).
+
+\bibitem{Moore_arXiv17.10} X.~Cao, V.~B.~Bulchandani, J.~E.~Moore, ``Incomplete thermalization from
+  trap-induced integrability breaking: lessons from classical hard rods'', arXiv:1710.09330.
+
+\bibitem{Guery-Odelin1999}
+D.~Gu\'ery-Odelin, F.~Zambelli, J.~Dalibard, and S.~Stringari, ``Collective
+  oscillations of a classical gas confined in harmonic traps,'' {\em Phys. Rev.
+  A}, {\bf 60}, 4851 (1999).
+
+\bibitem{Cornell_classsical_3Dexpt_NatPhys15} D.~S.~Lobser, A.~E.~S.~Barentine, E.~A.~Cornell, and
+  H.~J.~Lewandowski, ``Observation of a persistent non-equilibrium state in cold atoms'', Nat Phys
+  {\bf 11}, 1009 (2015).
+
 \bibitem{Dalfovo1997}
@@
   ``Collective and single-particle excitations of a trapped bose gas,'' {\em
-  Phys. Rev. A}, vol.~56, pp.~3840--3845, Nov. 1997.
+  Phys. Rev. A}, {\bf 56}, 3840 (1997).
 
@@
 
-\bibitem{Guery-Odelin1999}
-D.~Gu\'ery-Odelin, F.~Zambelli, J.~Dalibard, and S.~Stringari, ``Collective
-  oscillations of a classical gas confined in harmonic traps,'' {\em Phys. Rev.
-  A}, vol.~60, pp.~4851--4856, Dec 1999.
-
 \bibitem{Tsuchiya2000}
-T.~Tsuchiya and N.~Gouda, ``Relaxation and lyapunov time scales in a
-  one-dimensional gravitating sheet system,'' {\em Phys. Rev. E}, vol.~61,
-  pp.~948--951, Jan. 2000.
+T.~Tsuchiya and N.~Gouda, ``Relaxation and Lyapunov time scales in a
+  one-dimensional gravitating sheet system,'' {\em Phys. Rev. E}, {\bf 61}, 948 (2000).
 
@@
 
+\bibitem{GueryOdelin_thermalization_PRA06} M.~Anderlini and D.~Gu\'ery-Odelin, ``Thermalization in
+  mixtures of ultracold gases'', {\em Phys. Rev. A} {\bf 73}, 032706 (2006).
+
 \end{thebibliography}

### 2017-12-15 draft_07.tex
Reasonably complete draft

--- 2017-12-14 draft_06.tex
@@
-\documentclass[onecolumn,pra]{revtex4-1}
+\documentclass[a4paper, onecolumn]{revtex4-1}
 
@@
 %\documentclass[reprint, amsmath,amssymb,aps,]{revtex4-1}
-
-\bibliographystyle{apsrev4-1}
 
@@
  \usepackage{subfigure}
- \usepackage{enumerate}
- \usepackage{verbatim}% for \begin{comment} \end{comment}
+% \usepackage{enumerate}
+
+% \usepackage{verbatim}% for \begin{comment} \end{comment}
+
 \usepackage{color}
@@
 \begin{document}
-\title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
+
+\title{Classical Dynamics of Harmonically Trapped Interacting Particles}
 
@@
 
-Abstract --  to be written last
+  Motivated by the interest in the dynamics of trapped quantum gases, we study the microcanonical
+  dynamics of a trapped gas of classical particles interacting with a finite-range interaction of
+  tunable strength.  We examine two questions which have been of interest in quantum dynamics: (1)
+  the breathing mode (size oscillation) dynamics of the trapped gas and the dependence of the
+  breathing frequency on the interaction strength, and (2) the long-time relaxation and possible
+  thermalization of the finite isolated gas.
 
@@
 by the availability of experimental systems, e.g., trapped ultracold atomic and ionic systems, where
-non-dissipative dynamics can be studied explicitly due to excellent isolation (CITE).  There are
-also fundamental reasons for studying dynamics in isolation: recent activity has led to advances in
-the understanding of basic principles connecting quantum dynamics, quantum chaos and the emergence
-of statistical mechanics and thermalization (CITE).  For classical many-body systems, explorations
-of the connections between microscopic dynamical rules, chaos, ergodicity and statistical mechanics
-have a much longer history, dating back to the time of Boltzmann and Poincare.
+non-dissipative dynamics can be studied explicitly due to excellent isolation.  There are also
+foundational reasons for studying quantum dynamics in isolation: recent activity has led to advances
+in the understanding of basic principles connecting quantum dynamics, quantum chaos and the
+emergence of statistical mechanics and thermalization (CITE).  For classical many-body systems,
+explorations of the connections between microscopic dynamical rules, chaos, ergodicity and
+statistical mechanics have a much longer history, dating back to the time of Boltzmann and Poincare
 \cite{Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85}.
@@
 in a one-dimensional harmonic trap.  The analogs of two questions, studied intensively in the
-quantum literature, will be investigated: (1) the influence of interactions on the breathing mode
-frequency of the trapped gas, and (2) the relaxation and possible thermalization of the finite
-system under its own evolution, in the absence of any external baths or dissipation mechanisms.
-
-Experiments with cold atoms, which have had an essential motivational role for the current interest
-in many-body quantum dynamics, are generally performed in a trapping potential, either optical or
+quantum literature, will be investigated for this classical system: (1) the influence of
+interactions on the breathing mode frequency of the trapped gas, and (2) the relaxation and possible
+thermalization of the finite system under its own evolution, in the absence of any external baths or
+dissipation mechanisms.
+
+Experiments with cold atoms, which have an essential motivational role for the current interest in
+many-body quantum dynamics, are generally performed in a trapping potential, either optical or
 magnetic.  As a result, in the last two decades many questions of many-body quantum physics have
 been reformulated in the presence of a harmonic trap.  The presence of a harmonic trap often results
-in new dynamical phenomena; for example the motion of vortices in a trapped condensate (CITE) has
-new features (such as precession) compared to vortex motion in uniform condensates (CITE).  Trapping
+in new dynamical phenomena.  For example, the motion of vortices in a trapped condensate (CITE) has
+new features, such as precession, compared to vortex motion in uniform condensates (CITE).  Trapping
 also results in new collective phenomena which have no analog in uniform situations: for example,
@@
 
-The presence of harmonic trapping is thus a paradigmatic aspect in the field of quantum many-body
-dynamics.  This motivates our study of classical dynamics of trapped interacting systems.  Similarly
-motivated by quantum dynamics, classical trapped dynamics of hard rods has recently been studied in
-Refs.\ \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10}, focusing on integrability-breaking effects of
-the trap.  In this work, we consider trapped classical particles which interact via a simple
-finite-range potential between any pair of particles: a constant repulsive force acts whenever the
-particles are less than a certain distance apart.  The interaction strength can be tuned, leading to
-different regimes of behavior.
-
-Our first theme will be a study of the breathing mode of the classical interacting gas, and the
-effect of interactions on the frequency of the breathing mode.  In the quantum case, this has long
-been a topic of interest for both fermions and bosons.  For bosons with short-range interactions,
+The presence of harmonic trapping is thus a paradigmatic aspect in the field of quantum
+non-equilibrium physics.  This motivates our study of classical dynamics of trapped interacting
+particles.  Similarly motivated by quantum dynamics, classical trapped dynamics of hard rods has
+recently been studied in Refs.\ \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10}, focusing on
+integrability-breaking effects of the trap.  In this work, we consider trapped classical particles
+which interact via a simple finite-range potential between any pair of particles: a constant
+repulsive force acts whenever the particles are less than a certain distance apart.  The interaction
+strength can be tuned, leading to different regimes of behavior.
+
+Our first theme will be the breathing mode of the classical interacting gas, and the effect of
+interactions on the frequency of the breathing mode.  In the quantum case, this has long been a
+topic of interest for both bosons and fermions.  For bosons with short-range (contact) interactions,
 the situation has been studied in one, two and three dimensions.  At zero interactions, the
-breathing mode is twice the trapping frequency $\omega_0$ (assuming isotropic trapping) in each
-case.  A mean field (Gross-Pitaevskii) calculation gives the frequency to be $\sqrt{D+2}$ times the
+breathing mode is twice the trapping frequency $\omega_0$ in each case, assuming isotropic trapping.
+A mean field (Gross-Pitaevskii) calculation gives the frequency to be $\sqrt{D+2}$ times the
 trapping frequency, where $D$ is the spatial dimension.  For three-dimensional (3D) traps, the
@@
 $\sqrt{5}\omega_0$ at large interactions.  For 2D traps, the breathing frequency is exactly
-$2\omega_0$ for any interaction strength \cite{PitaevskiiRosch_PRA97}.  This remarkable result
-follows from a symmetry in 2D.  Classical trapped particles with scale-invariant interaction
-potentials also have breathing frequency $2\omega_0$ independent of interaction strength
-\cite{PitaevskiiRosch_PRA97}.  The interaction dependence in 1D (trapped Lieb-Liniger gas) is also
-remarkable: as the interaction is increased, the breathing frequency first decreases from
-$2\omega_0$ to the mean-field prediction $\sqrt{3}\omega_0$, and then at larger interactions
-increases again, returning to $2\omega_0$ in the infinite interaction (Tonks-Girardeau) limit
-\cite{Naegerl_Science2009, Tschischik_BHbreathing_PRA_2013, 1D_breathing_mode_recent,
-  Bouchoule_PRL2014, KroenkeSchmelcher_BM}.
+$2\omega_0$ for any interaction strength \cite{PitaevskiiRosch_PRA97}, due to a symmetry.  Classical
+trapped particles with scale-invariant interaction potentials also have breathing frequency
+$2\omega_0$ independent of interaction strength \cite{PitaevskiiRosch_PRA97}.  The interaction
+dependence in 1D (trapped Lieb-Liniger gas) is also remarkable: as the interaction is increased, the
+breathing frequency first decreases from $2\omega_0$ to the mean-field prediction
+$\sqrt{3}\omega_0$, and then at larger interactions increases again, returning to $2\omega_0$ in the
+infinite interaction (Tonks-Girardeau) limit \cite{Naegerl_Science2009,
+  Tschischik_BHbreathing_PRA_2013, 1D_breathing_mode_recent, Bouchoule_PRL2014,
+  KroenkeSchmelcher_BM}.
 %
@@
 
-In this work, we use an explicit microscopic model, rather than a Boltzmann equation approach.
-Unlike the quantum case, the harmonic potential does not impose a length scale or an energy scale.
-The interaction range can thus be scaled away by a redefinition of length, i.e., by measuring
-lengths in units of the interaction range.  There are only two important parameters determining the
-system behavior, namely the interaction strength and the energy per particle.  We find that the
-breathing mode frequency has a non-monotonic dependence on the interaction parameter.  At small
-interactions, when the particles pass through each other, the effect of collisions is to slow down
-the dynamics, so that the breathing frequency drops below the non-interacting value $2\omega_0$.  At
-very large interactions, the particles bounce off each other, a process which speeds up the size
-oscillations, resulting in the breathing frequency being larger than $2\omega_0$.
-
-Our second theme is the process of relaxation at long timescales, and possible thermalization.  This
-topic is also motivated by intense recent research in the quantum context.  In quantum isolated
+In this work, we use an explicit microscopic model treated microcanonically, rather than a Boltzmann
+equation approach.  Unlike the quantum case, the harmonic potential does not impose a length scale
+or an energy scale.  The interaction range can thus be scaled away by a redefinition of length,
+i.e., by measuring lengths in units of the interaction range.  There are thus only two important
+parameters determining the system behavior, namely the interaction strength and the energy per
+particle.  We find that the breathing mode frequency has a non-monotonic dependence on the
+interaction parameter.  At small interactions, when the particles pass through each other, the
+effect of collisions is to slow down the dynamics, so that the breathing frequency drops below the
+non-interacting value $2\omega_0$.  At very large interactions, the particles bounce off each other,
+a process which speeds up the size oscillations, resulting in the breathing frequency being larger
+than $2\omega_0$.
+
+Our second theme is the process of relaxation at longer timescales, and possible thermalization.
+This topic is also motivated by intense recent research in the quantum context.  In quantum isolated
 systems, thermalization is now understood in terms of the so-called eigenstate thermalization
@@
 the connection between microscopic dynamics and statistical mechanics has been continually studied
-since the 19th century.  It is generally understood that systems with positive Lyapunov exponents
-
----------
-
-Stat-mech from the `bottom up'.  Find papers that do the same.
-
-More detailed citations of breathing mode.  There are also papers on classical breathing mode, e.g.,
-by Bonitz.
-
-Controlled and tunable experimental realizations of confined quantum systems with ultracold atoms
-enable nonequilibrium studies of quantum many-body states in novel geometries. A common feature of
-many cold-atom experiments is the confinement of a many-body system in a harmonic trap. Trapping
-introduces many distinctive features which have no analog in uniform many-body states, including
-collective excitations such as breathing modes, dipole modes, and scissors modes. Such trap-related
-collective modes have been widely studied both experimentally and theoretically for continuum
-systems, especially in the mean-field regime, since the early days after quantum degeneracy was
-achieved with trapped atoms \cite{Dalfovo1997}\cite{Jin1996}.
-
-In mean-field perspective, the physics of atom gas in Bose-Einstein Condensation can be described by
-the Gross-Pitaevskii equation\cite{Dalfovo1999}\cite{Stringari1996}, where the breathing frequency
-for 1D Bose gas is calculated to be $\Omega_{GP}=\sqrt{3}\omega_0$. Meanwhile, the experiment of
-Ref.\cite{Haller2009} has found a regime of interactions where the breathing-mode frequency
-approaches the Gross-Pitaevskii prediction. However, since mean-field approach which generally omit
-quantum fluctuation is successful in this problem, one may wonder how quantum effects play the role
-in the breathing mode. Thus, a natural question would be asked is that how breathing frequency is
-dependent on interaction for classical gas. Though generated in BEC, the breathing mode phenomenon
-is not restricted to BEC. For a classical gas, the breathing mode still can be excited with a
-quench. Usually, a good knowledge of the classical version may help us understand the quantum one
-better. David Guery-Odelin, Francesca Zambelli, Jean Dalibard, and Sandro Stringari answered this
-question in ref.\cite{Guery-Odelin1999}. They used the Boltzmann equation as well as molecular
-dynamics simulation to study the monople mode and quarulple mode of the 2-D classical gas in a
-harmonic trap. But in that work, the interaction is elastic collision,
-i.e. zero-range-infinite-strength interaction. We think introducing a finite range for the repulsive
-interaction will definitely enrich the physics in this system which looks simple, thus producing a
-different equilibrium and non-equilibrium behaviour. Surprisingly, to the best of our knowledge,
-there is no in-depth study of this case. For this reason, more study is necessary.
-
-On the other hand, in a nonquilibrium many-body system, a more intriguing question is about its
-thermalization or relaxation property. Thermalization is among the most fundamental processes for a
-many-body interacting system. All systems do not thermalize. An example is the Fermi-Pasta-Ulam
-paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a
-long time. A lot of research on thermalization property has been done in other classical
-system. Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with
-Lyapunov exponents. Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment
-by examine the canonical distribution of a subsystem . In our paper, we will also probe the system's
-thermalization time scales from the perspective of canonical distribution as well as Lyapunov
-exponent.
-
-%With these approaches, we will show that the thermalization time scale manifest a
-%competition between total energy and interaction energy, so there is not any singular
-%behavior in the thermalization time scales except the trivial divergence at zero
-%interaction.
-
-------------------
-
-Breathing frequency, comparisong to quantum case ------
-
-Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state
-and then suddenly vary some parameter by a little, for instance,
-$\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R
-of the cloud oscillating at a certain frequency, which is usually called ``breathing mode".
-
-However, it is quite different in the classical version. Firstly, it is no longer necessary to focus
-on ground state. In quantum case, the reason why we care about ground state and low lying
-excitations is that BEC occur at low temperature. But in classical case, there is no BEC. So it is
-not necessary to focus on low lying excitations in classical case. Besides, since classical limit is
-$\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so even in low energy
-regime, the classical behaviors could be quite different from the quantum one. Secondly, it is no
-longer necessary to vary parameters ``by a little" in the quench. In quantum case, the small quench
-$\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum of Hamiltonian is shifted
-slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}). But in classical case,
-since $\hbar$ vanishes, no matter how small the quench is, the reason that cause beats in quantum
-case no longer work in classical context. Thus it is not necessary to limit ourselves to small
-quench.
-
-Let's consider quenching the harmonic potential, i.e.,
-$\omega_0\rightarrow\omega_0'=\omega_0+\Delta\omega_0$. We notice that X and P (scaled) are
-symmetric for simple harmonic oscillator. In weak interaction limit, the distribution cloud should
-be circular when the gas is completely thermalized. The difference between thermalized cloud before
-and after quench is that they are circular under different scaling ratio of P and X axis. If we look
-at both of them in the phase-space rescaled according to $\omega_0'$, we will find shape of the
-cloud before the quench is an ellipse while the final one is a circle.
-
-------------------
-
-The words ergodic, relaxation and thermalization
-
-Loss of memory of initial state --- our two definitions
-
-------------------
-
-This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
-reduce the number of parameters of the system. In addition, we briefly observe the ground state and
-reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak
-interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing
-frequency according to its mechanism, and compare that with our numerical simulation
-result. Besides, we also introduce a rotating frame method of treating this problem, which is a
-convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we
-focus on the thermalization property. We first examine the canonical distribution of energy to find
-out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very
-large. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and
-confirm the former discussion. Then we point out that there are two kind of thermalization behavior
-that could be measured in this system, one is about energy distribution while another is about shape
-of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
--- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
-when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
-it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
-the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
-discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
-
-\section{The model and its equilibrium properties}\label{section:preparation}
+since the 19th century \cite{Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book,
+  EckmannRuelle_RMP85}.  It is generally understood that systems with nonzero Lyapunov exponents,
+i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided there are enough
+degrees of freedom.  As in the quantum case, finite systems are particularly intricate.  In finite
+systems, defining thermalization is trickier as most observables will fluctuate or oscillate
+substantially.  In addition, the influence of Kolmogorov-Arnold-Moser (KAM) orbits may play a role
+in preventing thermalization; it is generally believed that the fraction of phase space where KAM
+physics might be relevant decreases rapidly with particle number \cite{Dumas_book_KAMstory}.
+
+In our work, we examine the relaxation of our trapped interacting classical system, explicity for
+finite numbers of particles.  We look for thermalization within finite timescales, by sampling
+single-particle energies periodically until such timescales and comparing the distribution of
+single-particle energies with the Boltzmann distribution.  We show that whether or not the system
+thermalizes in this sense depends on the ratio of interaction strength and energy per particle.  We
+also show that this result is reflected in the finite-time Lyapunov exponents of the system.
+%
+We also examine another notion of thermalization, according to which a system is thermalized when it
+loses memory of initial state, by following the dynamics of the particle distribution in phase
+space.  Remarkably, we find that one can observe energy thermaliztion even at timescales when the
+shape of the phase space distribution continues to perform seemingly coherent oscillations.
+
+There is a significant literature on calculating Lyapunov exponents in model statistical-mechanics
+systems and thus exploring ergodicity \cite{Dorfman_book_1999} (CITE).  This provides intuition of
+what types of microscopic interactions are likely to produce thermalizability, and is an important
+step in the program of understanding statistical mechanics ``from the bottom up''.  However, we are
+not aware of a significant literature on following explicitly the microcanonical dynamics of
+statistical-mechanical or few-body systems.  Several such studies have appeared recently (CITE),
+motivated by the quantum dynamics literature, like the present work.  A few earlier studies have
+also examined thermalization dynamics in one dimensional gravitational systems \cite{Yawn1997,
+  Tsuchiya2000}.
+%
+Investigating such real-time dynamics can be expected to provide insights on the timescales and
+microscopic mechanisms involved in the emergence of statistical mechanics from collections of
+particles.
+
+This paper is organized as follows: In Section \ref{sec:preparation}, we introduce the Hamiltonian,
+identify and introduce the essential scales, and describe some aspects of the model and our
+simulations.  The breathing frequency is treated in Section \ref{sec:breathing}.  We explain the
+main features using both real-space and phase-space pictures of the interaction process, obtain
+estimates for the interaction- and energy-dependence of the frequency shift, and compare these
+predictions with numerics.  Section \ref{sec:relaxation} treats relaxation and thermalization.  We
+propose a condition for relaxation in reasonable timescales from considerations of few-body
+dynamics, compare the energy distribution with the Boltzmann distribution, show how the largest
+finite-time Lyapunov exponent distribution reflects the relaxation condition, and examine shape
+dynamics of the particle distribution in phase space.  Concluding remarks appear in Section
+\ref{sec:concl}.
+
+%% This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to
+%% reduce the number of parameters of the system. In addition, we briefly observe the ground state and
+%% reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak
+%% interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing
+%% frequency according to its mechanism, and compare that with our numerical simulation
+%% result. Besides, we also introduce a rotating frame method of treating this problem, which is a
+%% convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we
+%% focus on the thermalization property. We first examine the canonical distribution of energy to find
+%% out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very
+%% large. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and
+%% confirm the former discussion. Then we point out that there are two kind of thermalization behavior
+%% that could be measured in this system, one is about energy distribution while another is about shape
+%% of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
+%% -- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
+%% when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
+%% it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
+%% the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
+%% discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
+
+\section{The model and its equilibrium properties}\label{sec:preparation}
 
@@
 \begin{equation}
-H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i
-v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
+  H ~=~
+  \frac{1}{2}m\omega_0^2\sum_{i}x_i^2
+  ~+~ \frac{1}{2}m\sum_i  v_i^2
+  ~+~ \sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
 \label{eq:preparation2}
@@
 It is useful to rescale the quantities.  We will measure distance, time, energy and force in units
-of $\sigma$, $1/\omega$, $m\omega_0^2\sigma^2$ and $m\omega_0^2\sigma$ respectively:
+of $\sigma$, $1/\omega_0$, $m\omega_0^2\sigma^2$ and $m\omega_0^2\sigma$ respectively:
 \begin{equation} \label{eq:transform}
@@
 rescaling is equivalent to setting $\sigma$, $\omega_0$ and $m$ to $1$; this is what we do in our
-numerical simulation.  In the rest of this paper, we will use ``E" and ``$F_0$" to denote the
+numerical simulation.  In the rest of this paper, we will use ``$E$" and ``$F_0$" to denote the
 reduced versions $\tilde{H}$ and $\tilde{F_0}$.
@@
 and refer to this quantity as the `radius' or `cloud radius'.
-
+%
 In the dilute gas limit, there are few or no interactions occuring at most times.  Thus the energy
@@
 behave as hard rods which bounce off each other very rapidly, so that at most instants one can
-expect no collisions to be taking place.  It is also expected to be a good approximation at very
-small $F_0$ since we can then simply neglect the interaction energy.  Thus, we will use this as a
-common estimate for $R$ in terms of the energy.
+expect no collisions to be taking place, provided the gas is dilute.  It is also expected to be a
+good approximation at very small $F_0$ since we can then simply neglect the interaction energy.
+Thus, we will use this as a common estimate for $R$ in terms of the energy.
 
@@
 excitation involves independent oscillation of the particles around their equilibrium position.
-
+%
 In this regime, the distance between the leftmost and rightmost particles is at most $\sigma=1$.
@@
 
-\subsection{Phase space snapshots}
+\subsection{Phase space distribution}
 
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure*}
+\begin{figure*}[tbph]
 \includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.pdf}  
@@
 
-\section{Breathing Frequency}\label{section:breathing frequency}
+\section{Breathing Frequency}\label{sec:breathing}
 
@@
 $R$), so that the frequency of $R(t)$ is $\omega_B=2$.  When there is interaction, the frequency
-will get shifted: $\omega_B = 2+\delta$.  We measure the radius of the cloud $R(t)$ and get the
-frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak frequency
-near 2 as the breathing mode frequency.
-
-The frequency measured in this way for different $E$ and $F_0$ is shown in the
-Fig.\ref{fig:Breathingfrequency1}, plotted as a function of $F_0$.  The points each correspond to
-breathing-mode dynamics following from a single initial state; there is no averaging.  The curves
-therefore show some randomness.  However, two prominent features are clear from these curves.  At
-large interactions, $F_0\gg E$, the breathing frequency is larger than $2$, and saturates around a
-value which decreases with the system energy $E$.  At small interactions, the breathing frequency is
-actually smaller than the non-interacting value $2$.
+will get shifted: $\omega_B = 2+\delta$.  Numerically, we measure the radius of the cloud $R(t)$ and
+get the frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak
+frequency near 2 as the breathing mode frequency.
+
+\subsection{Interaction-dependence}
+
+The frequency measured numerically for different $E$ and $F_0$ is shown in Figure
+\ref{fig:Breathingfrequency1} for a system with five particles, plotted as a function of $F_0$.  The
+points each correspond to breathing-mode dynamics following from a single initial state; there is no
+averaging.  The curves therefore show some noise.  However, two prominent features are clear from
+these curves.  At large interactions, $F_0\gg E$, the breathing frequency is larger than $2$, and
+saturates around a value which decreases with the system energy $E$.  At small interactions, the
+breathing frequency is actually smaller than the non-interacting value $2$.
 
@@
 real-space picture explains both effects qualitatively as well.  For very large $F_0$, when the
-interaction is `hard-core'-like, two particles exchange momentum immediately at a collision.  By
-exchanging the labels of the particles during the collision, this can be interpreted as follows:
+interaction is `hard-core'-like, two particles exchange momentum instantaneously during a collision.
+By exchanging the labels of the particles during the collision, this can be interpreted as follows:
 particle $A$ carrying momentum $P_A$ jumps by distance $\sigma$ to the right, while particle $B$
@@
 collisions.  In Figure \ref{fig:Breathingfrequency3}(a), we show schematics of such a collision near
-the trap center at strong interactions.  For very large $F_0$, the particles simply exchange momentum
-when they are at distance $\sigma$ from each other; this process is shown in red as two straight
-lines.  (The particles are initially at $X=\pm\frac{1}{2}\sigma$ and remain at these $X$ values,
-but exchange their momenta.)   For smaller $F_0$, there is change of both position and momentum, as shown in yellow, green
-and blue for successively weaker interactions. The blue line shows a case where $F_0$ is smaller
-enough such that the particles can actually cross each other.
+the trap center at strong interactions.  For very large $F_0$, the particles simply exchange
+momentum when they are at distance $\sigma$ from each other; this process is shown in red as two
+straight lines.  (The particles are initially at $X=\pm\frac{1}{2}\sigma$ and remain at these $X$
+values, but exchange their momenta.)  For smaller $F_0$, there is change of both position and
+momentum, as shown in yellow, green and blue for successively weaker interactions. The blue line
+shows a case where $F_0$ is smaller enough such that the particles can actually cross each other.
 
@@
 system has `relaxed' from the initial line distribution in phase space to a more spread-out cloud,
-as we have seen in Figure \ref{fig:Breathingfrequency2_1}.  In \ref{fig:Breathingfrequency4} we show
-the breathing frequency calculated from $R(t)$ oscillations in the first 100 time units, and also
-the frequency from data in a later time window. The frequencies appear to be overall stable and dependent
-primarily on $F_0$ and $E$.
-
-\section{Thermalization}\label{section:Thermalization}
+as we have seen in Figure \ref{fig:Breathingfrequency2_1}.  In Figure \ref{fig:Breathingfrequency4}
+we show the breathing frequency calculated from $R(t)$ oscillations in the first 100 time units, and
+also the frequency from data in a later time window. The frequencies appear to be overall stable and
+dependent primarily on $F_0$ and $E$.
+
+\section{Relaxation and Thermalization}\label{sec:relaxation}
 
@@
 
-In the subsections below, we first ***  then ****
+% In the subsections below, we first ***  then ****
 
@@
 
-Since we are interested in thermalization within finite timescales, it is useful to consider
-mechanisms which hinder relaxation or thermalization.  We begin with considerations of few-particle
-motion.  Since ergodicity and relaxation are generally expected to be more robust and efficient with
-larger particle numbers, consideration of small particle numbers will highlight effects which slow
-down relaxation.
+Since we are interested in thermalization within finite timescales, it is useful to first consider
+mechanisms which hinder relaxation or thermalization.  We begin with few-particle motion.  Since
+ergodicity and relaxation are generally expected to be more robust and efficient with larger
+particle numbers, consideration of small particle numbers will highlight effects which slow down
+relaxation.
 
@@
 Generally, whenever we have some particles with energy very different from others, the dynamics
-occurs mostly independently within particle groups of different energies.  For example, considering
-a situation with three particles, consider the situation where two of them, say A and B, have small
-internal energy, which means their mutual distance and relative velocity are both small, whereas the
-third particle (C) has some energy quite different from A and B.
+occurs mostly independently within particle groups of different energies.  For example, with three
+particles, consider the situation where two of them, say A and B, have small internal energy, which
+means their mutual distance and relative velocity are both small, whereas the third particle (C) has
+some energy quite different from A and B.
 %
@@
 enough statistics to investigate the distribution of single-particle energies.  Therefore,
-single-particle energies are recorded at once every time unit (i.e., at time intervals of
-$1/omega_0$) as the simulation evolves, up to around $t\sim10^4$.  The distribution of these
-observed values then shows whether or not the system has thermalized to a Boltzmann distribution.
-In the two panels of Figure \ref{fig:thermalization5}, we show the distributions obtained for a
-$N=5$ system and a $N=20$ system.  In both cases, we choose the total energy to be $E=1000N$.  In
-accordance with our conjectured condition, we find that the observed single-particle distributions
-are qualitatively different for $F_0\gtrsim10^3$ and for smaller interactions.  When the
-``thermalization condition'' $F_0\gtrsim E/N$ is satisfied, the distribution is roughly exponential
-($\sim e^{-\beta\epsilon}$.  For smaller $F_0$, thermalization in this sense is not seen in the
-single-particle energy distribution.  Since the systems are expected to be ergodic, it is assumed
-that the smaller-$F_0$ systems will also eventually show a Boltzmann distribution of energy, but
-that this appears only at (much) longer timescales.
+single-particle energies are recorded once every time unit (i.e., at time intervals of $1/\omega_0$)
+as the simulation evolves, up to around $t\sim10^4$.  The distribution of these observed values then
+shows whether or not the system has thermalized to a Boltzmann distribution.  In the two panels of
+Figure \ref{fig:thermalization5}, we show the distributions obtained for a $N=5$ system and a $N=20$
+system.  In both cases, we choose the total energy to be $E=1000N$.  In accordance with our
+conjectured condition, we find that the observed single-particle distributions are qualitatively
+different for $F_0\gtrsim10^3$ and for smaller interactions.  When the ``thermalization condition''
+$F_0\gtrsim E/N$ is satisfied, the distribution is roughly exponential ($\sim e^{-\beta\epsilon})$.
+For smaller $F_0$, thermalization in this sense is not seen in the single-particle energy
+distribution.  Since the systems are expected to be ergodic, the smaller-$F_0$ systems presumably
+will also eventually show a Boltzmann distribution of energy, but only at (much) longer timescales.
 
@@
 
-In several `thermalizing' situations, $F_0\gtrsim E/N$, we display the agreement with the Boltzmann
-distribution in Figure \ref{fig:thermalization9}.  In each panel, the calculated distributions from
-simulations is plotted against the Boltzmann distribution.  The overall agreement shows that the
-energy is well-thermalized among the particles on average within the timescales under consideration.
+In Figure \ref{fig:thermalization9}, we display the agreement with the Boltzmann distribution in
+several `thermalizing' situations, $F_0\gtrsim E/N$.  In each panel, the calculated distributions
+from simulations is plotted against the Boltzmann distribution.  The overall agreement shows that
+the energy is well-thermalized among the particles on average within the timescales under
+consideration.
 
@@
 oscillator, the DOS is constant.  The interaction deforms the energy shell in the small region
-$|x_i-x_j|<\sigma$; so that the DOS is no longer a constant.  The effect of interaction is
-conspicuous in low energy part: when interaction is weak, particles prefer to stay near zero energy
-according to Boltzmann distribution, but when interaction grows, they are no longer allowed to
-accumulate near zero energy, in another word DOS at low energy decreases with the increase of
-interaction. Therefore, counts at the low energy part of Fig.\ref{fig:thermalization9} is slightly
-lower than the Boltzmann prediction.  The correction to the density of states is not simple to
-calculate explicitly.  Since we are in the regime of a dilute gas ($\sigma\ll R$), the effect is
-very small.
+$|x_i-x_j|<\sigma$; so that the DOS is no longer a constant.  The measured distribution seems
+systematically slightly smaller than the Boltzmann curve at very small $\epsilon$: when interaction
+is weak, particles prefer to stay near zero energy according to the Boltzmann distribution, but when
+interaction grows, they are no longer allowed to accumulate near zero energy, in other words the DOS
+at low energy decreases with the increase of interaction. Therefore, counts at the low energy part
+of Fig.\ref{fig:thermalization9} is slightly lower than the Boltzmann prediction.  The correction to
+the density of states is not simple to calculate explicitly.  Since we are in the regime of a dilute
+gas ($\sigma\ll R$), the effect is very small.
 
@@
 exponents.  For high-dimensional systems, there is a spectrum of exponents which manifests the
-instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects
-the shortest time scale for the system lose memory of the initial state.  We follow the method
-described in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently
-late times, the LLE for an ergodic system is uniquely defined and independent of the starting
-state.  We would like to deal with parameter regimes both within and outside our relaxation
-condition $E<F_0N$ and $E>F_0N$, and in the latter case we have seen that ergodicity does not become
-apparent at reasonable timescales.  Therefore, we carry out the computation of the LLE upto
-$t\sim10^3$, which means that we can only get initial-configuration-dependent estimates.  The
-collection of these estimates forms a distribution which we show in Figure
-\ref{fig:LLEdistribution1}.
+instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects the
+shortest time scale for the system lose memory of the initial state.  We follow the method described
+in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently late times,
+the LLE for an ergodic system is uniquely defined and independent of the starting state.  We would
+like to deal with parameter regimes both within and outside our relaxation condition $E<F_0N$ and
+$E>F_0N$, and in the latter case we have seen that ergodicity does not become apparent at reasonable
+timescales.  Therefore, we carry out the computation of the LLE upto $t\sim10^3$, i.e, we consider
+finite-time Lyapunov exponents (CITE).  This means that we can only get
+initial-configuration-dependent estimates.  The collection of these estimates forms a distribution
+which we show in Figure \ref{fig:LLEdistribution1}.
 
@@
 %\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
-\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
+\includegraphics[width=0.55\textwidth]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
 \caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
-  energies.  The color indicates the probability of a measured LLE value being found in a bin; the
-  bins are of size 0.01}\label{fig:LLEdistribution1}
+  energies.  The color indicates the observed probability of a measured LLE value being found in a
+  bin; the bins are of size 0.01.  }  \label{fig:LLEdistribution1}
 \end{figure}
@@
 
-The LLE decreases with the growth of energy. The critical part is near $E=5000$. The most probable
-value of LLE goes down from around 1 to around 0.1,which indicates that the shortest time scale
-becomes longer than an oscillation period when $E\gtrsim5000$.  This is consistent with our
-predicted thermalization threshold.  As $E$ increases far beyond the thermalization threshold value,
-the LLE distribution is close to zero, suggesting a divergence of relaxation time.
-%
-We have thus shown a correspondence between energy thermalization and LLE.
+The LLE decreases with the growth of energy. The critical part is near $E = F_0N = 5000$.  Around
+this value, the most probable value of LLE decreases well below $\sim1$, which indicates that the
+shortest time scale becomes much longer than an oscillation period when $E\gtrsim5000$.  This is
+consistent with our predicted thermalization threshold.  As $E$ increases far beyond the
+thermalization threshold value, the LLE distribution is close to zero, suggesting a divergence of
+relaxation time.
+%
+We have thus shown an explicit correspondence between energy thermalization in real time and the
+(finite-time) LLE.
 
@@
 
-We have studied thermalization in terms of energy.  More generally, thermalization may be taken to
-mean that a many-body system loses memory of its initial state.  In the single-particle phase-space
-picture, Figures \ref{fig:Breathingfrequency2_0} and \ref{fig:Breathingfrequency2_1}, our initial
-state is very special: The particles are lined up along the $X$ axis.  The effect of interaction is
-to distort this line toward a circularly symmetric distribution.  Thus, we would consider that the
-memory of the initial state is lost when the distribution of points in the $X$-$P$ plane are not
-elongated in any one direction.
+Till now, we have studied formulated the thermalization question in terms of energy distributions.
+More generally, thermalization may be taken to mean that a many-body system loses memory of its
+initial state.  In the single-particle phase-space picture, Figures \ref{fig:Breathingfrequency2_0}
+and \ref{fig:Breathingfrequency2_1}, our initial state is very special: The particles are lined up
+along the $X$ axis.  The effect of interaction is to distort this line toward a circularly symmetric
+distribution.  Thus, we would consider that the memory of the initial state is lost when the
+distribution of points in the $X$-$P$ plane are not elongated in any one direction.
 
@@
 \end{equation}
-where $a$ and $b$ are long axis and short axis of inertia ellipse in phase space respectively. These
-can be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
+where $a$ and $b$ are long axis and short axis of the inertia ellipse in phase space respectively.
+These are calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
 I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.  The shape parameter is $S=1$ for line-shaped
@@
 
-------
-
-\section{Shape of Distribution in Phase-space}\label{section:Shape}
-
-When describing simple harmonic motion, it is usually convenient to use the language of phase-space
-(of single particle). In the phase-space, the motion becomes circular, so each of these particles
-has two independent degrees of freedom, i.e., modulus and phase angle. Here, ``independent" means
-that the simple harmonic oscillation never ``mix" these two degrees of freedom. In view of this,
-when it comes to ``thermalization", one will expect that the thermalization of energy, which is just
-the modulus, does not ensure the thermalization of phase angle. As ins explained in the Introduction
-part, in order to distinguish two kinds of meanings of ``thermalization", we will call the process
-of energy distribution going to equilibrium ``thermalization", while the process of phase angle
-going to equilibrium ``relaxation". The time scale of thermalization and relaxation could be quite
-different in principle. We will start with the configuration where particles' velocities are set to
-be zero, which means in phase-space the cloud is a rotating narrow ellipse at the beginning. If the
-time scale of thermalization is much longer than that of relaxation, we will see cloud going to some
-stable shape in a short time (a circle if interaction is not significant compared to total energy)
-while the distribution of particle number along radius slowly evolves to Boltzmann distribution. If
-the relaxation time is longer than the thermalization time, the cloud will maintain elliptical shape
-or some oscillation between different shapes for a long time while the energy distribution is
-already Boltzmann.
-
-To quantify the shape of distribution in phase-space, we defined a shape polarization S:
-\begin{equation}
-S=\frac{a-b}{a+b}
-\end{equation}
-where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can
-be calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
-I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$. S=1 for line-shape distribution, S=0 for circular
-distribution. The advantage of defining the S lies in that S is independent of all rotating behavior
-of the cloud in phase-space and thus extract the information of shape alone. One could also use
-eigenvalues of quadrupole moment Q to define S. Two choice of definition is equivalent, since I and
-Q are only different up to a factor and an identity matrix.
-
-%First, let's see the overall value of S in Fig.\ref{fig:shape}.
-In Fig.\ref{fig:shape}, each data point is the average of S over several periods to show the overall value of S.
-If the shape relax to equilibrium, the overall value should decrease to zero.
-At first sight, it seems S does relax, and the conclusion looks similar to the one we got from Boltzmann distribution--When energy is lower than thermalizing threshold(top pannel), S relax in almost no time; when energy is higher than thermalizing threshold(bottom pannel), it takes a relativly long time for S to relax.
-The reason why S never decay to zero could be explained as the contribution of random fluctuation, since S is defined to be positive.
-
-%However, it is not the whole story.
-If we inspect the original data or smoothen it by taking a finer average, e.g.
-average over 0.2 time units (Fig.\ref), we will see the ''sinusoidal"  oscillation of S (S is defined to be positive) with a period of about $2\pi$ time units.
-So the whole picture is that the shape of the cloud is oscillating: \\elliptical with long axis lying along x axis $\rightarrow$ circular $\rightarrow$ elliptical with long axis lying along y axis $\rightarrow$ circular ...
-
-%If we think of the cloud as 2D cloud in x-p space, we have 2D monopole, dipole and quadrupole mode.
-In our system, since energy conserves, $x^2+p^2$ is a constant interaction energy is neglected), the monopole mode do not exist.
-And dipole mode describes the center of mass of the cloud oscillate along x or p, but since we set center of mass to be stationary and at x=0, neither does this mode exist.
-The lowest order mode is quadrupole mode.
-
-The time evolution of S is shown in Fig.\ref{fig:time_evolution_of_S}.
-The top three pannels are the overall value of S, where every data point is the average value of original data over several period (about $2\pi$ time unit).
-The lower six pannels are the original data measured in the beginning and after thousands of time units, which shows the finer structure in one period.
-
-\begin{figure*}[h]
-\subfigure[$N=20, F_0=1000, E=3000$]{
-\begin{minipage}[b]{0.3\linewidth}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_2_crude_begin.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_2_crude_end.eps}
-\end{minipage}
-}
-\subfigure[$N=20, F_0=1000, E=20000$]{
-\begin{minipage}[b]{0.3\linewidth}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_1.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_2_crude_begin.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000_2_crude_end.eps}
-\end{minipage}
-}
-\subfigure[$N=20, F_0=1000, E=100000$]{
-\begin{minipage}[b]{0.3\linewidth}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_1.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_2_crude_begin.eps}
-\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000_2_crude_end.eps}
-\end{minipage}
-}
-\caption{Time evolution of S in low-energy regime(a), intermidiate(b), high-energy regime(c).
-The overall value (top three pannels), where every point represent the average of original data over several periods, show that S decays to a low value in a short time in low-energy case, but persist for a relative long time in high-energy case.
-The snapshots of original data at beginning and after thousands of periods evolution are shown in the lower six pannels.
-The finer structure of S(t) indicates that there is some long-lasting oscillating mode.
-Especially in low-energy case, the amplitude is more conspicuous.}\label{fig:time_evolution_of_S}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure*}[tbph]
+\includegraphics[width=\textwidth]{ZhiyuPictures/combine_shapedynamics_a_01-crop.pdf}
+\caption{$N=20, F_0=1000$. Time evolution of the shape parameter, $S(t)$, for $N=20$ particles,
+  $F_0=1000$.  The three columns correspond to $E<F_0N$ (low-energy or thermalizing regime),
+  $E=F_0N$ (intermediate regime), and $E>F_0N$ (high-energy or non-thermalizing regime).  In the top
+  row, coarse-grained values (averaged over 10 periods) are shown, for several initial states with
+  the same energy in each case.  The lower row shows original data (not averaged) in a window after
+  several thousand time steps.  }
+\label{fig:time_evolution_of_S}
 \end{figure*}
-
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1.eps}
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000.eps}
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000.eps}
-%\caption{N=20, F=1000, E=3000(top), E=20000(middle), E=100000(bottom).
-All start with initial states S=1.
-Five different curves in each picture represent simulating with 5 random initial states in each case.
-\label{fig:shape}}
-%\end{figure}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_original1.eps}
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_original2.eps}
-%\caption{N=20, F=1000, E=3000. Original data}
-%\end{figure*}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1_fine1.eps}
-%\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000_1_fine2.eps}
-%\caption{N=20, F=1000, E=3000. Start with initial states S=1. Smoothened (every point represents taking the average of S in 0.2 time unit)}
-%\end{figure*}
-
-The original data can be decomposed into two components: the background value and the frequent fluctuation(sharp peaks and dips) on the background.
-The fluctuation is generated from the two-particle transportation process(See Fig.\ref{fig:Breathingfrequency3}), e.g.
-a pair transportation event along the long-axis of the cloud makes a dip.
-In the thermalized regime (Fig.\ref{fig:time_evolution_of_S}), the background value of S is oscillating with an amplitude of 0.2-0.4 and does not decay to zero over 4000 time unit.
-In the high-energy case, the amplitude of background oscillation is small compared with fluctuation.
-We assume that over a long enough time, all macroscopic quantity should be constant because the randomness has wash out all possible orders to make entropy as large as possible.
-Since we see a periodical behavior of S, we know the whole system doesn't relax to its equilibrium state.
-
-The oscillating background value of S indicate that the shape of the cloud in phase space is deformed periodically between a circle and an ellipse($S=0.4$ means $\frac{a}{b}\sim 2.5$).
-To further reveal the nature of this oscillating mode, we focus on the low-energy case and plot the distribution of the cloud in the phase-space as Fig.\ref{fig:N=50_F=1000_E=30000_movie}.
-The time interval between each pannels is $0.1*2\pi$ time units.
-The direction of the yellow arrows and red arrows are the eigenvector of inertia tensor, while their lengths are the square root of correspondent eigenvalue (I take the squareroot to maintain the length unit).
-In most of the pannels in Fig.\ref{fig:N=50_F=1000_E=30000_movie}, the long and short axis are rotating and extending or contracting continuosly.
-The exception is the 3rd and 4th pannel in the first row, 2nd and 3rd pannel in the second row, 1st and 2nd pannel in the third row.
-At those moment, the long and short axis are almost equal, giving the system a chance to choose a new preferred axis to polarize.
-The whole picture of this collective mode can be described by Fig.\ref{fig:Schemetic_description_of_the_mode}, which is consistant with the pattern of time evolution of S shown in Fig.\ref{fig:N=50_F=1000_E=30000_Send}.
-
-\begin{figure*}[h]
-\centering
-\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s_1100_600_Font18.eps}
-\caption{Distribution in phase-space after evolving for about 500 time units ($N=50, F_0=1000, E=30000$).
-Please notice that the yellow(red) arrows shows the length of long(short) axis of inertia ellipse, which is prependicular to the long(short) axis of distribution cloud.
-For instance, if the yellow arrow lies in p-axis, it means the long axis of distribution cloud is lying along x-axis.}\label{fig:N=50_F=1000_E=30000_movie}
-\end{figure*}
-
-\begin{figure*}[h]
-\centering
-\includegraphics[scale=0.4]{ZhiyuPictures/quadrupole_mode_2.png}
-\caption{Schemetic description of the excited mode.
-Red ellipse is the shape of cloud in low-energy regime when there is repulsive interaction.
-Gray cloud is the imaginary shape of cloud when there is no interaction, which is plotted here as a reference.
-One may think of the effect of interaction as a kind of potential that prefer to place particles along x axis, because in low energy regime the system is not allowed to be squeezed too much along x axis since doing this cost a large amount of interaction energy.}\label{fig:Schemetic_description_of_the_mode}
-\end{figure*}
-
-\begin{figure*}[h]
-\centering
-\includegraphics[scale=0.4]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s_Send.eps}
-\caption{Time evolution of S after evolving for about 500 time units ($N=50, F_0=1000, E=30000$). The oscillating behaviour of S persists over 500 time units.}\label{fig:N=50_F=1000_E=30000_Send}
-\end{figure*}
-
-To sum up, the existence of the long-lasting oscillation of S indicate that the system does not relax to its equilibrium state in terms of shape although it is already thermalized in terms of energy distribution.
-With this long-lasting mode, the radius R of the cloud will keep oscillating, enabling the breathing mode to last for a long time.
-
-\section{Conclusion}
-
-Other forms of interaction.
-
-We studied the nonequilibrium property of one-dimensional classical gas with finite range repulsive
-interaction. We first studied the relation between breathing mode frequency and interaction
-parameter as well as total energy. We found the breathing frequency could be estimated by
-eq.\ref{eq:breathingfrequency1}. And the mechanism behind this relation is that the momentum
-transfer which happens instantly in collision saves the particles some time from traveling this
-distance. So the physics is completely the same as hardcore particle.
-
-We found that the thermalization behavior is controlled by the competition between the interaction
-strength and the average energy. We point out that there could be two independent time scales in
-simple harmonic system in principle. One of them corresponds to the relaxation time of the energy
-distribution. The other one corresponds to the relaxation time of the angular distribution in phase
-space, which will determine the decay rate of the amplitude of the breathing mode. We have shown
-that in the low-energy regime, although the energy distribution reach Boltzmann distribution within
-several periods of oscillation, the shape keep oscillating for thousands of periods.
-
-%However, with the form of interaction we used, i.e. finite range constant repulsive force, we found
-%those two time scales diverge only when interaction vanish, which is a trivial singular point. In
-%addition, the relaxation behavior of the angular distribution and radial distribution in phase
-%space are similar. We attribute it to the fact that there is no essential bias between angular and
-%radial transfer in phase-space for this simple form of interaction. The shortest time scale is
-%verified numerically by Largest Lyapunov Exponent. A further question could be asked is whether
-%there is a subtle form of interaction that could give those two time scales essentially different
-%behavior. The observation of two different time scales in one system would be interesting.
-
-%\begin{comment}
-%\section{others(those I haven't organized it into the text in logical order but may be useful)}
-
-%\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
-%Results are shown in Fig.\ref{fig:others1}
-
-%\begin{figure}[h]
-
-%\centering
-%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
-%\caption{fluctuation of R with time }
-%sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
-%\label{fig:others1}
-%\end{figure}
-
-%\subsection{Detailed discussion of two-particle motion}
-%{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization".
-But then I found we haven't used these result.
-So I put it at the end for the time being}}.
-
-%From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system.
-In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame.
-As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical).
-We label the position of center of mass as 0.
-And we may only analyze the motion on positive axis since positive and negative are symmetric.
-
-%Now, let's consider the interaction between them.
-Because of interaction, the potential curve between $+-\frac{\sigma}{2}$ should be modified to another parabolic curve that simultaneously satisfies the following two condition:\\
-%1) intersect with black curve at $+-\frac{\sigma}{2}$\\
-%2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
-%Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
-%1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
-%2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
-%3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
-%For those three types of curve, the significant difference is only at low energy case:\\
-%For the red one, particle will oscillate at constant frequency $\omega$;
-%For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
-%For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.
-
-%\begin{figure}
-%\subfigure[]{
-%\begin{minipage}[b]{0.3\textwidth}
-%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
-%\end{minipage}
-%}
-%\subfigure[]{
-%\begin{minipage}[b]{0.3\textwidth}
-%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
-%\end{minipage}
-%}
-%\subfigure[]{
-%\begin{minipage}[b]{0.3\textwidth}
-%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
-%\end{minipage}
-%}
-%\centering
-%\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value %of $\frac{F_0}{m\omega_0^2\sigma}$
-%\label{fig:thermalization3}
-%\end{figure}
-%\end{comment}
-
-%\bibliography{mybib}
-%\bibliographystyle{ieeetr}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
+The time evolution of the shape parameter $S$ is shown in Fig.\ref{fig:time_evolution_of_S}.
+%
+The top three pannels show averaged values of $S$ in order to highlight the overall behavior.  Every
+data point is the average of the original data over $10T = 20\pi$. The lower six pannels are the
+original data measured after several thousand time units.
+
+The coarse-grained (averaged) dynamics on top reflects our intuition that there is slower relaxation
+at larger $E/F_0$.  We see a much faster decay for small $E/F_0$, i.e., in the thermalizing regime.
+%
+The behavior of $S(t)$ at longer times shows (lower panel) that there are long-range coherent
+oscillations of the phase-space cloud shape at rather long timescales.  Strikingly, this is even
+true for the thermalizing regime (lower left panel), for which the time-averaged single-particle
+energies already are Boltzmann-distributed.  Thus, energy thermalization can occur at timescales
+much faster than it takes for other features of the gas to relax.
+
+\section{Discussion and Conclusions} \label{sec:concl}
+
+Considering classical interacting particles in a harmonic trap, we have addressed two
+non-equilibirum problems motivated by analogous questions in recent research on quantum many-body
+dynamics.  We have chosen to work with a simple finite-range interaction with variable interaction
+strength, in the `dilute gas' regime where the particles are at average distance significantly
+larger than the interaction range.
+
+The first question concerned the breathing mode of the classical trapped gas, and the influence of
+interaction on the breathing mode frequency.  We have shown nontrivial dependence of the breathing
+frequency on the interaction strength $F_0$: the breathing frequency first decreases as a function
+of $F_0$, and around the critical value $F_0 \sim E/N$, in increases above the non-interacting
+value.  Eventually at large $F_0$ the frequency shift reaches a plateau at a value
+$\propto\sqrt{N^3/E}$.  We have explained this behavior physically, using both real-space and
+phase-space pictures.
+
+The second question concerned the relaxation and thermalization behavior of the gas.  This is
+particularly interesting for a moderate number of particles, far from the thermodynamic limit.  We
+have examined thermalization in the sense of single-particle energy distribution; this has to be
+carefully defined when the number of particles is in the `mesoscopic' regime.  Sampling the
+single-particle energies from temporal snapshots of the system over a period of time, we find that
+the system `thermalizes' in reasonable time for $F_0 \gtrsim E/N$.  We have explained this condition
+in terms of relaxation-hindering mechanisms for few-particle systems.  We have also shown that this
+threshold corresponds to the largest finite-time Lyapunov exponent exceeding $\approx1$.  Finally,
+we have found that (for $F_0 > E/N$) thermalization occurs at timescales much faster than the
+timescale for the breathing mode oscillations to damp out.  This is remarkable if one expects
+thermalization to correspond to the loss of memory of  initial conditions: the initial shape
+ellipticity of the phase space cloud provides very-long-lived oscillations of the shape of the phase
+space distribution, even after energy thermalization has already occurred.
+
+The present work opens up various questions.  Our chosen form of interaction is simple and sensible
+as a model interaction; and we expect that the $F_0$-dependence of the breathing mode frequency
+represents the interaction-dependence for a wide class of interactions.  However, it would be
+interesting to ask how collective modes in general depend on the form of interactions.
+%
+While the connection between ergodicity and thermalization is expected to be simpler in large
+systems, for few-body systems like the present case the connection is less clear and raises
+questions of timescales.  Our study of a special case exemplifies the need for better general
+understanding of the connections between relaxation timescales, interaction strengths,
+thermalization, and finite-time Lyapunov expnents.
 
@@
 
-\bibitem{NewtonsCradle_Nature06}  
-T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, ``A quantum Newton's cradle'', {\em Nature}, {\bf 440,} 900 (2006).
-
-\bibitem{Naegerl_Science2009} E.~Haller, M.~Gustavsson, M.~J.~Mark, 
-J.~G.~Danzl,  R.~Hart, G.~Pupillo, H.-C.~N\"agerl, Science \textbf{325}, 1224 
-(2009).
+\bibitem{Naegerl_Science2009} E.~Haller, M.~Gustavsson, M.~J.~Mark, J.~G.~Danzl, R.~Hart,
+  G.~Pupillo, H.-C.~N\"agerl, ``Realization of an excited, strongly correlated quantum gas phase,''
+  {\em Science}, \textbf{325}, 1224 (2009).
 
@@
 %
+\\ 
+%
 M.-O.~Mewes, M.~R.~Andrews, N.~J.~van~Druten, D.~M.~Kurn, D.~S.~Durfee, 
@@
 %
+\\ 
+%
 M.~Amoruso, I.~Meccoli, A.~Minguzzi, and M.~P.~Tosi, Eur.\ Phys.\ J.~D \textbf{8}, 361 (2000);
 %
+\\ 
+%
 R.~Combescot and X.~Leyronas, Phys.\ Rev.\ Lett.\ \textbf{89}, 190405 (2002);
+%
+\\ 
 %
@@
 %
+\\ 
+%
 C.~Menotti and S.~Stringari, ``Collective oscillations of a one-dimensional trapped Bose-Einstein
 gas'', {\em Phys.\ Rev.\ A} \textbf{66}, 043610 (2002).
+%
+\\ 
 %
@@
 
-\bibitem{KohnMode} L.~Brey, N.~F.~Johnson, and B.~I.~Halperin, Phys.\ Rev.\ B 
-  \textbf{40}, 10647 (1989).  M.~Bonitz, K.~Balzer, and R.~van~Leeuwen, 
-  {\em Phys. Rev. B} \textbf{76}, 045341 (2007).
+\bibitem{KohnMode}
+%
+L.~Brey, N.~F.~Johnson, and B.~I.~Halperin, Phys.\ Rev.\ B \textbf{40}, 10647 (1989).
+%
+\\ 
+%
+M.~Bonitz, K.~Balzer, and R.~van~Leeuwen, {\em Phys. Rev. B} \textbf{76}, 045341 (2007).
+
+\bibitem{NewtonsCradle_Nature06}  
+T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, ``A quantum Newton's cradle'', {\em Nature}, {\bf 440,} 900 (2006).
 
@@
 
-\bibitem{Haller2009}
-E.~Haller, M.~Gustavsson, M.~J. Mark, J.~G. Danzl, R.~Hart, G.~Pupillo, and
-  H.-C. Nägerl, ``Realization of an excited, strongly correlated quantum gas
-  phase,'' {\em Science}, vol.~325, p.~1224, Sept. 2009.
-
 \bibitem{Tsuchiya2000}

### 2017-12-19 draft_09.tex
added many citations

--- 2017-12-15 draft_07.tex
@@
 Motivated by the interest in the dynamics of trapped quantum gases, we study the microcanonical
-  dynamics of a trapped gas of classical particles interacting with a finite-range interaction of
-  tunable strength.  We examine two questions which have been of interest in quantum dynamics: (1)
-  the breathing mode (size oscillation) dynamics of the trapped gas and the dependence of the
-  breathing frequency on the interaction strength, and (2) the long-time relaxation and possible
-  thermalization of the finite isolated gas.
+dynamics of a trapped one-dimensional gas of classical particles interacting via a finite-range
+repulsive force of tunable strength.  We examine two questions which have been of interest in
+quantum dynamics: (1) the breathing mode (size oscillation) dynamics of the trapped gas and the
+dependence of the breathing frequency on the interaction strength, and (2) the long-time relaxation
+and possible thermalization of the finite isolated gas.
+%
+We show that the breathing mode frequency has nonmonotonic dependence on the magnitude of the mutual
+repulsion, decreasing for small interactions and increasing for larger interactions.  We explain
+these dependences in terms of slowing-down or speeding-up effects of two-body collision processes.
+We find that the gas thermalizes within a reasonable finite timescale in the sense of
+single-particle energies acquiring a Boltzmann distribution, only when the interaction strength is
+large compared to the energy per particle.
 
@@
 by the availability of experimental systems, e.g., trapped ultracold atomic and ionic systems, where
-non-dissipative dynamics can be studied explicitly due to excellent isolation.  There are also
-foundational reasons for studying quantum dynamics in isolation: recent activity has led to advances
-in the understanding of basic principles connecting quantum dynamics, quantum chaos and the
-emergence of statistical mechanics and thermalization (CITE).  For classical many-body systems,
-explorations of the connections between microscopic dynamical rules, chaos, ergodicity and
-statistical mechanics have a much longer history, dating back to the time of Boltzmann and Poincare
-\cite{Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85}.
+non-dissipative dynamics can be studied explicitly due to excellent isolation from the environment.
+There are also foundational reasons for studying quantum dynamics in isolation: recent activity has
+led to advances in the understanding of basic principles connecting quantum dynamics, quantum chaos
+and the emergence of statistical mechanics and thermalization \cite{PolkovnikovRigol_AdvPhys2016,
+  BorgonoviIzrailevSantos_PhysRep2016}.  For classical many-body systems, explorations of the
+connections between microscopic dynamical rules, chaos, ergodicity and statistical mechanics have a
+much longer history, dating back to the time of Boltzmann and Poincare \cite{Gaspard_book_1998,
+  Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85,
+  Gaspard_PhysicaA06}.
 
@@
 been reformulated in the presence of a harmonic trap.  The presence of a harmonic trap often results
-in new dynamical phenomena.  For example, the motion of vortices in a trapped condensate (CITE) has
-new features, such as precession, compared to vortex motion in uniform condensates (CITE).  Trapping
-also results in new collective phenomena which have no analog in uniform situations: for example,
-collective modes like dipole, breathing and quadrupole modes are specific to trapped many-body
-systems.  Dipole modes (center of mass oscillations) and breathing modes (size oscillations) appear
-even for one-dimensional trapped systems; higher-dimensional systems display additional, more
-complicated modes like quadrupole and scissors modes.  Because of the omnipresence of trapping
-potentials in cold-atom experiments, dipole and breathing mode dynamics are pervasive across the
-field: These modes have been intensively studied and used for diagnostic purposes since the early
-days of research with trapped quantum-degenerate gases, and continue to generate interest today
-\cite{Naegerl_Science2009, Esslinger_exp_PRL2003, collective_modes_early_papers,
-  Tschischik_BHbreathing_PRA_2013, KroenkeSchmelcher_BM, Bonitz_Review, Bouchoule_PRL2014,
-  our_superTG_PRA_2015, STG_Astrakharchik_PRL2005, STG_Chen-etal_PRA2010,
-  br_mode_long_range_interactions, 1D_breathing_mode_recent, KohnMode, Cominotti_2015,
-  ZarembaTowers_PRA2014, Wetterich_JPB2011, fermion2Dbreathing, Stringari_lowDcollective_PRA15,
-  Mazets_1Dbreathing_EPJD11}.  (CITE).
+in new dynamical phenomena.  For example, the motion of vortices in a trapped condensate
+\cite{vortices_trappedBEC} has new features, such as precession, compared to vortex motion in
+uniform condensates \cite{vortices_uniformBEC}.  Trapping also results in new collective phenomena
+which have no analog in uniform situations: for example, collective modes like dipole, breathing and
+quadrupole modes are specific to trapped many-body systems.  Dipole modes (center of mass
+oscillations) and breathing modes (size oscillations) appear even for one-dimensional trapped
+systems; higher-dimensional systems display additional, more complicated modes like quadrupole and
+scissors modes.  Because of the omnipresence of trapping potentials in cold-atom experiments, dipole
+and breathing mode dynamics are pervasive across the field: These modes have been intensively
+studied and used for diagnostic purposes since the early days of research with trapped
+quantum-degenerate gases, and continue to generate interest today
+\cite{collective_modes_early_papers, PitaevskiiRosch_PRA97, Esslinger_exp_PRL2003, STG_Astrakharchik_PRL2005, 
+  GrimmSmith_unitaryfermions_PRA08, OrignacCitro_PRA08, Naegerl_Science09, Wetterich_JPB2011, Mazets_1Dbreathing_EPJD11,
+  fermion2Dbreathing, Tschischik_BHbreathing_PRA_2013, KroenkeSchmelcher_BM, Bouchoule_PRL2014,
+  br_mode_long_range_interactions, Bonitz_Review, QuinnHaque_PRA14, Tschischik_BH_2papers,
+   1D_breathing_mode_recent, Minguzzi_dipole_PRA2015, 
+  Stringari_lowDcollective_PRA15,    MistakidisSchmelcher_PRA17}. 
 %
@@
 seen to have ultraslow relaxation in a trap, supposedly due to integrability.  This experiment has
-led to continuing efforts to understand how a trap breaks integrability (CITE).
+led to continuing efforts to understand how a trap breaks integrability
+\cite{CauxKonik_glimmers_PRX15, CauxDoyonDubailKonik_1711, DoyonSpohn_JSTAT17, Moore_arXiv17.10}.
 
@@
 trapping frequency, where $D$ is the spatial dimension.  For three-dimensional (3D) traps, the
-mean-field description can be expected to be qualitatively correct, thus the breathing mode
-frequency is expected to change monotonically from $2\omega_0$ at zero interactions to
-$\sqrt{5}\omega_0$ at large interactions.  For 2D traps, the breathing frequency is exactly
-$2\omega_0$ for any interaction strength \cite{PitaevskiiRosch_PRA97}, due to a symmetry.  Classical
-trapped particles with scale-invariant interaction potentials also have breathing frequency
-$2\omega_0$ independent of interaction strength \cite{PitaevskiiRosch_PRA97}.  The interaction
-dependence in 1D (trapped Lieb-Liniger gas) is also remarkable: as the interaction is increased, the
-breathing frequency first decreases from $2\omega_0$ to the mean-field prediction
-$\sqrt{3}\omega_0$, and then at larger interactions increases again, returning to $2\omega_0$ in the
-infinite interaction (Tonks-Girardeau) limit \cite{Naegerl_Science2009,
-  Tschischik_BHbreathing_PRA_2013, 1D_breathing_mode_recent, Bouchoule_PRL2014,
-  KroenkeSchmelcher_BM}.
+mean-field description is expected to be qualitatively correct, thus the breathing mode frequency is
+expected to change monotonically from $2\omega_0$ at zero interactions to $\sqrt{5}\omega_0$ at
+large interactions.  For 2D traps, the breathing frequency is exactly $2\omega_0$ for any
+interaction strength \cite{PitaevskiiRosch_PRA97}, due to a symmetry.  Classical trapped particles
+with scale-invariant interaction potentials also have breathing frequency $2\omega_0$ independent of
+interaction strength \cite{PitaevskiiRosch_PRA97}.  The interaction dependence in 1D (trapped
+Lieb-Liniger gas) is also remarkable: as the interaction is increased, the breathing frequency first
+decreases from $2\omega_0$ to the mean-field prediction $\sqrt{3}\omega_0$, and then at larger
+interactions increases again, returning to $2\omega_0$ in the infinite interaction (Tonks-Girardeau)
+limit \cite{Naegerl_Science09, Tschischik_BHbreathing_PRA_2013, 1D_breathing_mode_recent,
+  Bouchoule_PRL2014, KroenkeSchmelcher_BM}.
 %
@@
   Stringari_lowDcollective_PRA15}, and also for fermionic and bosonic systems with long-range
-interactions \cite{br_mode_long_range_interactions, Bonitz_Review}.  The breathing mode has also
-been studied for a high-temperature trapped gas where a Boltzmann-equation description is valid,
-both theoretically \cite{Guery-Odelin1999} and experimentally
+interactions \cite{OrignacCitro_PRA08, br_mode_long_range_interactions, Bonitz_Review}.  The
+breathing mode has also been studied for a high-temperature trapped gas where a Boltzmann-equation
+description is valid, both theoretically \cite{Guery-Odelin1999} and experimentally
 \cite{Cornell_classsical_3Dexpt_NatPhys15}.
@@
 hypothesis (ETH), which postulates that in ergodic systems the expectation values of observables in
-individual eigenstates depend ony on the eigenenergy, and hence represents the thermal value (CITE).
-The connection to statistical mechanics is particularly difficult for explicitly finite systems, in
-which case ETH is to be understood in terms of finite size scaling (CITE).  In classical systems,
-the connection between microscopic dynamics and statistical mechanics has been continually studied
-since the 19th century \cite{Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book,
-  EckmannRuelle_RMP85}.  It is generally understood that systems with nonzero Lyapunov exponents,
-i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided there are enough
-degrees of freedom.  As in the quantum case, finite systems are particularly intricate.  In finite
-systems, defining thermalization is trickier as most observables will fluctuate or oscillate
-substantially.  In addition, the influence of Kolmogorov-Arnold-Moser (KAM) orbits may play a role
-in preventing thermalization; it is generally believed that the fraction of phase space where KAM
-physics might be relevant decreases rapidly with particle number \cite{Dumas_book_KAMstory}.
+individual eigenstates depend ony on the eigenenergy, and hence represent the thermal value
+\cite{PolkovnikovRigol_AdvPhys2016, BorgonoviIzrailevSantos_PhysRep2016,
+  ETH_Deutsch_Srednicki_Rigol}.  The connection to statistical mechanics is particularly difficult
+for explicitly finite systems, in which case ETH is to be understood in terms of finite size scaling
+\cite{Beugeling_ETHscaling_PRE14}.  In classical systems, the connection between microscopic dynamics and statistical mechanics
+has been continually studied since the 19th century \cite{Dorfman_book_1999, Dumas_book_KAMstory,
+  Boltzmann_legacy_book, EckmannRuelle_RMP85}.  It is generally understood that systems with nonzero
+Lyapunov exponents, i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided
+there are enough degrees of freedom.  As in the quantum case, finite systems are particularly
+intricate.  In finite systems, defining thermalization is trickier as most observables will
+fluctuate or oscillate substantially.  In addition, the influence of Kolmogorov-Arnold-Moser (KAM)
+orbits may play a role in preventing thermalization; it is generally believed that the fraction of
+phase space where KAM physics might be relevant decreases rapidly with particle number
+\cite{Dumas_book_KAMstory}.
 
@@
 There is a significant literature on calculating Lyapunov exponents in model statistical-mechanics
-systems and thus exploring ergodicity \cite{Dorfman_book_1999} (CITE).  This provides intuition of
-what types of microscopic interactions are likely to produce thermalizability, and is an important
-step in the program of understanding statistical mechanics ``from the bottom up''.  However, we are
-not aware of a significant literature on following explicitly the microcanonical dynamics of
-statistical-mechanical or few-body systems.  Several such studies have appeared recently (CITE),
-motivated by the quantum dynamics literature, like the present work.  A few earlier studies have
-also examined thermalization dynamics in one dimensional gravitational systems \cite{Yawn1997,
-  Tsuchiya2000}.
+systems and thus exploring ergodicity \cite{Dorfman_book_1999, deWijn_fine,
+  Lyapunov_numerical_calculations, Lyapunov_analytical_calculations, FiniteTimeLyapunov}.  This
+provides intuition of what types of microscopic interactions are likely to produce thermalizability,
+and is an important step in the program of understanding statistical mechanics ``from the bottom
+up''.  However, we are not aware of a significant literature on following explicitly the
+microcanonical dynamics of statistical-mechanical or few-body systems.  Several such studies have
+appeared recently \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10, JinKatsnelson_NJP13}, motivated by the
+quantum dynamics literature, like the present work.  A few earlier studies have also examined
+thermalization dynamics in one dimensional gravitational systems \cite{Yawn1997, Tsuchiya2000}.
 %
@@
 %
+Here $F_0\left(\sigma-\left|r\right|\right)\theta(\sigma-|r|)$, with $r=x_i-x_j$ and $\theta()$ the
+Heaviside theta function, is the potential corresponding to the force introduced in
+Eq.\ \eqref{eq:preparation1}.
+%
 It is useful to rescale the quantities.  We will measure distance, time, energy and force in units
@@
 numerical simulation.  In the rest of this paper, we will use ``$E$" and ``$F_0$" to denote the
-reduced versions $\tilde{H}$ and $\tilde{F_0}$.
+reduced versions $\tilde{H}$ and $\tilde{F_0}$, and omit the tilde when writing rescaled
+quantities.
+
+In the limit of infinite $F_0$, the particles maintain distance larger than $\sigma$ from each
+other.  In this limit each particle can then be thought of as a `hard rod' of length $2\sigma$.  In
+the absence of a trap, this would be the one-dimensional classical system shown by Tonks to be
+classically integrable \cite{Tonks_1936}.
+
+\subsection{Cloud size or `radius'}
 
@@
 \begin{equation}
-R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2} \, ,
+R ~=~ \left(\overline{x^2}\right)^\frac{1}{2} ~=~ \left(\frac{1}{N}\sum_i{x_i^2}\right)^\frac{1}{2} \, ,
 \label{eq:def_of_R}
@@
 \centering
-\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
+\includegraphics[scale=0.65]{ZhiyuPictures/N_5_GS_pre_2_rev-crop.pdf}
 \caption{The ground state of a system with $N=5$ particles, shown via the positions of each
@@
 
-Because of the `Heaviside theta' form of our interaction, at large enough interactions (large $F_0$)
-the particles are spaced exactly at distance equal to the range $\sigma$, which is distance $1$ in
-our rescaled units.  The interaction is then effectively a `hard-core' interaction.
+Because of the discontinuous `Heaviside theta' form of our interaction, at large enough interactions
+(large $F_0$) the particles are spaced exactly at distance equal to the range $\sigma$, which is
+distance $1$ in our rescaled units.  The interaction is then effectively a `hard-core' interaction,
+or alternatively, the particles can be thought of as hard rods of length $2\sigma$.
 
@@
 prominently visible.  In addition, the question of long-time relaxation has the simple
-interpretation of evolving from the line distribution to a circularly symmetric distribution.
+interpretation of evolving from the line distribution to a circularly symmetric distribution in
+phase space.
 
@@
 finite-size simulations start with a line distribution in phase space.  If we started with a state
-whose configuration in phase-space deviates only slightly from circular symmetry, the oscillating
+whose configuration deviates only slightly from circular symmetry in $X$-$P$ space, the oscillating
 amplitude would be too small to be distinguished from noise.
@@
 
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tbph]
+\includegraphics[width=0.95\textwidth]{ZhiyuPictures/phase-space_collisioncartoons_01.pdf}
+\caption{Schematic diagrams of two-particle collision process in the $X_{\rm rot}$-$P_{\rm rot}$
+  plane. 
+%
+The black filled dots shown locations of the two particles in $X_{\rm rot}$-$P_{\rm rot}$ space
+before the collision; the empty dots show locations after the collision.  The dashed lines show the
+trajectories during the collision process.  Collistions for different $F_0$ values are shown with
+different color.
+%
+\textbf{(a)} When $F_0$ is large, particles cannot pass each other: during the collision the
+momentum changes sign.  Being subject to a constant repulsive force, their trajectories during
+collision are curved arcs.  The weaker $F_0$ is, the longer the collision lasts, and hence the more
+curved is the corresponding arc.
+%
+For very strong interactions (red dashed line), particles exchange momenta instantaneously; hence
+the red dashed line is straight.  The locations of the particles after this collision are on the
+gray line; the angle $\alpha$ made by this gray line is estimated in the text.  The yellow, green,
+and blue dashed curves are for successively weaker interactions.  \textbf{(b)} When $F_0$ is small,
+particles pass each other, so that the force they feel is discontinuous (changes sign) at the moment
+when they cross each other.  Their trajectory in $X_{\rm rot}$-$P_{\rm rot}$ space has a
+corresponding turning point.  The dashed bright blue trajectory is identical with the one in (a),
+which is the critical situation between passing and bouncing. In that case, particles have zero
+relative velocity when they collide. }
+\label{fig:Breathingfrequency3}
+\end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
 \subsection{Estimates using the rotating phase space}
@@
 
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h
-]
-\subfigure[]{
-\begin{minipage}[b]{0.4\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/bounce.png}
-\end{minipage}
-}
-\subfigure[]{
-\begin{minipage}[b]{0.4\textwidth}
-\includegraphics[width=1\textwidth]{ZhiyuPictures/pass.png}
-\end{minipage}
-}
-\caption{Schematic diagrams of two-particle collision process in the $X_{\rm rot}$-$P_{\rm rot}$
-  plane. \textbf{(a)}When $F_0$ is large, particles cannot pass each other.  Being subject to a
-  constant repulsive force, their trajectories during collision are circular arcs.  For very strong
-  interactions (red dashed line, straight), they exchange momenta instantaneously.  The yellow,
-  green, and blue dashed curves are for successively weaker interactions.  \textbf{(b)} When $F_0$
-  is small, particles pass each other, so that the force they feel is not continuous.  Their
-  trajectory has a turning point. The dashed bright blue trajectory is identical with the one in
-  (a), which is the critical situation between passing and bouncing. In that case, particles have
-  zero relative velocity when they collide. }
-\label{fig:Breathingfrequency3}
-\end{figure}
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
-
 To analyze the rotation relative to the $X_{\rm rot}$-$P_{\rm rot}$ frame, we consider two-particle
-collisions.  In Figure \ref{fig:Breathingfrequency3}(a), we show schematics of such a collision near
-the trap center at strong interactions.  For very large $F_0$, the particles simply exchange
-momentum when they are at distance $\sigma$ from each other; this process is shown in red as two
-straight lines.  (The particles are initially at $X=\pm\frac{1}{2}\sigma$ and remain at these $X$
-values, but exchange their momenta.)  For smaller $F_0$, there is change of both position and
-momentum, as shown in yellow, green and blue for successively weaker interactions. The blue line
-shows a case where $F_0$ is smaller enough such that the particles can actually cross each other.
-
-In Figure \ref{fig:Breathingfrequency3}(a) we show collisions for small $F_0$, so that the particles
-pass each other.  The force changes direction discontinuously when the particles cross.  In the
-$X_{\rm rot}$-$P_{\rm rot}$ plane, this is seen as a sharp turning point in the trajectory.
+collisions.  In Figure \ref{fig:Breathingfrequency3}(a), we show schematics of such collisions near
+the trap center at strong interactions.  
+%
+During the collision, the particle momentum is changing at a constant rate (the force is a constant
+repulsion), so the particle trajectory has a component of motion in the direction of the $P$ axis.
+However, the $P$ axis itself is rotating in the $X_{\rm rot}$-$P_{\rm rot}$ frame, at frequency
+$\omega_0$.  Thus, the trajectories of the particles during the collision in the $X_{\rm
+  rot}$-$P_{\rm rot}$ plane are curved arcs.
+%
+As long as $F_0$ is large enough that the particles bounce off each other, the particle momentum
+will change sign, so a trajectory starting at negative $P$ will end at positive $P$.
+%
+For very large $F_0$, the particles simply exchange momentum when they are at distance $\sigma$ from
+each other; this process is shown in red as two straight lines.  (The particles are initially at
+$X=\pm\frac{1}{2}\sigma$ and remain at these $X$ values, but exchange their momenta.)  For smaller
+$F_0$, there is change of both position and momentum, as shown in yellow, green and blue for
+successively weaker interactions.
+
+The blue dashed line in Figure \ref{fig:Breathingfrequency3}(a) shows a case where $F_0$ is small
+enough such that the particles can just cross each other.
+%
+In Figure \ref{fig:Breathingfrequency3}(b) we show collisions for even smaller $F_0$, so that the
+particles pass each other.  The force changes direction discontinuously when the particles cross.
+In the $X_{\rm rot}$-$P_{\rm rot}$ plane, this is seen as a sharp turning point in the trajectory
+--- if the momentum is initially positive, it first decreases and then increases again.
+
+The boundary case between bouncing and passing behaviors is shown as the blue dashed curve in both
+\ref{fig:Breathingfrequency3}(a) and \ref{fig:Breathingfrequency3}(b).  In this case, the momentum
+decreases to just about zero when the relative distance reaches zero, so that the particles just
+manage to cross.
 
@@
 The precession angle is $\alpha\sim \sigma/P$.  In our rescaled units, the typical momenta of
-interacting partilces is of the order $R$.  (In phase space $R$ can be interpreted either as the
+interacting particles are of the order $R$.  (In phase space $R$ can be interpreted either as the
 extent in real space when the velocities are small, or as the extent in momentum space when the
@@
 
-The effect of interaction on breathing frequency is more complicated at smaller $F_0$.  As we have
-seen in Figure \ref{fig:Breathingfrequency1}, the effect of a small $F_0$ is to \emph{decrease} the
+The effect of interactions on the breathing frequency is more complicated at smaller $F_0$.  As we
+have seen in Figure \ref{fig:Breathingfrequency1}, the a small $F_0$ can \emph{decrease} the
 breathing frequency from its non-interacting value $\omega_B=2$.  This can also be understood using
-phase-space pictures of collision processes.  For $F_0$ is not very big, the finite interaction time
-needs to be taken into consideration.  During this time, the motion of each particle in phase-space
-is moving exactly along the direction of the real $P$ axis at the rate $F_0/m$. Since the real $P$
-axis is rotating counter-clockwise, the particle will follow a circular trajectory, e.g., following
-the orange or green dashed lines in Fig.~\ref{fig:Breathingfrequency3}(a).  The angle $\alpha$ that
-we used above to estimate $\delta$ thus decreases with the increase of interaction time; it is
-smaller for the yellow line and even opposite for the green line.  This explains the negative
-contribution of interaction to $\delta$, for small enough values of $F_0$.  At even smaller values
-of $F_0$, shown in Fig.~\ref{fig:Breathingfrequency3})(b), the particles cross each other.  The
-resulting final values are such that the line joining the post-interaction locations of the two
-particles has negative $\alpha$, i.e., is tilted clockwise with respect to the $X_{\rm rot}$ axis,
-meaning a negative contribution to the breathing frequency.
+phase-space pictures of collision processes.  For $F_0$ not very big, the finite interaction time
+needs to be taken into consideration.  During this time, the point describing a particle in phase
+space moves along the direction of the $P$ axis at the rate $F_0/m$.  Since the $P$ axis is itself
+rotating counter-clockwise in the $X_{\rm rot}$-$P_{\rm rot}$ frame, the particle will follow a
+curved trajectory in $X_{\rm rot}$-$P_{\rm rot}$ space, e.g., the yellow or green dashed lines in
+Fig.~\ref{fig:Breathingfrequency3}(a).  The angle $\alpha$ that we used above to estimate $\delta$
+thus decreases with the increase of interaction time; it is smaller for the yellow line and even
+opposite for the green line.  This explains the negative contribution of interaction to $\delta$,
+for small enough values of $F_0$.  At even smaller values of $F_0$, shown in
+Fig.~\ref{fig:Breathingfrequency3})(b), the particles cross each other.  The resulting final values
+are such that the line joining the post-interaction locations of the two particles has negative
+$\alpha$, i.e., is tilted clockwise with respect to the $X_{\rm rot}$ axis, meaning a negative
+contribution to the breathing frequency.
 
@@
 The time $\tau$ is approximately the time it takes for the momentum to change sign due to a constant
-force $F_0$, since the momentum is $\sim R$, this means $\tau\sim R/F_0$.  Using our previous
+force $F_0$.  Since the momentum is $\sim R$, this means $\tau\sim R/F_0$.  Using our previous
 estimate  $\alpha\sim \sigma/R$, together with $E\sim NR^2$, gives us the condition
@@
 same criterion for whether two particles will bounce or cross each other in a typical collision.
+(Note that this is only a rough correspondence: from the green arc in Figure
+\ref{fig:Breathingfrequency3}(a), we see that the contribution to $\delta$ can be negative even when
+$F_0$ is strong enough for two particles to bounce off rather than pass each other.)
 
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[h]
+\begin{figure}[tb]
 \centering
-\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
+\includegraphics[width=0.45\textwidth]{ZhiyuPictures/N_20_freq_vs_E_a.pdf}
 \caption{Dependence of breathing frequency, calculated for $N=20$ particles, on energy.  Different
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[tbph]
+\begin{figure}[tb]
 \centering
@@
 
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tb]
+\centering
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N_5_F0_unknown_E_100_Single_Particle_Energy.pdf}
+\caption{Time evolution of single-particle energies in a system of five particles, showing a case of
+  inefficient energy redistribution.  The energies of the two particles with highest energy (2 \& 3)
+  show a clear beating similar to the two-particle case, as does the pair 4 \& 5, although less
+  visible.  The `unpaired' particle 1 performs slow beating dynamics with the center of mass of the
+  4 \& 5 pair --- the energy of the particle 1 and of the center of mass of the 4 \& 5 pair undergo
+  long-period out-of-phase oscillations, of which approximately the first one-third of one period is
+  visible in the time window shown.}
+\label{fig:thermalization4}
+\end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
+
 \subsubsection{More particles}
@@
 the interaction is not effective in energy exchange.
-%
-An example is shown in Figure \ref{fig:thermalization4}, showing the dynamics of $N=5$ particles.
+
+An example is shown in Figure \ref{fig:thermalization4}, following the dynamics of $N=5$ particles.
 Two pairs of particles persist in performing `internal' dynamics.  The lone particle participates
@@
 mismatch acts as a hurdle to the relaxation process.
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{ZhiyuPictures/pair1_pre.eps}
-\caption{Time evolution of single-particle energies in a system of five particles, showing a case of
-  inefficient energy redistribution.  The energies of the two particles with highest energy (4 \& 5)
-  show a clear beating similar to the two-particle case, as does the pair 2 \& 3, although less
-  visible.  The `unpaired' particle 1 performs slow beating dynamics with the center of mass of the
-  2 \& 3 pair.}
-\label{fig:thermalization4}
-\end{figure}
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
@@
 the total energy $E$, we can estimate the typical internal energy by the average energy,
-$\frac{E}{N}$. At least they are of the same order.  Thus we have the condition
+$E/N$. At least they are of the same order.  Thus we have the condition
 \begin{equation}
@@
 \end{equation}
-for relaxation.  This is the same condition we obtained for the breathing frequency to be increased
-(rather than decreased) by the interaction.
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[tbhp]
+for relaxation.  This is the same condition we obtained in the previous section for the breathing
+frequency to be increased (rather than decreased) by the interaction.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tb]
 \centering
@@
 %
-\caption{The distribution of single-particle energies measured in $\sim 10000$ time units. Green
-  curves obey the relaxation condition \eqref{eq:thermalizatiton_condition}, and yellow/orange
-  corresponds to smaller $F_0$.  In each panel (different $N$), we choose $E/N$ identical ($=1000$),
-  so that the threshold interaction between the two behaviors is  $F_0\sim1000$. }
+\caption{The distribution of single-particle energies.  Snapshots of the single-particle energies
+  are taken at unit time steps during the simulation, up to $\sim 10000$ time units.  Green curves
+  obey the relaxation condition \eqref{eq:thermalizatiton_condition}, and yellow/orange corresponds
+  to smaller $F_0$.  The two panels correspond to different particle numbers $N$, but we choose
+  total energies such that $E/N$ is identical ($=1000$) in all cases.  Thus the threshold
+  \eqref{eq:thermalizatiton_condition} corresponds to the interaction $F_0\sim1000$. }
 \label{fig:thermalization5}
@@
 %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[tbph]
+\begin{figure}[tb]
 \includegraphics[width=0.8\textwidth]{ZhiyuPictures/Boltzmann_log_2panels_01-crop.pdf}
@@
 unsurprising given our small system sizes.  However, some deviation is also expected due to the
-contribution of the density of states (DOS).  The probability of finding an energy is actually
+contribution of the density of states (DOS), as the probability of finding an energy is actually
 proportional to the Boltzmann exponential factor multiplied by the DOS.  For the simple harmonic
@@
 $|x_i-x_j|<\sigma$; so that the DOS is no longer a constant.  The measured distribution seems
-systematically slightly smaller than the Boltzmann curve at very small $\epsilon$: when interaction
-is weak, particles prefer to stay near zero energy according to the Boltzmann distribution, but when
-interaction grows, they are no longer allowed to accumulate near zero energy, in other words the DOS
-at low energy decreases with the increase of interaction. Therefore, counts at the low energy part
-of Fig.\ref{fig:thermalization9} is slightly lower than the Boltzmann prediction.  The correction to
-the density of states is not simple to calculate explicitly.  Since we are in the regime of a dilute
-gas ($\sigma\ll R$), the effect is very small.
+systematically slightly smaller than the Boltzmann curve at very small $\epsilon$.  For larger
+interactions, small energies are expected to be penalized, as the interaction opposes particles
+clustering at small velocities near the bottom of the trap.  This may be the reason for the counts
+in Fig.\ref{fig:thermalization9} being slightly lower than the Boltzmann prediction at small
+$\epsilon$.  However, since we are in the regime of a dilute gas ($\sigma\ll R$), the effect is
+quite small.
+
+%% At weak interactions
+%% is weak, particles prefer to stay near zero energy according to the Boltzmann distribution, but when
+%% interaction grows, they are no longer allowed to accumulate near zero energy, in other words the DOS
+%% at low energy decreases with the increase of interaction. Therefore, counts at the low energy part
+%% of Fig.\ref{fig:thermalization9} is slightly lower than the Boltzmann prediction.  The correction to
+%% the density of states is not simple to calculate explicitly.  Since we are in the regime of a dilute
+%% gas ($\sigma\ll R$), the effect is very small.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure}[tb]
+\centering
+%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
+\includegraphics[width=0.55\textwidth]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
+\caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
+  energies.  The color indicates the observed probability of a measured LLE value being found in a
+  bin; the bins are of size 0.01.  The average of the distribution decreases monotonically with
+  energy.}  \label{fig:LLEdistribution1}
+\end{figure}
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
 
@@
 
-The general idea that thermalization is faster for larger $F_0$ can be seen through the Lyapunov
-exponents.  For high-dimensional systems, there is a spectrum of exponents which manifests the
-instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects the
-shortest time scale for the system lose memory of the initial state.  We follow the method described
-in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently late times,
-the LLE for an ergodic system is uniquely defined and independent of the starting state.  We would
-like to deal with parameter regimes both within and outside our relaxation condition $E<F_0N$ and
-$E>F_0N$, and in the latter case we have seen that ergodicity does not become apparent at reasonable
-timescales.  Therefore, we carry out the computation of the LLE upto $t\sim10^3$, i.e, we consider
-finite-time Lyapunov exponents (CITE).  This means that we can only get
-initial-configuration-dependent estimates.  The collection of these estimates forms a distribution
-which we show in Figure \ref{fig:LLEdistribution1}.
+The general idea that thermalization is faster for larger $F_0$ can be quantified through the
+Lyapunov exponents.  For high-dimensional systems, there is a spectrum of exponents which manifests
+the instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects
+the shortest time scale for the system lose memory of the initial state.  We follow the method
+described in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently
+late times, the LLE for an ergodic system is uniquely defined and independent of the starting state.
+We would like to deal with parameter regimes both within and outside our relaxation condition
+$E<F_0N$ and $E>F_0N$, and in the latter case we have seen that ergodicity does not become apparent
+at reasonable timescales.  Therefore, we carry out the computation of the LLE upto $t\sim10^2$, i.e,
+we consider finite-time Lyapunov exponents \cite{FiniteTimeLyapunov}.  This means that we can only
+get initial-configuration-dependent estimates.  The collection of these estimates forms a
+distribution which we show in Figure \ref{fig:LLEdistribution1}.  The distributions are obtained
+using 100 initial states in each case.
 
@@
 
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure}[tbph]
-\centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
-\includegraphics[width=0.55\textwidth]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
-\caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
-  energies.  The color indicates the observed probability of a measured LLE value being found in a
-  bin; the bins are of size 0.01.  }  \label{fig:LLEdistribution1}
-\end{figure}
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
-
-%% \begin{figure}[h]
-%% \centering
-%% \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
-%% \includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
-%% \caption{``bone". top(bottom):modified(reversed)}
-%% \end{figure}
-
 The LLE decreases with the growth of energy. The critical part is near $E = F_0N = 5000$.  Around
@@
 
-\subsection{Shape of distribution in single-particle phase space}\label{section:Shape}
-
-Till now, we have studied formulated the thermalization question in terms of energy distributions.
-More generally, thermalization may be taken to mean that a many-body system loses memory of its
-initial state.  In the single-particle phase-space picture, Figures \ref{fig:Breathingfrequency2_0}
-and \ref{fig:Breathingfrequency2_1}, our initial state is very special: The particles are lined up
-along the $X$ axis.  The effect of interaction is to distort this line toward a circularly symmetric
-distribution.  Thus, we would consider that the memory of the initial state is lost when the
-distribution of points in the $X$-$P$ plane are not elongated in any one direction.
-
-To quantify the shape of distribution in phase-space, we define a shape parameter $S$ measuring the
-degree of ellipticity:
-\begin{equation}
-S=\frac{a-b}{a+b}
-\end{equation}
-where $a$ and $b$ are long axis and short axis of the inertia ellipse in phase space respectively.
-These are calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
-I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.  The shape parameter is $S=1$ for line-shaped
-distributions and $S=0$ for circularly symmertic distributions.
-
-%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
-\begin{figure*}[tbph]
+For the largest $E$ values (smallest $F_0/E$) in Figure \ref{fig:LLEdistribution1}, we note large
+relative fluctuations.  This presumably reflects the fact that the relaxation time in these cases is
+much larger than the time used to calculate the finite-time LLE's.
+
+%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
+\begin{figure*}[tb]
 \includegraphics[width=\textwidth]{ZhiyuPictures/combine_shapedynamics_a_01-crop.pdf}
@@
 
+\subsection{Shape of distribution in single-particle phase space}\label{section:Shape}
+
+Until now, we have formulated the thermalization question in terms of energy distributions.  More
+generally, thermalization may be taken to mean that a many-body system loses memory of its initial
+state.  In the single-particle phase-space picture, Figures \ref{fig:Breathingfrequency2_0} and
+\ref{fig:Breathingfrequency2_1}, our initial state is very special: The particles are lined up along
+the $X$ axis.  The effect of interaction is to distort this line toward a circularly symmetric
+distribution.  Thus, we would consider that the memory of the initial state is lost when the
+distribution of points in the $X$-$P$ plane are not elongated in any one direction.
+
+To quantify the shape of distribution in phase-space, we define a shape parameter $S$ measuring the
+degree of ellipticity:
+\begin{equation}
+S=\frac{a-b}{a+b}
+\end{equation}
+where $a$ and $b$ are the long axis and the short axis of the inertia ellipse in phase space
+respectively.  These are calculated by diagonalizing the inertia tensor I: $I_{xx}=\sum{p^2},
+I_{xp}=I_{px}=-\sum{xp},I_{pp}=\sum{x^2}$.  The shape parameter is $S=1$ for line-shaped
+distributions and $S=0$ for circularly symmertic distributions.
+
+In a thermalizing system with very large $N$, one might expect that $S(t)$ will decrease rapidly to
+zero, and a reasonable conjecture is that the timescale for the decrease (relaxation) of $S(t)$
+should be related to the timescale for achieving energy thermalization.  However, in our finite
+systems, we will find that $S(t)$ can continue to perform coherent oscillations long after
+single-particle thermalization has been observed.
+
 The time evolution of the shape parameter $S$ is shown in Fig.\ref{fig:time_evolution_of_S}.
 %
-The top three pannels show averaged values of $S$ in order to highlight the overall behavior.  Every
-data point is the average of the original data over $10T = 20\pi$. The lower six pannels are the
-original data measured after several thousand time units.
+The top three panels show averaged values of $S$ in order to highlight the overall behavior.  Every
+data point is the average of the original data over $10T = 20\pi$.  (The dynamics for several
+initial states are shown to give an impression of typical $S(t)$ dynamics.)  The lower six panels
+are the original data measured after several thousand time units.
 
@@
 %
-The behavior of $S(t)$ at longer times shows (lower panel) that there are long-range coherent
-oscillations of the phase-space cloud shape at rather long timescales.  Strikingly, this is even
-true for the thermalizing regime (lower left panel), for which the time-averaged single-particle
-energies already are Boltzmann-distributed.  Thus, energy thermalization can occur at timescales
-much faster than it takes for other features of the gas to relax.
+The behavior of $S(t)$ at longer times shows (lower panel) that there are coherent oscillations of
+the phase-space cloud shape on rather long timescales.  Strikingly, this is even true for the
+thermalizing regime (lower left panel), for which the time-averaged single-particle energies already
+are Boltzmann-distributed.  Thus, energy thermalization can occur at timescales much faster than it
+takes for other features of the gas to relax.
 
@@
 dynamics.  We have chosen to work with a simple finite-range interaction with variable interaction
-strength, in the `dilute gas' regime where the particles are at average distance significantly
+strength, in the `dilute gas' regime where the particles are at an average distance significantly
 larger than the interaction range.
@@
 frequency on the interaction strength $F_0$: the breathing frequency first decreases as a function
-of $F_0$, and around the critical value $F_0 \sim E/N$, in increases above the non-interacting
-value.  Eventually at large $F_0$ the frequency shift reaches a plateau at a value
-$\propto\sqrt{N^3/E}$.  We have explained this behavior physically, using both real-space and
-phase-space pictures.
+of $F_0$, and around the critical value $F_0 \sim E/N$, increases above the non-interacting value.
+Eventually at large $F_0$ the frequency shift reaches a plateau at a value $\propto\sqrt{N^3/E}$.
+We have explained this behavior physically, using both real-space and phase-space pictures.
 
@@
 space distribution, even after energy thermalization has already occurred.  
+%
+Of course, it is known quite generally that different observables can have different equilibration
+times.
 
@@
 represents the interaction-dependence for a wide class of interactions.  However, it would be
-interesting to ask how collective modes in general depend on the form of interactions.
+interesting to ask how collective modes in general depend on the form of interactions.  For example,
+if the force were partially or totally attractive, e.g., if $F_0$ is negative, or with a
+Lennard-Jones type potential which is attractive for some separations, the effect on the breathing
+frequency is not obvious.
 %
@@
 systems, for few-body systems like the present case the connection is less clear and raises
-questions of timescales.  Our study of a special case exemplifies the need for better general
-understanding of the connections between relaxation timescales, interaction strengths,
-thermalization, and finite-time Lyapunov expnents.
+questions of the the parametric dependence of timescales on model parameters.  Our study of a
+special case exemplifies the need for better general understanding of the connections between
+relaxation timescales, interaction strengths, thermalization, and finite-time Lyapunov expnents.
 
 \begin{thebibliography}{1}
+
+\bibitem{PolkovnikovRigol_AdvPhys2016}
+L.~D'Alessio, Y.~Kafri, A.~Polkovnikov, and M.~Rigol, 
+``From quantum chaos and eigenstate thermalization to statistical mechanics and thermodynamics'', 
+{\em Adv.
+  Phys.}, {\bf 65}, 239 (2016).
+
+\bibitem{BorgonoviIzrailevSantos_PhysRep2016}
+F.~Borgonovi, F.~M.~Izrailev, L.~F.~Santos, and V.~G.~Zelevinsky,
+``Quantum chaos and thermalization in isolated systems of interacting particles'', 
+  {\em Phys. Rep.} {\bf 626}, 1 (2016).
+
+\bibitem{Gaspard_book_1998}
+P.~Gaspard, ``Chaos, Scattering, and Statistical Mechanics'', Cambridge University Press, 1998.
 
@@
 
-\bibitem{Naegerl_Science2009} E.~Haller, M.~Gustavsson, M.~J.~Mark, J.~G.~Danzl, R.~Hart,
-  G.~Pupillo, H.-C.~N\"agerl, ``Realization of an excited, strongly correlated quantum gas phase,''
-  {\em Science}, \textbf{325}, 1224 (2009).
-
-\bibitem{collective_modes_early_papers}
-S.~Stringari, Phys.\ Rev.\ Lett.\ \textbf{77}, 2360 (1996); 
+\bibitem{Gaspard_PhysicaA06}
+P.~Gaspard, 
+``Hamiltonian dynamics, nanosystems, and nonequilibrium statistical mechanics'', 
+{\em Physica A}, {\bf 369}, 201 (2006).
+
+\bibitem{vortices_trappedBEC}
+D. S. Rokhsar, 
+``Vortex Stability and Persistent Currents in Trapped Bose Gases'', 
+{\em Phys. Rev. Lett.}, {\bf 79}, 2164 (1997).
+%
+\\ 
+%
+A. A. Svidzinsky and A. L. Fetter, ``Stability of a Vortex in a Trapped Bose-Einstein Condensate'',
+{\em Phys. Rev. Lett.}, {\bf 84}, 5919 (2000).
+%
+\\ 
+%
+W.~Li, M.~Haque, and S.~Komineas, 
+``Vortex dipole in a trapped two-dimensional Bose-Einstein condensate'', 
+{\em Phys. Rev. A}, {\bf 77}, 053610 (2008).
+%
+\\ 
+%
+A.~L.~Fetter, ``Rotating trapped Bose-Einstein condensates'', {\em Rev. Mod. Phys.}, {\bf 81}, 647
+(2009).
+%
+\\ 
+%
+R.~Navarro, R.~Carretero-Gonz\'alez, P.~J.~Torres, P.~G.~Kevrekidis, D.~J.~Frantzeskakis, M.~W.~Ray,
+E.~Altunta\c{s}, and D.~S.~Hall, 
+``Dynamics of a Few Corotating Vortices in Bose-Einstein Condensates'', 
+{\em Phys. Rev. Lett.}, {\bf 110}, 225301 2013).
+
+\bibitem{vortices_uniformBEC}
+%
+A.~L.~Fetter, 
+``Vortices in an Imperfect Bose Gas. I. The Condensate'', 
+{\em Phys. Rev.}, {\bf 138}, A429 (1965).
+%
+\\ 
+%
+A.~L.~Fetter, 
+``Vortices in an Imperfect Bose Gas. IV. Translational Velocity'', 
+{\em Phys. Rev.}, {\bf 151}, 100 (1966)
+
+\bibitem{collective_modes_early_papers} S.~Stringari, ``Collective Excitations of a Trapped
+  Bose-Condensed Gas'', {\em Phys.\ Rev.\ Lett.}  \textbf{77}, 2360 (1996).
 %
@@
 M.-O.~Mewes, M.~R.~Andrews, N.~J.~van~Druten, D.~M.~Kurn, D.~S.~Durfee, 
-C.~G.~Townsend, and W.~Ketterle, Phys.\ Rev.\ Lett.\ \textbf{77}, 988 (1996);
-%
-\\ 
-%
-M.~Amoruso, I.~Meccoli, A.~Minguzzi, and M.~P.~Tosi, Eur.\ Phys.\ J.~D \textbf{8}, 361 (2000);
-%
-\\ 
-%
-R.~Combescot and X.~Leyronas, Phys.\ Rev.\ Lett.\ \textbf{89}, 190405 (2002);
+C.~G.~Townsend, and W.~Ketterle, ``Collective Excitations of a Bose-Einstein Condensate in a Magnetic
+Trap'', {\em Phys.\ Rev.\ Lett.}, \textbf{77}, 988 (1996).
+%
+\\ 
+%
+D.~S. Jin, J.~R. Ensher, M.~R. Matthews, C.~E. Wieman, and E.~A. Cornell,
+  ``Collective excitations of a bose-einstein condensate in a dilute gas,''
+  {\em Phys. Rev. Lett.}, {\bf 77}, 420 (1996).
+%
+\\
+%
+F.~Dalfovo, S.~Giorgini, M.~Guilleumas, L.~Pitaevskii, and S.~Stringari,
+  ``Collective and single-particle excitations of a trapped bose gas,'' {\em
+  Phys. Rev. A}, {\bf 56}, 3840 (1997).
+%
+\\
+%
+M.~Amoruso, I.~Meccoli, A.~Minguzzi, and M.~P.~Tosi,  ``Density profiles and collective excitations of
+a trapped two component Fermi vapour'', {\em Eur.\ Phys.\ J.~D} \textbf{8}, 361 (2000).
+%
+\\ 
+%
+R.~Combescot and X.~Leyronas, 
+``Hydrodynamic Modes in Dense Trapped Ultracold Gases'', {\em Phys.\ Rev.\ Lett.}, \textbf{89}, 190405 (2002).
 %
@@
 F.~Chevy, V.~Bretin, P.~Rosenbusch, K.~W.~Madison, and J.~Dalibard, 
-Phys.\ Rev.\ Lett.\ \textbf{88}, 250402 (2002);
+``Transverse Breathing Mode of an Elongated Bose-Einstein Condensate'', 
+{\em Phys.\ Rev.\ Lett.}, \textbf{88}, 250402 (2002).
 %
@@
 %
-J.~Fuchs, X.~Leyronas, and R.~Combescot, Phys.\ Rev.\ A \textbf{68}, 043610 (2003).
+J.~Fuchs, X.~Leyronas, and R.~Combescot, 
+``Hydrodynamic modes of a one-dimensional trapped Bose gas'', 
+{\em Phys.\ Rev.\ A}, \textbf{68}, 043610 (2003).
 
@@
 %
-L.~P.~Pitaevskii and A.~Rosch, {\em Phys.\ Rev.\ A} \textbf{55}, R853 (1997);
+L.~P.~Pitaevskii and A.~Rosch, 
+``Breathing modes and hidden symmetry of trapped atoms in two
+dimensions'', {\em Phys.\ Rev.\ A} \textbf{55}, R853 (1997);
 
@@
 T.~Esslinger,
-Phys.\ Rev.\ Lett.\ \textbf{91}, 250402 (2003).
-
-\bibitem{Wetterich_JPB2011}
-I.~Boettcher, S.~Floerchinger, and C.~Wetterich, J.~Phys.\ B \textbf{44}, 235301 (2011).
-
-\bibitem{Tschischik_BHbreathing_PRA_2013} W.~Tschischik, R.~Moessner, M.~Haque, Phys.\ Rev.~A 
-  \textbf{88}, 063636 (2013).
-
-\bibitem{KroenkeSchmelcher_BM} R.~Schmitz, S.~Kr\"onke, L.~Cao, and 
-  P.~Schmelcher, Phys.\ Rev.\ A \textbf{88}, 043601 (2013).
-
-\bibitem{Mazets_1Dbreathing_EPJD11}
-I. E. Mazets, ``Integrability breakdown in longitudinaly trapped, one-dimensional bosonic gases'', 
-{\em Eur.~Phys.~J.~D} {\bf 65}, 43 (2011).
-
-%%  \bibitem{GaoYu_fermionbreathing_PRA12} 
-%% Chao Gao and Zhenhua Yu, 
-%%   ``Breathing mode of two-dimensional atomic Fermi gases in harmonic traps'', 
-%% {\em Phys. Rev. A} {\bf 86}, 043609 (2012).
-
-\bibitem{fermion2Dbreathing}
-%
-
-E.~Vogt, M.~Feld, B.~Fr\"ohlich, D.~Pertot, M.~Koschorreck, and M.~K\"ohl, ``Scale Invariance and
-Viscosity of a Two-Dimensional Fermi Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 070404 (2012).
-%
-\\ 
-%
-Chao Gao and Zhenhua Yu, ``Breathing mode of two-dimensional atomic Fermi gases in harmonic traps'',
-{\em Phys. Rev. A} {\bf 86}, 043609 (2012).
-%
-\\ 
-%
-J.~Hofmann, ``Quantum Anomaly, Universal Relations, and Breathing Mode of a Two-Dimensional Fermi
-Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 185303 (2012).
-%
-\\ 
-%
-S.~K.~Baur, E.~Vogt, M.~K\"ohl, and G.~M.~Bruun, ``Collective modes of a two-dimensional spin-1/2
-Fermi gas in a harmonic trap'', {\em Phys. Rev. A} {\bf 87}, 043612 (2013).
-%
-\\ 
-%
-B.~P.~van~Zyl, E.~Zaremba, and J.~Towers,
-``Collective excitations of a harmonically trapped, two-dimensional, spin-polarized dipolar Fermi
-gas in the hydrodynamic regime'', 
-{\em Phys. Rev. A} {\bf 90}, 043621 (2014). 
-%
-\\ 
-%
-Yi-Cai Zhang and Shizhong Zhang, ``Strongly interacting p -wave Fermi gas in two dimensions:
-Universal relations and breathing mode'', {\em Phys. Rev. A} {\bf 95}, 023603 (2017).
-
-%% \bibitem{ZarembaTowers_PRA2014} B.~P.~van~Zyl, E.~Zaremba, and J.~Towers, Phys. Rev. A \textbf{90},
-%%   043621 (2014).
-
-\bibitem{Stringari_lowDcollective_PRA15}
-G.~De~Rosi and S.~Stringari, ``Collective oscillations of a trapped quantum gas in low dimensions'', 
-{\em Phys. Rev. A} {\bf 92}, 053617 (2015).
+``Transition from a Strongly Interacting 1D Superfluid to a Mott Insulator'',
+{\em Phys.\ Rev.\ Lett.}, \textbf{91}, 250402 (2003).
+
+\bibitem{STG_Astrakharchik_PRL2005} G.~E.~Astrakharchik, J.~Boronat, J.~Casulleras, and
+  S.~Giorgini, ``Beyond the Tonks-Girardeau Gas: Strongly Correlated Regime in Quasi-One-Dimensional
+  Bose Gases'', {\em Phys.\ Rev.\ Lett.}, \textbf{95}, 190407 (2005).
 
@@
 
+\bibitem{OrignacCitro_PRA08}
+~Pedri, S.~De~Palo, E.~Orignac, R.~Citro, and M.~L.~Chiofalo, 
+``Collective excitations of trapped one-dimensional dipolar quantum gases'', 
+{\em Phys. Rev. A}, {\bf 77}, 015601 (2008).
+
+\bibitem{Naegerl_Science09} E.~Haller, M.~Gustavsson, M.~J.~Mark, J.~G.~Danzl, R.~Hart,
+  G.~Pupillo, H.-C.~N\"agerl, ``Realization of an excited, strongly correlated quantum gas phase,''
+  {\em Science}, \textbf{325}, 1224 (2009).
+
+%% \bibitem{STG_Chen-etal_PRA2010} S.~Chen, L.~Guan, X.~Yin, Y.~Hao, and X-W.~Guan,   Phys.\ Rev.\ A
+%%   \textbf{81}, 031609(R) (2010).
+
+\bibitem{Wetterich_JPB2011} I.~Boettcher, S.~Floerchinger, and C.~Wetterich, ``Hydrodynamic
+  collective modes for cold trapped gases'', {\em J.~Phys.\ B}, \textbf{44}, 235301 (2011).
+
+\bibitem{Mazets_1Dbreathing_EPJD11}
+I. E. Mazets, ``Integrability breakdown in longitudinaly trapped, one-dimensional bosonic gases'', 
+{\em Eur.~Phys.~J.~D} {\bf 65}, 43 (2011).
+
+\bibitem{fermion2Dbreathing}
+%
+
+E.~Vogt, M.~Feld, B.~Fr\"ohlich, D.~Pertot, M.~Koschorreck, and M.~K\"ohl, ``Scale Invariance and
+Viscosity of a Two-Dimensional Fermi Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 070404 (2012).
+%
+\\ 
+%
+Chao Gao and Zhenhua Yu, ``Breathing mode of two-dimensional atomic Fermi gases in harmonic traps'',
+{\em Phys. Rev. A} {\bf 86}, 043609 (2012).
+%
+\\ 
+%
+J.~Hofmann, ``Quantum Anomaly, Universal Relations, and Breathing Mode of a Two-Dimensional Fermi
+Gas'', {\em Phys. Rev. Lett.} {\bf 108}, 185303 (2012).
+%
+\\ 
+%
+S.~K.~Baur, E.~Vogt, M.~K\"ohl, and G.~M.~Bruun, ``Collective modes of a two-dimensional spin-1/2
+Fermi gas in a harmonic trap'', {\em Phys. Rev. A} {\bf 87}, 043612 (2013).
+%
+\\ 
+%
+B.~P.~van~Zyl, E.~Zaremba, and J.~Towers,
+``Collective excitations of a harmonically trapped, two-dimensional, spin-polarized dipolar Fermi
+gas in the hydrodynamic regime'', 
+{\em Phys. Rev. A} {\bf 90}, 043621 (2014). 
+%
+\\ 
+%
+Y.-C.~Zhang and S.Zhang, ``Strongly interacting p -wave Fermi gas in two dimensions:
+Universal relations and breathing mode'', {\em Phys. Rev. A} {\bf 95}, 023603 (2017).
+
+\bibitem{Tschischik_BHbreathing_PRA_2013} W.~Tschischik, R.~Moessner, M.~Haque, 
+``Breathing mode in the Bose-Hubbard chain with a harmonic trapping potential'', 
+{\em Phys.\ Rev.~A}, \textbf{88}, 063636 (2013).
+
+\bibitem{KroenkeSchmelcher_BM} R.~Schmitz, S.~Kr\"onke, L.~Cao, and 
+  P.~Schmelcher, ``Quantum breathing dynamics of ultracold bosons in one-dimensional harmonic traps:
+  Unraveling the pathway from few- to many-body systems'', 
+{\em Phys.\ Rev.\ A}, \textbf{88}, 043601 (2013).
+
 \bibitem{Bouchoule_PRL2014}
-B.~Fang, G.~Carleo, A.~Johnson, and I.~Bouchoule,  Phys.\ Rev.\ Lett.\ 
-\textbf{113}, 035301 (2014).
-
-\bibitem{our_superTG_PRA_2015} W.~Tschischik and M.~Haque, Phys.\ Rev.~A 
-  \textbf{91}, 053607 (2015).
-
-\bibitem{Tschischik_ladder_PRA15} W.~Tschischik, R.~Moessner, and M.~Haque, ``Bose-Hubbard ladder
+B.~Fang, G.~Carleo, A.~Johnson, and I.~Bouchoule,  
+``Quench-Induced Breathing Mode of One-Dimensional Bose Gases'', 
+Phys.\ Rev.\ Lett.\ \textbf{113}, 035301 (2014).
+
+\bibitem{br_mode_long_range_interactions} 
+%
+S.~Bauch, K.~Balzer, C.~Henning, and M.~Bonitz, 
+``Quantum breathing mode of trapped bosons and fermions at arbitrary coupling'', 
+{\em Phys. Rev. B}, \textbf{80}, 054515 (2009).
+%
+\\
+%
+J.~W.~Abraham, K.~Balzer, D.~Hochstuhl, and M.~Bonitz, 
+``Quantum breathing mode of interacting particles in a one-dimensional harmonic trap'', 
+{\em Phys. Rev. B}, \textbf{86}, 125112 (2012).
+%
+\\
+%
+C.~R.~McDonald, G.~Orlando, J.~W.~Abraham, D.~Hochstuhl, M.~Bonitz, and T.~Brabec, 
+``Theory of the Quantum Breathing Mode in Harmonic Traps and its Use as a Diagnostic Tool'', 
+{\em Phys.\ Rev.\ Lett.}, \textbf{111}, 256801 (2013).
+%
+\\
+%
+J.~W.~Abraham, M.~Bonitz, C.~McDonald, G.~Orlando, and T.~Brabec, 
+``Quantum breathing mode of trapped systems in one and two dimensions'', 
+{\em New J.~Phys}, \textbf{16}, 013001 (2014).
+
+\bibitem{Bonitz_Review} J.~W.~Abraham, and M.~Bonitz, ``Quantum Breathing Mode of Trapped Particles:
+  from nanoplasmas to ultracold gases'', {\em Contrib.\ Plasma Physics}, \textbf{54}, 27
+  (2014).
+
+\bibitem{QuinnHaque_PRA14}
+E.~Quinn and M.~Haque, 
+``Modulated trapping of interacting bosons in one dimension'',  
+{\em Phys. Rev. A}, {\bf 90}, 053609 (2014).
+
+\bibitem{Tschischik_BH_2papers} W.~Tschischik and M.~Haque, ``Repulsive-to-attractive interaction
+  quenches of a one-dimensional Bose gas in a harmonic trap'', {\em Phys.\ Rev.~A}, \textbf{91},
+  053607 (2015).
+%
+\\
+% 
+W.~Tschischik, R.~Moessner, and M.~Haque, ``Bose-Hubbard ladder
   subject to effective magnetic field: Quench dynamics in a harmonic trap'',
@@
 
-% Dipole mode of a strongly correlated one-dimensional Bose gas in a split trap: 
-% parity effect and barrier renormalization
-\bibitem{Cominotti_2015} M.~Cominotti, F.~Hekking, and A.~Minguzzi, 
-arXiv:1503.07776.
-
-\bibitem{STG_Chen-etal_PRA2010} S.~Chen, L.~Guan, X.~Yin, Y.~Hao, and X-W.~Guan,   Phys.\ Rev.\ A
-  \textbf{81}, 031609(R) (2010).
-
-\bibitem{STG_Astrakharchik_PRL2005} G.~E.~Astrakharchik, J.~Boronat, J.~Casulleras, and
-  S.~Giorgini, Phys.\ Rev.\ Lett.\ \textbf{95}, 190407 (2005).
+%% \bibitem{Tschischik_superTG_PRA15} W.~Tschischik and M.~Haque, ``Repulsive-to-attractive interaction
+%%   quenches of a one-dimensional Bose gas in a harmonic trap'', {\em Phys.\ Rev.~A}, \textbf{91},
+%%   053607 (2015).
+
+%% \bibitem{Tschischik_ladder_PRA15} W.~Tschischik, R.~Moessner, and M.~Haque, ``Bose-Hubbard ladder
+%%   subject to effective magnetic field: Quench dynamics in a harmonic trap'',
+%% {\em Phys. Rev. A},  {\bf 92}, 023845 (2015).
+
+\bibitem{Stringari_lowDcollective_PRA15}
+G.~De~Rosi and S.~Stringari, ``Collective oscillations of a trapped quantum gas in low dimensions'', 
+{\em Phys. Rev. A} {\bf 92}, 053617 (2015).
+
+\bibitem{Minguzzi_dipole_PRA2015} M.~Cominotti, F.~Hekking, and A.~Minguzzi, 
+``Dipole mode of a strongly correlated one-dimensional Bose gas in a split trap: Parity effect and
+barrier renormalization'', 
+{\em Phys. Rev. A}, {\bf 92}, 033628 (2015).
 
@@
 breathing-mode-oscillation frequency in a one-dimensional Bose gas'', 
-Phys. Rev. A \textbf{92}, 021601(R) (2015). \\ 
+{\em Phys. Rev. A}, \textbf{92}, 021601(R) (2015). 
+%
+\\ 
 %
@@
 %
-X.-L.~Chen, Y.~Li, and H.~Hu,  Phys.\ Rev.\ A \textbf{91}, 063631 (2015).
-
-\bibitem{br_mode_long_range_interactions} 
-%
-S.~Bauch, K.~Balzer, C.~Henning, and M.~Bonitz, Phys. Rev. B \textbf{80}, 054515 
-(2009);
-%
-\\
-%
-J.~W.~Abraham, K.~Balzer, D.~Hochstuhl, and M.~Bonitz, Phys. Rev. B \textbf{86}, 
-125112 (2012);
-%
-\\
-%
-C.~R.~McDonald, G.~Orlando, J.~W.~Abraham, D.~Hochstuhl, M.~Bonitz, and T.~Brabec, Phys.\ Rev.\
-Lett.\ \textbf{111}, 256801 (2013);
-%
-\\
-%
-J.~W.~Abraham, M.~Bonitz, C.~McDonald, G.~Orlando, and T.~Brabec, New J.~Phys \textbf{16}, 013001
-(2014).
-
-\bibitem{Bonitz_Review} J.~W.~Abraham, and M.~Bonitz, ``Quantum Breathing Mode of Trapped Particles:
-  from nanoplasmas to ultracold gases'', {\em Contributions to Plasma Physics}, \textbf{54}, 27
-  (2014).
-
-\bibitem{KohnMode}
-%
-L.~Brey, N.~F.~Johnson, and B.~I.~Halperin, Phys.\ Rev.\ B \textbf{40}, 10647 (1989).
-%
-\\ 
-%
-M.~Bonitz, K.~Balzer, and R.~van~Leeuwen, {\em Phys. Rev. B} \textbf{76}, 045341 (2007).
+X.-L.~Chen, Y.~Li, and H.~Hu, 
+``Collective modes of a harmonically trapped one-dimensional Bose gas: The effects of finite particle
+number and nonzero temperature'', 
+{\em Phys.\ Rev.\ A} \textbf{91}, 063631 (2015).
+
+\bibitem{MistakidisSchmelcher_PRA17}
+S. I. Mistakidis and P. Schmelcher, 
+``Mode coupling of interaction quenched ultracold few-boson ensembles in periodically driven
+lattices'', 
+{\em Phys. Rev. A}, {\bf 95}, 013625 (2017).
+
+%% \bibitem{KohnMode}
+%% %
+%% L.~Brey, N.~F.~Johnson, and B.~I.~Halperin, Phys.\ Rev.\ B \textbf{40}, 10647 (1989).
+%% %
+%% \\ 
+%% %
+%% M.~Bonitz, K.~Balzer, and R.~van~Leeuwen, {\em Phys. Rev. B} \textbf{76}, 045341 (2007).
 
@@
 T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, ``A quantum Newton's cradle'', {\em Nature}, {\bf 440,} 900 (2006).
+
+\bibitem{CauxKonik_glimmers_PRX15}
+G.~P.~Brandino, J.-S.~Caux, R.~M.~Konik,
+``Glimmers of a Quantum KAM Theorem: Insights from Quantum Quenches in One Dimensional Bose Gases'', 
+{\em Phys. Rev. X}, {\bf 5}, 041043 (2015).
+
+\bibitem{CauxDoyonDubailKonik_1711} J.-S.~Caux, B.~Doyon, J.~Dubail, R.~Konik, and T.~Yoshimura,
+  ``Hydrodynamics of the interacting Bose gas in the Quantum Newton Cradle setup'',
+  arXiv:1711.00873.
 
@@
 
-\bibitem{Dalfovo1997}
-F.~Dalfovo, S.~Giorgini, M.~Guilleumas, L.~Pitaevskii, and S.~Stringari,
-  ``Collective and single-particle excitations of a trapped bose gas,'' {\em
-  Phys. Rev. A}, {\bf 56}, 3840 (1997).
-
-\bibitem{Jin1996}
-D.~S. Jin, J.~R. Ensher, M.~R. Matthews, C.~E. Wieman, and E.~A. Cornell,
-  ``Collective excitations of a bose-einstein condensate in a dilute gas,''
-  {\em Phys. Rev. Lett.}, vol.~77, pp.~420--423, July 1996.
-
-\bibitem{Dalfovo1999}
-F.~Dalfovo, S.~Giorgini, L.~P. Pitaevskii, and S.~Stringari, ``Theory of
-  bose-einstein condensation in trapped gases,'' {\em Rev. Mod. Phys.},
-  vol.~71, pp.~463--512, Apr. 1999.
-
-\bibitem{Stringari1996}
-S.~Stringari, ``Collective excitations of a trapped bose-condensed gas,'' {\em
-  Phys. Rev. Lett.}, vol.~77, pp.~2360--2363, Sept. 1996.
+% ETH --
+
+\bibitem{ETH_Deutsch_Srednicki_Rigol}
+J.~M.~Deutsch, ``Quantum statistical mechanics in a closed system'', {\em Phys. Rev. A}, {\bf 43}, 2046 (1991).
+%
+\\
+%
+M.~Srednicki, ``Chaos and quantum thermalization'', {\em Phys. Rev. E}, {\bf 50}, 888 (1994).
+%
+\\
+%
+M.~Rigol, V.~Dunjko, and M.~Olshanii, ``Thermalization and its mechanism for generic isolated
+quantum systems'', {\em Nature}, {\bf 452}, 854 (2008).
+
+\bibitem{Beugeling_ETHscaling_PRE14}
+W. Beugeling, R. Moessner, and M.~Haque, 
+``Finite-size scaling of eigenstate thermalization'', 
+{\em Phys. Rev. E}, {\bf 89}, 042112 (2014).
+
+% Lyapunov exponents in model systems --
+
+\bibitem{deWijn_fine}
+A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
+``Largest Lyapunov Exponents for Lattices of Interacting Classical Spins'', 
+{\em Phys. Rev. Lett.} {\bf 109}, 034101 (2012). 
+%
+\\
+%
+A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
+``Chaotic properties of spin lattices near second-order phase transitions'',
+{\em Phys. Rev. E}, {\bf 92}, 062929 (2015). 
+%
+\\
+%
+A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
+``Lyapunov instabilities in lattices of interacting classical spins at infinite temperature'', 
+{\em J.~Phys.~A: Math. Theor.}, {\bf 46}, 254012 (2013).
+
+\bibitem{Lyapunov_numerical_calculations}
+C.~Dellago and H.~A.~Posch, 
+``Kolmogorov-Sinai entropy and Lyapunov spectra of a hard-sphere gas''  
+{\em Physica A},  {\bf 240}, 68 (1997).
+%
+\\
+%
+V,~Latora, A.~Rapisarda, and S.~Ruffo, 
+``Lyapunov Instability and Finite Size Effects in a System with Long-Range Forces'', 
+{\em Phys. Rev. Lett.}, {\bf 80}, 692 (1998). 
+%
+\\
+%
+W.~G.~Hoover, H.~A.~Posch, C.~Forster, C.~Dellago, and M.~Zhou, 
+``Lyapunov Modes of Two-Dimensional Many-Body Systems; Soft Disks, Hard Disks, and Rotors'', 
+{\em J. Stat. Phys.} , {\bf 109}, 765 (2002).
+
+\bibitem{Lyapunov_analytical_calculations}
+D.~M.~Barnett, T.~Tajima, K.~Nishihara, Y.~Ueshima, and H.~Furukawa, 
+``Lyapunov Exponent of a Many Body System and Its Transport Coefficients'', 
+{\em Phys. Rev. Lett.},  {\bf 76}, 1812 (1996). 
+%
+\\
+%
+H.~van~Beijeren, J.~R.~Dorfman, H.~A.~Posch, and Ch.~Dellago, 
+``Kolmogorov-Sinai entropy for dilute gases in equilibrium'', 
+{\em Phys. Rev. E}, {\bf 56}, 5272 (1997). 
+%
+\\
+%
+R.~van~Zon, H.~van~Beijeren, and Ch.~Dellago, 
+``Largest Lyapunov Exponent for Many Particle Systems at Low Densities'', 
+{\em Phys. Rev. Lett.},  {\bf 80}, 2035 (1998). 
+%
+\\
+%
+S.~McNamara and M.~Mareschal, 
+``Origin of the hydrodynamic Lyapunov modes'', 
+{\em Phys. Rev. E},  {\bf 64}, 051103 (2001). 
+%
+\\
+%
+A.~S.~de~Wijn and H.~van~Beijeren, 
+``Goldstone modes in Lyapunov spectra of hard sphere systems'', 
+{\em Phys. Rev. E},  {\bf 70}, 016207 (2004).
+%
+\\
+%
+A.~S.~de~Wijn, 
+``Lyapunov spectra of billiards with cylindrical scatterers: Comparison with many-particle
+systems'', 
+{\em Phys. Rev. E},  {\bf 72}, 026216 (2005).
+
+% Katsnelson, classical dynamics
+
+\bibitem{JinKatsnelson_NJP13}
+F.~Jin, T.~Neuhaus, K.~Michielsen, S.~Miyashita, M.~A. Novotny, M.~I.
+  Katsnelson, and H.~D. Raedt, ``Equilibration and thermalization of classical
+  systems,'' {\em New Journal of Physics}, {\bf 15}, 033009 (2013).
+
+% gravitational systems --
 
@@
 
-\bibitem{Yawn1997}
-K.~R. Yawn and B.~N. Miller, ``Ergodic properties and equilibrium of
-  one-dimensional self-gravitating systems,'' {\em Phys. Rev. E}, vol.~56,
-  pp.~2429--2436, Sept. 1997.
-
-\bibitem{Jin2013}
-F.~Jin, T.~Neuhaus, K.~Michielsen, S.~Miyashita, M.~A. Novotny, M.~I.
-  Katsnelson, and H.~D. Raedt, ``Equilibration and thermalization of classical
-  systems,'' {\em New Journal of Physics}, vol.~15, no.~3, p.~033009, 2013.
+\bibitem{Yawn1997} K.~R. Yawn and B.~N. Miller, ``Ergodic properties and equilibrium of
+  one-dimensional self-gravitating systems,'' {\em Phys. Rev. E}, {\bf 56}, 2429 (1997).
+
+%%%
 
@@
 
+\bibitem{Tonks_1936}
+L.~Tonks, 
+``The Complete Equation of State of One, Two and Three-Dimensional Gases of Hard Elastic Spheres'', 
+{\em Phys. Rev.} {\bf 50}, 955 (1936).
+
+\bibitem{FiniteTimeLyapunov} 
+E.~Ott, ``Chaos in Dynamical Systems'', Cambridge University Press,  1993.
+%
+\\ 
+%
+M.~A.~Sep\'ulveda, R~Badii, and E.~Pollak, 
+``Spectral analysis of conservative dynamical systems'', 
+{\em Phys. Rev. Lett.}, {\bf 63}, 1226 (1989). 
+%
+\\ 
+%
+C.~Amitrano and R.~S.~Berry. 
+``Probability distributions of local Lyapunov exponents for Hamiltonian systems'', 
+{\em Phys. Rev. E}, {\bf 47}, 3158 (1993). 
+%
+\\ 
+%
+F.~K.~Diakonos, D.~Pingel, and P.~Schmelcher
+``Analyzing Lyapunov spectra of chaotic dynamical systems'', 
+{\em Phys. Rev. E}, {\bf 62}, 4413 (2000).
+%
+\\ 
+%
+H.~Schomerus and M.~Titov, 
+``Statistics of finite-time Lyapunov exponents in a random time-dependent potential'', 
+{\em Phys. Rev. E}, {\bf 66}, 066207 (2002). 
+%
+\\ 
+%
+M.~W.~Beims, C.~Manchein, and J.~M.~Rost, 
+``Origin of chaos in soft interactions and signatures of nonergodicity'', 
+{\em Phys. Rev. E}, {\bf 76}, 056203 (2007).
+%
+\\ 
+%
+C.~Manchein, M.~W.~Beims, and J.~M.~Rost, ``Characterizing the dynamics of higher dimensional
+nonintegrable conservative systems'', {\em Chaos}, {\bf 22}, 033137 (2012).
+%
+\\ 
+%
+K.~Kanno and A.~Uchida, ``Finite-time Lyapunov exponents in time-delayed nonlinear dynamical
+systems'',  {\em Phys. Rev. E}, {\bf 89}, 032918 (2014). 
+%
+\\ 
+%
+D,~Paz\'o, J.~M.~L\'opez, and A.~Politi, 
+``Diverging Fluctuations of the Lyapunov Exponents'' 
+{\em Phys. Rev. Lett.},  {\bf 117}, 034101 (2016).
+
 \end{thebibliography}

### 2017-12-21 arXiv_v1/draft_10_arXiv.tex
version submitted to arXiv

--- 2017-12-19 draft_09.tex
@@
 \documentclass[a4paper, onecolumn]{revtex4-1}
+
+\pdfoutput=1
 
@@
 
-\usepackage{amsmath}
- \usepackage{amsfonts}
- \usepackage{amssymb}
+\usepackage{amsmath,amsfonts,amssymb}
 \usepackage{graphicx}
- \usepackage{subfigure}
+\usepackage{color}
+
 % \usepackage{enumerate}
-
-% \usepackage{verbatim}% for \begin{comment} \end{comment}
-
-\usepackage{color}
-\usepackage{xcolor}
-\usepackage{bm}
-\usepackage[]{hyperref}
-\hypersetup{
-    colorlinks = false,
-    linkbordercolor = {red},
-    citebordercolor = {green},
-}
-
-\usepackage{epstopdf}
+% \usepackage{subfigure}
+% \usepackage{verbatim}
+% \usepackage{bm}
+% \usepackage{xcolor}
+% \usepackage{epstopdf}
+
+\usepackage[breaklinks=true,colorlinks,urlcolor=blue,citecolor=blue]{hyperref}
+
+%% \usepackage[]{hyperref}
+%% \hypersetup{
+%%     colorlinks = false,
+%%     linkbordercolor = {red},
+%%     citebordercolor = {green},
+%% }
 
@@
 
-Motivated by the interest in the dynamics of trapped quantum gases, we study the microcanonical
+Motivated by current interest in the dynamics of trapped quantum gases, we study the microcanonical
 dynamics of a trapped one-dimensional gas of classical particles interacting via a finite-range
@@
 %
-We show that the breathing mode frequency has nonmonotonic dependence on the magnitude of the mutual
-repulsion, decreasing for small interactions and increasing for larger interactions.  We explain
-these dependences in terms of slowing-down or speeding-up effects of two-body collision processes.
-We find that the gas thermalizes within a reasonable finite timescale in the sense of
+We show that the breathing mode frequency has non-monotonic dependence on the magnitude of the
+mutual repulsion, decreasing for small interactions and increasing for larger interactions.  We
+explain these dependences in terms of slowing-down or speeding-up effects of two-body collision
+processes.  We find that the gas thermalizes within a reasonable finite timescale in the sense of
 single-particle energies acquiring a Boltzmann distribution, only when the interaction strength is
@@
 connections between microscopic dynamical rules, chaos, ergodicity and statistical mechanics have a
-much longer history, dating back to the time of Boltzmann and Poincare \cite{Gaspard_book_1998,
+much longer history, dating back to the time of Boltzmann and Poincar\'e \cite{Gaspard_book_1998,
   Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85,
@@
 topic of interest for both bosons and fermions.  For bosons with short-range (contact) interactions,
-the situation has been studied in one, two and three dimensions.  At zero interactions, the
-breathing mode is twice the trapping frequency $\omega_0$ in each case, assuming isotropic trapping.
-A mean field (Gross-Pitaevskii) calculation gives the frequency to be $\sqrt{D+2}$ times the
-trapping frequency, where $D$ is the spatial dimension.  For three-dimensional (3D) traps, the
-mean-field description is expected to be qualitatively correct, thus the breathing mode frequency is
-expected to change monotonically from $2\omega_0$ at zero interactions to $\sqrt{5}\omega_0$ at
-large interactions.  For 2D traps, the breathing frequency is exactly $2\omega_0$ for any
+the situation has been studied in one, two and three dimensions.  At zero interaction, the breathing
+mode is twice the trapping frequency $\omega_0$ in each case, assuming isotropic trapping.  A mean
+field (Gross-Pitaevskii) calculation gives the frequency to be $\sqrt{D+2}$ times the trapping
+frequency, where $D$ is the spatial dimension.  For three-dimensional (3D) traps, the mean-field
+description is expected to be qualitatively correct, thus the breathing mode frequency is expected
+to change monotonically from $2\omega_0$ at zero interactions to $\sqrt{5}\omega_0$ at large
+interactions.  Remarkably, for 2D traps, the breathing frequency is exactly $2\omega_0$ for any
 interaction strength \cite{PitaevskiiRosch_PRA97}, due to a symmetry.  Classical trapped particles
@@
 for explicitly finite systems, in which case ETH is to be understood in terms of finite size scaling
-\cite{Beugeling_ETHscaling_PRE14}.  In classical systems, the connection between microscopic dynamics and statistical mechanics
-has been continually studied since the 19th century \cite{Dorfman_book_1999, Dumas_book_KAMstory,
-  Boltzmann_legacy_book, EckmannRuelle_RMP85}.  It is generally understood that systems with nonzero
+\cite{Beugeling_ETHscaling_PRE14}.  In classical systems, the connection between microscopic
+dynamics and statistical mechanics has been continually studied since the 19th century
+\cite{Gaspard_book_1998, Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book,
+  EckmannRuelle_RMP85, Gaspard_PhysicaA06}.  It is generally understood that systems with nonzero
 Lyapunov exponents, i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided
@@
 appeared recently \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10, JinKatsnelson_NJP13}, motivated by the
-quantum dynamics literature, like the present work.  A few earlier studies have also examined
-thermalization dynamics in one dimensional gravitational systems \cite{Yawn1997, Tsuchiya2000}.
+quantum dynamics literature, like the present work.  Another line of work has examined
+thermalization dynamics in one dimensional gravitational systems \cite{1Dgravitational}.
 %
@@
 simulations.  The breathing frequency is treated in Section \ref{sec:breathing}.  We explain the
-main features using both real-space and phase-space pictures of the interaction process, obtain
+main features using both real-space and phase space pictures of the interaction process, obtain
 estimates for the interaction- and energy-dependence of the frequency shift, and compare these
@@
 %% that could be measured in this system, one is about energy distribution while another is about shape
-%% of cloud in phase-space. Since here we find two sense of ``thermalizing", we will redefine our terms
+%% of cloud in phase space. Since here we find two sense of ``thermalizing", we will redefine our terms
 %% -- When a system's energy distribution goes to equilibrium, we still call it ``thermalized".  But
-%% when a system's distribution in phase-space goes to equilibrium, we call it ``relaxed" to distiguish
+%% when a system's distribution in phase space goes to equilibrium, we call it ``relaxed" to distiguish
 %% it from ``thermalized". So in section \ref{section:Shape} we actually study the ``thermalizing" of
-%% the shape of the cloud in phase-space, or the ``relaxation" behavior of the system. There we
-%% discovered a long-lasting mode, which turns out to be a quadruple mode in phase-space.
+%% the shape of the cloud in phase space, or the ``relaxation" behavior of the system. There we
+%% discovered a long-lasting mode, which turns out to be a quadruple mode in phase space.
 
@@
 \begin{equation}
-  E\approx NR^2 \, .
+  E ~\approx~ NR^2 \, .
   \label{eq:E_and_R}
@@
 \centering
-\includegraphics[scale=0.65]{ZhiyuPictures/N_5_GS_pre_2_rev-crop.pdf}
+\includegraphics[scale=0.65]{N_5_GS_pre_2_rev-crop.pdf}
 \caption{The ground state of a system with $N=5$ particles, shown via the positions of each
@@
 \begin{figure*}[tbph]
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.pdf}
+\includegraphics[width=0.9\textwidth]{stationary_and_rotating_frame_t_1-5_5T.pdf}
 %
@@
 \begin{figure*}[tbph]
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.pdf}  
+\includegraphics[width=0.9\textwidth]{rotating_frame_t_0-80T.pdf}  
 \caption{Phase space snapshots of the cloud dynamics viewed in the rotating frame, at longer
@@
 clockwise elliptical motion around the $X$-$P$ plane.  (In our units, the elliptical trajectory is
-actually circular.)  This results in the initial line remaining a straight line and rotating
+actually circular.)  This results in the distribution retaining its linear shape and rotating
 clockwise with exact period $T$.  The effect of the interaction is to smear out the line and spread
@@
 
-In the absence of interactions, each point (each particle) is stationary in the rotating-frame
-phase-space picture.  As seen in lower panel of Figure \ref{fig:Breathingfrequency2_0} and in Figure
+In the absence of interactions, each point (each particle) is stationary in the rotating-frame phase
+space picture.  As seen in the lower row of Figure \ref{fig:Breathingfrequency2_0} and in Figure
 \ref{fig:Breathingfrequency2_1}, interactions cause a gradual distortion of the line as well as some
@@
 The rotation that is visible in the already rotating $X_{\rm rot}$-$P_{\rm rot}$ frame is the
-interaction-induced shift of the breathing frequency from the noninteracting value,
-$\omega_B=2\omega_0$.  The distortion of the line toward an eventually rotationally invariant
-distribution may be regarded as thermalization or ergodicity.  In the next sections we explore these
-two interaction-induced effects.
+interaction-induced shift of the breathing frequency $\omega_B$ from the noninteracting value,
+$2\omega_0$.  The distortion of the line toward an eventually rotationally invariant distribution
+may be regarded as thermalization or ergodicity.  In the next sections we explore these two
+interaction-induced effects.
 
@@
 inexpensive, however, the theta function dependence of the force on particle positions requires the
-use of fine timesteps at the beginning and end of each collision process.
+use of fine timesteps at the beginning and end of each collision process.  The simulation is purely
+microcanonical: No external bath or thermalizing mechanisms are introduced.
 
@@
 \center
-\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
+\includegraphics[scale=0.32]{freq_scanF_differentE_log_2_with_oscillation_demo.png}
 \caption{Breathing mode frequency measured at different $E$ and $F_0$, for $N=5$ particles. Inset: a
@@
 
-Without interaction, the breathing mode frequency is exactly 2.  This is visualized readily from the
-top panel of \ref{fig:Breathingfrequency2_0}, where $R(t)$ is the extent of the distribution in the
-horizontal ($X$) direction.  As the line rotates clockwise with frequency $\omega_0=1$, within each
-period the line is twice horizontally aligned (maximum $R$) and twice vertically aligned (minimum
-$R$), so that the frequency of $R(t)$ is $\omega_B=2$.  When there is interaction, the frequency
-will get shifted: $\omega_B = 2+\delta$.  Numerically, we measure the radius of the cloud $R(t)$ and
-get the frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak
-frequency near 2 as the breathing mode frequency.
+Without interaction, the breathing mode frequency $\omega_B$ is exactly 2.  This is visualized
+readily from the top panel of Figure \ref{fig:Breathingfrequency2_0}, where $R(t)$ is the extent of
+the distribution in the horizontal ($X$) direction.  As the line rotates clockwise with frequency
+$\omega_0=1$, within each period the line is twice horizontally aligned (maximum $R$) and twice
+vertically aligned (minimum $R$), so that the frequency of $R(t)$ is $\omega_B=2$.  When there is
+interaction, the frequency will get shifted: $\omega_B = 2+\delta$.  Numerically, we measure the
+radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behavior by Fourier
+transform. Then we take the peak frequency near 2 as the breathing mode frequency.
 
@@
 saturates around a value which decreases with the system energy $E$.  At small interactions, the
-breathing frequency is actually smaller than the non-interacting value $2$.
-
-Below, we will provide a detailed phase-space argument for these behaviors.  However, a simple
+breathing frequency is smaller than the non-interacting value $2$.
+
+Below, we will provide a detailed phase space argument for these behaviors.  However, a simple
 real-space picture explains both effects qualitatively as well.  For very large $F_0$, when the
@@
 of the particles as hard rods; the collisions now take finite time during which the speeds of the
-particles are actually slowed down and then sped up again, as they either cross paths or bounce from
-each other.  When $F_0$ is small enough, this approaching time will at some critical value of $F_0$
+particles are slowed down and then sped up again, as they either cross paths or bounce from each
+other.  When $F_0$ is small enough, this approaching time will at some critical value of $F_0$
 consume the time saved by the finite range of the interaction.  This explains why there is a
@@
 \begin{figure}[tbph]
-\includegraphics[width=0.95\textwidth]{ZhiyuPictures/phase-space_collisioncartoons_01.pdf}
+\includegraphics[width=0.95\textwidth]{phase-space_collisioncartoons_01.pdf}
 \caption{Schematic diagrams of two-particle collision process in the $X_{\rm rot}$-$P_{\rm rot}$
@@
 
-The precession angle is $\alpha\sim \sigma/P$.  In our rescaled units, the typical momenta of
-interacting particles are of the order $R$.  (In phase space $R$ can be interpreted either as the
-extent in real space when the velocities are small, or as the extent in momentum space when the
-particles approach $x=0$, i.e. when the distribution is along the $P$ direction.)  Thus, we can
-estimate $\alpha\sim \sigma/R$, i.e., $\alpha\sim 1/R$, since our unit of length is $\sigma$.  This
-is the rotation per unit collision.  Since there are $\sim N$ collistions per period $T=2\pi$, we
-have the estimate for the interaction-induced rotation per unit time as
+The precession angle is $\alpha\sim \sigma/P$, where $P$ is the momentum of the colliding particles.
+In our rescaled units, the typical momenta of interacting particles are of the order $R$.  (In phase
+space $R$ can be interpreted either as the extent in real space when the velocities are small, or as
+the extent in momentum space when the particles approach $x=0$, i.e. when the distribution is along
+the $P$ direction.)  Thus, we can estimate $\alpha\sim \sigma/R$, i.e., $\alpha\sim 1/R$, since our
+unit of length is $\sigma$.  This is the rotation per unit collision.  Since there are $\sim N$
+collistions per period $T=2\pi$, we have the estimate for the interaction-induced rotation per unit
+time as
 \begin{equation}
@@
 corresponds to two breathing mode periods.  In the last step we have used the estimate $E\sim
-NR^2$.
+NR^2$, Eq.\ \eqref{eq:E_and_R}.
 
 The effect of interactions on the breathing frequency is more complicated at smaller $F_0$.  As we
-have seen in Figure \ref{fig:Breathingfrequency1}, the a small $F_0$ can \emph{decrease} the
-breathing frequency from its non-interacting value $\omega_B=2$.  This can also be understood using
-phase-space pictures of collision processes.  For $F_0$ not very big, the finite interaction time
-needs to be taken into consideration.  During this time, the point describing a particle in phase
-space moves along the direction of the $P$ axis at the rate $F_0/m$.  Since the $P$ axis is itself
-rotating counter-clockwise in the $X_{\rm rot}$-$P_{\rm rot}$ frame, the particle will follow a
-curved trajectory in $X_{\rm rot}$-$P_{\rm rot}$ space, e.g., the yellow or green dashed lines in
+have seen in Figure \ref{fig:Breathingfrequency1}, a small $F_0$ can \emph{decrease} the breathing
+frequency from its non-interacting value $\omega_B=2$.  This can also be understood using phase
+space pictures of collision processes.  For $F_0$ not very big, the finite interaction time needs to
+be taken into consideration.  During this time, the point describing a particle in phase space moves
+along the direction of the $P$ axis at the rate $F_0/m$.  Since the $P$ axis is itself rotating
+counter-clockwise in the $X_{\rm rot}$-$P_{\rm rot}$ frame, the particle will follow a curved
+trajectory in $X_{\rm rot}$-$P_{\rm rot}$ space, e.g., the yellow or green dashed lines in
 Fig.~\ref{fig:Breathingfrequency3}(a).  The angle $\alpha$ that we used above to estimate $\delta$
@@
 frequency.  Since the $P$ axis rotates with frequency $\omega_0=1$ in the $X_{\rm rot}$-$P_{\rm
-  rot}$ plane, the post-collistion position of the particle in the $X_{\rm rot}$-$P_{\rm rot}$ plane
+  rot}$ plane, the post-collision position of the particle in the $X_{\rm rot}$-$P_{\rm rot}$ plane
 makes angle $\omega_0\tau$ with the red line in Figure \ref{fig:Breathingfrequency3}(a).  Here
@@
 \centering
-\includegraphics[width=0.45\textwidth]{ZhiyuPictures/N_20_freq_vs_E_a.pdf}
+\includegraphics[width=0.45\textwidth]{N_20_freq_vs_E_a.pdf}
 \caption{Dependence of breathing frequency, calculated for $N=20$ particles, on energy.  Different
@@
 
-In Figure \ref{fig:Breathingfrequency4} we show a quantitative test of the main rotating-phase-space
-prediction, Eq.~\eqref{eq:breathingfrequency1}.  For large $F_0$, the frequency indeed scales as
-$E^{-1/2}$ and for $F_0=10^5$ is quite close to the actual numerical values prediction
-\eqref{eq:breathingfrequency1}.  Even for smaller $F_0$, at small enough energies (larger $E^{-1/2}$
-values) the breathing mode becomes proportional to  $E^{-1/2}$.
+In Figure \ref{fig:Breathingfrequency4} we show a quantitative test of the main prediction,
+Eq.~\eqref{eq:breathingfrequency1}, of our analysis of the collision process.  For large $F_0$, the
+frequency indeed scales as $E^{-1/2}$ and for $F_0=10^5$ is quite close to the actual numerical
+values prediction \eqref{eq:breathingfrequency1}.  Even for smaller $F_0$, at small enough energies
+(larger $E^{-1/2}$ values) the breathing mode becomes proportional to $E^{-1/2}$.
 
@@
 within reasonable timescales chosen to be (somewhat arbitrarily) in the timestep range of
-$10^3$--$10^4$.  Another question is the connection between thermalization, as defined by the
-appearance of a Boltzmann distribution and other intuitive characteristics of ergodic behavior such
+$10^3$--$10^4$.  Another question is the connection between energy thermalization as defined by the
+appearance of a Boltzmann distribution, and other intuitive characteristics of ergodic behavior such
 as whether the single-particle phase space is isotropically occupied.  We find cases where one
@@
 \centering
-\includegraphics[width=0.9\textwidth]{ZhiyuPictures/two_particles_a_01.pdf}
+\includegraphics[width=0.9\textwidth]{two_particles_a_01.pdf}
 \caption{Two-particle dynamics.  Left: Effective potential for relative motion.  Center and right:
@@
 \centering
-\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N_5_F0_unknown_E_100_Single_Particle_Energy.pdf}
+\includegraphics[width=0.5\textwidth]{N_5_F0_unknown_E_100_Single_Particle_Energy.pdf}
 \caption{Time evolution of single-particle energies in a system of five particles, showing a case of
@@
 Generally, whenever we have some particles with energy very different from others, the dynamics
-occurs mostly independently within particle groups of different energies.  For example, with three
-particles, consider the situation where two of them, say A and B, have small internal energy, which
-means their mutual distance and relative velocity are both small, whereas the third particle (C) has
-some energy quite different from A and B.
+occurs mostly independently within groups of particles with similar energies.  For example, with
+three particles, consider the situation where two of them, say A and B, have small internal energy,
+which means their mutual distance and relative velocity are both small, whereas the third particle
+(C) has some energy quite different from A and B.
 %
@@
 \centering
-%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
-%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
-% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
-% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
-% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
-%
-\includegraphics[width=0.85\textwidth]{ZhiyuPictures/Boltzmann_2panels_01-crop.pdf}
+%
+\includegraphics[width=0.85\textwidth]{Boltzmann_2panels_01-crop.pdf}
 %
@@
 conjectured condition, we find that the observed single-particle distributions are qualitatively
-different for $F_0\gtrsim10^3$ and for smaller interactions.  When the ``thermalization condition''
+different for $F_0\gtrsim1000$ and for smaller interactions.  When the ``thermalization condition''
 $F_0\gtrsim E/N$ is satisfied, the distribution is roughly exponential ($\sim e^{-\beta\epsilon})$.
@@
 \begin{figure}[tb]
-\includegraphics[width=0.8\textwidth]{ZhiyuPictures/Boltzmann_log_2panels_01-crop.pdf}
+\includegraphics[width=0.8\textwidth]{Boltzmann_log_2panels_01-crop.pdf}
 %
@@
 unsurprising given our small system sizes.  However, some deviation is also expected due to the
-contribution of the density of states (DOS), as the probability of finding an energy is actually
-proportional to the Boltzmann exponential factor multiplied by the DOS.  For the simple harmonic
-oscillator, the DOS is constant.  The interaction deforms the energy shell in the small region
-$|x_i-x_j|<\sigma$; so that the DOS is no longer a constant.  The measured distribution seems
-systematically slightly smaller than the Boltzmann curve at very small $\epsilon$.  For larger
-interactions, small energies are expected to be penalized, as the interaction opposes particles
-clustering at small velocities near the bottom of the trap.  This may be the reason for the counts
-in Fig.\ref{fig:thermalization9} being slightly lower than the Boltzmann prediction at small
-$\epsilon$.  However, since we are in the regime of a dilute gas ($\sigma\ll R$), the effect is
-quite small.
+contribution of the density of states (DOS), as the probability of finding an energy is proportional
+to the Boltzmann exponential factor multiplied by the DOS.  For the simple harmonic oscillator, the
+DOS is constant.  The interaction deforms the energy shell in the small region $|x_i-x_j|<\sigma$;
+so that the DOS is no longer a constant.  The measured distribution seems systematically slightly
+smaller than the Boltzmann curve at very small $\epsilon$.  For larger interactions, small energies
+are expected to be penalized, as the interaction opposes particles clustering at small velocities
+near the bottom of the trap.  This may be the reason for the counts in Fig.\ref{fig:thermalization9}
+being slightly lower than the Boltzmann prediction at small $\epsilon$.  However, since we are in
+the regime of a dilute gas ($\sigma\ll R$), the effect is quite small.
 
@@
 \centering
-%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
-\includegraphics[width=0.55\textwidth]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
+\includegraphics[width=0.55\textwidth]{LLEdistribution_1_11_pre_hot2_screenshot.png}
 \caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
@@
 
-The general idea that thermalization is faster for larger $F_0$ can be quantified through the
+The general idea that thermalization is faster for larger $F_0/E$ can be quantified through the
 Lyapunov exponents.  For high-dimensional systems, there is a spectrum of exponents which manifests
 the instability of the trajectory along each direction. The largest Lyapunov exponent (LLE) reflects
-the shortest time scale for the system lose memory of the initial state.  We follow the method
-described in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is carried out upto sufficiently
-late times, the LLE for an ergodic system is uniquely defined and independent of the starting state.
-We would like to deal with parameter regimes both within and outside our relaxation condition
-$E<F_0N$ and $E>F_0N$, and in the latter case we have seen that ergodicity does not become apparent
-at reasonable timescales.  Therefore, we carry out the computation of the LLE upto $t\sim10^2$, i.e,
-we consider finite-time Lyapunov exponents \cite{FiniteTimeLyapunov}.  This means that we can only
-get initial-configuration-dependent estimates.  The collection of these estimates forms a
-distribution which we show in Figure \ref{fig:LLEdistribution1}.  The distributions are obtained
-using 100 initial states in each case.
+the shortest time scale for the system to lose memory of the initial state.  To calculate the LLE,
+we follow the method described, e.g., in Ref.~\cite{EckmannRuelle_RMP85}.  If the calculation is
+carried out up to sufficiently late times, the LLE for an ergodic system is uniquely defined and
+independent of the starting state.  We would like to deal with parameter regimes both within and
+outside our relaxation condition, $E<F_0N$ and $E>F_0N$, and in the latter case we have seen that
+ergodicity does not become apparent at reasonable timescales.  Therefore, we carry out the
+computation of the LLE up to $t\sim10^3$, i.e, we consider finite-time Lyapunov exponents
+\cite{FiniteTimeLyapunov}.  The LLE estimates obtained in this way depend on the initial
+configuration.  The collection of these estimates forms a distribution.  We show the distributions
+in Figure \ref{fig:LLEdistribution1} for fixed $F_0$ and different values of the total energy $E$.
+The distributions are obtained using 100 initial states in each case.
+
+% The finite time used is $t\sim10^2$ for small $E$ and $t\sim10^3$ for larger $E$.
+
+%%  $t\sim10^3$, i.e, we consider finite-time Lyapunov exponents
+%% \cite{FiniteTimeLyapunov}.  This means that we can only get initial-configuration-dependent
+%% estimates.  The collection of these estimates forms a distribution which we show in Figure
+%% \ref{fig:LLEdistribution1}.  The distributions are obtained using 100 initial states in each case.
 
@@
 
-The LLE decreases with the growth of energy. The critical part is near $E = F_0N = 5000$.  Around
-this value, the most probable value of LLE decreases well below $\sim1$, which indicates that the
-shortest time scale becomes much longer than an oscillation period when $E\gtrsim5000$.  This is
+The average LLE decreases with the increase of energy. The critical part is near $E = F_0N = 5000$.
+Around this value, the most probable value of LLE decreases well below $\sim1$, which indicates that
+the shortest time scale becomes much longer than an oscillation period when $E\gtrsim5000$.  This is
 consistent with our predicted thermalization threshold.  As $E$ increases far beyond the
@@
 \begin{figure*}[tb]
-\includegraphics[width=\textwidth]{ZhiyuPictures/combine_shapedynamics_a_01-crop.pdf}
+\includegraphics[width=\textwidth]{combine_shapedynamics_a_01-crop.pdf}
 \caption{$N=20, F_0=1000$. Time evolution of the shape parameter, $S(t)$, for $N=20$ particles,
@@
 generally, thermalization may be taken to mean that a many-body system loses memory of its initial
-state.  In the single-particle phase-space picture, Figures \ref{fig:Breathingfrequency2_0} and
+state.  In the single-particle phase space picture, Figures \ref{fig:Breathingfrequency2_0} and
 \ref{fig:Breathingfrequency2_1}, our initial state is very special: The particles are lined up along
@@
 
-To quantify the shape of distribution in phase-space, we define a shape parameter $S$ measuring the
+To quantify the shape of distribution in phase space, we define a shape parameter $S$ measuring the
 degree of ellipticity:
@@
 data point is the average of the original data over $10T = 20\pi$.  (The dynamics for several
-initial states are shown to give an impression of typical $S(t)$ dynamics.)  The lower six panels
-are the original data measured after several thousand time units.
-
-The coarse-grained (averaged) dynamics on top reflects our intuition that there is slower relaxation
-at larger $E/F_0$.  We see a much faster decay for small $E/F_0$, i.e., in the thermalizing regime.
-%
-The behavior of $S(t)$ at longer times shows (lower panel) that there are coherent oscillations of
-the phase-space cloud shape on rather long timescales.  Strikingly, this is even true for the
-thermalizing regime (lower left panel), for which the time-averaged single-particle energies already
-are Boltzmann-distributed.  Thus, energy thermalization can occur at timescales much faster than it
-takes for other features of the gas to relax.
+initial states are shown to give an impression of typical $S(t)$ dynamics.)  The bottom-row panels
+show the original data measured in a time window starting after several thousand time units.
+
+The coarse-grained (averaged) dynamics in the top row reflects our intuition that there is slower
+relaxation at larger $E/F_0$.  We see a much faster decay for small $E/F_0$, i.e., in the
+thermalizing regime.
+%
+The behavior of $S(t)$ at longer times shows (bottom row) that there are coherent oscillations of
+the phase space cloud shape on rather long timescales.  Strikingly, this is even true for the
+thermalizing regime (bottom left panel), for which the time-averaged single-particle energies
+already are Boltzmann-distributed.  Thus, energy thermalization can occur at timescales much faster
+than it takes for other features of the gas to relax.
 
@@
 Eventually at large $F_0$ the frequency shift reaches a plateau at a value $\propto\sqrt{N^3/E}$.
-We have explained this behavior physically, using both real-space and phase-space pictures.
+We have explained this behavior physically, using both real-space and phase space pictures.
 
@@
 systems, for few-body systems like the present case the connection is less clear and raises
-questions of the the parametric dependence of timescales on model parameters.  Our study of a
-special case exemplifies the need for better general understanding of the connections between
-relaxation timescales, interaction strengths, thermalization, and finite-time Lyapunov expnents.
+questions of the parametric dependence of timescales on model parameters.  Our study of a special
+case exemplifies the need for better general understanding of the connections between relaxation
+timescales, interaction strengths, thermalization, and finite-time Lyapunov exponents.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Acknowledgements}
+
+MH thanks Arnd B\"acker and Astrid de Wijn for useful discussions.
 
@@
 \bibitem{Boltzmann_legacy_book} ``Boltzmann's Legacy'', edited by G.~Gallavotti, W.~L.~Reiter, and
-  J.~Yngvason; European Mathematical Society (2007).
+  J.~Yngvason; European Mathematical Society, 2007.
 
@@
 %
-A. A. Svidzinsky and A. L. Fetter, ``Stability of a Vortex in a Trapped Bose-Einstein Condensate'',
+A.~A.~Svidzinsky and A.~L.~Fetter, ``Stability of a Vortex in a Trapped Bose-Einstein Condensate'',
 {\em Phys. Rev. Lett.}, {\bf 84}, 5919 (2000).
+%
+\\ 
+%
+B.~P.~Anderson, P.~C.~Haljan, C.~E.~Wieman, and E.~A.~Cornell, 
+``Vortex Precession in Bose-Einstein Condensates: Observations with Filled and Empty Cores'',
+{\em Phys. Rev. Lett.} {\bf 85}, 2857 (2000).
+%
+\\
+%
+A.~L.~Fetter and A.~A.~Svidzinsky, 
+``Vortices in a trapped dilute Bose-Einstein condensate'', 
+{\em J. Phys.: Condens. Matter}, {\bf 13}, R135 (2001).
 %
@@
 %
+D.~V.~Freilich, D.~M.~Bianchi, A.~M.~Kaufman, T.~K.~Langin, and D.~S.~Hall, 
+``Real-Time Dynamics of Single Vortex Lines and Vortex Dipoles in a Bose-Einstein Condensate'', 
+{\em Science}, {\bf 329}, 1182 (2010).
+%
+\\
+%
+T.~W.~Neely, E.~C.~Samson, A.~S.~Bradley, M.~J.~Davis, and B.~P.~Anderson
+``Observation of Vortex Dipoles in an Oblate Bose-Einstein Condensate'', 
+{\em Phys. Rev. Lett.}, {\bf 104}, 160401 (2010).
+%
+\\
+%
 R.~Navarro, R.~Carretero-Gonz\'alez, P.~J.~Torres, P.~G.~Kevrekidis, D.~J.~Frantzeskakis, M.~W.~Ray,
@@
 ``Dynamics of a Few Corotating Vortices in Bose-Einstein Condensates'', 
-{\em Phys. Rev. Lett.}, {\bf 110}, 225301 2013).
+{\em Phys. Rev. Lett.}, {\bf 110}, 225301 (2013).
 
@@
 ``Vortices in an Imperfect Bose Gas. IV. Translational Velocity'', 
-{\em Phys. Rev.}, {\bf 151}, 100 (1966)
+{\em Phys. Rev.}, {\bf 151}, 100 (1966). 
+%
+\\
+%
+R.~J.~Donnelly, ``Quantized vortices in Helium II'', Cambridge University Press, 1991.
 
@@
 
+\bibitem{FiniteTimeLyapunov} 
+E.~Ott, ``Chaos in Dynamical Systems'', Cambridge University Press,  1993.
+%
+\\ 
+%
+M.~A.~Sep\'ulveda, R~Badii, and E.~Pollak, 
+``Spectral analysis of conservative dynamical systems'', 
+{\em Phys. Rev. Lett.}, {\bf 63}, 1226 (1989). 
+%
+\\ 
+%
+C.~Amitrano and R.~S.~Berry. 
+``Probability distributions of local Lyapunov exponents for Hamiltonian systems'', 
+{\em Phys. Rev. E}, {\bf 47}, 3158 (1993). 
+%
+\\ 
+%
+F.~K.~Diakonos, D.~Pingel, and P.~Schmelcher
+``Analyzing Lyapunov spectra of chaotic dynamical systems'', 
+{\em Phys. Rev. E}, {\bf 62}, 4413 (2000).
+%
+\\ 
+%
+H.~Schomerus and M.~Titov, 
+``Statistics of finite-time Lyapunov exponents in a random time-dependent potential'', 
+{\em Phys. Rev. E}, {\bf 66}, 066207 (2002). 
+%
+\\ 
+%
+M.~W.~Beims, C.~Manchein, and J.~M.~Rost, 
+``Origin of chaos in soft interactions and signatures of nonergodicity'', 
+{\em Phys. Rev. E}, {\bf 76}, 056203 (2007).
+%
+\\ 
+%
+C.~Manchein, M.~W.~Beims, and J.~M.~Rost, ``Characterizing the dynamics of higher dimensional
+nonintegrable conservative systems'', {\em Chaos}, {\bf 22}, 033137 (2012).
+%
+\\ 
+%
+S.~Sawada and T.~Taniguchi, 
+``Chaos and ergodicity of two hard disks within a circular billiard'', 
+{\em Phys. Rev. E}, {\bf 88}, 022907 (2013). 
+%
+\\ 
+%
+K.~Kanno and A.~Uchida, ``Finite-time Lyapunov exponents in time-delayed nonlinear dynamical
+systems'',  {\em Phys. Rev. E}, {\bf 89}, 032918 (2014). 
+%
+\\ 
+%
+D,~Paz\'o, J.~M.~L\'opez, and A.~Politi, 
+``Diverging Fluctuations of the Lyapunov Exponents'' 
+{\em Phys. Rev. Lett.},  {\bf 117}, 034101 (2016).
+
 % Katsnelson, classical dynamics
@@
 
-\bibitem{Tsuchiya2000}
+\bibitem{1Dgravitational}
+K.~R.~Yawn and B.~N.~Miller, ``Ergodic properties and equilibrium of
+  one-dimensional self-gravitating systems,'' {\em Phys. Rev. E}, {\bf 56}, 2429 (1997).
+%
+\\ 
+%
+Lj.~Milanovi\'c, H.~A.~Posch, and W.~Thirring, 
+``Statistical mechanics and computer simulation of systems with attractive positive power-law
+potentials'', 
+{\em Phys. Rev. E}, {\bf 57}, 2763 (1998). 
+%
+\\ 
+%
 T.~Tsuchiya and N.~Gouda, ``Relaxation and Lyapunov time scales in a
   one-dimensional gravitating sheet system,'' {\em Phys. Rev. E}, {\bf 61}, 948 (2000).
-
-\bibitem{Yawn1997} K.~R. Yawn and B.~N. Miller, ``Ergodic properties and equilibrium of
-  one-dimensional self-gravitating systems,'' {\em Phys. Rev. E}, {\bf 56}, 2429 (1997).
+%
+\\
+%
+K.~R.~Yawn and B.~N.~Miller, 
+``Incomplete relaxation in a two-mass one-dimensional self-gravitating system'', 
+{\em Phys. Rev. E} {\bf 68}, 056120  (2003).
+%
+\\
+%
+Lj.~Milanovi\'c, H.~A.~Posch, and W.~Thirring, 
+``Gravitational Collapse and Ergodicity in Confined Gravitational Systems'', 
+{\em J.~Stat.~Phys},  {\bf 124} 843 (2006).
+%
+\\
+%
+M.~Joyce and T.~Worrakitpoonpon, 
+``Relaxation to thermal equilibrium in the self-gravitating sheet model'', 
+{\em JSTAT}, P10012 (2010).
 
@@
 
-\bibitem{FiniteTimeLyapunov} 
-E.~Ott, ``Chaos in Dynamical Systems'', Cambridge University Press,  1993.
-%
-\\ 
-%
-M.~A.~Sep\'ulveda, R~Badii, and E.~Pollak, 
-``Spectral analysis of conservative dynamical systems'', 
-{\em Phys. Rev. Lett.}, {\bf 63}, 1226 (1989). 
-%
-\\ 
-%
-C.~Amitrano and R.~S.~Berry. 
-``Probability distributions of local Lyapunov exponents for Hamiltonian systems'', 
-{\em Phys. Rev. E}, {\bf 47}, 3158 (1993). 
-%
-\\ 
-%
-F.~K.~Diakonos, D.~Pingel, and P.~Schmelcher
-``Analyzing Lyapunov spectra of chaotic dynamical systems'', 
-{\em Phys. Rev. E}, {\bf 62}, 4413 (2000).
-%
-\\ 
-%
-H.~Schomerus and M.~Titov, 
-``Statistics of finite-time Lyapunov exponents in a random time-dependent potential'', 
-{\em Phys. Rev. E}, {\bf 66}, 066207 (2002). 
-%
-\\ 
-%
-M.~W.~Beims, C.~Manchein, and J.~M.~Rost, 
-``Origin of chaos in soft interactions and signatures of nonergodicity'', 
-{\em Phys. Rev. E}, {\bf 76}, 056203 (2007).
-%
-\\ 
-%
-C.~Manchein, M.~W.~Beims, and J.~M.~Rost, ``Characterizing the dynamics of higher dimensional
-nonintegrable conservative systems'', {\em Chaos}, {\bf 22}, 033137 (2012).
-%
-\\ 
-%
-K.~Kanno and A.~Uchida, ``Finite-time Lyapunov exponents in time-delayed nonlinear dynamical
-systems'',  {\em Phys. Rev. E}, {\bf 89}, 032918 (2014). 
-%
-\\ 
-%
-D,~Paz\'o, J.~M.~L\'opez, and A.~Politi, 
-``Diverging Fluctuations of the Lyapunov Exponents'' 
-{\em Phys. Rev. Lett.},  {\bf 117}, 034101 (2016).
-
 \end{thebibliography}

### 2017-12-21 draft_10.tex
version submitted to arXiv

--- 2017-12-21 arXiv_v1/draft_10_arXiv.tex
@@
 \centering
-\includegraphics[scale=0.65]{N_5_GS_pre_2_rev-crop.pdf}
+\includegraphics[scale=0.65]{ZhiyuPictures/N_5_GS_pre_2_rev-crop.pdf}
 \caption{The ground state of a system with $N=5$ particles, shown via the positions of each
@@
 \begin{figure*}[tbph]
-\includegraphics[width=0.9\textwidth]{stationary_and_rotating_frame_t_1-5_5T.pdf}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t_1-5_5T.pdf}
 %
@@
 \begin{figure*}[tbph]
-\includegraphics[width=0.9\textwidth]{rotating_frame_t_0-80T.pdf}  
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t_0-80T.pdf}  
 \caption{Phase space snapshots of the cloud dynamics viewed in the rotating frame, at longer
@@
 \center
-\includegraphics[scale=0.32]{freq_scanF_differentE_log_2_with_oscillation_demo.png}
+\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
 \caption{Breathing mode frequency measured at different $E$ and $F_0$, for $N=5$ particles. Inset: a
@@
 \begin{figure}[tbph]
-\includegraphics[width=0.95\textwidth]{phase-space_collisioncartoons_01.pdf}
+\includegraphics[width=0.95\textwidth]{ZhiyuPictures/phase-space_collisioncartoons_01.pdf}
 \caption{Schematic diagrams of two-particle collision process in the $X_{\rm rot}$-$P_{\rm rot}$
@@
 \centering
-\includegraphics[width=0.45\textwidth]{N_20_freq_vs_E_a.pdf}
+\includegraphics[width=0.45\textwidth]{ZhiyuPictures/N_20_freq_vs_E_a.pdf}
 \caption{Dependence of breathing frequency, calculated for $N=20$ particles, on energy.  Different
@@
 \centering
-\includegraphics[width=0.9\textwidth]{two_particles_a_01.pdf}
+\includegraphics[width=0.9\textwidth]{ZhiyuPictures/two_particles_a_01.pdf}
 \caption{Two-particle dynamics.  Left: Effective potential for relative motion.  Center and right:
@@
 \centering
-\includegraphics[width=0.5\textwidth]{N_5_F0_unknown_E_100_Single_Particle_Energy.pdf}
+\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N_5_F0_unknown_E_100_Single_Particle_Energy.pdf}
 \caption{Time evolution of single-particle energies in a system of five particles, showing a case of
@@
 \centering
-%
-\includegraphics[width=0.85\textwidth]{Boltzmann_2panels_01-crop.pdf}
+%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
+%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
+% \includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
+%
+\includegraphics[width=0.85\textwidth]{ZhiyuPictures/Boltzmann_2panels_01-crop.pdf}
 %
@@
 \begin{figure}[tb]
-\includegraphics[width=0.8\textwidth]{Boltzmann_log_2panels_01-crop.pdf}
+\includegraphics[width=0.8\textwidth]{ZhiyuPictures/Boltzmann_log_2panels_01-crop.pdf}
 %
@@
 \centering
-\includegraphics[width=0.55\textwidth]{LLEdistribution_1_11_pre_hot2_screenshot.png}
+%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
+\includegraphics[width=0.55\textwidth]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
 \caption{The distribution of largest Lyapunov exponents, for $N=5$, $F_0=1000$, at different
@@
 \begin{figure*}[tb]
-\includegraphics[width=\textwidth]{combine_shapedynamics_a_01-crop.pdf}
+\includegraphics[width=\textwidth]{ZhiyuPictures/combine_shapedynamics_a_01-crop.pdf}
 \caption{$N=20, F_0=1000$. Time evolution of the shape parameter, $S(t)$, for $N=20$ particles,

### 2018-01-27 draft_11.tex
minor revisions, references added

--- 2017-12-21 draft_10.tex
@@
 recently been studied in Refs.\ \cite{DoyonSpohn_JSTAT17, Moore_arXiv17.10}, focusing on
-integrability-breaking effects of the trap.  In this work, we consider trapped classical particles
-which interact via a simple finite-range potential between any pair of particles: a constant
-repulsive force acts whenever the particles are less than a certain distance apart.  The interaction
-strength can be tuned, leading to different regimes of behavior.
+integrability-breaking effects of the trap.  Classical dynamics in parabolic traps have also been
+studied for particles with long-range interactions, for which shell structures play an important
+role \cite{Peeters_shell}.  
+%
+In this work, we consider trapped classical particles which interact via a simple finite-range
+potential between any pair of particles: a constant repulsive force acts whenever the particles are
+less than a certain distance apart.  The interaction strength can be tuned, leading to different
+regimes of behavior.
 
@@
 breathing mode has also been studied for a high-temperature trapped gas where a Boltzmann-equation
-description is valid, both theoretically \cite{Guery-Odelin1999} and experimentally
-\cite{Cornell_classsical_3Dexpt_NatPhys15}.
+description is valid, both theoretically \cite{GueryOdelin1999, GueryOdelin_thermalization_PRA06}
+and experimentally \cite{Cornell_classsical_3Dexpt_NatPhys15}.
 
@@
 for explicitly finite systems, in which case ETH is to be understood in terms of finite size scaling
-\cite{Beugeling_ETHscaling_PRE14}.  In classical systems, the connection between microscopic
-dynamics and statistical mechanics has been continually studied since the 19th century
-\cite{Gaspard_book_1998, Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book,
-  EckmannRuelle_RMP85, Gaspard_PhysicaA06}.  It is generally understood that systems with nonzero
-Lyapunov exponents, i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided
-there are enough degrees of freedom.  As in the quantum case, finite systems are particularly
-intricate.  In finite systems, defining thermalization is trickier as most observables will
-fluctuate or oscillate substantially.  In addition, the influence of Kolmogorov-Arnold-Moser (KAM)
-orbits may play a role in preventing thermalization; it is generally believed that the fraction of
-phase space where KAM physics might be relevant decreases rapidly with particle number
-\cite{Dumas_book_KAMstory}.
+\cite{ETHscaling}.  In classical systems, the connection between microscopic dynamics and
+statistical mechanics has been studied since the 19th century \cite{Gaspard_book_1998,
+  Dorfman_book_1999, Dumas_book_KAMstory, Boltzmann_legacy_book, EckmannRuelle_RMP85,
+  Gaspard_PhysicaA06}.  It is generally understood that systems with nonzero Lyapunov exponents,
+i.e., chaotic or ergodic systems, thermalize in the long-time limit, provided there are enough
+degrees of freedom.  
+%
+However, various aspects deserve further study.  For example, given a certain strength of
+integrability-breaking (e.g., interaction strength), one might want to ask whether a system achieves
+a thermal distribution under purely Newtonian (non-dissipative) evolution, and if so, what the
+necessary timescale is for this thermalization.
+%
+As in the quantum case, finite systems are particularly intricate.  In finite systems, defining
+thermalization is trickier as most observables will fluctuate or oscillate substantially.  In
+addition, the influence of Kolmogorov-Arnold-Moser (KAM) orbits may play a role in preventing
+thermalization; it is generally believed that the fraction of phase space where KAM physics might be
+relevant decreases rapidly with particle number \cite{Dumas_book_KAMstory}.
 
@@
 thermalizes in this sense depends on the ratio of interaction strength and energy per particle.  We
-also show that this result is reflected in the finite-time Lyapunov exponents of the system.
+also show that this result is reflected in the Lyapunov exponents of the system.  (Since we include
+weak ergodicity breaking for which thermalization takes ultra-long times, we find it convenient to
+consider \emph{finite-time} Lyapunov exponents.)
 %
@@
 
-Our model for the interacting classical gas involves particles with a simple finite-range repulsive
+Our model for the interacting classical gas involves particles with a finite-range repulsive
 interaction.  Two particles repel each other whenever they are within a distance $\sigma$ from each
@@
 
-\bibitem{Guery-Odelin1999}
+\bibitem{Peeters_shell} V.~M.~Bedanov and and F.~M.~Peeters, ``Ordering and phase transitions of
+  charged particles in a classical finite two-dimensional system'', {\em Phys. Rev. B}, {\bf 49},
+  2667 (1994).
+%
+\\
+%
+V.~A.~Schweigert and F.~M.~Peeters, ``Time-dependent properties of classical
+  artificial atoms'', {\em J. Phys.: Condens. Matter}, {\bf 10}, 2417 (1998).
+
+\bibitem{GueryOdelin1999}
 D.~Gu\'ery-Odelin, F.~Zambelli, J.~Dalibard, and S.~Stringari, ``Collective
@@
 
+\bibitem{GueryOdelin_thermalization_PRA06} M.~Anderlini and D.~Gu\'ery-Odelin, ``Thermalization in
+  mixtures of ultracold gases'', {\em Phys. Rev. A} {\bf 73}, 032706 (2006).
+
 \bibitem{Cornell_classsical_3Dexpt_NatPhys15} D.~S.~Lobser, A.~E.~S.~Barentine, E.~A.~Cornell, and
@@
 
-\bibitem{Beugeling_ETHscaling_PRE14}
+\bibitem{ETHscaling}
 W. Beugeling, R. Moessner, and M.~Haque, 
@@
 {\em Phys. Rev. E}, {\bf 89}, 042112 (2014). 
+%
+M.~Haque and P.~McClarty, ``Eigenstate Thermalization Scaling in Majorana Clusters: from Chaotic to
+Integrable Sachdev-Ye-Kitaev Models'', arXiv:1711.02360.
 
@@
 A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
+``Lyapunov instabilities in lattices of interacting classical spins at infinite temperature'', 
+{\em J.~Phys.~A: Math. Theor.}, {\bf 46}, 254012 (2013). 
+\\
+%
+T.~A.~Elsayed, B.~Hess, and B.~V.~Fine, 
+``Signatures of chaos in time series generated by many-spin systems at high temperatures'',
+{\em Phys. Rev. E}, {\bf 90}, 022910 (2014). 
+%
+\\
+%
+A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
 ``Chaotic properties of spin lattices near second-order phase transitions'',
@@
 %
-\\
-%
-A.~S.~de~Wijn, B.~Hess, and B.~V.~Fine, 
-``Lyapunov instabilities in lattices of interacting classical spins at infinite temperature'', 
-{\em J.~Phys.~A: Math. Theor.}, {\bf 46}, 254012 (2013).
 
@@
 {\em J. Stat. Phys.} , {\bf 109}, 765 (2002).
+%
+\\
+%
+A.~Das, S.~Chakrabarty, A.~Dhar, A.~Kundu, R.~Moessner, S.~S.~Ray, and S.~Bhattacharjee,
+``Light-cone spreading of perturbations and the butterfly effect in a classical spin chain'',
+arXiv:1711.07505.
 
@@
 {\em Phys. Rev. Lett.},  {\bf 117}, 034101 (2016). 
+%
+\\ 
+%
+M.~Hanada, H.~Shimada, and M.~Tezuka, ``Universality in Chaos: Lyapunov Spectrum and
+Random Matrix Theory'', arXiv:1702.06935.
 
@@
 
-\bibitem{GueryOdelin_thermalization_PRA06} M.~Anderlini and D.~Gu\'ery-Odelin, ``Thermalization in
-  mixtures of ultracold gases'', {\em Phys. Rev. A} {\bf 73}, 032706 (2006).
-
 \bibitem{Tonks_1936}
